### 2019-09-04 text/apa.tex
clean slate

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The title},
            pdfauthor={First Author~\& Ernst-August Doelle},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{The title}
    \author{First Author\textsuperscript{1}~\& Ernst-August Doelle\textsuperscript{1,2}}
    \date{}

\shorttitle{Title}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.

}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.5.1; R Core Team, 2018) and the R-package \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2018). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2019-09-04 text/manuscript_assa.Rmd
clean slate

---
title: "Machine Learning, Building Vintage and Property Values"
author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: Externalities of architecture, machine learning
fig_caption: yes
header-includes:
   - \usepackage{soul}
   - \usepackage{color}
   - \sethlcolor{yellow}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{graphicx}
   - \usepackage{grffile}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{setspace}
   - \usepackage{multirow}
   - \doublespacing
   - \usepackage[backend=bibtex, style=authoryear]{biblatex}
fig_width: 6
fig_height: 4
output: 
  pdf_document:
    keep_tex: true
bibliography: references.bib
abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View. Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of building vintages. Third, it investigates whether architectural styles influence house prices. For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings. This indicates that any premia are for vintage-related quality characteristics and not for a home's ``beauty''." 
---

# Introduction
\let\svthefootnote\thefootnote
\let\thefootnote\relax\footnote{{*Corresponding author: Thies Lindenthal (htl24@cam.ac.uk). Replication files are available from the author's Github repository \href{https://github.com/thies}{https://github.com/thies}. Paul E. Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance. Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp and seminar participants at UCL/Bartlett and at the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
\addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
If new developments were only pleasing to the eye, so Britain's *Building Better, Building Beautiful Commission*, nimbyism would cease and housing supply could finally reach the levels demanded by a growing and more affluent population [@economistlineofbeauty2018]. The inaugural chair of this new governmental commission boldly suggests that we should *``build, as our Georgian and Victorian forebears built* [...]. *All objections to new building would slip away in the sheer relief of the public''* [@scruton2018]. Even Prince Charles, in similar spirit, put forward ten principles for urban growth and architecture that emphasize tradition and aesthetics [@princecharles2014]. When governments and princes occupy themselves with beauty, economists surely may take a closer look as well. In this paper, we aim to identify the architectural styles of residential buildings using computer vision techniques and to empirically search for any transaction price premia associated with these styles. If aesthetics were as strong a force in the built environment as claimed, we should indeed find a significant effect on property prices.

This paper will assess architectural aesthetics heads on and analyze the visual appearance of residential buildings using street level images. Recent work illustrates how street level imagery and machine learning classification is an efficient and powerful combination for measuring previously unobserved characteristics of the urban environment. @Naik2017 describe how neighborhood demographics may impact the physical appearance of neighborhoods. @Gebru2017 use classified vehicle make and model to predict income, race, education, and voting patterns at the precinct level. @Glaeser2016 predict income in New York City. @Naik2016AER create a neighborhood safety based Streetscore which is shown to be highly correlated with neighborhood population density and household income. @Nadai2016 find that greenery and street facing windows contribute to a positive appearance of safety while @Liu2017 evaluate the quality and upkeep of the built environment along Beijing's streets.

@GlaeserKincaidNaik2018 push the level of observation from the block, street, or street-section level to the individual \emph{building level}. Utilizing images of buildings' exteriors collected from Google Street View\footnote{\href{https://www.google.co.uk/maps}{https://www.google.co.uk/maps}}, and to a lesser degree interior images from Zillow, they find that looks matter, at least in Boston: A one standard deviation improvement of a building's exterior is associated with an additional USD 70,000 in home value. Intuitively, the link between good looks and value is bi-directional: The appearance of buildings that went through foreclosure deteriorated significantly [@GlaeserKincaidNaik2018].

Zooming in at individual buildings significantly increases the benefits of using mass collected street level imagery in economic research: property characteristics previously deemed "unobservable" can be directly observed in an accurate, objective, automatic and therefore cost effective way. Deriving additional variables from unconventional data sources like 3D airborne laser scanning (or in our case Google Street View) is fundamental since this provides "essential determinants influencing real estate prices [which] are constantly missing and are not accessible in official and mass appraiser databases" [@Helbich2013].

In this paper we suggest a method to collect a large number of images of individual UK buildings from Google Street View, classify the depicted buildings using deep convolutional neural networks, combine the derived information with sales price data and, ultimately, estimate marginal prices for the estimated building characteristics. Our work demonstrates that utilizing pretrained convolutional neural networks to detect complex characteristics such as housing vintages with relatively high accuracy comes at low computational costs and is feasible with only modestly-sized training data. No supercomputers are needed, a modern laptop will do.

## Building vintage and property values

The aesthetics of different architectural eras make for an easy cocktail party conversation topic -- and they also influence market prices. Using architectural assessments by human experts, @Buitelaar2017 find a sizable premium of 5\% for new buildings in the Netherlands that refer to traditional styles and a staggering 15\% premium for new buildings that closely follow traditional shapes, facade composition and details. Their study carefully disentangles the architectural style from other unobserved characteristics such as building quality, differences in location or year of construction. These controls are crucial, as earlier work has established that age and vintage variables tend to be highly correlated. @Coulson2008, for instance, suggest a non-parametric estimator and establish a U-shaped age function and distinct price discounts for postwar and contemporary vintages (vis-à-vis more historic vintages). @Francke2017a investigate the depreciation of residential real estate in the Netherlands and decompose land versus structure values singling out the effect of "physical deterioration, functional obsolescence and and vintage effects". They find that buildings from the 1930s carry a strong price premium.

A large scale assessment of buildings' exteriors will allow for an analysis of the externalities of architecture. Buildings hardly ever stand in isolation and @Ahlfeldt2012 investigate the influence a building's architecture exerts on its surroundings. They observe a positive price effect for residential buildings in the direct proximity of iconic homes by Frank Lloyd Wright in Oak Park, Illinois. A building's exterior does not need to be an architectural masterpiece to co-determine the value of other houses close by. Homogeneity of building shapes within street segments does influence property values. A similarly shaped neighboring building is value enhancing while proximity to a wildly different neighboring shape, everything else remaining equal, is detrimental to property values [@Lindenthal2017b].

Unfortunately, the traditional approaches chosen by e.g. @Buitelaar2017 or @Ahlfeldt2012 do not scale well. Each observation has to be classified into architectural styles by a human expert, which is time-consuming and costly, imposing an upper limit on the number of observations and the level of detail captured for each observation in any given sample. Google Street View offers a solution to this nexus as it captures the images of almost all buildings in many cities around the world at high level of accuracy and detail. The challenge we address in this paper is to extract and utilize building level information from this ubiquitous sensor.

# Methodology

## Image collection

The first challenge when trying to collect building images in the UK is fundamental: How can one identify the building of interest correctly? Simply looking up an address on Google Maps too often leads to imprecise `street views' and not the building-level portraits needed. Fig. \ref{fig:84Vin} presents a typical result from an address level search, showing a broad ensemble of buildings instead of singling out the building of interest (in this case, the partly captured terraced house at the very left margin).

\begin{center}
  -- Insert Figure \ref{fig:84Vin} about here --
\end{center}

Previous work sourcing imagery from Google Street View has mostly focused on neighborhood or precinct characteristics where exact spatial assignment of objects is not required and street-level images suffice. For major US cities, the accuracy of building image search results is higher, which should help studies such as @GlaeserKincaidNaik2018.

Self-evidently, the images we use for classifying architectural style must focus on specific buildings of interest. For the UK, and many other countries, the Google Street View API returns the coordinates of the nearest camera snapshot for a given location but fails to provide an accurate orientation and zoom-level of the camera needed to capture the front of the building. To estimate the best possible view, we combine Street View metadata queries and Ordnance Survey maps to find the optimal camera orientation to center images on the front door of the building of interest.

\begin{center}
  -- Insert Figure \ref{fig:fan} about here --
\end{center}

Specifically, we first look up the nearest Google Street View panorama point (green dot in Figure \ref{fig:fan}) based on the centroid (red dot) coordinates of a given building obtained from Ordnance Survey maps. We then perform a viewshed analysis and identify which exterior walls are visible from the panorama point, ignoring any wall segments where the direct line of sight from the panorama point is obstructed by other buildings. We can then estimate the camera bearing (green line) and zoom factor, based on the fan of the lines of sight (in blue).\footnote{Code necessary to replicate this analysis is available from the author's GitHub.com code repositories: \href{https://github.com/thies}{https://github.com/thies}.}

Obstructed lines of sight due to greenery, fences, garden walls or large vehicles cannot be detected from the Ordnance Survey maps. We therefore use a first stage image classification procedure to identify if the building image is obstructed and we proceed the second-closest location if the line of sight is obstructed.

By combining land registry maps with the snapshot location, we are able to automatically build a set of building frontage images for approximately 48,000 properties in Cambridge (UK). The Ordnance Survey maps do not provide any use type classifications so we collect images on all buildings that have a ground plate between 40 and 250 $m^2$. This method, however, could easily be adapted to photograph buildings in locations for which high-resolution building level maps are not available by using LIDAR based building outlines instead, which would be in the spirit of @Glaeser2016.

### From pixels to computer vision

We download all pictures at the highest resolution offered by Google's Street View API\footnote{\href{https://developers.google.com/maps/documentation/streetview/intro}{https://developers.google.com/maps/documentation/streetview/intro}} (640x640 color pixels). We then obtain 2048-dimensional feature vectors for each picture, using the \emph{Inception-v3} deep convolutional neural network [@Szegedy2015]. \emph{Inception-v3} has been trained for the ImageNet Large Scale Visual Recognition Challenge (ILSVRC)\footnote{\url{http://image-net.org/challenges/LSVRC/}}, which evaluates image classification and object detection algorithms for a wide range of objects. The pretrained classifications would allow us to identify pets, vehicles or people on the pictures -- assessing architectural finesse, however, is beyond the canned classifiers' capabilities.

@GlaeserKincaidNaik2018 rely on an different ILSVRC competitor, \emph{Resnet-101} [@He2016]. They reduce the extracted feature vectors to lower dimensionality (1024 to 100 dimensions) based on principal component analysis (PCA). We follow a different strategy and double the dimensionality by including the feature vector of the building's nearest neighbor. Doubling up allows us to model spatial dependencies in building styles, similar to spatially correlated land cover classifications in @Ghimire2010a.

## Image classification

Cambridge's houses can be classified into seven broad eras: \footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general vintage descriptions.}

* \emph{Georgian} (c1714--1837) houses feature key characteristics such as sash windows, fan lights above doors, the use of stucco on facades, often wrought work grilles, railings etc.\label{def_eras}

* In the \emph{Early Victorian} era (c1837--c1870s), a growing taste for individualized embellishment led to the development of elaborate features such as carved barge boards or finials. The development of sheet glass led to sash windows becoming more affordable, and, increasingly, wider.

* In the \emph{Late Victorian} era (c1870s--1901), bay windows became more and more widespread, and increasingly substantial. Stylistic movements such as the Queen Anne revival style contributed richly ornamental details to the formal repertoire employed by designers. Stained glass became more popular. \emph{Edwardian} architecture (1901-1910) tends to be less ornate than late Victorian architecture.

* The \emph{Interwar} period (1918--1939) saw the cost of building construction fall, amidst a drive to provide better housing for the working classes. New housing types were being favored.

* The \emph{Postwar} (1950-1980) era continued on this path, with an embrace of high-rise as well as low rise housing. Facades vary greatly between brick, tiling, pebbledash and render.

* The cut-off year for our \emph{Contemporary} era to begin is 1980. \emph{Revival} are contemporary buildings trying to emulate historic, mostly Victorian, architecture.

Two final-year architectural students classified a large sub-sample of approximately 25,000 images from our data set of Cambridge houses. This is a much larger sample than needed in our case. In our case, each category requires less than 250 observations to reach saturated training accuracy levels. We greatly exceed this number for the purpose of this paper so that we can compare the out-of-sample convolutional neural network predictions to the ground truth as assigned by the experts. This allows us to examine the power and size of the assignment tests. In addition having both human and machine classification for a large sample of the data allows for a robustness checks on the machine comparisons.

We create stratified training samples of 600 buildings from each category but *Georgian*, which is the least common style in Cambridge and for which we can only sample 330 examples. This leaves a sufficiently sized out-of-sample verification data set.

The multinomial classifier model design remains parsimonious, comprising of:

* an input layer the size of the feature vectors,

* one dense layer (relu) half the size of the input layer, one subsequent dropout (rate 0.5) layer,

* one dense layer (relu) a quarter the size of the input layer, one subsequent dropout (rate 0.5) layer,

* and the final dense output layer with softmax activation.

All classifiers are implemented using the Keras/Tensorflow APIs\footnote{Keras: \href{https://keras.io/}{https://keras.io/}, Tensorflow: \href{https://github.com/tensorflow/tensorflow}{https://github.com/tensorflow/tensorflow}}. The computational burden of this rather shallow model design is modest.

For 100 randomly drawn, stratified data sets, we train two models each: The first is based on the building specific feature vectors (2048 dimensions) only while the second also incorporates the feature vector of the nearest neighbor (combined 4096 dimensions). In cases where trees, fences or large vehicles obstruct the view or where the front of a building cannot be classified with high certainty, the image of the nearest neighbor provides a ``second opinion'' that is spatially correlated with the observation of interest. Finally we classify all buildings not used in training or evaluating the model (truly out-of-sample).

When classifying a building picture, each models returns a vector of vintage-scores, each between 0 to 1, that jointly sum up to 1. We select the vintage with the highest score as the best estimate. By not excluding observations where multiple scores are vying for the top rank we retain as many observations as possible but risk a higher misclassification rate.

Two variables are obtained from the distribution of classifications per observation: The ensemble classifier arrives at predictions by majority vote. In addition, a confidence measure is computed as the Herfindahl index of classifications by ensemble member models.\footnote{If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*. The corresponding Herfindahl score is calculated as $(20/100)^2 + (80/100)^2 = 0.68$.}

We tabulate confusion matrices and evaluate the classification performance in terms of recall, precision and $F_1$-scores. The next step regresses the true vintage observed, captured by binomial variables $D_{TrueVint}$, against a vector of hedonic variables $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's $\mathbf{Vintage}$, estimated both with and without spatial dependencies. The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients, and $\epsilon$ is the error term.

\begin{equation} \label{eq:rev}
  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
\end{equation}

The logit regressions are estimated by generalized least squares. For a well-performing classifier, the $\delta$ coefficients will be statistically significant and, more importantly, differences in the Akaike Information Criterion (AIC) allow for comparisons across the suggested ML classifiers.

Will the resulting classifiers be biased with respect to property values, picking up correlated but irrelevant cues such as greenery, upkeep, or cars brands instead of building exteriors? Are, for instance, more valuable houses more likely to be classified as the popular *Late Victorian* vintage while starter homes are disproportionally more likely to be classified as e.g. *Early Victorian*? We expect that in cases in which the ensemble provided a high confidence score, building features are clearly detectable on the pictures. For close calls, however, where models within the ensemble cannot agree, other factors might tilt the scale towards an incorrect class. A sizable difference in estimated marginal prices for estimated vintages versus values for ground truth vintages in the subsequent hedonic regression (Eq. \ref{eq:hed}, below) would indicate such a bias.

## Building era and property price

Merging the estimated vintage classification with sales data [@LandRegistry2016a] we estimate a hedonic regression equation that establishes marginal prices for the building vintage [similar to @Moorhouse1994; @Asabere1989; @Vandell1989; @Fuerst2011; @Plaut2006], among other characteristics:
\begin{equation} \label{eq:hed}
  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i + \eta\mathbf{VintNeigh}_i + \iota\mathbf{Vintage\cdot VintNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
\end{equation}

Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Vintage}$ and the prevailing vintage of other buildings in the direct proximity $(\mathbf{VintNeigh})$. The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\eta}$, $\bm{\iota}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients. $\epsilon$ is the IID error term. Heteroscedastic robust standard errors will be reported.

Are buildings from different eras imperfect substitutes catering to multiple groups of households with distinct vintage preferences? @Buitelaar2017 indicate that any premium for an architectural style must stem from either differences in construction prices (which they do not find in their Dutch sample) or from supply constraints, as new construction potentially does not capture the demand for traditional styles. For Cambridge, new supply will inevitably be of either contemporary or revival style as historic vintage buildings, by definition, are not supplied any more. Estimating Eq. \ref{eq:hed} for a subset of newly constructed buildings will show whether construction prices or supply constraints for new homes built according to different architectural styles persist -- if too few vernacular buildings were built, prices should reflect such a shortage.

# Data

Residential real estate transactions are public data in the UK, collected and published by the Land Registry [@LandRegistry2016a]. The records include the date of transaction, price paid, street address, a classification of the property type (flat, detached, semi-detached, or terraced house), the estate type (freehold or leasehold) and an indicator for newly built properties. We select transactions from Cambridge proper which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000. Linking recently taken images to sales data from 24 years assumes that houses have not changed their architectural styles -- which seems reasonable. We are not aware of any conversions of just the exterior of buildings. Full redevelopments, did occur and we exclude sales for a given address pre-dating any redevelopment. Table \ref{tab:sumstats} presents summary statistics for the sample.

The Ordnance Survey *AddressBase* [@OrdnanceSurvey2017] links street addresses to building outlines on Ordnance Survey maps [@OrdnanceSurvey2017a], which allows us to calculate the buildings floor plate (in $m^2$) and to estimate the building's volume from digital elevation models [@EnvironmentAgency2015], as suggested by @Lindenthal2017. We control for the location of each building by calculating the distance to the city center proxied by Great St. Mary's Church, and non-parametrically by using 69 indicator variables for each of the smallest census tracts (*Lower Super Output Areas*, LSOA) subdividing Cambridge [@ONS2017]. LSOAs typically have 1,000--3,000 residents and 400--1,200 households of comparable economic and socio-demographic characteristics [@ONS2017b].

Overall, we collect pictures of more than 48,000 distinct buildings from the Google Street View API. The subset of 25,000 pictures that has been classified by trained architects into the seven vintages will serve as \emph{ground truth} for our study. Two additional categories identify buildings hidden by *greenery* or uninformative pictures featuring *plain walls*. The classified images are available at the authors' websites.

# Results

Almost 16,000 of the 25,000 buildings for which we have the architects' ground truth could be matched to the 23,768 sales transactions that have been recorded for Cambridge between 1995 and 2018. Thus, we observe both the machine *estimated vintage* and architect defined *ground truth* classification for the majority of buildings in the data set.

\begin{center}
  -- Insert Table \ref{tab:confmat} about here --
\end{center}

The agreement between vintage estimates and the corresponding ground truth classifications by experts is reassuringly strong. When relying on feature vectors of the buildings and their closest neighbors, 67 to 84 percent of true classifications are matched with correctly estimated labels (Table \ref{tab:confmat}, Panel A). The recall rates are especially high for older vintages: For *Georgians*, it is 79 percent, *Early Victorian* 81 percent, *Late Victorian/Edwardian* 78 percent, *Interwar* 84 percent, respectively. For more recent *Postwar* buildings, the rate drops to 71 percent, for *Contemporary* to 72 percent and for *Revival* to 67 percent.

A visual inspection of classifications is additionally reassuring. Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each vintage. The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.

The Herfindahl scores for classifications vary substantially across ground truth vintages (Table \ref{tab:herftab}), indicating that the models within the ensemble, for instance, agree more often on a building being *Georgian* than finding consensus for other vintages. For *Contemporary* or *Revival* vintages, individual classifications differ most. All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the ensemble is not really sure when misclassifying images.

A closer inspection of the misclassified images sheds some light on the limits of automatically collected street level imagery. What do misclassified images have in common? Off-the-shelf object detection algorithms can identify broadly defined objects such as trees, vehicles, houses, doors, or windows without any additional training. Using an Inception/Resnet object detection model trained on Open Images\footnote{In this case, "faster rcnn inception resnet v2 atrous oidv2", available from \url{https://github.com/tensorflow/models/blob/master/research/object_detection/g3doc/detection_model_zoo.md}}, we calculate the share of the image area taken up by cars or trees as a measure of view obstruction. The more image area is showing buildings and, importantly, windows the more meaningful input an automatic classifier can draw from, resulting in better classifications. In addition, images not taken at an optimal angle or zoom factor are detected by calculating the distance between the bounding box for the largest building detected on the image and the center of the image: For well-centered images, this offset will be small.

Table \ref{tab:imgqualsumstats} presents the mean values for the image quality variables. Table \ref{tab:diffimgchar}, Panel A, compares the mean values for views obstructed by trees or vehicles for correctly (on diagonal) and incorrectly classified images. In most cases, the off-diagonal values are positive, showing that more obstacles in the view of sight correlate with higher odds of misclassifications. Similarly, if more of the image area shows a house (Panel B), misclassifications are reduced (negative differences). This effect is stronger for windows, which appear to give valuable cues about a house's vintage (Panel C). Finally, houses that are not in the center of the building tend to be misclassified more frequently (positive differences in Panel D). In sum, bad quality images lead to misclassifications.

\begin{center}
  -- Insert Table \ref{tab:herftab}, Table \ref{tab:imgqualsumstats} and Table \ref{tab:diffimgchar} about here --
\end{center}

The number of misclassifications decreases decidedly when considering observations with high ensemble confidence only: The majority vote based on the most confident two-thirds of predictions only are more in line with ground truth, as higher recall, precision and $F_1$-scores in Table \ref{tab:confmat}, Panel B, show. The improvement is most evident in the precision rates. For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different ground truth class -- the precision shoots up to 0.70 for *Georgian* and 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.

The majority of misclassification is concentrated in temporally adjacent eras: 10 percent of *Late Victorian/Edwardian* buildings are labelled as *Early Victorian* or 18 percent of *Postwar* buildings are erroneously regarded as stemming from the *Interwar* period. Hardly ever is a contemporary building mistaken for a historic home.

\begin{center}
  -- Insert Figure \ref{fig:vint_examples} about here --
\end{center}

Overall, the spatial softmax classification incorporating the nearest neighbor's feature vector outperforms the base classifier: pairwise differences of the $F_1$-scores from the spatial and the base classifier are clearly positive (Fig. \ref{fig:boxplot}). AIC values for 28 binomial models based on Eq. \ref{eq:rev} decrease as hedonic characteristics, location and time dummies are augmented by the base and spatial ML predictor. For all building vintages, the AIC are lowest for the spatial ML predictor. In sum, the spatial classifier performs better for UK vintage data than a classifier based on single buildings only.

\begin{center}
  -- Insert Table \ref{tab:aic} and Figure \ref{fig:boxplot} about here --
\end{center}

## Hedonic regression estimates

Successively, the estimated coefficients from 8 different versions of the hedonic regression specified in Eq. (\ref{eq:hed}) are reported in Tables \ref{tab:hedreg} and \ref{tab:hedregint}. For all models, the hedonic control variables show the expected signs: Negative coefficients for the relative distance to the city center, discounts for terraced homes and semi-detached homes relative to detached houses, positive elasticities for building floor plate and building volumes and a price premium for new buildings compared to second-hand homes, when applicable. Year and neighborhood dummies control for time effects and local amenities but their coefficients are not reported due to space constraints. The combination of location dummies and the distance to the city center measure controls for proximity to the city center \emph{within} each neighborhood.

\begin{center}
  -- Insert Table \ref{tab:sumstats} and Table \ref{tab:hedreg} about here --
\end{center}

The first column in Table \ref{tab:hedreg} presents the estimated regression coefficients for ground truth vintages. The base vintage *Contemporary* is more expensive than almost all other vintages, which show negative coefficients that are significantly different from 0. A clear pecking order appears: *Georgian* and *Revival* buildings are the dearest $(+0.04)$,  followed by *Late Victorian/Edwardian* $(+0.01)$, *Contemporary* (base), *Early Victorian* $(-0.13)$,  *Interwar* $(-0.15)$ and *Postwar* $(-0.22)$.

The sample of ground truth images is not necessarily representative of the overall population so we re-estimate the model using predicted vintages for *all* buildings for which we were able to extract usable pictures from Google Street View. Overall, the vintage coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify unattractive buildings to the *Contemporary* vintage. Reversely, more attractive buildings are disproportionally often misclassified as *Late Vic./Edw.*, pushing up the corresponding coefficient to $0.11$. This bias vanishes in the third model, which uses only confidently predicted vintages (Column 3).

Models 4--6 follow the same logic as 1--3 but are estimated for *new* buildings only. Basically this contrasts houses which might *look* different from the street, having either contemporary or revival facades, but which are all modern homes at their core. Differences in e.g. materials, floor plans, green space and gardens are minimal. For newly built homes, no effect of *Revival* architecture on price can be found, neither for ground truth classifications nor for high confidence ML estimates. After controlling for location, building characteristics and quality, buyers show no willingness to pay a premium for *Revival* architecture.

Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{VintNeigh}$) does not change the pecking order of building vintages much (Table \ref{tab:hedreg}, Column 7). Neighboring styles are compared to the base case of a *Contemporary* house in a *Contemporary* street. The negative coefficients on dissimilar neighboring styles support a finding by @Lindenthal2017 that shows that a harmonious match of a building's shape with its direct environment leads to a price premium -- or a discount in case of shape mismatches. In relative terms, *Postwar* buildings are the least popular neighbors. The difference between *Revival* and *Contemporary* neighbors is not statistically significant. We fail to find evidence in favor of positive externalities from revival architecture. Everything else equal, buildings within ensembles of *Contemporary* buildings generally do not achieve higher transaction prices than buildings in more historic areas (as Table \ref{tab:comb} will confirm later).

Table \ref{tab:hedregint} presents the $\iota$ interaction coefficients (Eq. \ref{eq:hed}) for vintage-neighboring vintage combinations with sufficient numbers of observations (see Table \ref{tab:vintneigh}). The last row suggests that a general claim that *Revival* neighbors exert positive externalities and increase property values relative to *Contemporary* surroundings cannot be confirmed empirically. Again, we find no statistically significant difference.

\begin{center}
  -- Insert  Table \ref{tab:vintneigh}, Table \ref{tab:hedregint} and Table \ref{tab:comb} about here --
\end{center}

In Table \ref{tab:comb}, the combined effect of building styles on property values is calculated by adding up the direct, neighborhood and interaction effects (Tables \ref{tab:hedreg} and \ref{tab:hedregint}). When filling in lots in historical neighborhoods, however, a premium for *Revival* facades over modern designs can be observed (differences in last two columns of Table \ref{tab:comb}). For large scale new construction, however, *Revival* buildings surrounded by other historicizing buildings do not sell for more than *Contemporary* buildings in a more modern setting.

# Conclusion

The contributions of this paper are threefold: First, it introduced an algorithm that collects pictures of *individual* buildings from Google Street View. Earlier work has not achieved this level of detail and was, at least in the UK, limited to street sections only. A large-scale application of automatic classification of individual buildings' characteristics using Google Street View has potential not only in the UK. The image collection and classification method can easily be ported to other study areas which have existing Street View data and either LIDAR based building outlines or high resolution satellite images. In a follow-up project, we are working on an improved classification workflow in which a customized object detection model is able to recognize specific building outlines without the need for additional maps or other data.

Second, we developed a new database of 25,000 building pictures that have been classified by architecture experts into relevant architectural styles or vintages. We subsequently trained a neural network classifier to automatically classify all residential buildings of a mid-sized English city into architectural styles or vintages. The suggested classifier is trained on feature vectors of buildings and their nearest neighbors to exploit spatial correlation in observed classifications.

The large ground truth data set allows for a comparison of human expert classifications with predictions made by ML classifiers. Poor image quality, for instance obstructed views or the lack of informative features such as windows, is correlated with misclassifications. Importantly, for cases in which the ML classifiers are relatively indecisive between classes, visual cues that are correlated with vintage but not part of a building's architecture (for instance trees or cars) bias the estimates. Fore these less certain cases, more valuable homes are systematically more likely to be classified as e.g. *Late Victorian/Edw.* and less likely to be considered *Contemporary*. A follow up study could investigate which elements in the building pictures lead to the misclassifications [@Ribeiro2016]. Given the danger of systematic biases, one should remain wary of ML estimates derived from ground truth data sizable enough to train models -- but too small to investigate any biases.

Third, we test whether revival or vernacular architecture leads to price premia over contemporary architecture. We do not find evidence for a preference of residents for specific architecture after controlling for quality and location of buildings. This applies to both direct price effects but also indirect effects of a buildings appearance on the value of neighboring homes. Further work will extend the spatial scope of the study area to the UK in general and to other countries.

\newpage
\clearpage

# Tables and Figures

\begin{figure}[hbt]
  \caption{`Street View', not `Building View' -- Identification of buildings remains a challenge in the UK}
  \centering
  \vspace{0.25cm}
    \includegraphics[width=0.8\textwidth]{figures/84VineryRD.png}
  \label{fig:84Vin}
\begin{minipage}{0.8\textwidth}
\footnotesize 
\vspace{0.25cm}
\emph{Notes:} For the UK, the Google Street View API returns the coordinates of the nearest camera snapshot for a given location but fails to provide an accurate orientation and zoom-level of the camera needed to capture the front of the building exactly. In this typical example, the building of interest is only partially shown at the very left margin of this result.  \emph{Image source}: Google Street View. 
\end{minipage}
\end{figure}

\begin{figure}[hbt]
  \caption{Image Collection on Google Street View: Camera Direction and Zoom}
  \centering
    \includegraphics[width=0.8\textwidth]{figures/fan.png}
  \label{fig:fan}
\begin{minipage}{0.8\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} We first look up the nearest Google Street View panorama point (green dot) based on the centroid (red dot) coordinates of a given building obtained from Ordnance Survey maps. A viewshed analysis identifies which exterior walls are visible from the panorama point, ignoring any wall segments where the direct line of sight from the panorama point is obstructed by other buildings. The camera bearing (green line) and zoom factor are based on the angle of the most outer lines of sight (blue lines).
\end{minipage}
\end{figure}

\input{confusion_matrix.tex}

\begin{table}[!htb] 
\caption{Prediction certainty: Herfindahl index from ensemble model} 
\label{tab:herftab} 
\footnotesize
\begin{tabular}{lccccccc}
\toprule 
  & \multicolumn{7}{c}{\emph{Ground truth}} \\ 
  \cmidrule(lr){2-8} 
& Georgian &  Early Vic. & Late V. /Edw. & Interwar & Postwar & Cont. & Revival \\

Mean Herf. & 0.88 &  0.80 & 0.79 & 0.77 & 0.68 &  0.70 &  0.70 \\  
 \midrule 
\emph{Pred. vintage} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
\cmidrule(lr){2-8} 
Georgian & -- & -0.21 (-9.87) & -0.28 (-13.11) & -0.33 (-9.95) & -0.27 (-6.30) & -0.25 (-7.97) & -0.25 (-7.54) \\
 Early Vic. & -0.22 (-6.28) &  -- & -0.19 (-19.20) & -0.31 (-13.70) & -0.21 (-10.05) & -0.21 (-7.53) & -0.15 (-3.84) \\
 Late V./Edw. & -0.36 (-5.89) & -0.24 (-18.03) &  -- & -0.26 (-21.88) & -0.23 (-9.08) & -0.24 (-4.96) & -0.16 (-4.33) \\
 Interwar & -0.12 (-1.55) & -0.32 (-12.77) & -0.24 (-19.87) &  -- & -0.13 (-22.67) & -0.25 (-12.58) & -0.16 (-6.49) \\
 Postwar & -0.51 (-33.71) & -0.30 (-6.24) & -0.36 (-13.13) & -0.26 (-34.82) & -- & -0.22 (-10.34) & -0.24 (-7.70) \\
 Cont. & -0.44 (-3.31) & -0.37 (-17.78) & -0.38 (-17.63) & -0.39 (-25.39) & -0.18 (-15.67) & -- & -0.19 (-7.71) \\
 Revival & -0.09 (-0.42) & -0.40 (-20.64) & -0.41 (-22.54) & -0.31 (-19.71) & -0.28 (-24.06) & -0.22 (-12.40) &  -- \\
\bottomrule 
\end{tabular}
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 vintages $v$ received, calculated as: $Herf_i=\sum_{v=1}^{v=7} (votes_v/votes_{all})^2$. A high score indicates high levels of consensus within the ensemble. The Herf. scores tend to be lower at off-diagonal cells, indicating lower consensus for misclassifications.
\end{minipage}
\end{table}

\begin{table}[ht] 
\centering 
 \caption{Mean Values for image quality variables, by vintage}

\label{tab:imgqualsumstats}
\begin{tabular}{lcccc} 
\toprule 
Ground Truth & Share Blocked & House Area & Window Area & Image Offset \\ 
\midrule
 Georgian & 0.07 & 0.81 & 0.15 & 0.07 \\ 
 Early Vic. & 0.06 & 0.86 & 0.16 & 0.05 \\ 
 Late V./Edw. & 0.11 & 0.84 & 0.17 & 0.08 \\ 
 Interwar & 0.19 & 0.70 & 0.11 & 0.12 \\ 
 Postwar & 0.16 & 0.64 & 0.07 & 0.11 \\ 
 Cont. & 0.09 & 0.72 & 0.11 & 0.09 \\ 
 Revival & 0.10 & 0.78 & 0.11 & 0.09 \\ 
 \bottomrule
\end{tabular}
\begin{minipage}{0.9\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated. Images taken not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
\end{minipage}
\end{table}

\begin{table}[!htb] 
\caption{Difference in photo characteristics by correctly and incorrectly classified images} 
\label{tab:diffimgchar} 
\centering 
\begingroup\scriptsize 
\begin{tabular}{lrrrrrrr}

\toprule

\emph{Predicted} & \multicolumn{7}{c}{\emph{Ground truth}} \\ 
  \cmidrule(lr){2-8} 
& Georgian & Early Vic. & Late V./Edw. & Interwar & Postwar & Cont. & Revival \\

 \cmidrule(lr){2-8} 
 & \multicolumn{7}{c}{\emph{ Panel A: Total share of house blocked by vehicles or trees}}\\ 
\cmidrule(lr){1-1} \cmidrule(lr){2-8}

Georgian &  -- &  0 (0.16) & -0.03 (-1.37) & -0.07 (-2.16) & -0.06 (-0.91) & -0.02 (-0.86) &  0.02 (0.39) \\  
  Early Vic. & -0.04 (-2.80) &  -- & -0.04 (-7.42) & -0.11 (-8.26) & -0.09 (-5.45) & -0.03 (-1.97) &  0.01 (0.47) \\  
  Late V./Edw. &  0.03 (0.91) &  0.03 (2.55) &  -- &  0.01 (0.40) &  0.01 (0.57) &  0.01 (0.17) &  0.08 (1.89) \\  
  Interwar &  0.17 (2.24) &  0.11 (3.71) &  0.09 (5.73) &  -- &  0.03 (4.16) &  0.18 (4.42) &  0.07 (2.40) \\  
  Postwar &  0.13 (0.96) &  0.03 (1.44) &  0.11 (2.88) & -0.01 (-1.20) &  -- &  0.09 (3.39) &  0.04 (1.09) \\  
  Cont. &  0.16 (0.77) & -0.02 (-1.91) &  0.03 (1.14) & -0.03 (-0.92) & -0.04 (-3.06) &  -- & -0.03 (-1.32) \\  
  Revival &  0.18 (0.74) &  0.03 (0.92) &  0.01 (0.26) & -0.05 (-3.03) & -0.06 (-4.90) &  0.04 (2.02) &  -- \\

\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
 & \multicolumn{7}{c}{\emph{ Panel B: Share of house area}}\\ 
\cmidrule(lr){1-1} \cmidrule(lr){2-8}

  Georgian &  -- & -0.11 (-3.43) & -0.10 (-2.67) &  0.09 (1.94) &  0.10 (0.96) &  0.11 (1.29) & -0.02 (-0.31) \\  
  Early Vic. &  0.05 (1.30) &  -- &  0.03 (1.75) &  0.07 (2.45) &  0.18 (5.01) &  0.12 (2.19) &  0.05 (1.03) \\  
  Late V./Edw. & -0.09 (-2.08) & -0.07 (-3.10) &  -- &  0.02 (1.07) &  0.08 (2.23) & -0.08 (-1.29) &  0.04 (0.71) \\  
  Interwar &  0.08 (0.55) & -0.16 (-3.68) & -0.14 (-6.48) &  -- &  0.03 (2.92) & -0.04 (-1.03) & -0.09 (-2.65) \\  
  Postwar & -0.33 (-1.98) & -0.24 (-3.82) & -0.18 (-3.25) & -0.05 (-4.60) &  -- & -0.12 (-2.78) & -0.16 (-4.57) \\  
  Cont. & -0.21 (-1.58) & -0.16 (-2.99) & -0.15 (-3.45) & -0.02 (-0.55) &  0.01 (0.23) &  -- & -0.06 (-1.43) \\  
  Revival & -0.03 (-0.15) & -0.04 (-0.69) & -0.11 (-2.70) &  0.06 (2.51) &  0.08 (3.30) &  0.05 (1.30) &  -- \\

\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
 & \multicolumn{7}{c}{\emph{ Panel C: Share of window area}}\\ 
\cmidrule(lr){1-1} \cmidrule(lr){2-8}

 Georgian &  -- & -0.06 (-6.02) & -0.02 (-1.10) & -0.02 (-1.92) &  0.03 (1.26) & -0.03 (-1.28) & -0.01 (-0.42) \\  
  Early Vic. & -0.01 (-0.60) &  -- & -0.01 (-1.51) &  0.03 (2.72) &  0.04 (5.30) &  0.01 (0.70) &  0.02 (1.83) \\  
  Late V./Edw. &  0 (0.09) & -0.02 (-2.67) &  -- &  0.04 (4.85) &  0.02 (1.81) &  0.02 (0.98) &  0.02 (1.59) \\  
  Interwar & -0.03 (-0.92) & -0.09 (-10) & -0.08 (-13.20) &  -- &  0.01 (2.98) & -0.03 (-2.41) & -0.03 (-3.48) \\  
  Postwar & -0.07 (-4.42) & -0.09 (-5.80) & -0.08 (-4.50) & -0.02 (-4.95) &  -- & -0.05 (-4.42) & -0.05 (-5.63) \\  
  Cont. & -0.07 (-2.04) & -0.08 (-6.97) & -0.05 (-3.73) & -0.01 (-1.46) &  0.01 (2.50) &  -- & -0.02 (-2.58) \\  
  Revival & -0.02 (-0.18) & -0.06 (-4.39) & -0.03 (-1.71) &  0.01 (1.04) &  0.02 (2.50) & -0.02 (-2.33) &  -- \\

\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
 & \multicolumn{7}{c}{\emph{ Panel D: Image offset}}\\ 
\cmidrule(lr){1-1} \cmidrule(lr){2-8}

 Georgian &  -- &  0.04 (5.44) &  0.02 (2.61) & -0.02 (-1.71) & -0.03 (-1.33) &  0.01 (1) &  0.01 (0.55) \\  
  Early Vic. &  0.01 (0.64) &  -- & -0.02 (-6.59) & -0.03 (-3.82) & -0.04 (-4.98) & -0.01 (-0.93) & -0.03 (-2.78) \\  
  Late V./Edw. &  0.04 (1.96) &  0.03 (4.68) &  -- & -0.01 (-1.25) & -0.02 (-2.14) &  0.01 (0.46) &  0 (0.25) \\  
  Interwar &  0.03 (1.16) &  0.06 (6.28) &  0.05 (9.75) &  -- &  0.01 (2.35) &  0 (0.06) &  0.03 (3.19) \\  
  Postwar &  0.04 (1.07) &  0.06 (3.31) &  0.04 (3.37) &  0 (1.11) &  -- &  0.02 (1.95) &  0.06 (4.20) \\  
  Cont. &  0.08 (2.11) &  0.05 (3.87) &  0.04 (3.40) & -0.01 (-1.32) & -0.02 (-4.26) &  -- &  0 (0.20) \\  
  Revival &  0 (0.02) &  0.03 (2.06) &  0.01 (1) & -0.01 (-1.85) & -0.01 (-1.02) &  0.02 (2.22) &  -- \\  
\bottomrule

\end{tabular} 
 \begin{minipage}{\textwidth} 
\footnotesize 
\vspace{0.25cm}
\emph{Notes:} Cross-tabulation of photo characteristics by projected and ground truth. Off-diagonal elements ($Predicted_{j}-Ground Truth_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given ground truth vintage. For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic. to the set of correctly classified Georgian photos. The numbers in italic represent the mean characteristic value for each set of correctly classified photos. T-stats are in parenthesis.
\end{minipage} 
\endgroup 
\end{table}

\begin{figure}[htb!]
\caption{Examples of Estimated Building Vintages}
```{r plot_top_pictures, cache=TRUE, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Examples of Buildings, classified into Vintages"}
source("../R/plot_top_pictures.R")
plot_top_pictures(img.width = "45px")
```
\label{fig:vint_examples}
\begin{minipage}{0.7\textwidth}
\footnotesize \emph{Notes:} For a brief discussion of the building vintages see page \pageref{def_eras}.
\end{minipage}
\end{figure}

\begin{figure}[htb!]
  \caption{Difference of $F_1$-scores: spatial model vs. base model }
  \centering
    \includegraphics[width=0.8\textwidth]{figures/barplot_f1scores.jpg}
  \label{fig:boxplot}
\begin{minipage}{0.7\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} The bar plot shows difference in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs. a classifier using building level information only (red).
\end{minipage}
\end{figure}

\begin{table}[htb!]
\caption{Vintage predictions as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
\label{tab:aic}
\centering
\begin{tabular}{lrrrr}
  \toprule
 & \emph{No ML pred.} & \emph{Base pred.} & \emph{Spatial pred., all} & \emph{Spatial pred., high certainty} \\ 
  \midrule
  Georgian & 1,282 & 1,052 & 1,037 & 714 \\ 
  Early Victorian & 10,231 & 7,597 & 7,259 & 4,594 \\ 
  Late Vic./Edw. & 16,204 & 11,059 & 10,491 & 6,173 \\ 
  Interwar & 18,333 & 14,471 & 13,637 & 7,670 \\ 
  Postwar & 16,845 & 14,873 & 14,648 & 7,613 \\ 
  Contemporary & 2,885 & 2,281 & 2,240 & 1,054 \\ 
  Revival & 3,336 & 2,564 & 2,480 & 1,089 \\ 
   \bottomrule
\end{tabular}
\begin{minipage}{0.7\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:}
AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), the suggested spatial ML predictor (Column 3 \& 4). Across building styles, the AIC are lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4). This suggests that the spatial predictor performs best.
\end{minipage}
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Summary statistics residential property transactions} 
  \label{tab:sumstats} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\toprule
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\midrule
Price & 23,768 & 253,646.20 & 170,987.20 & 10,000 & 127,000 & 326,374.8 & 1,000,000 \\ 
Year & 23,768 & 2,004.89 & 6.59 & 1,995 & 1,999 & 2,010 & 2,018 \\ 
ln(volume) & 23,768 & 286.00 & 188.14 & 0.00 & 215.50 & 370.89 & 1,926.45 \\ 
ln(area) & 23,768 & 63.25 & 28.44 & 4.94 & 45.74 & 72.46 & 1,058.70 \\ 
ln(dist. city center) & 23,768 & 2,477.63 & 1,007.55 & 112.78 & 1,652.39 & 3,166.05 & 5,023.62 \\ 
New & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
Type: detached & 23,768 & 0.13 & 0.34 & 0 & 0 & 0 & 1 \\ 
Type: semi-detached & 23,768 & 0.35 & 0.48 & 0 & 0 & 1 & 1 \\ 
Type: terraced & 23,768 & 0.52 & 0.50 & 0 & 0 & 1 & 1 \\ 
Georgian & 23,768 & 0.03 & 0.16 & 0 & 0 & 0 & 1 \\ 
Early Vic. & 23,768 & 0.15 & 0.36 & 0 & 0 & 0 & 1 \\ 
Late Vic./Edw. & 23,768 & 0.21 & 0.40 & 0 & 0 & 0 & 1 \\ 
Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
Postwar & 23,768 & 0.23 & 0.42 & 0 & 0 & 0 & 1 \\ 
Contemporary & 23,768 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
Revival & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
Neigh: Georgian & 23,768 & 0.02 & 0.12 & 0 & 0 & 0 & 1 \\ 
Neigh: Early Vic. & 23,768 & 0.14 & 0.35 & 0 & 0 & 0 & 1 \\ 
Neigh: Late V./Edw. & 23,768 & 0.22 & 0.41 & 0 & 0 & 0 & 1 \\ 
Neigh: Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
Neigh: Postwar & 23,768 & 0.25 & 0.43 & 0 & 0 & 1 & 1 \\ 
Neigh: Contemporary & 23,768 & 0.02 & 0.15 & 0 & 0 & 0 & 1 \\ 
Neigh: Revival & 23,768 & 0.03 & 0.18 & 0 & 0 & 0 & 1 \\ 
\bottomrule
\end{tabular} 
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\singlespacing
\footnotesize \emph{Notes:} Summary statistics for sample of 23,768 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images. The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models, as suggested by @Lindenthal2017a. We control for the location of each building by calculating the distance to the city center proxied by Great St. Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA). The estimated scores for building vintages are inferred from the Google Street View classification model.
\end{minipage}
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Hedonic Regression Estimates} 
  \label{tab:hedreg} 
\footnotesize 
\begin{tabular}{@{\extracolsep{5pt}}lcccccccc} 
\toprule
 & \multicolumn{6}{c}{Dependent variable: \emph{ln(price)}} \\ 
\cmidrule{2-9} 
 & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\midrule
Constant & 13.20$^{***}$ & 13.45$^{***}$ & 13.29$^{***}$ & 13.21$^{***}$ & 15.61$^{***}$ & 18.89$^{***}$ & 13.14$^{***}$ & 13.20$^{***}$ \\ 
  & (0.20) & (0.17) & (0.20) & (1.74) & (1.72) & (3.77) & (0.20) & (0.20) \\ 
  ln(dist. city center) & $-$0.45$^{***}$ & $-$0.50$^{***}$ & $-$0.47$^{***}$ & $-$0.48$^{**}$ & $-$0.72$^{***}$ & $-$1.12$^{***}$ & $-$0.44$^{***}$ & $-$0.45$^{***}$ \\ 
  & (0.03) & (0.02) & (0.03) & (0.23) & (0.21) & (0.07) & (0.03) & (0.03) \\ 
  Type: semi-detached & $-$0.12$^{***}$ & $-$0.14$^{***}$ & $-$0.13$^{***}$ & 0.01 & $-$0.12$^{**}$ & $-$0.10 & $-$0.13$^{***}$ & $-$0.13$^{***}$ \\ 
  & (0.01) & (0.01) & (0.01) & (0.04) & (0.05) & (0.07) & (0.01) & (0.01) \\ 
  Type: terraced & $-$0.19$^{***}$ & $-$0.20$^{***}$ & $-$0.19$^{***}$ & $-$0.01 & $-$0.10$^{*}$ & $-$0.12 & $-$0.20$^{***}$ & $-$0.20$^{***}$ \\ 
  & (0.01) & (0.01) & (0.01) & (0.04) & (0.05) & (0.11) & (0.01) & (0.01) \\ 
  ln(area) & 0.40$^{***}$ & 0.40$^{***}$ & 0.40$^{***}$ & 0.33$^{***}$ & 0.29$^{***}$ & 0.21$^{***}$ & 0.39$^{***}$ & 0.39$^{***}$ \\ 
  & (0.01) & (0.01) & (0.01) & (0.07) & (0.09) & (0.01) & (0.01) & (0.01) \\ 
  ln(volume) & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & 0.01 & 0.02$^{***}$ & 0.02 & 0.01$^{***}$ & 0.01$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.01) & (0.01) & (0.09) & (0.001) & (0.002) \\ 
  New & 0.09$^{***}$ & 0.18$^{***}$ & 0.13$^{***}$ &  &  &  & 0.11$^{***}$ & 0.10$^{***}$ \\ 
  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.02) \\ 
  \cmidrule{2-9}
  & \multicolumn{8}{c}{\emph{Base: Contemporary}} \\
  Georgian & $-$0.04 & 0.06$^{***}$ & $-$0.04 &  &  &  & 0.01 & 0.15$^{**}$ \\ 
  & (0.03) & (0.02) & (0.03) &  &  &  & (0.03) & (0.06) \\ 
  Early Vic. & $-$0.13$^{***}$ & $-$0.01 & $-$0.11$^{***}$ &  &  &  & $-$0.04$^{**}$ & 0.01 \\ 
  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.07) \\ 
  Late Vic./Edw. & 0.01 & 0.11$^{***}$ & 0.04$^{**}$ &  &  &  & 0.06$^{***}$ & 0.15$^{**}$ \\ 
  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.08) \\ 
  Interwar & $-$0.15$^{***}$ & $-$0.02$^{**}$ & $-$0.13$^{***}$ &  &  &  & $-$0.08$^{***}$ & $-$0.15$^{**}$ \\ 
  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.06) \\ 
  Postwar & $-$0.22$^{***}$ & $-$0.06$^{***}$ & $-$0.19$^{***}$ &  &  &  & $-$0.12$^{***}$ & $-$0.17$^{***}$ \\ 
  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.04) \\ 
  Revival & 0.04$^{**}$ & 0.05$^{***}$ & 0.03 & $-$0.10 & 0.13$^{***}$ & 0.12 & 0.05$^{**}$ & 0.07$^{*}$ \\ 
  & (0.02) & (0.01) & (0.02) & (0.09) & (0.04) &  (0.09) & (0.02) & (0.04) \\ 
    \cmidrule{2-9}
  & \multicolumn{8}{c}{\emph{Base: Neigh. Contemporary}} \\

   Neigh: Georgian &  &  &  &  &  &  & $-$0.10$^{**}$ & $-$0.44$^{***}$ \\ 
  &  &  &  &  &  &  & (0.04) & (0.05) \\ 
  Neigh: Early Vic. &  &  &  &  &  &  & $-$0.13$^{***}$ & $-$0.15$^{***}$ \\ 
  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
  Neigh: Late V./Edw. &  &  &  &  &  &  & $-$0.05$^{**}$ & $-$0.15$^{*}$ \\ 
  &  &  &  &  &  &  & (0.02) & (0.08) \\ 
  Neigh: Interwar &  &  &  &  &  &  & $-$0.11$^{***}$ & $-$0.01 \\ 
  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
  Neigh: Postwar &  &  &  &  &  &  & $-$0.14$^{***}$ & $-$0.24$^{***}$ \\ 
  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
  Neigh: Revival &  &  &  &  &  &  & $-$0.03 & $-$0.03 \\ 
  &  &  &  &  &  &  & (0.02) & (0.06) \\  
\midrule
Year dummies & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Neigh. dummies & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Interaction terms & No & No & No & No & No & No & No & Table \ref{tab:hedregint} \\ 
Observations & 15,642 & 23,415 & 15,721 & 377 & 567 & 348 & 15,503 & 15,503 \\ 
Adjusted R$^{2}$ & 0.88 & 0.88 & 0.88 & 0.93 & 0.91 & 0.92 & 0.89 & 0.89 \\ 
\bottomrule
\end{tabular} 
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01. Standard errors are robust (White's estimator). Models (1) and (4) are estimated using ground truth classifications only. Models (2) and (5) are estimated based on all observations that have been automatically classified. Models (3) and (6) are also based on automatic classifications but the sample is reduced to high confidence predictions only. Models (4-6) are estimated on sales of newly completed buildings only. The interaction terms for Model (8) are in Table \ref{tab:hedregint}.  
\end{minipage}
\end{table}

\begin{table}[ht]
\caption{Counts: Building vintage and neighboring buildings' vintage}
\label{tab:vintneigh}
\centering
\begin{tabular}{lrrrrrrr}
\toprule
\emph{Neigh.} & \multicolumn{7}{c}{\emph{Building}} \\
 \cmidrule(lr){1-1}
 \cmidrule(lr){2-8}
& \emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interw.} & \emph{Postw.} & \emph{Cont.} & \emph{Revival} \\ 
  \cmidrule(lr){2-8}
Georgian & 164 &  44 &   7 &   0 &   0 &   0 &   1 \\ 
  Early Vic. &  20 & 2205 & 274 &  34 &  18 &  18 &  27 \\ 
  Late Vic./Edw. &  22 & 473 & 3128 & 226 &  22 &   9 &  10 \\ 
  Interwar &   7 &  47 & 176 & 4165 & 450 &  22 &  45 \\ 
  Postwar &   1 &  10 &  25 & 553 & 2712 &  38 &  32 \\ 
  Contemporary &   0 &   0 &   5 &  16 &  42 & 348 &  12 \\ 
  Revival &   2 &  17 &   5 &  62 &  36 &  19 & 153 \\ 
   \bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} The vintage of direct neighborhoods is defined as the most frequent detected style on the same street and within 100m. 
\end{minipage}
\end{table}

\begin{table}[ht]
\centering
\caption{Coefficients interaction terms: Building and neighborhood style}
\label{tab:hedregint}
\begin{tabular}{lccccccc}
\toprule
\emph{Neigh.} & \multicolumn{7}{c}{\emph{Building}} \\
 \cmidrule(lr){1-1}
 \cmidrule(lr){2-8}
& \emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interw.} & \emph{Postw.} & \emph{Cont.} & \emph{Revival} \\ 
  \cmidrule(lr){2-8}

Georgian & 0.19 & 0.25 & 0.56** & -- & -- & -- & -- \\ 
   & (0.29) & (0.25) & (0.27) & -- & -- & -- & -- \\ 
Early Vic. & -0.14 & -0.04 & -0.13 & 0.03 & 0.07 & -- & 0.10 \\ 
  & (0.18) & (0.09) & (0.12) & (0.09) & (0.08) & -- & (0.10) \\ 
Late V./Edw. & -0.004 & 0.002 & -0.01 & 0.18* & 0.08 & -- & 0.13 \\ 
   & (0.19) & (0.11) & (0.13) & (0.10) & (0.10) & -- & (0.12) \\ 
Interwar & -0.23 & -0.20** & -0.17 & -0.03 & -0.07 & -- & -0.15 \\ 
  & (0.19) & (0.09) & (0.11) & (0.08) & (0.06) & -- & (0.09) \\ 
Postwar & 0.18 & 0.03 & -0.05 & 0.15** & 0.14*** & -- & 0.01 \\ 
   & (0.28) & (0.11) & (0.12) & (0.07) & (0.05) & -- & (0.09) \\ 
Contemporary & -- & -- & -- & -- & -- & -- & -- \\ 
  & -- & -- & -- & -- & -- & -- & -- \\ 
  Revival & -- & -- & -0.43*** & 0.09 & 0.04 & -- & -0.04 \\ 
   & -- & -- & (0.15) & (0.08) & (0.07) & -- & (0.09) \\ 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01. Standard errors are robust (White's estimator). This table features the coefficients for interaction terms of building style and neighborhood styles only, while Table \ref{tab:hedreg}, Column 8 presents all other coefficients for this model.
\end{minipage}

\end{table}

\begin{table}[ht]
\centering
\caption{Combined effect: Sum of direct, neighborhood and interaction coefficients}
\label{tab:comb}
\begin{tabular}{lccccccc}
\toprule
\emph{Neigh.} & \multicolumn{7}{c}{\emph{Building}} \\
 \cmidrule(lr){1-1}
 \cmidrule(lr){2-8}
& \emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interw.} & \emph{Postw.} & \emph{Cont.} & \emph{Revival} \\ 
  \cmidrule(lr){2-8}
Georgian & -0.11 & -0.17 & 0.27 & -- &--  & -0.44 &--  \\ 
  Early Vic. & -0.15 & -0.18 & -0.13 & -0.28 & -0.25 & -0.15 & 0.02 \\ 
  Late Vic./Edw. & -0.00 & -0.13 & -0.00 & -0.12 & -0.24 & -0.15 & 0.06 \\ 
  Interwar & -0.10 & -0.19 & -0.03 & -0.20 & -0.26 & -0.01 & -0.09 \\ 
  Postwar & 0.09 & -0.19 & -0.13 & -0.23 & -0.27 & -0.24 & -0.16 \\ 
  Contemporary & 0.15 & 0.01 & 0.15 & -0.15 & -0.17 & 0.00 & 0.07 \\ 
  Revival & -- & -- & -0.30 & -0.09 & -0.16 & -0.03 & 0.00 \\ 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\vspace{0.25cm}
\footnotesize \emph{Notes:} The combined effect of building styles on property values is calculated by adding up the direct, neighborhood and interaction effects (Table \ref{tab:hedregint}). A revival building surrounded by other revival buildings, for instance, commands no premium over a contemporary building in a new neighborhood.
\end{minipage}
\end{table}

\clearpage

# Bibliography

### 2019-09-04 text/manuscript_assa.tex
clean slate

--- 2019-09-04 text/manuscript_assa.Rmd
@@
----
-title: "Machine Learning, Building Vintage and Property Values"
-author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
-date: "`r format(Sys.time(), '%d %B %Y')`"
-tags: Externalities of architecture, machine learning
-fig_caption: yes
-header-includes:
-   - \usepackage{soul}
-   - \usepackage{color}
-   - \sethlcolor{yellow}
-   - \usepackage{float}
-   - \usepackage{booktabs}
-   - \usepackage{graphicx}
-   - \usepackage{grffile}
-   - \usepackage{bm}
-   - \usepackage{amsmath}
-   - \usepackage{setspace}
-   - \usepackage{multirow}
-   - \doublespacing
-   - \usepackage[backend=bibtex, style=authoryear]{biblatex}
-fig_width: 6
-fig_height: 4
-output: 
-  pdf_document:
-    keep_tex: true
-bibliography: references.bib
-abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View.
-Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of building vintages.
-Third, it investigates whether architectural styles influence house prices.
-For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings.
-This indicates that any premia are for vintage-related quality characteristics and not for a home's ``beauty''."
----
-
-# Introduction
+\documentclass[]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Machine Learning, Building Vintage and Property Values},
+            pdfauthor={Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson (University of Alabama)},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\providecommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+
+  \title{Machine Learning, Building Vintage and Property Values}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+    \author{Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson
+(University of Alabama)}
+    \preauthor{\centering\large\emph}
+  \postauthor{\par}
+      \predate{\centering\large\emph}
+  \postdate{\par}
+    \date{04 September 2019}
+
+\usepackage{soul}
+\usepackage{color}
+\sethlcolor{yellow}
+\usepackage{float}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{grffile}
+\usepackage{bm}
+\usepackage{amsmath}
+\usepackage{setspace}
+\usepackage{multirow}
+\doublespacing
+\usepackage[backend=bibtex, style=authoryear]{biblatex}
+
+\begin{document}
+\maketitle
+\begin{abstract}
+This paper first introduces an algorithm that collects pictures of
+individual buildings from Google Street View. Second, it trains a deep
+convolutional neural network (CNN) to classify residential buildings
+into architectural styles, taking into account spatial dependencies of
+building vintages. Third, it investigates whether architectural styles
+influence house prices. For re-sales, the architectural style is a
+significant determinant of transaction prices while no such effect is
+found for new buildings. This indicates that any premia are for
+vintage-related quality characteristics and not for a home's ``beauty''.
+\end{abstract}
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
 \let\svthefootnote\thefootnote
-\let\thefootnote\relax\footnote{{*Corresponding author: Thies Lindenthal (htl24@cam.ac.uk).
+\let\thefootnote\relax
+
+\footnote{{*Corresponding author: Thies Lindenthal (htl24@cam.ac.uk).
 Replication files are available from the author's Github repository \href{https://github.com/thies}{https://github.com/thies}.
@@
 Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp and seminar participants at UCL/Bartlett and at the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
+
 \addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
-If new developments were only pleasing to the eye, so Britain's *Building Better, Building Beautiful Commission*, nimbyism would cease and housing supply could finally reach the levels demanded by a growing and more affluent population [@economistlineofbeauty2018].
-The inaugural chair of this new governmental commission boldly suggests that we should *``build, as our Georgian and Victorian forebears built* [...].
-*All objections to new building would slip away in the sheer relief of the public''* [@scruton2018].
-Even Prince Charles, in similar spirit, put forward ten principles for urban growth and architecture that emphasize tradition and aesthetics [@princecharles2014].
-When governments and princes occupy themselves with beauty, economists surely may take a closer look as well.
-In this paper, we aim to identify the architectural styles of residential buildings using computer vision techniques and to empirically search for any transaction price premia associated with these styles.
-If aesthetics were as strong a force in the built environment as claimed, we should indeed find a significant effect on property prices.
-
-This paper will assess architectural aesthetics heads on and analyze the visual appearance of residential buildings using street level images.
-Recent work illustrates how street level imagery and machine learning classification is an efficient and powerful combination for measuring previously unobserved characteristics of the urban environment.
-@Naik2017 describe how neighborhood demographics may impact the physical appearance of neighborhoods.
-@Gebru2017 use classified vehicle make and model to predict income, race, education, and voting patterns at the precinct level.
-@Glaeser2016 predict income in New York City.
-@Naik2016AER create a neighborhood safety based Streetscore which is shown to be highly correlated with neighborhood population density and household income.
-@Nadai2016 find that greenery and street facing windows contribute to a positive appearance of safety while @Liu2017 evaluate the quality and upkeep of the built environment along Beijing's streets.
-
-@GlaeserKincaidNaik2018 push the level of observation from the block, street, or street-section level to the individual \emph{building level}.
-Utilizing images of buildings' exteriors collected from Google Street View\footnote{\href{https://www.google.co.uk/maps}{https://www.google.co.uk/maps}}, and to a lesser degree interior images from Zillow, they find that looks matter, at least in Boston: A one standard deviation improvement of a building's exterior is associated with an additional USD 70,000 in home value.
-Intuitively, the link between good looks and value is bi-directional: The appearance of buildings that went through foreclosure deteriorated significantly [@GlaeserKincaidNaik2018].
-
-Zooming in at individual buildings significantly increases the benefits of using mass collected street level imagery in economic research: property characteristics previously deemed "unobservable" can be directly observed in an accurate, objective, automatic and therefore cost effective way.
-Deriving additional variables from unconventional data sources like 3D airborne laser scanning (or in our case Google Street View) is fundamental since this provides "essential determinants influencing real estate prices [which] are constantly missing and are not accessible in official and mass appraiser databases" [@Helbich2013].
-
-In this paper we suggest a method to collect a large number of images of individual UK buildings from Google Street View, classify the depicted buildings using deep convolutional neural networks, combine the derived information with sales price data and, ultimately, estimate marginal prices for the estimated building characteristics.
-Our work demonstrates that utilizing pretrained convolutional neural networks to detect complex characteristics such as housing vintages with relatively high accuracy comes at low computational costs and is feasible with only modestly-sized training data.
-No supercomputers are needed, a modern laptop will do.
-
-## Building vintage and property values
-
-The aesthetics of different architectural eras make for an easy cocktail party conversation topic -- and they also influence market prices.
-Using architectural assessments by human experts, @Buitelaar2017 find a sizable premium of 5\% for new buildings in the Netherlands that refer to traditional styles and a staggering 15\% premium for new buildings that closely follow traditional shapes, facade composition and details.
-Their study carefully disentangles the architectural style from other unobserved characteristics such as building quality, differences in location or year of construction.
-These controls are crucial, as earlier work has established that age and vintage variables tend to be highly correlated.
-@Coulson2008, for instance, suggest a non-parametric estimator and establish a U-shaped age function and distinct price discounts for postwar and contemporary vintages (vis-à-vis more historic vintages).
-@Francke2017a investigate the depreciation of residential real estate in the Netherlands and decompose land versus structure values singling out the effect of "physical deterioration, functional obsolescence and and vintage effects".
-They find that buildings from the 1930s carry a strong price premium.
-
-A large scale assessment of buildings' exteriors will allow for an analysis of the externalities of architecture.
-Buildings hardly ever stand in isolation and @Ahlfeldt2012 investigate the influence a building's architecture exerts on its surroundings.
-They observe a positive price effect for residential buildings in the direct proximity of iconic homes by Frank Lloyd Wright in Oak Park, Illinois.
-A building's exterior does not need to be an architectural masterpiece to co-determine the value of other houses close by.
-Homogeneity of building shapes within street segments does influence property values.
-A similarly shaped neighboring building is value enhancing while proximity to a wildly different neighboring shape, everything else remaining equal, is detrimental to property values [@Lindenthal2017b].
-
-Unfortunately, the traditional approaches chosen by e.g.
-@Buitelaar2017 or @Ahlfeldt2012 do not scale well.
-Each observation has to be classified into architectural styles by a human expert, which is time-consuming and costly, imposing an upper limit on the number of observations and the level of detail captured for each observation in any given sample.
-Google Street View offers a solution to this nexus as it captures the images of almost all buildings in many cities around the world at high level of accuracy and detail.
-The challenge we address in this paper is to extract and utilize building level information from this ubiquitous sensor.
-
-# Methodology
-
-## Image collection
-
-The first challenge when trying to collect building images in the UK is fundamental: How can one identify the building of interest correctly?
-Simply looking up an address on Google Maps too often leads to imprecise `street views' and not the building-level portraits needed.
-Fig.
-\ref{fig:84Vin} presents a typical result from an address level search, showing a broad ensemble of buildings instead of singling out the building of interest (in this case, the partly captured terraced house at the very left margin).
+
+If new developments were only pleasing to the eye, so Britain's
+\emph{Building Better, Building Beautiful Commission}, nimbyism would
+cease and housing supply could finally reach the levels demanded by a
+growing and more affluent population (The Economist 2018). The inaugural
+chair of this new governmental commission boldly suggests that we should
+\emph{``build, as our Georgian and Victorian forebears built}
+{[}\ldots{}{]}. \emph{All objections to new building would slip away in
+the sheer relief of the public''} (Scruton 2018). Even Prince Charles,
+in similar spirit, put forward ten principles for urban growth and
+architecture that emphasize tradition and aesthetics (HRH The Prince of
+Wales 2014). When governments and princes occupy themselves with beauty,
+economists surely may take a closer look as well. In this paper, we aim
+to identify the architectural styles of residential buildings using
+computer vision techniques and to empirically search for any transaction
+price premia associated with these styles. If aesthetics were as strong
+a force in the built environment as claimed, we should indeed find a
+significant effect on property prices.
+
+This paper will assess architectural aesthetics heads on and analyze the
+visual appearance of residential buildings using street level images.
+Recent work illustrates how street level imagery and machine learning
+classification is an efficient and powerful combination for measuring
+previously unobserved characteristics of the urban environment. Naik et
+al. (2017) describe how neighborhood demographics may impact the
+physical appearance of neighborhoods. Gebru et al. (2017) use classified
+vehicle make and model to predict income, race, education, and voting
+patterns at the precinct level. Glaeser et al. (2018) predict income in
+New York City. Naik, Raskar, and Hidalgo (2016) create a neighborhood
+safety based Streetscore which is shown to be highly correlated with
+neighborhood population density and household income. De Nadai et al.
+(2016) find that greenery and street facing windows contribute to a
+positive appearance of safety while Liu et al. (2017) evaluate the
+quality and upkeep of the built environment along Beijing's streets.
+
+Glaeser, Kincaid, and Naik (2018) push the level of observation from the
+block, street, or street-section level to the individual
+\emph{building level}. Utilizing images of buildings' exteriors
+collected from Google Street
+View\footnote{\href{https://www.google.co.uk/maps}{https://www.google.co.uk/maps}},
+and to a lesser degree interior images from Zillow, they find that looks
+matter, at least in Boston: A one standard deviation improvement of a
+building's exterior is associated with an additional USD 70,000 in home
+value. Intuitively, the link between good looks and value is
+bi-directional: The appearance of buildings that went through
+foreclosure deteriorated significantly (Glaeser, Kincaid, and Naik
+2018).
+
+Zooming in at individual buildings significantly increases the benefits
+of using mass collected street level imagery in economic research:
+property characteristics previously deemed ``unobservable'' can be
+directly observed in an accurate, objective, automatic and therefore
+cost effective way. Deriving additional variables from unconventional
+data sources like 3D airborne laser scanning (or in our case Google
+Street View) is fundamental since this provides ``essential determinants
+influencing real estate prices {[}which{]} are constantly missing and
+are not accessible in official and mass appraiser databases'' (Helbich
+et al. 2013).
+
+In this paper we suggest a method to collect a large number of images of
+individual UK buildings from Google Street View, classify the depicted
+buildings using deep convolutional neural networks, combine the derived
+information with sales price data and, ultimately, estimate marginal
+prices for the estimated building characteristics. Our work demonstrates
+that utilizing pretrained convolutional neural networks to detect
+complex characteristics such as housing vintages with relatively high
+accuracy comes at low computational costs and is feasible with only
+modestly-sized training data. No supercomputers are needed, a modern
+laptop will do.
+
+\hypertarget{building-vintage-and-property-values}{%
+\subsection{Building vintage and property
+values}\label{building-vintage-and-property-values}}
+
+The aesthetics of different architectural eras make for an easy cocktail
+party conversation topic -- and they also influence market prices. Using
+architectural assessments by human experts, Buitelaar and Schilder
+(2017) find a sizable premium of 5\% for new buildings in the
+Netherlands that refer to traditional styles and a staggering 15\%
+premium for new buildings that closely follow traditional shapes, facade
+composition and details. Their study carefully disentangles the
+architectural style from other unobserved characteristics such as
+building quality, differences in location or year of construction. These
+controls are crucial, as earlier work has established that age and
+vintage variables tend to be highly correlated. Coulson and McMillen
+(2008), for instance, suggest a non-parametric estimator and establish a
+U-shaped age function and distinct price discounts for postwar and
+contemporary vintages (vis-à-vis more historic vintages). Francke and
+Minne (2017) investigate the depreciation of residential real estate in
+the Netherlands and decompose land versus structure values singling out
+the effect of ``physical deterioration, functional obsolescence and and
+vintage effects''. They find that buildings from the 1930s carry a
+strong price premium.
+
+A large scale assessment of buildings' exteriors will allow for an
+analysis of the externalities of architecture. Buildings hardly ever
+stand in isolation and Ahlfeldt and Mastro (2012) investigate the
+influence a building's architecture exerts on its surroundings. They
+observe a positive price effect for residential buildings in the direct
+proximity of iconic homes by Frank Lloyd Wright in Oak Park, Illinois. A
+building's exterior does not need to be an architectural masterpiece to
+co-determine the value of other houses close by. Homogeneity of building
+shapes within street segments does influence property values. A
+similarly shaped neighboring building is value enhancing while proximity
+to a wildly different neighboring shape, everything else remaining
+equal, is detrimental to property values (Lindenthal 2017a).
+
+Unfortunately, the traditional approaches chosen by e.g. Buitelaar and
+Schilder (2017) or Ahlfeldt and Mastro (2012) do not scale well. Each
+observation has to be classified into architectural styles by a human
+expert, which is time-consuming and costly, imposing an upper limit on
+the number of observations and the level of detail captured for each
+observation in any given sample. Google Street View offers a solution to
+this nexus as it captures the images of almost all buildings in many
+cities around the world at high level of accuracy and detail. The
+challenge we address in this paper is to extract and utilize building
+level information from this ubiquitous sensor.
+
+\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}}
+
+\hypertarget{image-collection}{%
+\subsection{Image collection}\label{image-collection}}
+
+The first challenge when trying to collect building images in the UK is
+fundamental: How can one identify the building of interest correctly?
+Simply looking up an address on Google Maps too often leads to imprecise
+`street views' and not the building-level portraits needed. Fig.
+\ref{fig:84Vin} presents a typical result from an address level search,
+showing a broad ensemble of buildings instead of singling out the
+building of interest (in this case, the partly captured terraced house
+at the very left margin).
 
@@
 
-Previous work sourcing imagery from Google Street View has mostly focused on neighborhood or precinct characteristics where exact spatial assignment of objects is not required and street-level images suffice.
-For major US cities, the accuracy of building image search results is higher, which should help studies such as @GlaeserKincaidNaik2018.
-
-Self-evidently, the images we use for classifying architectural style must focus on specific buildings of interest.
-For the UK, and many other countries, the Google Street View API returns the coordinates of the nearest camera snapshot for a given location but fails to provide an accurate orientation and zoom-level of the camera needed to capture the front of the building.
-To estimate the best possible view, we combine Street View metadata queries and Ordnance Survey maps to find the optimal camera orientation to center images on the front door of the building of interest.
+Previous work sourcing imagery from Google Street View has mostly
+focused on neighborhood or precinct characteristics where exact spatial
+assignment of objects is not required and street-level images suffice.
+For major US cities, the accuracy of building image search results is
+higher, which should help studies such as Glaeser, Kincaid, and Naik
+(2018).
+
+Self-evidently, the images we use for classifying architectural style
+must focus on specific buildings of interest. For the UK, and many other
+countries, the Google Street View API returns the coordinates of the
+nearest camera snapshot for a given location but fails to provide an
+accurate orientation and zoom-level of the camera needed to capture the
+front of the building. To estimate the best possible view, we combine
+Street View metadata queries and Ordnance Survey maps to find the
+optimal camera orientation to center images on the front door of the
+building of interest.
 
@@
 
-Specifically, we first look up the nearest Google Street View panorama point (green dot in Figure \ref{fig:fan}) based on the centroid (red dot) coordinates of a given building obtained from Ordnance Survey maps.
-We then perform a viewshed analysis and identify which exterior walls are visible from the panorama point, ignoring any wall segments where the direct line of sight from the panorama point is obstructed by other buildings.
-We can then estimate the camera bearing (green line) and zoom factor, based on the fan of the lines of sight (in blue).\footnote{Code necessary to replicate this analysis is available from the author's GitHub.com code repositories: \href{https://github.com/thies}{https://github.com/thies}.}
-
-Obstructed lines of sight due to greenery, fences, garden walls or large vehicles cannot be detected from the Ordnance Survey maps.
-We therefore use a first stage image classification procedure to identify if the building image is obstructed and we proceed the second-closest location if the line of sight is obstructed.
-
-By combining land registry maps with the snapshot location, we are able to automatically build a set of building frontage images for approximately 48,000 properties in Cambridge (UK).
-The Ordnance Survey maps do not provide any use type classifications so we collect images on all buildings that have a ground plate between 40 and 250 $m^2$.
-This method, however, could easily be adapted to photograph buildings in locations for which high-resolution building level maps are not available by using LIDAR based building outlines instead, which would be in the spirit of @Glaeser2016.
-
-### From pixels to computer vision
-
-We download all pictures at the highest resolution offered by Google's Street View API\footnote{\href{https://developers.google.com/maps/documentation/streetview/intro}{https://developers.google.com/maps/documentation/streetview/intro}} (640x640 color pixels).
-We then obtain 2048-dimensional feature vectors for each picture, using the \emph{Inception-v3} deep convolutional neural network [@Szegedy2015].
-\emph{Inception-v3} has been trained for the ImageNet Large Scale Visual Recognition Challenge (ILSVRC)\footnote{\url{http://image-net.org/challenges/LSVRC/}}, which evaluates image classification and object detection algorithms for a wide range of objects.
-The pretrained classifications would allow us to identify pets, vehicles or people on the pictures -- assessing architectural finesse, however, is beyond the canned classifiers' capabilities.
-
-@GlaeserKincaidNaik2018 rely on an different ILSVRC competitor, \emph{Resnet-101} [@He2016].
-They reduce the extracted feature vectors to lower dimensionality (1024 to 100 dimensions) based on principal component analysis (PCA).
-We follow a different strategy and double the dimensionality by including the feature vector of the building's nearest neighbor.
-Doubling up allows us to model spatial dependencies in building styles, similar to spatially correlated land cover classifications in @Ghimire2010a.
-
-## Image classification
-
-Cambridge's houses can be classified into seven broad eras: \footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general vintage descriptions.}
-
-* \emph{Georgian} (c1714--1837) houses feature key characteristics such as sash windows, fan lights above doors, the use of stucco on facades, often wrought work grilles, railings etc.\label{def_eras}
-
-* In the \emph{Early Victorian} era (c1837--c1870s), a growing taste for individualized embellishment led to the development of elaborate features such as carved barge boards or finials.
-The development of sheet glass led to sash windows becoming more affordable, and, increasingly, wider.
-
-* In the \emph{Late Victorian} era (c1870s--1901), bay windows became more and more widespread, and increasingly substantial.
-Stylistic movements such as the Queen Anne revival style contributed richly ornamental details to the formal repertoire employed by designers.
-Stained glass became more popular.
-\emph{Edwardian} architecture (1901-1910) tends to be less ornate than late Victorian architecture.
-
-* The \emph{Interwar} period (1918--1939) saw the cost of building construction fall, amidst a drive to provide better housing for the working classes. New housing types were being favored.
-
-* The \emph{Postwar} (1950-1980) era continued on this path, with an embrace of high-rise as well as low rise housing. Facades vary greatly between brick, tiling, pebbledash and render.
-
-* The cut-off year for our \emph{Contemporary} era to begin is 1980. \emph{Revival} are contemporary buildings trying to emulate historic, mostly Victorian, architecture.
-
-Two final-year architectural students classified a large sub-sample of approximately 25,000 images from our data set of Cambridge houses.
-This is a much larger sample than needed in our case.
-In our case, each category requires less than 250 observations to reach saturated training accuracy levels.
-We greatly exceed this number for the purpose of this paper so that we can compare the out-of-sample convolutional neural network predictions to the ground truth as assigned by the experts.
-This allows us to examine the power and size of the assignment tests.
-In addition having both human and machine classification for a large sample of the data allows for a robustness checks on the machine comparisons.
-
-We create stratified training samples of 600 buildings from each category but *Georgian*, which is the least common style in Cambridge and for which we can only sample 330 examples.
-This leaves a sufficiently sized out-of-sample verification data set.
-
-The multinomial classifier model design remains parsimonious, comprising of:
-
-* an input layer the size of the feature vectors,
-
-* one dense layer (relu) half the size of the input layer, one subsequent dropout (rate 0.5) layer,
-
-* one dense layer (relu) a quarter the size of the input layer, one subsequent dropout (rate 0.5) layer,
-
-* and the final dense output layer with softmax activation.
-
-All classifiers are implemented using the Keras/Tensorflow APIs\footnote{Keras: \href{https://keras.io/}{https://keras.io/}, Tensorflow: \href{https://github.com/tensorflow/tensorflow}{https://github.com/tensorflow/tensorflow}}.
+Specifically, we first look up the nearest Google Street View panorama
+point (green dot in Figure \ref{fig:fan}) based on the centroid (red
+dot) coordinates of a given building obtained from Ordnance Survey maps.
+We then perform a viewshed analysis and identify which exterior walls
+are visible from the panorama point, ignoring any wall segments where
+the direct line of sight from the panorama point is obstructed by other
+buildings. We can then estimate the camera bearing (green line) and zoom
+factor, based on the fan of the lines of sight (in
+blue).\footnote{Code necessary to replicate this analysis is available from the author's GitHub.com code repositories: \href{https://github.com/thies}{https://github.com/thies}.}
+
+Obstructed lines of sight due to greenery, fences, garden walls or large
+vehicles cannot be detected from the Ordnance Survey maps. We therefore
+use a first stage image classification procedure to identify if the
+building image is obstructed and we proceed the second-closest location
+if the line of sight is obstructed.
+
+By combining land registry maps with the snapshot location, we are able
+to automatically build a set of building frontage images for
+approximately 48,000 properties in Cambridge (UK). The Ordnance Survey
+maps do not provide any use type classifications so we collect images on
+all buildings that have a ground plate between 40 and 250 \(m^2\). This
+method, however, could easily be adapted to photograph buildings in
+locations for which high-resolution building level maps are not
+available by using LIDAR based building outlines instead, which would be
+in the spirit of Glaeser et al. (2018).
+
+\hypertarget{from-pixels-to-computer-vision}{%
+\subsubsection{From pixels to computer
+vision}\label{from-pixels-to-computer-vision}}
+
+We download all pictures at the highest resolution offered by Google's
+Street View
+API\footnote{\href{https://developers.google.com/maps/documentation/streetview/intro}{https://developers.google.com/maps/documentation/streetview/intro}}
+(640x640 color pixels). We then obtain 2048-dimensional feature vectors
+for each picture, using the \emph{Inception-v3} deep convolutional
+neural network (Szegedy et al. 2015). \emph{Inception-v3} has been
+trained for the ImageNet Large Scale Visual Recognition Challenge
+(ILSVRC)\footnote{\url{http://image-net.org/challenges/LSVRC/}}, which
+evaluates image classification and object detection algorithms for a
+wide range of objects. The pretrained classifications would allow us to
+identify pets, vehicles or people on the pictures -- assessing
+architectural finesse, however, is beyond the canned classifiers'
+capabilities.
+
+Glaeser, Kincaid, and Naik (2018) rely on an different ILSVRC
+competitor, \emph{Resnet-101} (He et al. 2016). They reduce the
+extracted feature vectors to lower dimensionality (1024 to 100
+dimensions) based on principal component analysis (PCA). We follow a
+different strategy and double the dimensionality by including the
+feature vector of the building's nearest neighbor. Doubling up allows us
+to model spatial dependencies in building styles, similar to spatially
+correlated land cover classifications in Ghimire, Rogan, and Miller
+(2010).
+
+\hypertarget{image-classification}{%
+\subsection{Image classification}\label{image-classification}}
+
+Cambridge's houses can be classified into seven broad eras:
+\footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general vintage descriptions.}
+
+\begin{itemize}
+\item
+  \emph{Georgian} (c1714--1837) houses feature key characteristics such
+  as sash windows, fan lights above doors, the use of stucco on facades,
+  often wrought work grilles, railings etc.\label{def_eras}
+\item
+  In the \emph{Early Victorian} era (c1837--c1870s), a growing taste for
+  individualized embellishment led to the development of elaborate
+  features such as carved barge boards or finials. The development of
+  sheet glass led to sash windows becoming more affordable, and,
+  increasingly, wider.
+\item
+  In the \emph{Late Victorian} era (c1870s--1901), bay windows became
+  more and more widespread, and increasingly substantial. Stylistic
+  movements such as the Queen Anne revival style contributed richly
+  ornamental details to the formal repertoire employed by designers.
+  Stained glass became more popular. \emph{Edwardian} architecture
+  (1901-1910) tends to be less ornate than late Victorian architecture.
+\item
+  The \emph{Interwar} period (1918--1939) saw the cost of building
+  construction fall, amidst a drive to provide better housing for the
+  working classes. New housing types were being favored.
+\item
+  The \emph{Postwar} (1950-1980) era continued on this path, with an
+  embrace of high-rise as well as low rise housing. Facades vary greatly
+  between brick, tiling, pebbledash and render.
+\item
+  The cut-off year for our \emph{Contemporary} era to begin is 1980.
+  \emph{Revival} are contemporary buildings trying to emulate historic,
+  mostly Victorian, architecture.
+\end{itemize}
+
+Two final-year architectural students classified a large sub-sample of
+approximately 25,000 images from our data set of Cambridge houses. This
+is a much larger sample than needed in our case. In our case, each
+category requires less than 250 observations to reach saturated training
+accuracy levels. We greatly exceed this number for the purpose of this
+paper so that we can compare the out-of-sample convolutional neural
+network predictions to the ground truth as assigned by the experts. This
+allows us to examine the power and size of the assignment tests. In
+addition having both human and machine classification for a large sample
+of the data allows for a robustness checks on the machine comparisons.
+
+We create stratified training samples of 600 buildings from each
+category but \emph{Georgian}, which is the least common style in
+Cambridge and for which we can only sample 330 examples. This leaves a
+sufficiently sized out-of-sample verification data set.
+
+The multinomial classifier model design remains parsimonious, comprising
+of:
+
+\begin{itemize}
+\item
+  an input layer the size of the feature vectors,
+\item
+  one dense layer (relu) half the size of the input layer, one
+  subsequent dropout (rate 0.5) layer,
+\item
+  one dense layer (relu) a quarter the size of the input layer, one
+  subsequent dropout (rate 0.5) layer,
+\item
+  and the final dense output layer with softmax activation.
+\end{itemize}
+
+All classifiers are implemented using the Keras/Tensorflow
+APIs\footnote{Keras: \href{https://keras.io/}{https://keras.io/}, Tensorflow: \href{https://github.com/tensorflow/tensorflow}{https://github.com/tensorflow/tensorflow}}.
 The computational burden of this rather shallow model design is modest.
 
-For 100 randomly drawn, stratified data sets, we train two models each: The first is based on the building specific feature vectors (2048 dimensions) only while the second also incorporates the feature vector of the nearest neighbor (combined 4096 dimensions).
-In cases where trees, fences or large vehicles obstruct the view or where the front of a building cannot be classified with high certainty, the image of the nearest neighbor provides a ``second opinion'' that is spatially correlated with the observation of interest.
-Finally we classify all buildings not used in training or evaluating the model (truly out-of-sample).
-
-When classifying a building picture, each models returns a vector of vintage-scores, each between 0 to 1, that jointly sum up to 1.
-We select the vintage with the highest score as the best estimate.
-By not excluding observations where multiple scores are vying for the top rank we retain as many observations as possible but risk a higher misclassification rate.
-
-Two variables are obtained from the distribution of classifications per observation: The ensemble classifier arrives at predictions by majority vote.
-In addition, a confidence measure is computed as the Herfindahl index of classifications by ensemble member models.\footnote{If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*.
+For 100 randomly drawn, stratified data sets, we train two models each:
+The first is based on the building specific feature vectors (2048
+dimensions) only while the second also incorporates the feature vector
+of the nearest neighbor (combined 4096 dimensions). In cases where
+trees, fences or large vehicles obstruct the view or where the front of
+a building cannot be classified with high certainty, the image of the
+nearest neighbor provides a ``second opinion'' that is spatially
+correlated with the observation of interest. Finally we classify all
+buildings not used in training or evaluating the model (truly
+out-of-sample).
+
+When classifying a building picture, each models returns a vector of
+vintage-scores, each between 0 to 1, that jointly sum up to 1. We select
+the vintage with the highest score as the best estimate. By not
+excluding observations where multiple scores are vying for the top rank
+we retain as many observations as possible but risk a higher
+misclassification rate.
+
+Two variables are obtained from the distribution of classifications per
+observation: The ensemble classifier arrives at predictions by majority
+vote. In addition, a confidence measure is computed as the Herfindahl
+index of classifications by ensemble member
+models.\footnote{If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*.
 The corresponding Herfindahl score is calculated as $(20/100)^2 + (80/100)^2 = 0.68$.}
 
-We tabulate confusion matrices and evaluate the classification performance in terms of recall, precision and $F_1$-scores.
-The next step regresses the true vintage observed, captured by binomial variables $D_{TrueVint}$, against a vector of hedonic variables $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's $\mathbf{Vintage}$, estimated both with and without spatial dependencies.
-The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients, and $\epsilon$ is the error term.
+We tabulate confusion matrices and evaluate the classification
+performance in terms of recall, precision and \(F_1\)-scores. The next
+step regresses the true vintage observed, captured by binomial variables
+\(D_{TrueVint}\), against a vector of hedonic variables \(\mathbf{X}\),
+vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
+variables and the building's \(\mathbf{Vintage}\), estimated both with
+and without spatial dependencies. The intercept is denoted by \(\alpha\)
+while \(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\gamma}\) and
+\(\bm{\lambda}\) are vectors of regression coefficients, and
+\(\epsilon\) is the error term.
 
@@
 
-The logit regressions are estimated by generalized least squares.
-For a well-performing classifier, the $\delta$ coefficients will be statistically significant and, more importantly, differences in the Akaike Information Criterion (AIC) allow for comparisons across the suggested ML classifiers.
-
-Will the resulting classifiers be biased with respect to property values, picking up correlated but irrelevant cues such as greenery, upkeep, or cars brands instead of building exteriors?
-Are, for instance, more valuable houses more likely to be classified as the popular *Late Victorian* vintage while starter homes are disproportionally more likely to be classified as e.g.
-*Early Victorian*?
-We expect that in cases in which the ensemble provided a high confidence score, building features are clearly detectable on the pictures.
-For close calls, however, where models within the ensemble cannot agree, other factors might tilt the scale towards an incorrect class.
-A sizable difference in estimated marginal prices for estimated vintages versus values for ground truth vintages in the subsequent hedonic regression (Eq.
-\ref{eq:hed}, below) would indicate such a bias.
-
-## Building era and property price
-
-Merging the estimated vintage classification with sales data [@LandRegistry2016a] we estimate a hedonic regression equation that establishes marginal prices for the building vintage [similar to @Moorhouse1994; @Asabere1989; @Vandell1989; @Fuerst2011; @Plaut2006], among other characteristics:
-\begin{equation} \label{eq:hed}
+The logit regressions are estimated by generalized least squares. For a
+well-performing classifier, the \(\delta\) coefficients will be
+statistically significant and, more importantly, differences in the
+Akaike Information Criterion (AIC) allow for comparisons across the
+suggested ML classifiers.
+
+Will the resulting classifiers be biased with respect to property
+values, picking up correlated but irrelevant cues such as greenery,
+upkeep, or cars brands instead of building exteriors? Are, for instance,
+more valuable houses more likely to be classified as the popular
+\emph{Late Victorian} vintage while starter homes are disproportionally
+more likely to be classified as e.g. \emph{Early Victorian}? We expect
+that in cases in which the ensemble provided a high confidence score,
+building features are clearly detectable on the pictures. For close
+calls, however, where models within the ensemble cannot agree, other
+factors might tilt the scale towards an incorrect class. A sizable
+difference in estimated marginal prices for estimated vintages versus
+values for ground truth vintages in the subsequent hedonic regression
+(Eq. \ref{eq:hed}, below) would indicate such a bias.
+
+\hypertarget{building-era-and-property-price}{%
+\subsection{Building era and property
+price}\label{building-era-and-property-price}}
+
+Merging the estimated vintage classification with sales data (Land
+Registry 2017) we estimate a hedonic regression equation that
+establishes marginal prices for the building vintage (similar to
+Moorhouse and Smith 1994; Asabere, Hachey, and Grubaugh 1989; Vandell
+and Lane 1989; Fuerst, McAllister, and Murray 2011; Plaut and Uzulena
+2006), among other characteristics: \begin{equation} \label{eq:hed}
   ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i + \eta\mathbf{VintNeigh}_i + \iota\mathbf{Vintage\cdot VintNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
@@
 
-Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Vintage}$ and the prevailing vintage of other buildings in the direct proximity $(\mathbf{VintNeigh})$.
-The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\eta}$, $\bm{\iota}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients.
-$\epsilon$ is the IID error term.
-Heteroscedastic robust standard errors will be reported.
-
-Are buildings from different eras imperfect substitutes catering to multiple groups of households with distinct vintage preferences?
-@Buitelaar2017 indicate that any premium for an architectural style must stem from either differences in construction prices (which they do not find in their Dutch sample) or from supply constraints, as new construction potentially does not capture the demand for traditional styles.
-For Cambridge, new supply will inevitably be of either contemporary or revival style as historic vintage buildings, by definition, are not supplied any more.
-Estimating Eq.
-\ref{eq:hed} for a subset of newly constructed buildings will show whether construction prices or supply constraints for new homes built according to different architectural styles persist -- if too few vernacular buildings were built, prices should reflect such a shortage.
-
-# Data
-
-Residential real estate transactions are public data in the UK, collected and published by the Land Registry [@LandRegistry2016a].
-The records include the date of transaction, price paid, street address, a classification of the property type (flat, detached, semi-detached, or terraced house), the estate type (freehold or leasehold) and an indicator for newly built properties.
-We select transactions from Cambridge proper which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000.
-Linking recently taken images to sales data from 24 years assumes that houses have not changed their architectural styles -- which seems reasonable.
-We are not aware of any conversions of just the exterior of buildings.
-Full redevelopments, did occur and we exclude sales for a given address pre-dating any redevelopment.
-Table \ref{tab:sumstats} presents summary statistics for the sample.
-
-The Ordnance Survey *AddressBase* [@OrdnanceSurvey2017] links street addresses to building outlines on Ordnance Survey maps [@OrdnanceSurvey2017a], which allows us to calculate the buildings floor plate (in $m^2$) and to estimate the building's volume from digital elevation models [@EnvironmentAgency2015], as suggested by @Lindenthal2017.
-We control for the location of each building by calculating the distance to the city center proxied by Great St.
-Mary's Church, and non-parametrically by using 69 indicator variables for each of the smallest census tracts (*Lower Super Output Areas*, LSOA) subdividing Cambridge [@ONS2017].
-LSOAs typically have 1,000--3,000 residents and 400--1,200 households of comparable economic and socio-demographic characteristics [@ONS2017b].
-
-Overall, we collect pictures of more than 48,000 distinct buildings from the Google Street View API.
-The subset of 25,000 pictures that has been classified by trained architects into the seven vintages will serve as \emph{ground truth} for our study.
-Two additional categories identify buildings hidden by *greenery* or uninformative pictures featuring *plain walls*.
-The classified images are available at the authors' websites.
-
-# Results
-
-Almost 16,000 of the 25,000 buildings for which we have the architects' ground truth could be matched to the 23,768 sales transactions that have been recorded for Cambridge between 1995 and 2018.
-Thus, we observe both the machine *estimated vintage* and architect defined *ground truth* classification for the majority of buildings in the data set.
+Here, the natural logarithm of sales prices is explained by a linear
+combination of hedonic attributes described in vector \(\mathbf{X}\),
+vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
+variables and the building's estimated \(\mathbf{Vintage}\) and the
+prevailing vintage of other buildings in the direct proximity
+\((\mathbf{VintNeigh})\). The intercept is denoted by \(\alpha\) while
+\(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\eta}\), \(\bm{\iota}\),
+\(\bm{\gamma}\) and \(\bm{\lambda}\) are vectors of regression
+coefficients. \(\epsilon\) is the IID error term. Heteroscedastic robust
+standard errors will be reported.
+
+Are buildings from different eras imperfect substitutes catering to
+multiple groups of households with distinct vintage preferences?
+Buitelaar and Schilder (2017) indicate that any premium for an
+architectural style must stem from either differences in construction
+prices (which they do not find in their Dutch sample) or from supply
+constraints, as new construction potentially does not capture the demand
+for traditional styles. For Cambridge, new supply will inevitably be of
+either contemporary or revival style as historic vintage buildings, by
+definition, are not supplied any more. Estimating Eq. \ref{eq:hed} for a
+subset of newly constructed buildings will show whether construction
+prices or supply constraints for new homes built according to different
+architectural styles persist -- if too few vernacular buildings were
+built, prices should reflect such a shortage.
+
+\hypertarget{data}{%
+\section{Data}\label{data}}
+
+Residential real estate transactions are public data in the UK,
+collected and published by the Land Registry (Land Registry 2017). The
+records include the date of transaction, price paid, street address, a
+classification of the property type (flat, detached, semi-detached, or
+terraced house), the estate type (freehold or leasehold) and an
+indicator for newly built properties. We select transactions from
+Cambridge proper which were recorded between January 1995 and October
+2018, excluding any leaseholds, flats and properties classified as type
+``other'', and sales with prices below £50,000 or in excess of
+£2,000,000. Linking recently taken images to sales data from 24 years
+assumes that houses have not changed their architectural styles -- which
+seems reasonable. We are not aware of any conversions of just the
+exterior of buildings. Full redevelopments, did occur and we exclude
+sales for a given address pre-dating any redevelopment. Table
+\ref{tab:sumstats} presents summary statistics for the sample.
+
+The Ordnance Survey \emph{AddressBase} (Ordnance Survey 2017a) links
+street addresses to building outlines on Ordnance Survey maps (Ordnance
+Survey 2017b), which allows us to calculate the buildings floor plate
+(in \(m^2\)) and to estimate the building's volume from digital
+elevation models (Environment Agency 2015), as suggested by Lindenthal
+(2017b). We control for the location of each building by calculating the
+distance to the city center proxied by Great St.~Mary's Church, and
+non-parametrically by using 69 indicator variables for each of the
+smallest census tracts (\emph{Lower Super Output Areas}, LSOA)
+subdividing Cambridge (Office for National Statistics 2019). LSOAs
+typically have 1,000--3,000 residents and 400--1,200 households of
+comparable economic and socio-demographic characteristics (Office for
+National Statistics 2017).
+
+Overall, we collect pictures of more than 48,000 distinct buildings from
+the Google Street View API. The subset of 25,000 pictures that has been
+classified by trained architects into the seven vintages will serve as
+\emph{ground truth} for our study. Two additional categories identify
+buildings hidden by \emph{greenery} or uninformative pictures featuring
+\emph{plain walls}. The classified images are available at the authors'
+websites.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+Almost 16,000 of the 25,000 buildings for which we have the architects'
+ground truth could be matched to the 23,768 sales transactions that have
+been recorded for Cambridge between 1995 and 2018. Thus, we observe both
+the machine \emph{estimated vintage} and architect defined \emph{ground
+truth} classification for the majority of buildings in the data set.
 
@@
 
-The agreement between vintage estimates and the corresponding ground truth classifications by experts is reassuringly strong.
-When relying on feature vectors of the buildings and their closest neighbors, 67 to 84 percent of true classifications are matched with correctly estimated labels (Table \ref{tab:confmat}, Panel A).
-The recall rates are especially high for older vintages: For *Georgians*, it is 79 percent, *Early Victorian* 81 percent, *Late Victorian/Edwardian* 78 percent, *Interwar* 84 percent, respectively.
-For more recent *Postwar* buildings, the rate drops to 71 percent, for *Contemporary* to 72 percent and for *Revival* to 67 percent.
+The agreement between vintage estimates and the corresponding ground
+truth classifications by experts is reassuringly strong. When relying on
+feature vectors of the buildings and their closest neighbors, 67 to 84
+percent of true classifications are matched with correctly estimated
+labels (Table \ref{tab:confmat}, Panel A). The recall rates are
+especially high for older vintages: For \emph{Georgians}, it is 79
+percent, \emph{Early Victorian} 81 percent, \emph{Late
+Victorian/Edwardian} 78 percent, \emph{Interwar} 84 percent,
+respectively. For more recent \emph{Postwar} buildings, the rate drops
+to 71 percent, for \emph{Contemporary} to 72 percent and for
+\emph{Revival} to 67 percent.
 
 A visual inspection of classifications is additionally reassuring.
-Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each vintage.
-The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.
-
-The Herfindahl scores for classifications vary substantially across ground truth vintages (Table \ref{tab:herftab}), indicating that the models within the ensemble, for instance, agree more often on a building being *Georgian* than finding consensus for other vintages.
-For *Contemporary* or *Revival* vintages, individual classifications differ most.
-All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the ensemble is not really sure when misclassifying images.
-
-A closer inspection of the misclassified images sheds some light on the limits of automatically collected street level imagery.
-What do misclassified images have in common?
-Off-the-shelf object detection algorithms can identify broadly defined objects such as trees, vehicles, houses, doors, or windows without any additional training.
-Using an Inception/Resnet object detection model trained on Open Images\footnote{In this case, "faster rcnn inception resnet v2 atrous oidv2", available from \url{https://github.com/tensorflow/models/blob/master/research/object_detection/g3doc/detection_model_zoo.md}}, we calculate the share of the image area taken up by cars or trees as a measure of view obstruction.
-The more image area is showing buildings and, importantly, windows the more meaningful input an automatic classifier can draw from, resulting in better classifications.
-In addition, images not taken at an optimal angle or zoom factor are detected by calculating the distance between the bounding box for the largest building detected on the image and the center of the image: For well-centered images, this offset will be small.
-
-Table \ref{tab:imgqualsumstats} presents the mean values for the image quality variables.
-Table \ref{tab:diffimgchar}, Panel A, compares the mean values for views obstructed by trees or vehicles for correctly (on diagonal) and incorrectly classified images.
-In most cases, the off-diagonal values are positive, showing that more obstacles in the view of sight correlate with higher odds of misclassifications.
-Similarly, if more of the image area shows a house (Panel B), misclassifications are reduced (negative differences).
-This effect is stronger for windows, which appear to give valuable cues about a house's vintage (Panel C).
-Finally, houses that are not in the center of the building tend to be misclassified more frequently (positive differences in Panel D).
-In sum, bad quality images lead to misclassifications.
+Figure \ref{fig:vint_examples} displays the pictures which carry the
+highest out-of-sample scores for each vintage. The model is clearly able
+to differentiate based on small cues, even when only parts of the facade
+are captured on the picture.
+
+The Herfindahl scores for classifications vary substantially across
+ground truth vintages (Table \ref{tab:herftab}), indicating that the
+models within the ensemble, for instance, agree more often on a building
+being \emph{Georgian} than finding consensus for other vintages. For
+\emph{Contemporary} or \emph{Revival} vintages, individual
+classifications differ most. All off-diagonal elements in the lower
+panel of Table \ref{tab:herftab} are negative, suggesting that, in
+general, the ensemble is not really sure when misclassifying images.
+
+A closer inspection of the misclassified images sheds some light on the
+limits of automatically collected street level imagery. What do
+misclassified images have in common? Off-the-shelf object detection
+algorithms can identify broadly defined objects such as trees, vehicles,
+houses, doors, or windows without any additional training. Using an
+Inception/Resnet object detection model trained on Open
+Images\footnote{In this case, "faster rcnn inception resnet v2 atrous oidv2", available from \url{https://github.com/tensorflow/models/blob/master/research/object_detection/g3doc/detection_model_zoo.md}},
+we calculate the share of the image area taken up by cars or trees as a
+measure of view obstruction. The more image area is showing buildings
+and, importantly, windows the more meaningful input an automatic
+classifier can draw from, resulting in better classifications. In
+addition, images not taken at an optimal angle or zoom factor are
+detected by calculating the distance between the bounding box for the
+largest building detected on the image and the center of the image: For
+well-centered images, this offset will be small.
+
+Table \ref{tab:imgqualsumstats} presents the mean values for the image
+quality variables. Table \ref{tab:diffimgchar}, Panel A, compares the
+mean values for views obstructed by trees or vehicles for correctly (on
+diagonal) and incorrectly classified images. In most cases, the
+off-diagonal values are positive, showing that more obstacles in the
+view of sight correlate with higher odds of misclassifications.
+Similarly, if more of the image area shows a house (Panel B),
+misclassifications are reduced (negative differences). This effect is
+stronger for windows, which appear to give valuable cues about a house's
+vintage (Panel C). Finally, houses that are not in the center of the
+building tend to be misclassified more frequently (positive differences
+in Panel D). In sum, bad quality images lead to misclassifications.
 
@@
 
-The number of misclassifications decreases decidedly when considering observations with high ensemble confidence only: The majority vote based on the most confident two-thirds of predictions only are more in line with ground truth, as higher recall, precision and $F_1$-scores in Table \ref{tab:confmat}, Panel B, show.
-The improvement is most evident in the precision rates.
-For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different ground truth class -- the precision shoots up to 0.70 for *Georgian* and 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.
-
-The majority of misclassification is concentrated in temporally adjacent eras: 10 percent of *Late Victorian/Edwardian* buildings are labelled as *Early Victorian* or 18 percent of *Postwar* buildings are erroneously regarded as stemming from the *Interwar* period.
-Hardly ever is a contemporary building mistaken for a historic home.
+The number of misclassifications decreases decidedly when considering
+observations with high ensemble confidence only: The majority vote based
+on the most confident two-thirds of predictions only are more in line
+with ground truth, as higher recall, precision and \(F_1\)-scores in
+Table \ref{tab:confmat}, Panel B, show. The improvement is most evident
+in the precision rates. For the relatively rare categories of
+\emph{Georgian} and \emph{Revival} about the same number of buildings
+classified as \emph{Georgian/Revival} in Panel A actually belong to a
+different ground truth class -- the precision shoots up to 0.70 for
+\emph{Georgian} and 0.82 for \emph{Revival} when excluding the not so
+confident lower third of predictions in Panel B.
+
+The majority of misclassification is concentrated in temporally adjacent
+eras: 10 percent of \emph{Late Victorian/Edwardian} buildings are
+labelled as \emph{Early Victorian} or 18 percent of \emph{Postwar}
+buildings are erroneously regarded as stemming from the \emph{Interwar}
+period. Hardly ever is a contemporary building mistaken for a historic
+home.
 
@@
 
-Overall, the spatial softmax classification incorporating the nearest neighbor's feature vector outperforms the base classifier: pairwise differences of the $F_1$-scores from the spatial and the base classifier are clearly positive (Fig.
-\ref{fig:boxplot}).
-AIC values for 28 binomial models based on Eq.
-\ref{eq:rev} decrease as hedonic characteristics, location and time dummies are augmented by the base and spatial ML predictor.
-For all building vintages, the AIC are lowest for the spatial ML predictor.
-In sum, the spatial classifier performs better for UK vintage data than a classifier based on single buildings only.
+Overall, the spatial softmax classification incorporating the nearest
+neighbor's feature vector outperforms the base classifier: pairwise
+differences of the \(F_1\)-scores from the spatial and the base
+classifier are clearly positive (Fig. \ref{fig:boxplot}). AIC values for
+28 binomial models based on Eq. \ref{eq:rev} decrease as hedonic
+characteristics, location and time dummies are augmented by the base and
+spatial ML predictor. For all building vintages, the AIC are lowest for
+the spatial ML predictor. In sum, the spatial classifier performs better
+for UK vintage data than a classifier based on single buildings only.
 
@@
 
-## Hedonic regression estimates
-
-Successively, the estimated coefficients from 8 different versions of the hedonic regression specified in Eq.
-(\ref{eq:hed}) are reported in Tables \ref{tab:hedreg} and \ref{tab:hedregint}.
-For all models, the hedonic control variables show the expected signs: Negative coefficients for the relative distance to the city center, discounts for terraced homes and semi-detached homes relative to detached houses, positive elasticities for building floor plate and building volumes and a price premium for new buildings compared to second-hand homes, when applicable.
-Year and neighborhood dummies control for time effects and local amenities but their coefficients are not reported due to space constraints.
-The combination of location dummies and the distance to the city center measure controls for proximity to the city center \emph{within} each neighborhood.
+\hypertarget{hedonic-regression-estimates}{%
+\subsection{Hedonic regression
+estimates}\label{hedonic-regression-estimates}}
+
+Successively, the estimated coefficients from 8 different versions of
+the hedonic regression specified in Eq. (\ref{eq:hed}) are reported in
+Tables \ref{tab:hedreg} and \ref{tab:hedregint}. For all models, the
+hedonic control variables show the expected signs: Negative coefficients
+for the relative distance to the city center, discounts for terraced
+homes and semi-detached homes relative to detached houses, positive
+elasticities for building floor plate and building volumes and a price
+premium for new buildings compared to second-hand homes, when
+applicable. Year and neighborhood dummies control for time effects and
+local amenities but their coefficients are not reported due to space
+constraints. The combination of location dummies and the distance to the
+city center measure controls for proximity to the city center
+\emph{within} each neighborhood.
 
@@
 
-The first column in Table \ref{tab:hedreg} presents the estimated regression coefficients for ground truth vintages.
-The base vintage *Contemporary* is more expensive than almost all other vintages, which show negative coefficients that are significantly different from 0.
-A clear pecking order appears: *Georgian* and *Revival* buildings are the dearest $(+0.04)$,  followed by *Late Victorian/Edwardian* $(+0.01)$, *Contemporary* (base), *Early Victorian* $(-0.13)$,  *Interwar* $(-0.15)$ and *Postwar* $(-0.22)$.
-
-The sample of ground truth images is not necessarily representative of the overall population so we re-estimate the model using predicted vintages for *all* buildings for which we were able to extract usable pictures from Google Street View.
-Overall, the vintage coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify unattractive buildings to the *Contemporary* vintage.
-Reversely, more attractive buildings are disproportionally often misclassified as *Late Vic./Edw.*, pushing up the corresponding coefficient to $0.11$.
-This bias vanishes in the third model, which uses only confidently predicted vintages (Column 3).
-
-Models 4--6 follow the same logic as 1--3 but are estimated for *new* buildings only.
-Basically this contrasts houses which might *look* different from the street, having either contemporary or revival facades, but which are all modern homes at their core.
-Differences in e.g.
-materials, floor plans, green space and gardens are minimal.
-For newly built homes, no effect of *Revival* architecture on price can be found, neither for ground truth classifications nor for high confidence ML estimates.
-After controlling for location, building characteristics and quality, buyers show no willingness to pay a premium for *Revival* architecture.
-
-Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{VintNeigh}$) does not change the pecking order of building vintages much (Table \ref{tab:hedreg}, Column 7).
-Neighboring styles are compared to the base case of a *Contemporary* house in a *Contemporary* street.
-The negative coefficients on dissimilar neighboring styles support a finding by @Lindenthal2017 that shows that a harmonious match of a building's shape with its direct environment leads to a price premium -- or a discount in case of shape mismatches.
-In relative terms, *Postwar* buildings are the least popular neighbors.
-The difference between *Revival* and *Contemporary* neighbors is not statistically significant.
-We fail to find evidence in favor of positive externalities from revival architecture.
-Everything else equal, buildings within ensembles of *Contemporary* buildings generally do not achieve higher transaction prices than buildings in more historic areas (as Table \ref{tab:comb} will confirm later).
-
-Table \ref{tab:hedregint} presents the $\iota$ interaction coefficients (Eq.
-\ref{eq:hed}) for vintage-neighboring vintage combinations with sufficient numbers of observations (see Table \ref{tab:vintneigh}).
-The last row suggests that a general claim that *Revival* neighbors exert positive externalities and increase property values relative to *Contemporary* surroundings cannot be confirmed empirically.
-Again, we find no statistically significant difference.
+The first column in Table \ref{tab:hedreg} presents the estimated
+regression coefficients for ground truth vintages. The base vintage
+\emph{Contemporary} is more expensive than almost all other vintages,
+which show negative coefficients that are significantly different from
+0. A clear pecking order appears: \emph{Georgian} and \emph{Revival}
+buildings are the dearest \((+0.04)\), followed by \emph{Late
+Victorian/Edwardian} \((+0.01)\), \emph{Contemporary} (base),
+\emph{Early Victorian} \((-0.13)\), \emph{Interwar} \((-0.15)\) and
+\emph{Postwar} \((-0.22)\).
+
+The sample of ground truth images is not necessarily representative of
+the overall population so we re-estimate the model using predicted
+vintages for \emph{all} buildings for which we were able to extract
+usable pictures from Google Street View. Overall, the vintage
+coefficients become more positive relative to the base, implying that
+our automatic classification is biased and tends to classify
+unattractive buildings to the \emph{Contemporary} vintage. Reversely,
+more attractive buildings are disproportionally often misclassified as
+\emph{Late Vic./Edw.}, pushing up the corresponding coefficient to
+\(0.11\). This bias vanishes in the third model, which uses only
+confidently predicted vintages (Column 3).
+
+Models 4--6 follow the same logic as 1--3 but are estimated for
+\emph{new} buildings only. Basically this contrasts houses which might
+\emph{look} different from the street, having either contemporary or
+revival facades, but which are all modern homes at their core.
+Differences in e.g.~materials, floor plans, green space and gardens are
+minimal. For newly built homes, no effect of \emph{Revival} architecture
+on price can be found, neither for ground truth classifications nor for
+high confidence ML estimates. After controlling for location, building
+characteristics and quality, buyers show no willingness to pay a premium
+for \emph{Revival} architecture.
+
+Introducing a variable capturing the most prominent style of buildings
+on the same street and within 100 m (\(\mathbf{VintNeigh}\)) does not
+change the pecking order of building vintages much (Table
+\ref{tab:hedreg}, Column 7). Neighboring styles are compared to the base
+case of a \emph{Contemporary} house in a \emph{Contemporary} street. The
+negative coefficients on dissimilar neighboring styles support a finding
+by Lindenthal (2017b) that shows that a harmonious match of a building's
+shape with its direct environment leads to a price premium -- or a
+discount in case of shape mismatches. In relative terms, \emph{Postwar}
+buildings are the least popular neighbors. The difference between
+\emph{Revival} and \emph{Contemporary} neighbors is not statistically
+significant. We fail to find evidence in favor of positive externalities
+from revival architecture. Everything else equal, buildings within
+ensembles of \emph{Contemporary} buildings generally do not achieve
+higher transaction prices than buildings in more historic areas (as
+Table \ref{tab:comb} will confirm later).
+
+Table \ref{tab:hedregint} presents the \(\iota\) interaction
+coefficients (Eq. \ref{eq:hed}) for vintage-neighboring vintage
+combinations with sufficient numbers of observations (see Table
+\ref{tab:vintneigh}). The last row suggests that a general claim that
+\emph{Revival} neighbors exert positive externalities and increase
+property values relative to \emph{Contemporary} surroundings cannot be
+confirmed empirically. Again, we find no statistically significant
+difference.
 
@@
 
-In Table \ref{tab:comb}, the combined effect of building styles on property values is calculated by adding up the direct, neighborhood and interaction effects (Tables \ref{tab:hedreg} and \ref{tab:hedregint}).
-When filling in lots in historical neighborhoods, however, a premium for *Revival* facades over modern designs can be observed (differences in last two columns of Table \ref{tab:comb}).
-For large scale new construction, however, *Revival* buildings surrounded by other historicizing buildings do not sell for more than *Contemporary* buildings in a more modern setting.
-
-# Conclusion
-
-The contributions of this paper are threefold: First, it introduced an algorithm that collects pictures of *individual* buildings from Google Street View.
-Earlier work has not achieved this level of detail and was, at least in the UK, limited to street sections only.
-A large-scale application of automatic classification of individual buildings' characteristics using Google Street View has potential not only in the UK.
-The image collection and classification method can easily be ported to other study areas which have existing Street View data and either LIDAR based building outlines or high resolution satellite images.
-In a follow-up project, we are working on an improved classification workflow in which a customized object detection model is able to recognize specific building outlines without the need for additional maps or other data.
-
-Second, we developed a new database of 25,000 building pictures that have been classified by architecture experts into relevant architectural styles or vintages.
-We subsequently trained a neural network classifier to automatically classify all residential buildings of a mid-sized English city into architectural styles or vintages.
-The suggested classifier is trained on feature vectors of buildings and their nearest neighbors to exploit spatial correlation in observed classifications.
-
-The large ground truth data set allows for a comparison of human expert classifications with predictions made by ML classifiers.
-Poor image quality, for instance obstructed views or the lack of informative features such as windows, is correlated with misclassifications.
-Importantly, for cases in which the ML classifiers are relatively indecisive between classes, visual cues that are correlated with vintage but not part of a building's architecture (for instance trees or cars) bias the estimates.
-Fore these less certain cases, more valuable homes are systematically more likely to be classified as e.g.
-*Late Victorian/Edw.* and less likely to be considered *Contemporary*.
-A follow up study could investigate which elements in the building pictures lead to the misclassifications [@Ribeiro2016].
-Given the danger of systematic biases, one should remain wary of ML estimates derived from ground truth data sizable enough to train models -- but too small to investigate any biases.
-
-Third, we test whether revival or vernacular architecture leads to price premia over contemporary architecture.
-We do not find evidence for a preference of residents for specific architecture after controlling for quality and location of buildings.
-This applies to both direct price effects but also indirect effects of a buildings appearance on the value of neighboring homes.
-Further work will extend the spatial scope of the study area to the UK in general and to other countries.
+In Table \ref{tab:comb}, the combined effect of building styles on
+property values is calculated by adding up the direct, neighborhood and
+interaction effects (Tables \ref{tab:hedreg} and \ref{tab:hedregint}).
+When filling in lots in historical neighborhoods, however, a premium for
+\emph{Revival} facades over modern designs can be observed (differences
+in last two columns of Table \ref{tab:comb}). For large scale new
+construction, however, \emph{Revival} buildings surrounded by other
+historicizing buildings do not sell for more than \emph{Contemporary}
+buildings in a more modern setting.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+The contributions of this paper are threefold: First, it introduced an
+algorithm that collects pictures of \emph{individual} buildings from
+Google Street View. Earlier work has not achieved this level of detail
+and was, at least in the UK, limited to street sections only. A
+large-scale application of automatic classification of individual
+buildings' characteristics using Google Street View has potential not
+only in the UK. The image collection and classification method can
+easily be ported to other study areas which have existing Street View
+data and either LIDAR based building outlines or high resolution
+satellite images. In a follow-up project, we are working on an improved
+classification workflow in which a customized object detection model is
+able to recognize specific building outlines without the need for
+additional maps or other data.
+
+Second, we developed a new database of 25,000 building pictures that
+have been classified by architecture experts into relevant architectural
+styles or vintages. We subsequently trained a neural network classifier
+to automatically classify all residential buildings of a mid-sized
+English city into architectural styles or vintages. The suggested
+classifier is trained on feature vectors of buildings and their nearest
+neighbors to exploit spatial correlation in observed classifications.
+
+The large ground truth data set allows for a comparison of human expert
+classifications with predictions made by ML classifiers. Poor image
+quality, for instance obstructed views or the lack of informative
+features such as windows, is correlated with misclassifications.
+Importantly, for cases in which the ML classifiers are relatively
+indecisive between classes, visual cues that are correlated with vintage
+but not part of a building's architecture (for instance trees or cars)
+bias the estimates. Fore these less certain cases, more valuable homes
+are systematically more likely to be classified as e.g. \emph{Late
+Victorian/Edw.} and less likely to be considered \emph{Contemporary}. A
+follow up study could investigate which elements in the building
+pictures lead to the misclassifications (Ribeiro, Singh, and Guestrin
+2016). Given the danger of systematic biases, one should remain wary of
+ML estimates derived from ground truth data sizable enough to train
+models -- but too small to investigate any biases.
+
+Third, we test whether revival or vernacular architecture leads to price
+premia over contemporary architecture. We do not find evidence for a
+preference of residents for specific architecture after controlling for
+quality and location of buildings. This applies to both direct price
+effects but also indirect effects of a buildings appearance on the value
+of neighboring homes. Further work will extend the spatial scope of the
+study area to the UK in general and to other countries.
 
@@
 
-# Tables and Figures
+\hypertarget{tables-and-figures}{%
+\section{Tables and Figures}\label{tables-and-figures}}
 
@@
 \caption{Examples of Estimated Building Vintages}
-```{r plot_top_pictures, cache=TRUE, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Examples of Buildings, classified into Vintages"}
-source("../R/plot_top_pictures.R")
-plot_top_pictures(img.width = "45px")
-```
+\begin{tabular}{lllllll}
+  \hline
+\emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interwar} & \emph{Postwar} & \emph{Contemp.} & \emph{Revival} \\ 
+  \hline
+\includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058205_KqBBtZS8ecncUe8oqjErqQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102767_u_7T3iAyG9xNgeN_ETY7aQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141478_FT9houQ2x66NPnNEGxTkvA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065714_pzExlR026vDKdQaJiLkdkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010137600_qYxYCsLRPpOfCyv8IjfnlA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677225_srJnz_31ujVFzn-xh_DYfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413689_VylY6Sy3vLvjqbtHeryMdQ.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010056385_XQsTJ2p5Te54CScFmblMHA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102769_c_e4WlmafqN2JXQ2ZhYEkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017237_yWs7fxQ0r8Ecx_ajaYc-rg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141115_xG0eSas79cN59fH4xvm5Yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023665_B2Is2WMV8SGjf7Tg9tLS7w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748070_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176986_bNOie2HS7GPQxPOtoevEHw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058145_xBAz4f8lI2MTivvvWv6wyQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103488_Y1L2niOkEGB1IKe4tsl1yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021367_JF-P4lOQQouZ6lHtM4J3oA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065349_HDvoqsiHXGx4xc62JSUNJA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009993819_748OTBKSFyJZU2DP7TbboQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677000_8l6ywNIej2136uZeb3qKqA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500088807_4vu-eMLHmhX3JmHNwyulmQ.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059206__nUymOPxCgpQugahoE7EPw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103870_ywN_BuvuLW6kbLLP0QgJMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017412_aOsldmaOT-MAce6q6qkmTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010107971_veilqmDOA-AfCuz4tWyg7g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025542_8rvXwCYBTCQu0eVM9nhN9Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555322_FffLx_XVBUOvZgiXRdSAnA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066754_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060140_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103819_mF6OqQrRTOlAoGdaraQsTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010097999_xTD3YceIrtPJZwPz5d0G6Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065347_pouLRqJd7pkk41jryvYQ4A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992776_QxMV8eRavS1riXfGzpSkBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555341_NVXmLF7mim1nGBZAdgw_ew.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500569086_g5RwBQ7D5edS2obfSogNIw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060139_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101711_wNQ403N-0pQd5fChNztfYA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021374_55tKverBLF4C0oo8U4XABg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065352_kDKqKaGpPwLeCBKJIQmeCg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010015484_zlR1vVJ7F0L6hcsFoZEydw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500548748_i6QAKtN2HhGsTVDBan2DKw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057955271_dMXMWNaIwddWdHidEuXowA.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060141_W3ZIE8mPY6LJb-_hKatlUw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103226_XO6qx_5Q9tNnNF958OBO3g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017109_MbGvl1GxhZjQ_qhD7puDBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009995496_N4NgCofyWASyYfcSPTjdBA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010068890_aswyTpwrE_IfdbINnYx7XQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010104229_qFV1-weLxn8SRW4Ib2wexQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010199676_smIagQ34MLIcJOrjvIu9uw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059966_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101704_ZQFxujswdAj7EGqRlp8sXQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017361_WxMCM3nht5EX_K9pqIK-kQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066620_4TqmJVLf3urSJo4ESg1zfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023689_KpXUKEdjoQ9swgoB2oXA3w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748058_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066718_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060813_VlKeIvrTv6UwOE9HD2LgJg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103859_P5YwPMree6QCxExkKqIzbw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141515_5g5Bhsn_4iW-90aFMrIaSA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066361_gliMrVbagcfkfZjLw4mKlw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500527045_p4zTtg8OzsbWjHYscCf-rA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748076_zDr74LLmVeyKyx7dPnXK6A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413682_drSMg0SQ9TU4Og8pXOgSxw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059967_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103388_CZH157SXYmF3dEVMKlWBfQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025644_bJ8zv37pDsP0CImvDMKC0w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010144910_COpJNwPw67J78VXCoN_HMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992797_JUTa4GsWaXplyCP6XeVAvw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500086356_n92s3snPX2zAwEiJnA-Pxg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176201_dDyXoyEbeMXUhCagwazbiA.jpg} \\
+   \hline
+\end{tabular}
 \label{fig:vint_examples}
@@
 
-# Bibliography
+\hypertarget{bibliography}{%
+\section*{Bibliography}\label{bibliography}}
+\addcontentsline{toc}{section}{Bibliography}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Ahlfeldt2012}{}%
+Ahlfeldt, Gabriel, and Alexandra Mastro. 2012. ``Valuing Iconic Design:
+Frank Lloyd Wright Architecture in Oak Park, Illinois.'' \emph{Housing
+Studies} 27 (8): 1079--99.
+\url{https://doi.org/10.1080/02673037.2012.728575}.
+
+\leavevmode\hypertarget{ref-Asabere1989}{}%
+Asabere, Paul K., George Hachey, and Steven Grubaugh. 1989.
+``Architecture , Historic Zoning , and the Value of Homes.''
+\emph{Journal of Real Estate Finance and Economics} 2 (3): 181--95.
+\url{https://doi.org/10.1007/BF00152347}.
+
+\leavevmode\hypertarget{ref-Buitelaar2017}{}%
+Buitelaar, Edwin, and Frans Schilder. 2017. ``The Economics of Style:
+Measuring the Price Effect of Neo-Traditional Architecture in Housing.''
+\emph{Real Estate Economics} 45 (1): 7--27.
+\url{https://doi.org/10.1111/1540-6229.12137}.
+
+\leavevmode\hypertarget{ref-Coulson2008}{}%
+Coulson, N. Edward, and Daniel P. McMillen. 2008. ``Estimating time, age
+and vintage effects in housing prices.'' \emph{Journal of Housing
+Economics} 17 (2): 138--51.
+\url{https://doi.org/10.1016/j.jhe.2008.03.002}.
+
+\leavevmode\hypertarget{ref-Nadai2016}{}%
+De Nadai, Marco, Radu L. Vieriu, Gloria Zen, Stefan Dragicevic, Nikhil
+Naik, Michele Caraviello, Cesar A. Hidalgo, Nicu Sebe, and Bruno Lepri.
+2016. ``Are Safer Looking Neighborhoods More Lively? A Multimodal
+Investigation into Urban Life,'' August.
+\url{http://arxiv.org/abs/1608.00462}.
+
+\leavevmode\hypertarget{ref-EnvironmentAgency2015}{}%
+Environment Agency. 2015. ``LIDAR Composite DSM - 1m.''
+\url{https://data.gov.uk/dataset/lidar-composite-dsm-1m1}.
+
+\leavevmode\hypertarget{ref-Francke2017a}{}%
+Francke, Marc K., and Alex M. van de Minne. 2017. ``Land, Structure and
+Depreciation.'' \emph{Real Estate Economics} 45 (2): 415--51.
+\url{https://doi.org/10.1111/1540-6229.12146}.
+
+\leavevmode\hypertarget{ref-Fuerst2011}{}%
+Fuerst, Franz, Patrick McAllister, and Claudia B Murray. 2011.
+``Designer buildings: estimating the economic value of `signature'
+architecture.'' \emph{Environment and Planning A} 43 (1): 166--84.
+\url{https://doi.org/10.1068/a43270}.
+
+\leavevmode\hypertarget{ref-Gebru2017}{}%
+Gebru, Timnit, Jonathan Krause, Yilun Wang, Duyun Chen, Jia Deng, Erez
+Lieberman Aiden, and Li Fei-Fei. 2017. ``Using Deep Learning and Google
+Street View to Estimate the Demographic Makeup of the US.'' \emph{PNAS}
+114 (50): 13108--13. \url{https://doi.org/10.1073/pnas.1700035114}.
+
+\leavevmode\hypertarget{ref-Ghimire2010a}{}%
+Ghimire, B., J. Rogan, and J. Miller. 2010. ``Contextual land-cover
+classification: Incorporating spatial dependence in land-cover
+classification models using random forests and the Getis statistic.''
+\emph{Remote Sensing Letters} 1 (1): 45--54.
+\url{https://doi.org/10.1080/01431160903252327}.
+
+\leavevmode\hypertarget{ref-GlaeserKincaidNaik2018}{}%
+Glaeser, Edward L., Michael Scott Kincaid, and Nikhil Naik. 2018.
+``Computer Vision and Real Estate: Do Looks Matter and Do Incentives
+Determine Looks?'' \url{http://www.nber.org/papers/w25174}.
+
+\leavevmode\hypertarget{ref-Glaeser2016}{}%
+Glaeser, Edward L., Scott Duke Kominers, Michael Luca, and Nikhil Naik.
+2018. ``Big Data and Big Cities: The Promises and Limitations of
+Improved Measures of Urban Life.'' \emph{Economic Inquiry} 56 (1):
+114--37. \url{https://doi.org/10.1111/ecin.12364}.
+
+\leavevmode\hypertarget{ref-He2016}{}%
+He, Kaiming, Xiangyu Zhang, Shaoqing Ren, and Jian Sun. 2016. ``Deep
+Residual Learning for Image Recognition.'' \emph{The IEEE Conference on
+Computer Vision and Pattern Recognition (CVPR)}, 770--78.
+
+\leavevmode\hypertarget{ref-Helbich2013}{}%
+Helbich, Marco, Andreas Jochem, Werner Mücke, and Bernhard Höfle. 2013.
+``Boosting the predictive accuracy of urban hedonic house price models
+through airborne laser scanning.'' \emph{Computers, Environment and
+Urban Systems} 39. Elsevier Ltd: 81--92.
+\url{https://doi.org/10.1016/j.compenvurbsys.2013.01.001}.
+
+\leavevmode\hypertarget{ref-princecharles2014}{}%
+HRH The Prince of Wales. 2014. ``Facing up to the future: Prince Charles
+on 21st century architecture.'' \emph{Architectural Review}, December.
+\url{https://www.architectural-review.com/essays/viewpoints/facing-up-to-the-future-prince-charles-on-21st-century-architecture/8674119.article}.
+
+\leavevmode\hypertarget{ref-LandRegistry2016a}{}%
+Land Registry. 2017. ``Price Paid Data.''
+\url{http://landregistry.data.gov.uk/app/ppd}.
+
+\leavevmode\hypertarget{ref-Lindenthal2017b}{}%
+Lindenthal, Thies. 2017a. ``Beauty in the Eye of the Home-Owner:
+Aesthetic Zoning and Residential Property Values.'' \emph{Real Estate
+Economics}, 1--26. \url{https://doi.org/10.1111/1540-6229.12204}.
+
+\leavevmode\hypertarget{ref-Lindenthal2017}{}%
+---------. 2017b. \emph{Estimating Supply Elasticities for Residential
+Real Estate in the United Kingdom}. Comprehens. Elsevier Inc.
+\url{https://doi.org/https://doi.org/10.1016/B978-0-12-409548-9.09682-2}.
+
+\leavevmode\hypertarget{ref-Liu2017}{}%
+Liu, Lun, Elisabete A. Silva, Chunyang Wu, and Hui Wang. 2017. ``A
+machine learning-based method for the large-scale evaluation of the
+qualities of the urban environment.'' \emph{Computers, Environment and
+Urban Systems} 65. The Authors: 113--25.
+\url{https://doi.org/10.1016/j.compenvurbsys.2017.06.003}.
+
+\leavevmode\hypertarget{ref-Moorhouse1994}{}%
+Moorhouse, John C., and Margaret Supplee Smith. 1994. ``The Market for
+Residential Architecture: 19th century Row Houses in Boston's South
+End.'' \emph{Journal of Urban Economics} 35 (3): 267--77.
+\url{https://doi.org/10.1006/juec.1994.1016}.
+
+\leavevmode\hypertarget{ref-Naik2017}{}%
+Naik, Nikhil, Scott Duke Kominers, Ramesh Raskar, Edward L. Glaeser, and
+César A. Hidalgo. 2017. ``Computer vision uncovers predictors of
+physical urban change.'' \emph{Proceedings of the National Academy of
+Sciences} 114 (29): 7571--6.
+\url{https://doi.org/10.1073/pnas.1619003114}.
+
+\leavevmode\hypertarget{ref-Naik2016AER}{}%
+Naik, Nikhil, Ramesh Raskar, and César A. Hidalgo. 2016. ``Cities Are
+Physical Too: Using Computer Vision to Measure the Quality and Impact of
+Urban Appearance.'' \emph{American Economic Review} 106 (5): 128--32.
+\url{https://doi.org/10.1257/aer.p20161030}.
+
+\leavevmode\hypertarget{ref-ONS2017b}{}%
+Office for National Statistics. 2017. ``A Beginner's Guide to UK
+Geography.''
+
+\leavevmode\hypertarget{ref-ONS2017}{}%
+---------. 2019. ``Open Geography Portal -- 2011 Census Boundaries.''
+\url{https://www.ons.gov.uk/methodology/geography/ukgeographies/censusgeography}.
+
+\leavevmode\hypertarget{ref-OrdnanceSurvey2017}{}%
+Ordnance Survey. 2017a. ``AddressBase.''
+\url{https://www.ordnancesurvey.co.uk/business-and-government/help-and-support/products/addressbase-premium.html}.
+
+\leavevmode\hypertarget{ref-OrdnanceSurvey2017a}{}%
+---------. 2017b. ``OS Maps Local.''
+\url{https://www.ordnancesurvey.co.uk/business-and-government/products/os-open-map-local.html}.
+
+\leavevmode\hypertarget{ref-Plaut2006}{}%
+Plaut, Steven, and Egita Uzulena. 2006. ``Architectural Design and the
+Value of Housing in Riga, Latvia.'' \emph{International Real Estate
+Review} 9 (1): 112--31.
+
+\leavevmode\hypertarget{ref-Ribeiro2016}{}%
+Ribeiro, Marco Tulio, Sameer Singh, and Carlos Guestrin. 2016. ``"Why
+Should I Trust You?" Explaining the Predictions of Any Classifier.'' In
+\emph{22nd Acm Sigkdd International Conference on Knowledge Discovery
+and Data Mining}, 1135-----1144. San Francisco.
+
+\leavevmode\hypertarget{ref-scruton2018}{}%
+Scruton, Roger. 2018. ``The Fabric of the City.'' Colin Amery Memorial
+Lecture. Policy Exchange.
+\url{https://policyexchange.org.uk/wp-content/uploads/2018/11/The-Fabric-of-the-City.pdf}.
+
+\leavevmode\hypertarget{ref-Szegedy2015}{}%
+Szegedy, Christian, Vincent Vanhoucke, Sergey Ioffe, Jonathon Shlens,
+and Zbigniew Wojna. 2015. ``Rethinking the Inception Architecture for
+Computer Vision.'' \url{https://doi.org/10.1109/CVPR.2016.308}.
+
+\leavevmode\hypertarget{ref-economistlineofbeauty2018}{}%
+The Economist. 2018. ``The line of beauty.'' \emph{The Economist},
+November. London.
+\url{https://www.economist.com/britain/2018/11/17/how-to-defeat-nimbyism-build-more-beautiful-houses}.
+
+\leavevmode\hypertarget{ref-Vandell1989}{}%
+Vandell, Kerry D., and Jonathan S. Lane. 1989. ``The Economics of
+Architecture and Urban Design: Some Preliminary Findings.'' \emph{AREUEA
+Journal} 17 (2): 235--60.
+
+\end{document}

### 2019-09-04 R/augment_sales_data.R

@@ -1,0 +1,128 @@
+# =========================================================
+#  Merge sales data with additional data
+#   - TOID, to link to OS maps
+#   - Volume and footprind area
+#   - Estimated style 
+#   - Groundtruth style
+#   - distance to city centre
+# =========================================================
+
+# Load additional libraries
+library(stargazer)
+library(spdep)
+library(raster)
+library(wesanderson)
+library(sp)
+library(rgeos)
+library(knitr)
+library(xtable)
+library(stringr)
+library(stringdist)
+library(data.table)
+
+source("./settings.R")
+
+sales <- read.csv("https://www.dropbox.com/s/mlybx4io84us0n6/sales_cambridge-2018-10.csv?dl=1", as.is=TRUE, header=FALSE)
+colnames(sales) <- c("id","price","date","postcode","propertytype","new","estatetype","paon","saon","street","locality","town","district","county","PPDcategory","recordstatus")
+sales$date <- strptime(sales$date,"%Y-%m-%d")
+# create time dummy variables, monthly and yearly 
+sales$month <- format(sales$date, format="%Y-%m" )
+sales$year <- as.factor(format(sales$date, format="%Y"))
+
+
+l.price <- list()
+l.price$upper <- 5000000
+l.price$lower <- 10000
+
+
+# Match addresses to TOID using AddressBase
+ab <- read.csv("~/Dropbox (Cambridge University)/Cambridge/data/addresses/OsAddressBase/ID28_DPA_Records.csv", as.is=TRUE)
+ab <- subset(ab, select=c("UPRN","POSTCODE","BUILDING_NUMBER","SUB_BUILDING_NAME","BUILDING_NAME","THOROUGHFARE"))
+ab$paon <- ab$BUILDING_NUMBER
+ab$paon[ is.na( ab$BUILDING_NUMBER) ] <- ab$BUILDING_NAME[ is.na( ab$BUILDING_NUMBER) ]
+ab$saon <- ab$SUB_BUILDING_NAME
+
+abxref <- read.csv("~/Dropbox (Cambridge University)/Cambridge/data/addresses/OsAddressBase/ID23_XREF_Records.csv", as.is=TRUE)
+abxref <- subset(abxref, grepl('osgb', CROSS_REFERENCE))
[…]

### 2019-09-04 R/f1_score_plot.R

@@ -1,0 +1,11 @@
+f1 <- rbind(c(0.61 , 0.75 , 0.82 , 0.82 , 0.77 , 0.64 , 0.59),c(0.73 , 0.87 , 0.90 , 0.90 , 0.86 , 0.81 , 0.77),c(0.54 , 0.72 , 0.78 , 0.78 , 0.70 , 0.58 , 0.51))
+colnames(f1) <- c("Georg.","Early Vic.","Late V./E.","Interw.","Postw.","Cont.","Revival")
+colours <- c("lightblue","darkblue","darkred")
+
+jpeg(filename = "../text/figures/barplot_f1scores.jpg", quality = 100, width=1000, height=500)
+par(mar=c(3,5,1,1))
+par(cex.lab=1.5)
+barplot(f1, ylim=c(0,1.1), beside = TRUE, col=colours, ylab="F1-Score", cex.names=1.5, cex.axis = 1.5)
+box()
+legend("top", bty="n", c("Spatial classifier","Spatial class., high conf. only","Base classifier"), horiz=TRUE, fill=colours, cex=1.5, pt.cex=1)
+dev.off()

### 2019-09-04 R/functions_mugshots.R

@@ -1,0 +1,394 @@
+#============ Some Helpers
+# Create a set of 360 points, evenly distributed around the origin
+# We can shift them later to the position of any panorama
+createEndpoints <- function( radius=50, numpoints=360){
+  endpoints <- list()
+  # first point, just go north
+  endpoints[[1]] <- c(0, radius)
+  for(a in 1:(numpoints-1)){
+    ang <- (2* pi) * (a / numpoints)
+    endpoints[[ a+1 ]] <- c( endpoints[[1]][1] *cos(ang) - endpoints[[1]][2] *sin(ang),  endpoints[[1]][2] *cos(ang) + endpoints[[1]][1] *sin(ang), ang )
+  }
+  # 
+  ep <- rbindlist(lapply(endpoints, function(x) data.table(lon=x[1], lat=x[2], rad=x[3])))
+  return(ep)
+}
+# find the first polygon that intersects with a direct line from pano
+firstHit <- function(line, pano, poly){
+  hits <- list()
+  for(p in 1:nrow(poly)){
+    if(gIntersects(line, poly[p,])){
+      chopped <- gIntersection(line, poly[p,])
+   #   plot(chopped, add=TRUE, col="green", lwd=3)
+      poly.id <- as.character( as.data.frame(poly[p,])$TOID )
+      hits[[ poly.id ]] <- c( poly.id, gDistance(pano, chopped))
+    }
+  }
+  if(length(hits) > 0){
+    h <- as.data.frame( do.call(rbind, hits), stringsAsFactors=FALSE)
+    colnames(h)<- c("id","dist")
+    h$dist <- as.numeric(h$dist)
+    rownames(h) <- NULL
+    h <- h[order(h$dist), ]
+    return(h[1, ])
+  } else {
+    return(c(NA, NA))
+  }
+}
+firstHitRecursive <- function( d, pano, poly ){
+  fh[[ d ]] <- firstHit(los[[d]], pano, poly)
+  if(!is.na( fh[[ d ]][1] )){
+    if(d>1){
+      fh[[ (d-1) ]] <- fhfirstHitRecursive( (d-1), pano, poly )
+    }
+    if(d<360){
+      fh[[ d+1 ]] <- firstHitRecursive( (d+1), pano, poly )
+    }
+   return(TRUE)
+  }
+  return(FALSE)
+}
+coords2points <- function(DT, l.p4string){
+  # Input file:
+  ## DT: data.table with lat, long
[…]

### 2019-09-04 R/helper.R

@@ -1,0 +1,24 @@
+colour <- c("#230356","#076391","#2fd1d1","#b51676","#e90d3a","#f98e19","#ffc217")
+custom.labels <- list(
+  "a.georgian" = "Georgian",
+  "b.victorian" = "Early Vic.",
+  "c.edwardian.late.victorian" = "Late V./Edw.",
+  "d.interwar" = "Interwar",
+  "e.postwar" = "Postwar",
+  "f.contemporary" = "Contemporary",
+  "g.cont.victorian" ="Revival",
+  "a georgian" = "Georgian",
+  "b victorian" = "Early Vic.",
+  "c edwardian late victorian" = "Late V./Edw.",
+  "d interwar" = "Interwar",
+  "e postwar" = "Postwar",
+  "f contemporary" = "Contemporary",
+  "g cont victorian" ="Revival"
+  
+)
+replace.labels <- function(x, y){
+  return( y[[x]])
+}
+replace.all.labels <- function(x,y){
+  return( unlist(sapply(x, replace.labels, y) ))
+}

### 2019-09-04 R/plot_top_pictures.R

@@ -1,0 +1,49 @@
+# Table with pictures of estimate vintages 
+
+plot_top_pictures <- function( regsam=NA, n=10, labels_short=NA, figpath = "/home/thies/db/Cambridge/data/images/cambridge/", img.width="50px"){
+  library(xtable)
+  options(xtable.sanitize.text.function=identity)
+  
+  # load data
+  if( is.na(regsam) ){
+    require(RCurl)
+    remote.file <-  "https://www.dropbox.com/s/he3hfquk8claaa1/regsamples.csv?dl=1"  
+    tmp.file <- tempfile()
+    download.file(remote.file, tmp.file)
+    regsam <- read.csv(tmp.file)
+    file.remove(tmp.file)
+  }
+  if( is.na(labels_short) ){
+    labels_short <- c("Georg.","Early Vic.","Late V./Edw.","Interwar","Postwar","Contemp.","Revival")
+  }
+  eras <- unique(regsam$era)
+  eras <- eras[grepl("^[a-z]", eras)]
+  
+  eras <- eras[ order(eras) ]
+  names(labels_short) <- eras
+  
+  files <- list.files( figpath )
+  files <- files[grepl(".jpg", files)]
+  
+  tab <- matrix("", n , length(eras))
+  colnames(tab) <- eras
+  
+  for(e in eras){
+    tmp <- unique( subset(regsam, era == e, select=c("TOID","max","era")))
+    tmp <- tmp[rev(order(tmp$max)),]
+    for(i in 1:n){
+      tab[i, e ] <- files[ grepl( as.character( tmp$TOID[i] ), files )]
+      tab[ i, e] <- paste("\\includegraphics[width=",img.width,"]{", figpath ,tab[i,e],"}", sep="")
+    }
+  }
+  colnames(tab) <- paste("\\emph{",labels_short,"}", sep="")
+  xtab <- xtable( tab, 
+                  booktabs=TRUE,
+                  comment=FALSE,
+                  row.names=FALSE)
+  print(xtab, 
+        comment=FALSE,
+        include.rownames=FALSE,
+        floating=FALSE)
+}
+#plot_top_pictures(regsam=regsample)

### 2019-09-04 R/regression_repeat_sales.R

@@ -1,0 +1,232 @@
+### Hedonic regression analysis
+
+library(xtable)
+library(stargazer)
+
+# load sales data
+v <- read.csv("~/research/paper-uk-vintages/data/derived/predicted_styles.csv", as.is=TRUE)
+v$pred_era <- v$pred4096
+#s <- read.csv("https://www.dropbox.com/s/hu3mlar1n155w7m/sales_2018-10.csv?dl=1", as.is=TRUE)
+s <- read.csv("~/Dropbox (Cambridge University)/Cambridge/data/derived/sales_2018-10.csv", as.is=TRUE)
+
+s$toid <- s$TOID
+s$TOID <- NULL
+s$true_era <- NULL
+sales <- merge( s, v,  by="toid", all.x=TRUE)
+# remove flats or "other"
+sales <- subset(sales, propertytype %in% c("D","S","T"))
+sales$date <- as.Date(sales$date)
+# remove sales with prices above 1m
+sales <- subset(sales, price <= 1000000)
+
+
+# define a unique ID for each property
+sales$id <- apply(sales, 1, function(x){ paste(x['paon'], x['saon'], x['street'], x['postcode'] ) }) 
+
+# age of building (new at the very first sale)
+firstsaledate <- subset(sales, new=="Y", select=c("id","date"))
+colnames(firstsaledate) <- c("id","dob")
+
+# drop leaseholds
+sales <- subset(sales, estatetype =="F")
+
+# add lsoaid 
+#lsoa <- read.csv("https://www.dropbox.com/s/8wfw8tdq2sgxza8/lsoa_x_toid.csv?dl=1", as.is=TRUE)
+lsoa <- read.csv("~/Dropbox (Cambridge University)/Cambridge/data/derived/lsoa_x_toid.csv", as.is=TRUE)
+sales <- merge(sales, lsoa, by="toid", all.x=TRUE)
+
+# only keep sales with era predictions
+sales <- subset(sales, !is.na(pred_era) )
+
+
+############## REPEAT SALES
+sales$md5 <- ""
+sales <- subset(sales, select=c("id","price","date","pred_era","centrX", "centrY","toid","md5","lsoa11cd"))
+sales <- sales[order( sales$id, sales$date),]
+
+# create pairs
+pairs <- cbind( sales[2:nrow(sales),], sales[1:(nrow(sales)-1),])
[…]

### 2019-09-04 R/regressions_hedonic_price.R

@@ -1,0 +1,455 @@
+### Hedonic regression analysis
+
+library(xtable)
+library(stargazer)
+library(spdep)
+
+# 
+setwd("~/research/paper-uk-vintages/R/") 
+
+
+# Paths to datasets
+paths <- list()
+local.paths <- TRUE
+if(local.paths){
+  paths[["full_samples"]] <- "~/db/paper-uk-vintages/pred_full_sample.csv"
+  paths[["preds"]] <- "~/db/paper-uk-vintages/predicted_styles.csv"
+  paths[["sales"]] <- "~/Dropbox (Cambridge University)/Cambridge/data/derived/sales_2018-10.csv"
+  paths[["lsoa"]] <- "~/Dropbox (Cambridge University)/Cambridge/data/derived/lsoa_x_toid.csv"
+} else {
+  paths[["full_samples"]] <- "https://www.dropbox.com/s/v26ofbxg2zmzbrp/pred_full_sample.csv?dl=1"
+  paths[["preds"]] <- "https://www.dropbox.com/s/3ked11qizv37lpj/predicted_styles.csv?dl=1"
+  paths[["sales"]] <- "https://www.dropbox.com/s/hu3mlar1n155w7m/sales_2018-10.csv?dl=1"
+  paths[["lsoa"]] <- "https://www.dropbox.com/s/8wfw8tdq2sgxza8/lsoa_x_toid.csv?dl=1"
+}
+
+
+source("./helper.R")
+
+
+# load sales data
+v <- read.csv(paths[['full_samples']], as.is=TRUE)
+v$pred_era_4096 <- NULL
+v$pred_era_2048 <- NULL
+v$true_era <- NULL
+preds <- read.csv(paths[["preds"]], as.is=TRUE)
+v <- unique( merge(v, preds, by="toid", all=TRUE ))
+
+v$pred_era <- v$pred4096
+v$true_era[v$true_era %in% c("x greenery", "w walls")] <- NA 
+v$true_era_aug <- v$pred_era
+v$true_era_aug[! is.na(v$true_era)] <- v$true_era[!is.na(v$true_era)] 
+
+
+s <- read.csv(paths[["sales"]], as.is=TRUE)
+s$toid <- s$TOID
+s$TOID <- NULL
+s$true_era <- NULL
+s$pred_era <- NULL
+sales <- merge( s, v,  by="toid", all=TRUE)
+# remove flats or "other"
[…]

### 2019-09-04 R/regressions_hedonic_price_load_data.R

@@ -1,0 +1,175 @@
+# Hedonic regression of era
+
+library(stargazer)
+library(sandwich)
+library(lmtest)
+library(xtable)
+library(xtable)
+
+
+# load data, in case it needs to be updated: source(augment_sales_data.R)
+s <- read.csv("https://www.dropbox.com/s/4sdxm6x5lfhesrp/sales_toids_eras.csv?dl=1")
+s$date <- as.Date(s$date)
+s$year <- format(s$date, format="%Y")
+
+# load lsoa ids, for spatial controls
+lsoa <- read.csv("https://www.dropbox.com/s/8wfw8tdq2sgxza8/lsoa_x_toid.csv?dl=1", as.is=TRUE)
+colnames(lsoa) <- c("lsoaid","TOID" )
+
+# merge back to sales
+s <- merge(s, lsoa, by="TOID", all.x=TRUE)
+
+
+# load ground truth
+groundtruth <- read.csv("https://www.dropbox.com/s/04wwhdaqtuqzadt/groundtruth.csv?dl=1", as.is=TRUE)
+s$true_era <- NULL
+s <- merge(s, groundtruth, by="TOID", all.x = TRUE)
+
+
+#####################################
+# add classification based on 
+# - Google Streetview
+# - Map classification
+scores <- read.csv("https://www.dropbox.com/s/f2m77qexdzhywtk/scores_gsv_toid.csv?dl=1", as.is=TRUE)
+scores2D <- read.csv("~/db/Cambridge/data/derived/scores2D_toid.csv", as.is=TRUE)
+scorecols <- c("a.georgian","b.victorian","c.edwardian.late.victorian","d.interwar","e.postwar","f.contemporary","g.cont.victorian")
+colnames(scores2D) <- paste("sc2D", colnames(scores2D), sep="")
+scores2D$TOID <- scores2D$sc2DTOID
+scores2D$sc2DTOID <- NULL
+colnames(scores) <- paste("gsv", colnames(scores), sep="")
+scores$TOID <- scores$gsvTOID
+scores$gsvTOID <- NULL
+
+sco <- merge(scores, scores2D, by="TOID", all.x=TRUE)
+# calculate average scores, 
+# classify buildings based on the combined score
+p <- 0.5
+####
+for(c in scorecols){
+  sco[ , c ] <- sco[, paste("gsv", c, sep="")]*p + sco[,paste("sc2D", c, sep="")]*(1-p)
[…]

### 2019-09-04 R/settings.R

@@ -1,0 +1,4 @@
+### BASIC SETTINGS
+
+eras <- c("a georgian", "b victorian", "c edwardian late victorian", "d interwar", "e postwar", "f contemporary", "g cont victorian") 
+labels_short <- c("Georg.","Early Vic.","Late Vic./Edw.","Interwar","Postwar","Contemp.","Faux Vic.")

### 2019-09-04 R/spatial_dependency.R

@@ -1,0 +1,147 @@
+# analysis of spatial dependency in groundtruth and predicted style values
+
+library(spdep)
+library(keras)
+library(dplyr)
+colour <- c("#230356","#076391","#2fd1d1","#b51676","#e90d3a","#f98e19","#ffc217")
+
+
+# load stacked Inception vectors 
+# 2048 from obs (Variables "V123"), 2048 from neares neighbour ("VV123")
+v <- read.csv("~/research/paper-cambridge-vintages/data/groundtruth_image_vectors_1nn.csv", as.is=TRUE)
+
+# Exclude observations with bad images (those not showing home)
+# There is no point in training with those
+vv <- subset(v, true_era != "x greenery" & true_era != "w walls" )
+vv <- subset(vv, !is.na(true_era))
+
+# rescale inception vectors
+vector.columns <- grepl('^V+\\d+$', colnames(vv), perl=TRUE)
+vv[,vector.columns] <- vv[,vector.columns]/max(vv[,vector.columns])
+vv$true_era <- factor(vv$true_era)
+
+
+if(FALSE){
+  # stratified training sample
+  train <- vv %>%
+    group_by(true_era) %>%
+    sample_n(330)
+  # there are not that many Georgians in the sample, unfortunately
+  # trainng sample will be not fully balanced...
+  tmp <- subset(vv, ! toid %in% unique(train$toid))
+  tmp <- subset(tmp, true_era != "a georgian")
+  train.tmp <- tmp %>%
+    group_by(true_era) %>%
+    sample_n(270)
+  train <- rbind(train, train.tmp)
+  
+  # test with the rest, true out of sample
+  test <- subset(vv, ! toid %in% unique(train$toid))
+  
+  ###### TRAIN 2 MODELS
+  # - based on one picture only
+  # - based on the nearest neighbour as well
+  # ----------
+  model1cols <- colnames(train)[grepl('^V\\d+$', colnames(train), perl=TRUE)]
+  model2cols <- colnames(train)[grepl('^V+\\d+$', colnames(train), perl=TRUE)]
+  
+  pred <- list()
+  for(vector.columns in list(model2cols, model1cols ) ){
+    veclength <- length(vector.columns)
+    # define the train and test data
+    x_train <- as.matrix( vv[,vector.columns] )
[…]

### 2019-09-04 data/derived/derive_groundtruth.R

@@ -1,0 +1,19 @@
+setwd("~/Dropbox (Cambridge University)/COMBINED_0926/")
+folders <- list.files()
+
+gt <- list()
+for (f in folders){
+  gt[[f]] <-  as.data.frame( list.files(f) )
+}
+gt <- do.call(rbind, gt) 
+colnames(gt) <- "TOID"
+gt$true_era <- rownames(gt)
+gt$true_era <- gsub("_"," ",gt$true_era)
+gt$true_era <- tolower(gt$true_era)
+gt$true_era <- gsub(".(\\d+)$","",gt$true_era, perl=TRUE)
+gt$true_era <- gsub("\\."," ",gt$true_era, perl=TRUE)
+gt$true_era <- gsub("  "," ",gt$true_era, perl=TRUE)
+
+gt$TOID <- gsub("^(\\d+)_.+$","\\1",gt$TOID, perl=TRUE)
+
+write.csv(gt, file="~/Dropbox (Cambridge University)/Cambridge/data/derived/groundtruth.csv", row.names=FALSE)

### 2019-09-04 data/derived/derive_scores.R

@@ -1,0 +1,26 @@
+library(rjson)
+
+setwd("~/tf_files/scores/")
+scorefiles <- list.files(".")
+
+js <- list()
+for(f in scorefiles){
+  js[[f]] <- unlist(fromJSON(file=f))
+}
+
+js.df <- as.data.frame( do.call(rbind, js) )
+eras <- colnames(js.df)
+js.df$max <- apply(js.df, 1, max)
+js.df$TOID <- rownames(js.df)
+rownames(js.df) <- NULL
+js.df$TOID <- gsub("^(\\d+)_.+$","\\1",js.df$TOID, perl=TRUE)
+js.df$era <- NULL
+for(e in eras){
+  js.df$era[ js.df[,e] == js.df$max ] <- e
+}
+write.csv(js.df, "~/Dropbox (Cambridge University)/Cambridge/data/derived/scores_toid.csv", row.names=FALSE)
+
+
+
+
+

### 2019-09-04 data/derived/infill_neighbors_15m_toids.R

@@ -1,0 +1,48 @@
+# load data, in case it needs to be updated: source(augment_sales_data.R)
+s <- read.csv("https://www.dropbox.com/s/4sdxm6x5lfhesrp/sales_toids_eras.csv?dl=1")
+s$date <- as.Date(s$date)
+s$year <- format(s$date, format="%Y")
+
+
+newTOIDs <- unique( s$TOID[s$new=="Y" & !is.na(s$TOID)] )
+
+
+
+# ======================= WHICH LSOA does the buidling belong to?
+# in case a building is on the boundary, pick the one with the bigger overlap
+library('RPostgreSQL')
+con <- dbConnect(PostgreSQL(), user= "thies", dbname="gis", password='gis', port=5432)
+for( toid in newTOIDs){
+  sql <- paste("UPDATE cbg_os_buildings SET new = TRUE where cast(toid as numeric) = ",toid, sep="")
+  print(sql)
+  dbGetQuery(con, sql)
+}
+
+# ALTER TABLE cbg_os_buildings ADD COLUMN geom_buffer_15m geometry(Geometry,27700)
+# UDPATE cbg_os_buildings SET geom_buffer_15m = ST_BUFFER( geom, 15);
+# CREATE INDEX cbg_os_buildings_geom_buffer_15m ON cbg_os_buildings USING GIST (geom_buffer_15m);
+
+
+
+sql <- "SELECT
+          a.toid AS neigh_toid,
+          n.toid AS infill_toid
+        FROM
+          cbg_os_buildings  as a,
+          cbg_os_buildings as n
+        WHERE 
+          n.new = TRUE
+          AND n.toid != a.TOID
+          AND ST_Intersects(n.geom_buffer_15m, a.geom)"
+
+infill_neighbours <- dbGetQuery(con, sql)
+
+write.csv(infill_neighbours, file="~/db/Cambridge/data/derived/infill_15m.csv", row.names=FALSE)
+# =============================================================================
+
+
+
+
+
+
+

### 2019-09-04 data/merge_data_sales_addresses.R

@@ -1,0 +1,196 @@
+# Load OS AddressBase data (stored on Dropbox)
+library(data.table)
+library(stringr)
+# Postal Addressess
+ab <- fread("https://www.dropbox.com/s/4328cqcd3j8auam/ID28_DPA_Records.csv?dl=1")
+ab <- readRDS('~/Dropbox/pkg.data/cambridge/Raw/ID28_DPA_Records.rds')
+setkey(ab, UPRN)
+# TOID
+xref <- fread("https://www.dropbox.com/s/ng6k8ud90wehoyf/ID23_XREF_Records.csv?dl=1")
+xref <- readRDS('~/Dropbox/pkg.data/cambridge/Raw/ID23_XREF_Records.rds')
+xref <- xref[grepl('osgb', CROSS_REFERENCE), ][,.(UPRN, CROSS_REFERENCE)]
+setkey(xref, UPRN)
+a <- copy(xref[ab])
+a <- as.data.table(a)
+a$TOID <- gsub('osgb','', a$CROSS_REFERENCE)
+a <- a[nchar(TOID)==13, TOID:=str_pad(TOID,width = 16,side = 'left',pad = '0')]
+table(as.character(nchar(a$TOID)))
+table(str_sub(a[nchar(TOID)==13]$TOID,1,4))
+table(str_sub(a[nchar(TOID)==16]$TOID,1,4))
+table(str_sub(a$TOID, 1, 4))
+# Subset a to only inludde leading digits same as building.data
+a <- a[str_sub(a$TOID, 1, 4) != '4000']
+
+# Check the actual ids in the map
+building.data <- as.data.table(read.dbf(file = '~/Dropbox/pkg.data/cambridge/Raw/os_cambridge_buildings.dbf', as.is=TRUE))
+setkey(building.data, TOID)
+
+shape.address <- a[building.data]
+shape.address <- shape.address[!is.na(CROSS_REFERENCE)]
+write.csv(shape.address, file='data/shape.address.csv')
+
+# Check first four digits of TOID in building data
+table(nchar(building.data$TOID))
+table(str_sub(building.data$TOID, 1, 4))
+
+# Check how many TOIDs from a are not in building.data
+cat('There are ', length(a$TOID[a$TOID %in% building.data$TOID]), 'a$TOID in building.data$TOID', 
+    'and', length(a$TOID[!(a$TOID %in% building.data$TOID)]), 'that are unmatched')
+
+# Examine the unmatched
[…]

### 2019-09-04 data/shapefiles/calculate_centroid_area_volume.R

@@ -1,0 +1,77 @@
+# ==============================================
+# OS Shapefiles 
+# add information on lon, lat, volume and area to attributes
+# for regressions or subsetting later
+
+setwd("~/Dropbox (Cambridge University)/Cambridge/data/shapefiles/")
+# 27700 epsg
+# load libraries
+library(rgdal)
+library(rgeos)
+library(raster)
+
+# load shapefile
+s <- shapefile("os_cambridge_buildings.shp")
+
+# load raster of building volumes
+r <- raster("DEM Cambridge Volumetric Map.tif")
+
+s$volume3D <- NA
+s$area2D <- NA
+
+s$centrX <- NA
+s$centrY <- NA
+
+print( dim(s) )
+
+# save centroid coordinates for each polygon....
+for(i in 1:nrow(s)){
+  s[i, c("centrX","centrY")]<- bbox(gCentroid(s[i,]))[,1]
+  if(i %% 1000 == 0)  {
+    print(i)
+  }
+}
+
+# loop through each polygon in shape file, calculate area and volume of each building
+for(i in 1:nrow(s)){
+  # 2D area 
+  s$area2D[i] <- gArea(s[i,])
+  # 3D, total volume
+  s$volume3D[i] <- sum( unlist( extract(r, s[i,]) ), na.rm=TRUE)
+  if(i %% 100 == 0)  {
+    print(i)
+  }
+}
+
+# save everything to new shape file
+writeOGR(s, "buildings_with_centroids_area_volume.shp", driver="ESRI Shapefile", layer="buildingswithdens")
+
+# Do we have a mugshot from streetview?
+
+pics <- as.data.frame( list.files("../images/cambridge/") )
+colnames(pics) <- "filename"
+pics$TOID <- gsub("_.*$","",pics$filename, perl=TRUE)
+pics$PanoID <- gsub("^[^_]*_(.*)\\....$","\\1",pics$filename, perl=TRUE)
+
+ss <- merge(s, pics, by="TOID", all.x=TRUE)
+ss$mugshot <- "N"
+ss$mugshot[!is.na(ss$PanoID)] <- "Y"
+ss$mugshot[ss$PanoID =="nopanorama"] <- "nopanorama"
+
+# save everything to new shape file
+writeOGR(ss, "buildings_with_centroids_area_volume_panoid.shp", driver="ESRI Shapefile", layer="buildingswithdens")
+
+
[…]

### 2019-09-04 ensemble_model_training.R

@@ -1,0 +1,242 @@
+# load additional libraries
+library(spdep)
+library(keras)
+library(dplyr)
+
+
+source("~/research/paper-uk-vintages/R/helper.R")
+
+
+#==================================
+# Create 4096 vectors, by stacking 2048 from nearest neighbour
+# Most of the time, this won't be necessary....
+if(FALSE){
+  v <- read.csv("~/research/paper-cambridge-vintages/data/groundtruth_image_vectors.csv", as.is=TRUE)
+  v <- unique(v)
+  #vv <- subset(v, !is.na(x) & true_era != "x greenery" & true_era != "w walls" )
+  v$true_era <- factor(v$true_era)
+  
+  vector.columns <- grepl('^V\\d+$', colnames(v), perl=TRUE)
+  
+  # find nearest neighbours
+  k <- 1
+  col.knn <- knearneigh(as.matrix(v[,c("x","y")]), k=30)
+  # calculate average vector for n nearest neighbours 
+  indices <- as.matrix(col.knn[[1]])
+  # only keep neighbours that offer clean view on building,
+  # exclude greenery and walls
+  walls.greenery.index <- which(v$true %in% c("x greenery","w walls"))
+  indices[indices %in% walls.greenery.index] <- NA
+  
+  nnvec <- list()
+  
+  for(i in 1:nrow(v)){
+    if(i %% 200 == 0){ print(i) }
+    toid.tmp <- as.character( v$toid[i] )
+    ind.tmp <- indices[i,]
+    ind.tmp <- ind.tmp[!is.na(ind.tmp)][1]
+    nnvec[[ toid.tmp ]] <- as.list( v[ ind.tmp , vector.columns])
+  }  
+  nnvecs <- as.data.frame( do.call( rbind, nnvec ))
+  toids.tmp <- rownames(nnvecs)
+  nnvecs <- matrix(unlist(nnvecs), ncol=2048 )
+  colnames(nnvecs) <- paste("VV", 1:ncol(nnvecs), sep="")
+  nnvecs <- as.data.frame(nnvecs)
+  nnvecs$toid <- as.numeric(unlist(toids.tmp))
+  rm(nnvec)
+  vvv <- merge(v, nnvecs, by="toid")
+  rm(nnvecs)
+  write.csv(vvv, "~/research/paper-cambridge-vintages/data/groundtruth_image_vectors_1nn.csv", row.names = FALSE)
+}
+
+
+
+#############################################
[…]

### 2019-09-04 text/manuscript_assa.Rmd
Small text changes, Table 1 more condensed

@@
 For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings.
-This indicates that any premia are for vintage-related quality characteristics and not for a home's ``beauty''."
+Additionally, through the comparison of expert classification and deep learning methods, we are able to illustrate some of the limitations of machine learning methods and provide guidance on how to detect and overcome these limitations."
 ---
@@
 Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance.
-Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp and seminar participants at UCL/Bartlett and at the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
+Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
 \addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
@@
 
-This paper will assess architectural aesthetics heads on and analyze the visual appearance of residential buildings using street level images.
+This paper assesses the value of architectural aesthetics heads on by classifying the vintage of residential buildings using street level images.
 Recent work illustrates how street level imagery and machine learning classification is an efficient and powerful combination for measuring previously unobserved characteristics of the urban environment.
@@
 Our work demonstrates that utilizing pretrained convolutional neural networks to detect complex characteristics such as housing vintages with relatively high accuracy comes at low computational costs and is feasible with only modestly-sized training data.
-No supercomputers are needed, a modern laptop will do.
+Additionally, we illustrate how machine classifications may be sensitive to photo quality by comparing predicted vintages to those made by human experts.
 
@@
 
-The aesthetics of different architectural eras make for an easy cocktail party conversation topic -- and they also influence market prices.
+The aesthetics of different architectural vintages\footnote{We use ``style'',``era'' or ``vintage'' interchangeably in this paper.} make for an easy cocktail party conversation topic -- and they may also influence market prices.
 Using architectural assessments by human experts, @Buitelaar2017 find a sizable premium of 5\% for new buildings in the Netherlands that refer to traditional styles and a staggering 15\% premium for new buildings that closely follow traditional shapes, facade composition and details.
@@
 Google Street View offers a solution to this nexus as it captures the images of almost all buildings in many cities around the world at high level of accuracy and detail.
-The challenge we address in this paper is to extract and utilize building level information from this ubiquitous sensor.
+The challenge we address in this paper is to extract and utilize building level information from this ubiquitous sensor, using freely available deep learning techniques.
 
@@
 \emph{Inception-v3} has been trained for the ImageNet Large Scale Visual Recognition Challenge (ILSVRC)\footnote{\url{http://image-net.org/challenges/LSVRC/}}, which evaluates image classification and object detection algorithms for a wide range of objects.
-The pretrained classifications would allow us to identify pets, vehicles or people on the pictures -- assessing architectural finesse, however, is beyond the canned classifiers' capabilities.
+The pretrained classifications would allow us to identify pets, vehicles or people on the pictures -- assessing architectural style, however, is beyond the canned classifiers' capabilities.
 
@@
 This allows us to examine the power and size of the assignment tests.
-In addition having both human and machine classification for a large sample of the data allows for a robustness checks on the machine comparisons.
+In addition having both human and machine classification for a large sample of the data allows for robustness checks on the machine comparisons.
 
@@
 Two variables are obtained from the distribution of classifications per observation: The ensemble classifier arrives at predictions by majority vote.
-In addition, a confidence measure is computed as the Herfindahl index of classifications by ensemble member models.\footnote{If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*.
-The corresponding Herfindahl score is calculated as $(20/100)^2 + (80/100)^2 = 0.68$.}
+In addition, a confidence measure is computed as the Herfindahl index of classifications by ensemble member models.
+If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*.
+The corresponding Herfindahl score is calculated as $(20/100)^2 + (80/100)^2 = 0.68$.
 
@@
 We are not aware of any conversions of just the exterior of buildings.
-Full redevelopments, did occur and we exclude sales for a given address pre-dating any redevelopment.
+Full redevelopments did occur and we exclude sales for a given address pre-dating any redevelopment.
 Table \ref{tab:sumstats} presents summary statistics for the sample.
@@
 For *Contemporary* or *Revival* vintages, individual classifications differ most.
-All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the ensemble is not really sure when misclassifying images.
+All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the Herfindahl index is a good predictor of misclassified images.
 
@@
 Table \ref{tab:diffimgchar}, Panel A, compares the mean values for views obstructed by trees or vehicles for correctly (on diagonal) and incorrectly classified images.
-In most cases, the off-diagonal values are positive, showing that more obstacles in the view of sight correlate with higher odds of misclassifications.
+In most cases, the off-diagonal values are positive, showing that more obstacles in the view of sight correlate with a higher likelihood of misclassifications.
 Similarly, if more of the image area shows a house (Panel B), misclassifications are reduced (negative differences).
@@
 The improvement is most evident in the precision rates.
-For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different ground truth class -- the precision shoots up to 0.70 for *Georgian* and 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.
+For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different ground truth class -- the precision shoots up from 0.50 to 0.70 for *Georgian* and from 0.52 to 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.
 
@@
 (\ref{eq:hed}) are reported in Tables \ref{tab:hedreg} and \ref{tab:hedregint}.
-For all models, the hedonic control variables show the expected signs: Negative coefficients for the relative distance to the city center, discounts for terraced homes and semi-detached homes relative to detached houses, positive elasticities for building floor plate and building volumes and a price premium for new buildings compared to second-hand homes, when applicable.
+For all models, the hedonic control variables show the expected signs: Negative coefficients for the relative distance to the city center, discounts for terraced homes and semi-detached homes relative to detached houses, positive elasticities for building floor plate and building volumes and a price premium for new buildings compared to second-hand homes.
 Year and neighborhood dummies control for time effects and local amenities but their coefficients are not reported due to space constraints.
@@
 The base vintage *Contemporary* is more expensive than almost all other vintages, which show negative coefficients that are significantly different from 0.
-A clear pecking order appears: *Georgian* and *Revival* buildings are the dearest $(+0.04)$,  followed by *Late Victorian/Edwardian* $(+0.01)$, *Contemporary* (base), *Early Victorian* $(-0.13)$,  *Interwar* $(-0.15)$ and *Postwar* $(-0.22)$.
+A clear pecking order appears: *Georgian* and *Revival* buildings demand the highest premium $(+0.04)$,  followed by *Late Victorian/Edwardian* $(+0.01)$, *Contemporary* (base), *Early Victorian* $(-0.13)$,  *Interwar* $(-0.15)$ and *Postwar* $(-0.22)$.
 
@@
 We fail to find evidence in favor of positive externalities from revival architecture.
-Everything else equal, buildings within ensembles of *Contemporary* buildings generally do not achieve higher transaction prices than buildings in more historic areas (as Table \ref{tab:comb} will confirm later).
+Everything else equal, buildings within ensembles of *Contemporary* generally do not achieve higher transaction prices than buildings in more historic areas (as Table \ref{tab:comb} will confirm later).
 
@@
 
-The contributions of this paper are threefold: First, it introduced an algorithm that collects pictures of *individual* buildings from Google Street View.
+The contributions of this paper are threefold: First, it introduces an algorithm that collects pictures of *individual* buildings from Google Street View.
 Earlier work has not achieved this level of detail and was, at least in the UK, limited to street sections only.

### 2019-09-04 text/manuscript_assa.tex
Small text changes, Table 1 more condensed

@@
 significant determinant of transaction prices while no such effect is
-found for new buildings. This indicates that any premia are for
-vintage-related quality characteristics and not for a home's ``beauty''.
+found for new buildings. Additionally, through the comparison of expert
+classification and deep learning methods, we are able to illustrate some
+of the limitations of machine learning methods and provide guidance on
+how to detect and overcome these limitations.
 \end{abstract}
@@
 Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance.
-Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp and seminar participants at UCL/Bartlett and at the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
+Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
 
@@
 
-This paper will assess architectural aesthetics heads on and analyze the
-visual appearance of residential buildings using street level images.
-Recent work illustrates how street level imagery and machine learning
-classification is an efficient and powerful combination for measuring
-previously unobserved characteristics of the urban environment. Naik et
-al. (2017) describe how neighborhood demographics may impact the
-physical appearance of neighborhoods. Gebru et al. (2017) use classified
-vehicle make and model to predict income, race, education, and voting
-patterns at the precinct level. Glaeser et al. (2018) predict income in
-New York City. Naik, Raskar, and Hidalgo (2016) create a neighborhood
-safety based Streetscore which is shown to be highly correlated with
-neighborhood population density and household income. De Nadai et al.
-(2016) find that greenery and street facing windows contribute to a
-positive appearance of safety while Liu et al. (2017) evaluate the
-quality and upkeep of the built environment along Beijing's streets.
+This paper assesses the value of architectural aesthetics heads on by
+classifying the vintage of residential buildings using street level
+images. Recent work illustrates how street level imagery and machine
+learning classification is an efficient and powerful combination for
+measuring previously unobserved characteristics of the urban
+environment. Naik et al. (2017) describe how neighborhood demographics
+may impact the physical appearance of neighborhoods. Gebru et al. (2017)
+use classified vehicle make and model to predict income, race,
+education, and voting patterns at the precinct level. Glaeser et al.
+(2018) predict income in New York City. Naik, Raskar, and Hidalgo (2016)
+create a neighborhood safety based Streetscore which is shown to be
+highly correlated with neighborhood population density and household
+income. De Nadai et al. (2016) find that greenery and street facing
+windows contribute to a positive appearance of safety while Liu et al.
+(2017) evaluate the quality and upkeep of the built environment along
+Beijing's streets.
 
@@
 accuracy comes at low computational costs and is feasible with only
-modestly-sized training data. No supercomputers are needed, a modern
-laptop will do.
+modestly-sized training data. Additionally, we illustrate how machine
+classifications may be sensitive to photo quality by comparing predicted
+vintages to those made by human experts.
 
@@
 
-The aesthetics of different architectural eras make for an easy cocktail
-party conversation topic -- and they also influence market prices. Using
-architectural assessments by human experts, Buitelaar and Schilder
-(2017) find a sizable premium of 5\% for new buildings in the
-Netherlands that refer to traditional styles and a staggering 15\%
-premium for new buildings that closely follow traditional shapes, facade
-composition and details. Their study carefully disentangles the
-architectural style from other unobserved characteristics such as
-building quality, differences in location or year of construction. These
-controls are crucial, as earlier work has established that age and
-vintage variables tend to be highly correlated. Coulson and McMillen
-(2008), for instance, suggest a non-parametric estimator and establish a
-U-shaped age function and distinct price discounts for postwar and
-contemporary vintages (vis-à-vis more historic vintages). Francke and
-Minne (2017) investigate the depreciation of residential real estate in
-the Netherlands and decompose land versus structure values singling out
-the effect of ``physical deterioration, functional obsolescence and and
-vintage effects''. They find that buildings from the 1930s carry a
-strong price premium.
+The aesthetics of different architectural
+vintages\footnote{We use ``style'',``era'' or ``vintage'' interchangeably in this paper.}
+make for an easy cocktail party conversation topic -- and they may also
+influence market prices. Using architectural assessments by human
+experts, Buitelaar and Schilder (2017) find a sizable premium of 5\% for
+new buildings in the Netherlands that refer to traditional styles and a
+staggering 15\% premium for new buildings that closely follow
+traditional shapes, facade composition and details. Their study
+carefully disentangles the architectural style from other unobserved
+characteristics such as building quality, differences in location or
+year of construction. These controls are crucial, as earlier work has
+established that age and vintage variables tend to be highly correlated.
+Coulson and McMillen (2008), for instance, suggest a non-parametric
+estimator and establish a U-shaped age function and distinct price
+discounts for postwar and contemporary vintages (vis-à-vis more historic
+vintages). Francke and Minne (2017) investigate the depreciation of
+residential real estate in the Netherlands and decompose land versus
+structure values singling out the effect of ``physical deterioration,
+functional obsolescence and and vintage effects''. They find that
+buildings from the 1930s carry a strong price premium.
 
@@
 challenge we address in this paper is to extract and utilize building
-level information from this ubiquitous sensor.
+level information from this ubiquitous sensor, using freely available
+deep learning techniques.
 
@@
 identify pets, vehicles or people on the pictures -- assessing
-architectural finesse, however, is beyond the canned classifiers'
+architectural style, however, is beyond the canned classifiers'
 capabilities.
@@
 addition having both human and machine classification for a large sample
-of the data allows for a robustness checks on the machine comparisons.
+of the data allows for robustness checks on the machine comparisons.
 
@@
 vote. In addition, a confidence measure is computed as the Herfindahl
-index of classifications by ensemble member
-models.\footnote{If, for instance, 20 models classified a building as *Contemporary* but 80 others as *Revival*, the ensemble majority vote is *Revival*.
-The corresponding Herfindahl score is calculated as $(20/100)^2 + (80/100)^2 = 0.68$.}
+index of classifications by ensemble member models. If, for instance, 20
+models classified a building as \emph{Contemporary} but 80 others as
+\emph{Revival}, the ensemble majority vote is \emph{Revival}. The
+corresponding Herfindahl score is calculated as
+\((20/100)^2 + (80/100)^2 = 0.68\).
 
@@
 seems reasonable. We are not aware of any conversions of just the
-exterior of buildings. Full redevelopments, did occur and we exclude
+exterior of buildings. Full redevelopments did occur and we exclude
 sales for a given address pre-dating any redevelopment. Table
@@
 panel of Table \ref{tab:herftab} are negative, suggesting that, in
-general, the ensemble is not really sure when misclassifying images.
+general, the Herfindahl index is a good predictor of misclassified
+images.
 
@@
 off-diagonal values are positive, showing that more obstacles in the
-view of sight correlate with higher odds of misclassifications.
+view of sight correlate with a higher likelihood of misclassifications.
 Similarly, if more of the image area shows a house (Panel B),
@@
 classified as \emph{Georgian/Revival} in Panel A actually belong to a
-different ground truth class -- the precision shoots up to 0.70 for
-\emph{Georgian} and 0.82 for \emph{Revival} when excluding the not so
-confident lower third of predictions in Panel B.
+different ground truth class -- the precision shoots up from 0.50 to
+0.70 for \emph{Georgian} and from 0.52 to 0.82 for \emph{Revival} when
+excluding the not so confident lower third of predictions in Panel B.
 
@@
 elasticities for building floor plate and building volumes and a price
-premium for new buildings compared to second-hand homes, when
-applicable. Year and neighborhood dummies control for time effects and
-local amenities but their coefficients are not reported due to space
-constraints. The combination of location dummies and the distance to the
-city center measure controls for proximity to the city center
-\emph{within} each neighborhood.
+premium for new buildings compared to second-hand homes. Year and
+neighborhood dummies control for time effects and local amenities but
+their coefficients are not reported due to space constraints. The
+combination of location dummies and the distance to the city center
+measure controls for proximity to the city center \emph{within} each
+neighborhood.
 
@@
 0. A clear pecking order appears: \emph{Georgian} and \emph{Revival}
-buildings are the dearest \((+0.04)\), followed by \emph{Late
+buildings demand the highest premium \((+0.04)\), followed by \emph{Late
 Victorian/Edwardian} \((+0.01)\), \emph{Contemporary} (base),
@@
 from revival architecture. Everything else equal, buildings within
-ensembles of \emph{Contemporary} buildings generally do not achieve
-higher transaction prices than buildings in more historic areas (as
-Table \ref{tab:comb} will confirm later).
+ensembles of \emph{Contemporary} generally do not achieve higher
+transaction prices than buildings in more historic areas (as Table
+\ref{tab:comb} will confirm later).
 
@@
 
-The contributions of this paper are threefold: First, it introduced an
+The contributions of this paper are threefold: First, it introduces an
 algorithm that collects pictures of \emph{individual} buildings from

### 2019-09-04 text/manuscript_assa.Rmd
Small text changes, abstract

@@
 For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings.
-Additionally, through the comparison of expert classification and deep learning methods, we are able to illustrate some of the limitations of machine learning methods and provide guidance on how to detect and overcome these limitations."
+Additionally, we are able to provide guidance on how to detect and overcome some of the limitations of machine learning methods through a large-scale comparison of predictions and expert classifications."
 ---

### 2019-09-04 text/manuscript_assa.tex
Small text changes, abstract

@@
 significant determinant of transaction prices while no such effect is
-found for new buildings. Additionally, through the comparison of expert
-classification and deep learning methods, we are able to illustrate some
-of the limitations of machine learning methods and provide guidance on
-how to detect and overcome these limitations.
+found for new buildings. Additionally, we are able to provide guidance
+on how to detect and overcome some of the limitations of machine
+learning methods through a large-scale comparison of predictions and
+expert classifications.
 \end{abstract}

### 2019-09-13 text/manuscript_assa.Rmd
vintage/era replaced by style

@@
 ---
-title: "Machine Learning, Building Vintage and Property Values"
+title: "Machine Learning, Building Styles and Property Values"
 author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
@@
     keep_tex: true
+    number_sections: true
 bibliography: references.bib
 abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View.
-Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of building vintages.
+Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of these styles.
 Third, it investigates whether architectural styles influence house prices.
@@
 Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance.
-Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
+Carolin Schmidt, Peter Brummund, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
 \addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
-If new developments were only pleasing to the eye, so Britain's *Building Better, Building Beautiful Commission*, nimbyism would cease and housing supply could finally reach the levels demanded by a growing and more affluent population [@economistlineofbeauty2018].
-The inaugural chair of this new governmental commission boldly suggests that we should *``build, as our Georgian and Victorian forebears built* [...].
+If new developments were only pleasing to the eye, so Britain's *Building Better, Building Beautiful Commission* advising Government, nimbyism would cease and housing supply could finally reach the levels demanded by a growing and more affluent population [@economistlineofbeauty2018].
+The inaugural chair of this new commission boldly suggested that if we built *``as our Georgian and Victorian forebears built* [...].
 *All objections to new building would slip away in the sheer relief of the public''* [@scruton2018].
@@
 
-This paper assesses the value of architectural aesthetics heads on by classifying the vintage of residential buildings using street level images.
+This paper assesses the value of architectural aesthetics head on by classifying the exterior styles of residential buildings using street level images.
 Recent work illustrates how street level imagery and machine learning classification is an efficient and powerful combination for measuring previously unobserved characteristics of the urban environment.
 @Naik2017 describe how neighborhood demographics may impact the physical appearance of neighborhoods.
-@Gebru2017 use classified vehicle make and model to predict income, race, education, and voting patterns at the precinct level.
+@Gebru2017 use classified vehicle make and model information to predict income, race, education, and voting patterns at the precinct level.
 @Glaeser2016 predict income in New York City.
@@
 In this paper we suggest a method to collect a large number of images of individual UK buildings from Google Street View, classify the depicted buildings using deep convolutional neural networks, combine the derived information with sales price data and, ultimately, estimate marginal prices for the estimated building characteristics.
-Our work demonstrates that utilizing pretrained convolutional neural networks to detect complex characteristics such as housing vintages with relatively high accuracy comes at low computational costs and is feasible with only modestly-sized training data.
-Additionally, we illustrate how machine classifications may be sensitive to photo quality by comparing predicted vintages to those made by human experts.
+Our work demonstrates that utilizing pretrained convolutional neural networks to detect complex characteristics such as housing appearances with relatively high accuracy comes at low computational costs and is feasible with only modestly-sized training data.
+Additionally, we illustrate how machine classifications may be sensitive to photo quality by comparing machine classifications to those made by human experts.
 
-## Building vintage and property values
+## Building styles and property values
 
-The aesthetics of different architectural vintages\footnote{We use ``style'',``era'' or ``vintage'' interchangeably in this paper.} make for an easy cocktail party conversation topic -- and they may also influence market prices.
+The aesthetics of different architectural styles make for an easy cocktail party conversation topic -- and they may also influence market prices.
 Using architectural assessments by human experts, @Buitelaar2017 find a sizable premium of 5\% for new buildings in the Netherlands that refer to traditional styles and a staggering 15\% premium for new buildings that closely follow traditional shapes, facade composition and details.
-Their study carefully disentangles the architectural style from other unobserved characteristics such as building quality, differences in location or year of construction.
-These controls are crucial, as earlier work has established that age and vintage variables tend to be highly correlated.
-@Coulson2008, for instance, suggest a non-parametric estimator and establish a U-shaped age function and distinct price discounts for postwar and contemporary vintages (vis-à-vis more historic vintages).
+Their study carefully disentangles the architectural style from other unobserved characteristics such as building quality, differences in location, or year of construction.
+These controls are crucial, as earlier work has established that age and style variables tend to be highly correlated.
+@Coulson2008, for instance, suggest a non-parametric estimator and establish a U-shaped age function and distinct price discounts for postwar and contemporary styles (vis-à-vis more historic styles).
 @Francke2017a investigate the depreciation of residential real estate in the Netherlands and decompose land versus structure values singling out the effect of "physical deterioration, functional obsolescence and and vintage effects".
@@
 They reduce the extracted feature vectors to lower dimensionality (1024 to 100 dimensions) based on principal component analysis (PCA).
-We follow a different strategy and double the dimensionality by including the feature vector of the building's nearest neighbor.
+We follow a different strategy and double the dimensionality by including the feature vector of the closest building in the sample, which, in most cases, is the direct neighbor.
+The feature vectors of neighbors have been collected in exactly the same way as those for other buildings in the sample.
 Doubling up allows us to model spatial dependencies in building styles, similar to spatially correlated land cover classifications in @Ghimire2010a.
@@
 
-Cambridge's houses can be classified into seven broad eras: \footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general vintage descriptions.}
+Cambridge's houses can be classified into seven broad styles: \footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general style descriptions.}
 
@@
 Stained glass became more popular.
-\emph{Edwardian} architecture (1901-1910) tends to be less ornate than late Victorian architecture.
+
+* \emph{Edwardian} architecture (1901-1910) tends to be less ornate than late Victorian architecture.
 
@@
 
-* The \emph{Postwar} (1950-1980) era continued on this path, with an embrace of high-rise as well as low rise housing. Facades vary greatly between brick, tiling, pebbledash and render.
+* The \emph{Postwar} (1950-1980) styles continued on this path, with an embrace of high-rise as well as low rise housing. Facades vary greatly between brick, tiling, pebbledash and render.
 
-* The cut-off year for our \emph{Contemporary} era to begin is 1980. \emph{Revival} are contemporary buildings trying to emulate historic, mostly Victorian, architecture.
+* The cut-off year for our \emph{Contemporary} era to begin is 1980. \emph{Revival} style-homes are contemporary buildings trying to emulate historic, mostly Victorian, architecture.
 
@@
 In our case, each category requires less than 250 observations to reach saturated training accuracy levels.
-We greatly exceed this number for the purpose of this paper so that we can compare the out-of-sample convolutional neural network predictions to the ground truth as assigned by the experts.
+We greatly exceed this number for the purpose of this paper so that we can compare the out-of-sample convolutional neural network predictions to the architects' classifications.
 This allows us to examine the power and size of the assignment tests.
@@
 We create stratified training samples of 600 buildings from each category but *Georgian*, which is the least common style in Cambridge and for which we can only sample 330 examples.
-This leaves a sufficiently sized out-of-sample verification data set.
+This leaves a sufficiently sized out-of-sample verification data set of 21,000 homes.
 
@@
 
-For 100 randomly drawn, stratified data sets, we train two models each: The first is based on the building specific feature vectors (2048 dimensions) only while the second also incorporates the feature vector of the nearest neighbor (combined 4096 dimensions).
+For 100 randomly drawn data sets, all stratified on style, we train two models each: The first is based on the building specific feature vectors (2048 dimensions) only while the second also incorporates the feature vector of the nearest neighbor (combined 4096 dimensions).
 In cases where trees, fences or large vehicles obstruct the view or where the front of a building cannot be classified with high certainty, the image of the nearest neighbor provides a ``second opinion'' that is spatially correlated with the observation of interest.
@@
 
-When classifying a building picture, each models returns a vector of vintage-scores, each between 0 to 1, that jointly sum up to 1.
-We select the vintage with the highest score as the best estimate.
+When classifying a building picture, each models returns a vector of style-scores, each between 0 to 1, that jointly sum up to 1.
+We select the style with the highest score as the best estimate.
 By not excluding observations where multiple scores are vying for the top rank we retain as many observations as possible but risk a higher misclassification rate.
@@
 We tabulate confusion matrices and evaluate the classification performance in terms of recall, precision and $F_1$-scores.
-The next step regresses the true vintage observed, captured by binomial variables $D_{TrueVint}$, against a vector of hedonic variables $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's $\mathbf{Vintage}$, estimated both with and without spatial dependencies.
+More formally, the next step regresses the style classifications by architects, captured by binomial variables $D_{TrueVint}$, against a vector of hedonic variables $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's $\mathbf{Style}$, estimated both with and without spatial dependencies.
 The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients, and $\epsilon$ is the error term.
@@
 \begin{equation} \label{eq:rev}
-  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
 \end{equation}
@@
 Will the resulting classifiers be biased with respect to property values, picking up correlated but irrelevant cues such as greenery, upkeep, or cars brands instead of building exteriors?
-Are, for instance, more valuable houses more likely to be classified as the popular *Late Victorian* vintage while starter homes are disproportionally more likely to be classified as e.g.
+Are, for instance, more valuable houses more likely to be classified as the popular *Late Victorian* style while starter homes are disproportionally more likely to be classified as e.g.
 *Early Victorian*?
@@
 For close calls, however, where models within the ensemble cannot agree, other factors might tilt the scale towards an incorrect class.
-A sizable difference in estimated marginal prices for estimated vintages versus values for ground truth vintages in the subsequent hedonic regression (Eq.
+A sizable difference in estimated marginal prices for machine's classifications versus the estimates for architects' classifications in the subsequent hedonic regression (Eq.
 \ref{eq:hed}, below) would indicate such a bias.
 
-## Building era and property price
+## Building style and property price
 
-Merging the estimated vintage classification with sales data [@LandRegistry2016a] we estimate a hedonic regression equation that establishes marginal prices for the building vintage [similar to @Moorhouse1994; @Asabere1989; @Vandell1989; @Fuerst2011; @Plaut2006], among other characteristics:
+Merging the machine's classification with sales data [@LandRegistry2016a] we estimate a hedonic regression equation that establishes marginal prices for the building style [similar to @Moorhouse1994; @Asabere1989; @Vandell1989; @Fuerst2011; @Plaut2006], among other characteristics:
 \begin{equation} \label{eq:hed}
-  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i + \eta\mathbf{VintNeigh}_i + \iota\mathbf{Vintage\cdot VintNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i + \eta\mathbf{StyleNeigh}_i + \iota\mathbf{Style\cdot StyleNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
 \end{equation}
 
-Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Vintage}$ and the prevailing vintage of other buildings in the direct proximity $(\mathbf{VintNeigh})$.
+Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Style}$ and the prevailing vintage of other buildings in the direct proximity $(\mathbf{StyleNeigh})$.
 The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\eta}$, $\bm{\iota}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients.
@@
 
-Are buildings from different eras imperfect substitutes catering to multiple groups of households with distinct vintage preferences?
+Are buildings with different appearances imperfect substitutes catering to multiple groups of households with distinct style preferences?
 @Buitelaar2017 indicate that any premium for an architectural style must stem from either differences in construction prices (which they do not find in their Dutch sample) or from supply constraints, as new construction potentially does not capture the demand for traditional styles.
-For Cambridge, new supply will inevitably be of either contemporary or revival style as historic vintage buildings, by definition, are not supplied any more.
+For Cambridge, new supply will inevitably be of either contemporary or revival style as historic vintages (and their styles), by definition, are not supplied any more.
 Estimating Eq.
@@
 Overall, we collect pictures of more than 48,000 distinct buildings from the Google Street View API.
-The subset of 25,000 pictures that has been classified by trained architects into the seven vintages will serve as \emph{ground truth} for our study.
+The subset of 25,000 pictures that has been classified by trained architects into the seven styles will serve as \emph{ground truth} for our study.
 Two additional categories identify buildings hidden by *greenery* or uninformative pictures featuring *plain walls*.
@@
 
-Almost 16,000 of the 25,000 buildings for which we have the architects' ground truth could be matched to the 23,768 sales transactions that have been recorded for Cambridge between 1995 and 2018.
-Thus, we observe both the machine *estimated vintage* and architect defined *ground truth* classification for the majority of buildings in the data set.
+Almost 16,000 of the 25,000 buildings for which we have an architect's classification could be matched to the 23,768 sales transactions that have been recorded for Cambridge between 1995 and 2018.
+The remaining 9,000 houses have not been sold since 1995 - but the information on their architectural style is still valuable for our measures of neighborhood styles.
+Thus, we observe both the machine's and the architects' classification for the majority of buildings in the data set.
 
@@
 
-The agreement between vintage estimates and the corresponding ground truth classifications by experts is reassuringly strong.
+The agreement between classifications by the machine and by the architects is reassuringly strong.
 When relying on feature vectors of the buildings and their closest neighbors, 67 to 84 percent of true classifications are matched with correctly estimated labels (Table \ref{tab:confmat}, Panel A).
-The recall rates are especially high for older vintages: For *Georgians*, it is 79 percent, *Early Victorian* 81 percent, *Late Victorian/Edwardian* 78 percent, *Interwar* 84 percent, respectively.
+The recall rates are especially high for older styles: For *Georgians*, it is 79 percent, *Early Victorian* 81 percent, *Late Victorian/Edwardian* 78 percent, *Interwar* 84 percent, respectively.
 For more recent *Postwar* buildings, the rate drops to 71 percent, for *Contemporary* to 72 percent and for *Revival* to 67 percent.
@@
 A visual inspection of classifications is additionally reassuring.
-Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each vintage.
-The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.
+Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each style The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.
 
-The Herfindahl scores for classifications vary substantially across ground truth vintages (Table \ref{tab:herftab}), indicating that the models within the ensemble, for instance, agree more often on a building being *Georgian* than finding consensus for other vintages.
-For *Contemporary* or *Revival* vintages, individual classifications differ most.
+The Herfindahl scores for classifications vary substantially across styles, as classified by the architects (Table \ref{tab:herftab}), indicating that the models within the ensemble, for instance, agree more often on a building being *Georgian* than finding consensus for other styles.
+For *Contemporary* or *Revival* styles, individual classifications differ most.
 All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the Herfindahl index is a good predictor of misclassified images.
@@
 Similarly, if more of the image area shows a house (Panel B), misclassifications are reduced (negative differences).
-This effect is stronger for windows, which appear to give valuable cues about a house's vintage (Panel C).
+This effect is stronger for windows, which appear to give valuable cues about a house's style (Panel C).
 Finally, houses that are not in the center of the building tend to be misclassified more frequently (positive differences in Panel D).
@@
 
-The number of misclassifications decreases decidedly when considering observations with high ensemble confidence only: The majority vote based on the most confident two-thirds of predictions only are more in line with ground truth, as higher recall, precision and $F_1$-scores in Table \ref{tab:confmat}, Panel B, show.
+The number of misclassifications decreases decidedly when considering observations with high ensemble confidence only: The majority vote based on the most confident two-thirds of machine classifications only are more in line with the architects' classifications, as higher recall, precision and $F_1$-scores in Table \ref{tab:confmat}, Panel B, show.
 The improvement is most evident in the precision rates.
-For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different ground truth class -- the precision shoots up from 0.50 to 0.70 for *Georgian* and from 0.52 to 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.
+For the relatively rare categories of *Georgian* and *Revival* about the same number of buildings classified as *Georgian/Revival* in Panel A actually belong to a different style, according to the human experts.
+The precision shoots up from 0.50 to 0.70 for *Georgian* and from 0.52 to 0.82 for *Revival* when excluding the not so confident lower third of predictions in Panel B.
 
@@
 AIC values for 28 binomial models based on Eq.
-\ref{eq:rev} decrease as hedonic characteristics, location and time dummies are augmented by the base and spatial ML predictor.
-For all building vintages, the AIC are lowest for the spatial ML predictor.
-In sum, the spatial classifier performs better for UK vintage data than a classifier based on single buildings only.
+\ref{eq:rev} decrease as hedonic characteristics, location and time dummies are augmented by the base and spatial ML predictor (Table \ref{tab:aic}).
+For all building styles, the AIC are lowest for the spatial ML predictor.
+In sum, the spatial classifier performs better for UK style data than a classifier based on single buildings only.
 
@@
 
-The first column in Table \ref{tab:hedreg} presents the estimated regression coefficients for ground truth vintages.
-The base vintage *Contemporary* is more expensive than almost all other vintages, which show negative coefficients that are significantly different from 0.
+The first column in Table \ref{tab:hedreg} presents the estimated regression coefficients for the architects' classifications.
+The base style *Contemporary* is more expensive than almost all other styles, which show negative coefficients that are significantly different from 0.
 A clear pecking order appears: *Georgian* and *Revival* buildings demand the highest premium $(+0.04)$,  followed by *Late Victorian/Edwardian* $(+0.01)$, *Contemporary* (base), *Early Victorian* $(-0.13)$,  *Interwar* $(-0.15)$ and *Postwar* $(-0.22)$.
 
-The sample of ground truth images is not necessarily representative of the overall population so we re-estimate the model using predicted vintages for *all* buildings for which we were able to extract usable pictures from Google Street View.
-Overall, the vintage coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify unattractive buildings to the *Contemporary* vintage.
+The sample images classified by architects is not necessarily representative of the overall population so we re-estimate the model using machine classifications for *all* buildings for which we were able to extract usable pictures from Google Street View.
+Overall, the style coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify unattractive buildings to the *Contemporary* style.
 Reversely, more attractive buildings are disproportionally often misclassified as *Late Vic./Edw.*, pushing up the corresponding coefficient to $0.11$.
-This bias vanishes in the third model, which uses only confidently predicted vintages (Column 3).
+This bias vanishes in the third model, which uses only confidently estimated machine styles (Column 3).
 
@@
 materials, floor plans, green space and gardens are minimal.
-For newly built homes, no effect of *Revival* architecture on price can be found, neither for ground truth classifications nor for high confidence ML estimates.
-After controlling for location, building characteristics and quality, buyers show no willingness to pay a premium for *Revival* architecture.
+For newly built homes, no effect of *Revival* architecture on price can be found for high confidence ML estimates, neither for classifications by machines nor by architects.
+After controlling for location, building characteristics and quality, buyers show no willingness to pay a premium for *Revival* architecture (Columns 4 and 6).
 
-Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{VintNeigh}$) does not change the pecking order of building vintages much (Table \ref{tab:hedreg}, Column 7).
+Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{VintNeigh}$) does not change the pecking order of building styles much (Table \ref{tab:hedreg}, Column 7).
 Neighboring styles are compared to the base case of a *Contemporary* house in a *Contemporary* street.
@@
 Table \ref{tab:hedregint} presents the $\iota$ interaction coefficients (Eq.
-\ref{eq:hed}) for vintage-neighboring vintage combinations with sufficient numbers of observations (see Table \ref{tab:vintneigh}).
+\ref{eq:hed}) for style-neighboring style combinations with sufficient numbers of observations (see Table \ref{tab:vintneigh}).
 The last row suggests that a general claim that *Revival* neighbors exert positive externalities and increase property values relative to *Contemporary* surroundings cannot be confirmed empirically.
@@
 
-Second, we developed a new database of 25,000 building pictures that have been classified by architecture experts into relevant architectural styles or vintages.
-We subsequently trained a neural network classifier to automatically classify all residential buildings of a mid-sized English city into architectural styles or vintages.
+Second, we developed a new database of 25,000 building pictures that have been classified by architecture experts into relevant architectural styles.
+We subsequently trained a neural network classifier to automatically classify all residential buildings of a mid-sized English city into architectural styles.
 The suggested classifier is trained on feature vectors of buildings and their nearest neighbors to exploit spatial correlation in observed classifications.
 
-The large ground truth data set allows for a comparison of human expert classifications with predictions made by ML classifiers.
+The large ground truth data set allows for a comparison of human expert versus machine classifications.
 Poor image quality, for instance obstructed views or the lack of informative features such as windows, is correlated with misclassifications.
-Importantly, for cases in which the ML classifiers are relatively indecisive between classes, visual cues that are correlated with vintage but not part of a building's architecture (for instance trees or cars) bias the estimates.
+Importantly, for cases in which the ML classifiers are relatively indecisive between classes, visual cues that are correlated with the exterior's style but not part of a building's architecture (for instance trees or cars) bias the estimates.
 Fore these less certain cases, more valuable homes are systematically more likely to be classified as e.g.
@@
 A follow up study could investigate which elements in the building pictures lead to the misclassifications [@Ribeiro2016].
-Given the danger of systematic biases, one should remain wary of ML estimates derived from ground truth data sizable enough to train models -- but too small to investigate any biases.
+Given the danger of systematic biases, one should remain wary of ML estimates derived from data sets sizable enough to train models -- but too small to investigate any biases.
 
@@
 \toprule 
-  & \multicolumn{7}{c}{\emph{Ground truth}} \\ 
+  & \multicolumn{7}{c}{\emph{Architects}} \\ 
   \cmidrule(lr){2-8} 
@@
  \midrule 
-\emph{Pred. vintage} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
+\emph{Machine} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
 \cmidrule(lr){2-8} 
@@
 \vspace{0.25cm}
-\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 vintages $v$ received, calculated as: $Herf_i=\sum_{v=1}^{v=7} (votes_v/votes_{all})^2$.
+\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 styles $s$ received, calculated as: $Herf_i=\sum_{s=1}^{s=7} (votes_s/votes_{all})^2$.
 A high score indicates high levels of consensus within the ensemble.
@@
 \centering 
- \caption{Mean Values for image quality variables, by vintage}
+ \caption{Mean Values for image quality variables, by style}
 
@@
 \toprule 
-Ground Truth & Share Blocked & House Area & Window Area & Image Offset \\ 
+Architects' classifications & Share Blocked & House Area & Window Area & Image Offset \\ 
 \midrule
@@
 
-\emph{Predicted} & \multicolumn{7}{c}{\emph{Ground truth}} \\ 
+\emph{Machine} & \multicolumn{7}{c}{\emph{Architects}} \\ 
   \cmidrule(lr){2-8} 
@@
 \vspace{0.25cm}
-\emph{Notes:} Cross-tabulation of photo characteristics by projected and ground truth.
-Off-diagonal elements ($Predicted_{j}-Ground Truth_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given ground truth vintage.
+\emph{Notes:} Cross-tabulation of photo characteristics by machine and architects' classifications.
+Off-diagonal elements ($Machine_{j}-Architects_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given classification by architects.
 For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic.
@@
 \begin{figure}[htb!]
-\caption{Examples of Estimated Building Vintages}
-```{r plot_top_pictures, cache=TRUE, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Examples of Buildings, classified into Vintages"}
+\caption{Examples of machine-based style classifications}
+```{r plot_top_pictures, cache=TRUE, results='asis', echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Examples of Buildings, classified into Styles"}
 source("../R/plot_top_pictures.R")
@@
 \begin{minipage}{0.7\textwidth}
-\footnotesize \emph{Notes:} For a brief discussion of the building vintages see page \pageref{def_eras}.
+\footnotesize \emph{Notes:} For a brief discussion of the building styles see page \pageref{def_eras}.
 \end{minipage}
@@
 \begin{table}[htb!]
-\caption{Vintage predictions as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
+\caption{Machine style classifications as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
 \label{tab:aic}
@@
 Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA).
-The estimated scores for building vintages are inferred from the Google Street View classification model.
+Building styles based on machine classifications.
 \end{minipage}
@@
 Standard errors are robust (White's estimator).
-Models (1) and (4) are estimated using ground truth classifications only.
+Models (1) and (4) are estimated using the architects' classifications only.
 Models (2) and (5) are estimated based on all observations that have been automatically classified.
@@
 \begin{table}[ht]
-\caption{Counts: Building vintage and neighboring buildings' vintage}
+\caption{Counts: Building style and neighboring buildings' style}
 \label{tab:vintneigh}
@@
 \vspace{0.25cm}
-\footnotesize \emph{Notes:} The vintage of direct neighborhoods is defined as the most frequent detected style on the same street and within 100m. 
+\footnotesize \emph{Notes:} The style of direct neighborhoods is defined as the most frequent detected style on the same street, within 100m. 
 \end{minipage}

### 2019-09-13 text/manuscript_assa.tex
vintage/era replaced by style

@@
 \hypersetup{unicode=true,
-            pdftitle={Machine Learning, Building Vintage and Property Values},
+            pdftitle={Machine Learning, Building Styles and Property Values},
             pdfauthor={Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson (University of Alabama)},
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 % Redefines (sub)paragraphs to behave more like sections
@@
 
-  \title{Machine Learning, Building Vintage and Property Values}
+  \title{Machine Learning, Building Styles and Property Values}
     \pretitle{\vspace{\droptitle}\centering\huge}
@@
   \postdate{\par}
-    \date{04 September 2019}
+    \date{13 September 2019}
 
@@
 into architectural styles, taking into account spatial dependencies of
-building vintages. Third, it investigates whether architectural styles
+these styles. Third, it investigates whether architectural styles
 influence house prices. For re-sales, the architectural style is a
@@
 Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance.
-Carolin Schmidt, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
+Carolin Schmidt, Peter Brummund, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
 
@@
 If new developments were only pleasing to the eye, so Britain's
-\emph{Building Better, Building Beautiful Commission}, nimbyism would
-cease and housing supply could finally reach the levels demanded by a
-growing and more affluent population (The Economist 2018). The inaugural
-chair of this new governmental commission boldly suggests that we should
-\emph{``build, as our Georgian and Victorian forebears built}
-{[}\ldots{}{]}. \emph{All objections to new building would slip away in
-the sheer relief of the public''} (Scruton 2018). Even Prince Charles,
-in similar spirit, put forward ten principles for urban growth and
-architecture that emphasize tradition and aesthetics (HRH The Prince of
-Wales 2014). When governments and princes occupy themselves with beauty,
-economists surely may take a closer look as well. In this paper, we aim
-to identify the architectural styles of residential buildings using
-computer vision techniques and to empirically search for any transaction
-price premia associated with these styles. If aesthetics were as strong
-a force in the built environment as claimed, we should indeed find a
-significant effect on property prices.
-
-This paper assesses the value of architectural aesthetics heads on by
-classifying the vintage of residential buildings using street level
-images. Recent work illustrates how street level imagery and machine
-learning classification is an efficient and powerful combination for
-measuring previously unobserved characteristics of the urban
+\emph{Building Better, Building Beautiful Commission} advising
+Government, nimbyism would cease and housing supply could finally reach
+the levels demanded by a growing and more affluent population (The
+Economist 2018). The inaugural chair of this new commission boldly
+suggested that if we built \emph{``as our Georgian and Victorian
+forebears built} {[}\ldots{}{]}. \emph{All objections to new building
+would slip away in the sheer relief of the public''} (Scruton 2018).
+Even Prince Charles, in similar spirit, put forward ten principles for
+urban growth and architecture that emphasize tradition and aesthetics
+(HRH The Prince of Wales 2014). When governments and princes occupy
+themselves with beauty, economists surely may take a closer look as
+well. In this paper, we aim to identify the architectural styles of
+residential buildings using computer vision techniques and to
+empirically search for any transaction price premia associated with
+these styles. If aesthetics were as strong a force in the built
+environment as claimed, we should indeed find a significant effect on
+property prices.
+
+This paper assesses the value of architectural aesthetics head on by
+classifying the exterior styles of residential buildings using street
+level images. Recent work illustrates how street level imagery and
+machine learning classification is an efficient and powerful combination
+for measuring previously unobserved characteristics of the urban
 environment. Naik et al. (2017) describe how neighborhood demographics
 may impact the physical appearance of neighborhoods. Gebru et al. (2017)
-use classified vehicle make and model to predict income, race,
-education, and voting patterns at the precinct level. Glaeser et al.
-(2018) predict income in New York City. Naik, Raskar, and Hidalgo (2016)
-create a neighborhood safety based Streetscore which is shown to be
-highly correlated with neighborhood population density and household
+use classified vehicle make and model information to predict income,
+race, education, and voting patterns at the precinct level. Glaeser et
+al. (2018) predict income in New York City. Naik, Raskar, and Hidalgo
+(2016) create a neighborhood safety based Streetscore which is shown to
+be highly correlated with neighborhood population density and household
 income. De Nadai et al. (2016) find that greenery and street facing
@@
 that utilizing pretrained convolutional neural networks to detect
-complex characteristics such as housing vintages with relatively high
+complex characteristics such as housing appearances with relatively high
 accuracy comes at low computational costs and is feasible with only
 modestly-sized training data. Additionally, we illustrate how machine
-classifications may be sensitive to photo quality by comparing predicted
-vintages to those made by human experts.
-
-\hypertarget{building-vintage-and-property-values}{%
-\subsection{Building vintage and property
-values}\label{building-vintage-and-property-values}}
-
-The aesthetics of different architectural
-vintages\footnote{We use ``style'',``era'' or ``vintage'' interchangeably in this paper.}
-make for an easy cocktail party conversation topic -- and they may also
-influence market prices. Using architectural assessments by human
-experts, Buitelaar and Schilder (2017) find a sizable premium of 5\% for
-new buildings in the Netherlands that refer to traditional styles and a
-staggering 15\% premium for new buildings that closely follow
-traditional shapes, facade composition and details. Their study
-carefully disentangles the architectural style from other unobserved
-characteristics such as building quality, differences in location or
-year of construction. These controls are crucial, as earlier work has
-established that age and vintage variables tend to be highly correlated.
-Coulson and McMillen (2008), for instance, suggest a non-parametric
-estimator and establish a U-shaped age function and distinct price
-discounts for postwar and contemporary vintages (vis-à-vis more historic
-vintages). Francke and Minne (2017) investigate the depreciation of
-residential real estate in the Netherlands and decompose land versus
-structure values singling out the effect of ``physical deterioration,
-functional obsolescence and and vintage effects''. They find that
-buildings from the 1930s carry a strong price premium.
+classifications may be sensitive to photo quality by comparing machine
+classifications to those made by human experts.
+
+\hypertarget{building-styles-and-property-values}{%
+\subsection{Building styles and property
+values}\label{building-styles-and-property-values}}
+
+The aesthetics of different architectural styles make for an easy
+cocktail party conversation topic -- and they may also influence market
+prices. Using architectural assessments by human experts, Buitelaar and
+Schilder (2017) find a sizable premium of 5\% for new buildings in the
+Netherlands that refer to traditional styles and a staggering 15\%
+premium for new buildings that closely follow traditional shapes, facade
+composition and details. Their study carefully disentangles the
+architectural style from other unobserved characteristics such as
+building quality, differences in location, or year of construction.
+These controls are crucial, as earlier work has established that age and
+style variables tend to be highly correlated. Coulson and McMillen
+(2008), for instance, suggest a non-parametric estimator and establish a
+U-shaped age function and distinct price discounts for postwar and
+contemporary styles (vis-à-vis more historic styles). Francke and Minne
+(2017) investigate the depreciation of residential real estate in the
+Netherlands and decompose land versus structure values singling out the
+effect of ``physical deterioration, functional obsolescence and and
+vintage effects''. They find that buildings from the 1930s carry a
+strong price premium.
 
@@
 different strategy and double the dimensionality by including the
-feature vector of the building's nearest neighbor. Doubling up allows us
-to model spatial dependencies in building styles, similar to spatially
-correlated land cover classifications in Ghimire, Rogan, and Miller
-(2010).
+feature vector of the closest building in the sample, which, in most
+cases, is the direct neighbor. The feature vectors of neighbors have
+been collected in exactly the same way as those for other buildings in
+the sample. Doubling up allows us to model spatial dependencies in
+building styles, similar to spatially correlated land cover
+classifications in Ghimire, Rogan, and Miller (2010).
 
@@
 
-Cambridge's houses can be classified into seven broad eras:
-\footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general vintage descriptions.}
+Cambridge's houses can be classified into seven broad styles:
+\footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general style descriptions.}
 
@@
   ornamental details to the formal repertoire employed by designers.
-  Stained glass became more popular. \emph{Edwardian} architecture
-  (1901-1910) tends to be less ornate than late Victorian architecture.
+  Stained glass became more popular.
+\item
+  \emph{Edwardian} architecture (1901-1910) tends to be less ornate than
+  late Victorian architecture.
 \item
@@
 \item
-  The \emph{Postwar} (1950-1980) era continued on this path, with an
+  The \emph{Postwar} (1950-1980) styles continued on this path, with an
   embrace of high-rise as well as low rise housing. Facades vary greatly
@@
   The cut-off year for our \emph{Contemporary} era to begin is 1980.
-  \emph{Revival} are contemporary buildings trying to emulate historic,
-  mostly Victorian, architecture.
+  \emph{Revival} style-homes are contemporary buildings trying to
+  emulate historic, mostly Victorian, architecture.
 \end{itemize}
@@
 paper so that we can compare the out-of-sample convolutional neural
-network predictions to the ground truth as assigned by the experts. This
-allows us to examine the power and size of the assignment tests. In
-addition having both human and machine classification for a large sample
-of the data allows for robustness checks on the machine comparisons.
+network predictions to the architects' classifications. This allows us
+to examine the power and size of the assignment tests. In addition
+having both human and machine classification for a large sample of the
+data allows for robustness checks on the machine comparisons.
 
@@
 Cambridge and for which we can only sample 330 examples. This leaves a
-sufficiently sized out-of-sample verification data set.
+sufficiently sized out-of-sample verification data set of 21,000 homes.
 
@@
 
-For 100 randomly drawn, stratified data sets, we train two models each:
-The first is based on the building specific feature vectors (2048
-dimensions) only while the second also incorporates the feature vector
-of the nearest neighbor (combined 4096 dimensions). In cases where
-trees, fences or large vehicles obstruct the view or where the front of
-a building cannot be classified with high certainty, the image of the
-nearest neighbor provides a ``second opinion'' that is spatially
+For 100 randomly drawn data sets, all stratified on style, we train two
+models each: The first is based on the building specific feature vectors
+(2048 dimensions) only while the second also incorporates the feature
+vector of the nearest neighbor (combined 4096 dimensions). In cases
+where trees, fences or large vehicles obstruct the view or where the
+front of a building cannot be classified with high certainty, the image
+of the nearest neighbor provides a ``second opinion'' that is spatially
 correlated with the observation of interest. Finally we classify all
@@
 When classifying a building picture, each models returns a vector of
-vintage-scores, each between 0 to 1, that jointly sum up to 1. We select
-the vintage with the highest score as the best estimate. By not
-excluding observations where multiple scores are vying for the top rank
-we retain as many observations as possible but risk a higher
-misclassification rate.
+style-scores, each between 0 to 1, that jointly sum up to 1. We select
+the style with the highest score as the best estimate. By not excluding
+observations where multiple scores are vying for the top rank we retain
+as many observations as possible but risk a higher misclassification
+rate.
 
@@
 We tabulate confusion matrices and evaluate the classification
-performance in terms of recall, precision and \(F_1\)-scores. The next
-step regresses the true vintage observed, captured by binomial variables
-\(D_{TrueVint}\), against a vector of hedonic variables \(\mathbf{X}\),
-vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
-variables and the building's \(\mathbf{Vintage}\), estimated both with
-and without spatial dependencies. The intercept is denoted by \(\alpha\)
-while \(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\gamma}\) and
-\(\bm{\lambda}\) are vectors of regression coefficients, and
-\(\epsilon\) is the error term.
+performance in terms of recall, precision and \(F_1\)-scores. More
+formally, the next step regresses the style classifications by
+architects, captured by binomial variables \(D_{TrueVint}\), against a
+vector of hedonic variables \(\mathbf{X}\), vectors of year
+\(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy variables and the
+building's \(\mathbf{Style}\), estimated both with and without spatial
+dependencies. The intercept is denoted by \(\alpha\) while
+\(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\gamma}\) and \(\bm{\lambda}\)
+are vectors of regression coefficients, and \(\epsilon\) is the error
+term.
 
 \begin{equation} \label{eq:rev}
-  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
 \end{equation}
@@
 more valuable houses more likely to be classified as the popular
-\emph{Late Victorian} vintage while starter homes are disproportionally
+\emph{Late Victorian} style while starter homes are disproportionally
 more likely to be classified as e.g. \emph{Early Victorian}? We expect
@@
 factors might tilt the scale towards an incorrect class. A sizable
-difference in estimated marginal prices for estimated vintages versus
-values for ground truth vintages in the subsequent hedonic regression
-(Eq. \ref{eq:hed}, below) would indicate such a bias.
-
-\hypertarget{building-era-and-property-price}{%
-\subsection{Building era and property
-price}\label{building-era-and-property-price}}
-
-Merging the estimated vintage classification with sales data (Land
-Registry 2017) we estimate a hedonic regression equation that
-establishes marginal prices for the building vintage (similar to
-Moorhouse and Smith 1994; Asabere, Hachey, and Grubaugh 1989; Vandell
-and Lane 1989; Fuerst, McAllister, and Murray 2011; Plaut and Uzulena
-2006), among other characteristics: \begin{equation} \label{eq:hed}
-  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Vintage}_i + \eta\mathbf{VintNeigh}_i + \iota\mathbf{Vintage\cdot VintNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+difference in estimated marginal prices for machine's classifications
+versus the estimates for architects' classifications in the subsequent
+hedonic regression (Eq. \ref{eq:hed}, below) would indicate such a bias.
+
+\hypertarget{building-style-and-property-price}{%
+\subsection{Building style and property
+price}\label{building-style-and-property-price}}
+
+Merging the machine's classification with sales data (Land Registry
+2017) we estimate a hedonic regression equation that establishes
+marginal prices for the building style (similar to Moorhouse and Smith
+1994; Asabere, Hachey, and Grubaugh 1989; Vandell and Lane 1989; Fuerst,
+McAllister, and Murray 2011; Plaut and Uzulena 2006), among other
+characteristics: \begin{equation} \label{eq:hed}
+  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i + \eta\mathbf{StyleNeigh}_i + \iota\mathbf{Style\cdot StyleNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
 \end{equation}
@@
 vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
-variables and the building's estimated \(\mathbf{Vintage}\) and the
+variables and the building's estimated \(\mathbf{Style}\) and the
 prevailing vintage of other buildings in the direct proximity
-\((\mathbf{VintNeigh})\). The intercept is denoted by \(\alpha\) while
+\((\mathbf{StyleNeigh})\). The intercept is denoted by \(\alpha\) while
 \(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\eta}\), \(\bm{\iota}\),
@@
 
-Are buildings from different eras imperfect substitutes catering to
-multiple groups of households with distinct vintage preferences?
+Are buildings with different appearances imperfect substitutes catering
+to multiple groups of households with distinct style preferences?
 Buitelaar and Schilder (2017) indicate that any premium for an
@@
 for traditional styles. For Cambridge, new supply will inevitably be of
-either contemporary or revival style as historic vintage buildings, by
-definition, are not supplied any more. Estimating Eq. \ref{eq:hed} for a
-subset of newly constructed buildings will show whether construction
-prices or supply constraints for new homes built according to different
-architectural styles persist -- if too few vernacular buildings were
-built, prices should reflect such a shortage.
+either contemporary or revival style as historic vintages (and their
+styles), by definition, are not supplied any more. Estimating Eq.
+\ref{eq:hed} for a subset of newly constructed buildings will show
+whether construction prices or supply constraints for new homes built
+according to different architectural styles persist -- if too few
+vernacular buildings were built, prices should reflect such a shortage.
 
@@
 the Google Street View API. The subset of 25,000 pictures that has been
-classified by trained architects into the seven vintages will serve as
+classified by trained architects into the seven styles will serve as
 \emph{ground truth} for our study. Two additional categories identify
@@
 
-Almost 16,000 of the 25,000 buildings for which we have the architects'
-ground truth could be matched to the 23,768 sales transactions that have
-been recorded for Cambridge between 1995 and 2018. Thus, we observe both
-the machine \emph{estimated vintage} and architect defined \emph{ground
-truth} classification for the majority of buildings in the data set.
+Almost 16,000 of the 25,000 buildings for which we have an architect's
+classification could be matched to the 23,768 sales transactions that
+have been recorded for Cambridge between 1995 and 2018. The remaining
+9,000 houses have not been sold since 1995 - but the information on
+their architectural style is still valuable for our measures of
+neighborhood styles. Thus, we observe both the machine's and the
+architects' classification for the majority of buildings in the data
+set.
 
@@
 
-The agreement between vintage estimates and the corresponding ground
-truth classifications by experts is reassuringly strong. When relying on
-feature vectors of the buildings and their closest neighbors, 67 to 84
-percent of true classifications are matched with correctly estimated
-labels (Table \ref{tab:confmat}, Panel A). The recall rates are
-especially high for older vintages: For \emph{Georgians}, it is 79
-percent, \emph{Early Victorian} 81 percent, \emph{Late
-Victorian/Edwardian} 78 percent, \emph{Interwar} 84 percent,
-respectively. For more recent \emph{Postwar} buildings, the rate drops
-to 71 percent, for \emph{Contemporary} to 72 percent and for
-\emph{Revival} to 67 percent.
+The agreement between classifications by the machine and by the
+architects is reassuringly strong. When relying on feature vectors of
+the buildings and their closest neighbors, 67 to 84 percent of true
+classifications are matched with correctly estimated labels (Table
+\ref{tab:confmat}, Panel A). The recall rates are especially high for
+older styles: For \emph{Georgians}, it is 79 percent, \emph{Early
+Victorian} 81 percent, \emph{Late Victorian/Edwardian} 78 percent,
+\emph{Interwar} 84 percent, respectively. For more recent \emph{Postwar}
+buildings, the rate drops to 71 percent, for \emph{Contemporary} to 72
+percent and for \emph{Revival} to 67 percent.
 
@@
 Figure \ref{fig:vint_examples} displays the pictures which carry the
-highest out-of-sample scores for each vintage. The model is clearly able
-to differentiate based on small cues, even when only parts of the facade
+highest out-of-sample scores for each style The model is clearly able to
+differentiate based on small cues, even when only parts of the facade
 are captured on the picture.
@@
 The Herfindahl scores for classifications vary substantially across
-ground truth vintages (Table \ref{tab:herftab}), indicating that the
-models within the ensemble, for instance, agree more often on a building
-being \emph{Georgian} than finding consensus for other vintages. For
-\emph{Contemporary} or \emph{Revival} vintages, individual
-classifications differ most. All off-diagonal elements in the lower
-panel of Table \ref{tab:herftab} are negative, suggesting that, in
+styles, as classified by the architects (Table \ref{tab:herftab}),
+indicating that the models within the ensemble, for instance, agree more
+often on a building being \emph{Georgian} than finding consensus for
+other styles. For \emph{Contemporary} or \emph{Revival} styles,
+individual classifications differ most. All off-diagonal elements in the
+lower panel of Table \ref{tab:herftab} are negative, suggesting that, in
 general, the Herfindahl index is a good predictor of misclassified
@@
 stronger for windows, which appear to give valuable cues about a house's
-vintage (Panel C). Finally, houses that are not in the center of the
+style (Panel C). Finally, houses that are not in the center of the
 building tend to be misclassified more frequently (positive differences
@@
 observations with high ensemble confidence only: The majority vote based
-on the most confident two-thirds of predictions only are more in line
-with ground truth, as higher recall, precision and \(F_1\)-scores in
-Table \ref{tab:confmat}, Panel B, show. The improvement is most evident
-in the precision rates. For the relatively rare categories of
-\emph{Georgian} and \emph{Revival} about the same number of buildings
-classified as \emph{Georgian/Revival} in Panel A actually belong to a
-different ground truth class -- the precision shoots up from 0.50 to
-0.70 for \emph{Georgian} and from 0.52 to 0.82 for \emph{Revival} when
-excluding the not so confident lower third of predictions in Panel B.
+on the most confident two-thirds of machine classifications only are
+more in line with the architects' classifications, as higher recall,
+precision and \(F_1\)-scores in Table \ref{tab:confmat}, Panel B, show.
+The improvement is most evident in the precision rates. For the
+relatively rare categories of \emph{Georgian} and \emph{Revival} about
+the same number of buildings classified as \emph{Georgian/Revival} in
+Panel A actually belong to a different style, according to the human
+experts. The precision shoots up from 0.50 to 0.70 for \emph{Georgian}
+and from 0.52 to 0.82 for \emph{Revival} when excluding the not so
+confident lower third of predictions in Panel B.
 
@@
 characteristics, location and time dummies are augmented by the base and
-spatial ML predictor. For all building vintages, the AIC are lowest for
-the spatial ML predictor. In sum, the spatial classifier performs better
-for UK vintage data than a classifier based on single buildings only.
+spatial ML predictor (Table \ref{tab:aic}). For all building styles, the
+AIC are lowest for the spatial ML predictor. In sum, the spatial
+classifier performs better for UK style data than a classifier based on
+single buildings only.
 
@@
 The first column in Table \ref{tab:hedreg} presents the estimated
-regression coefficients for ground truth vintages. The base vintage
-\emph{Contemporary} is more expensive than almost all other vintages,
-which show negative coefficients that are significantly different from
-0. A clear pecking order appears: \emph{Georgian} and \emph{Revival}
-buildings demand the highest premium \((+0.04)\), followed by \emph{Late
-Victorian/Edwardian} \((+0.01)\), \emph{Contemporary} (base),
-\emph{Early Victorian} \((-0.13)\), \emph{Interwar} \((-0.15)\) and
-\emph{Postwar} \((-0.22)\).
-
-The sample of ground truth images is not necessarily representative of
-the overall population so we re-estimate the model using predicted
-vintages for \emph{all} buildings for which we were able to extract
-usable pictures from Google Street View. Overall, the vintage
-coefficients become more positive relative to the base, implying that
-our automatic classification is biased and tends to classify
-unattractive buildings to the \emph{Contemporary} vintage. Reversely,
-more attractive buildings are disproportionally often misclassified as
+regression coefficients for the architects' classifications. The base
+style \emph{Contemporary} is more expensive than almost all other
+styles, which show negative coefficients that are significantly
+different from 0. A clear pecking order appears: \emph{Georgian} and
+\emph{Revival} buildings demand the highest premium \((+0.04)\),
+followed by \emph{Late Victorian/Edwardian} \((+0.01)\),
+\emph{Contemporary} (base), \emph{Early Victorian} \((-0.13)\),
+\emph{Interwar} \((-0.15)\) and \emph{Postwar} \((-0.22)\).
+
+The sample images classified by architects is not necessarily
+representative of the overall population so we re-estimate the model
+using machine classifications for \emph{all} buildings for which we were
+able to extract usable pictures from Google Street View. Overall, the
+style coefficients become more positive relative to the base, implying
+that our automatic classification is biased and tends to classify
+unattractive buildings to the \emph{Contemporary} style. Reversely, more
+attractive buildings are disproportionally often misclassified as
 \emph{Late Vic./Edw.}, pushing up the corresponding coefficient to
 \(0.11\). This bias vanishes in the third model, which uses only
-confidently predicted vintages (Column 3).
+confidently estimated machine styles (Column 3).
 
@@
 minimal. For newly built homes, no effect of \emph{Revival} architecture
-on price can be found, neither for ground truth classifications nor for
-high confidence ML estimates. After controlling for location, building
-characteristics and quality, buyers show no willingness to pay a premium
-for \emph{Revival} architecture.
+on price can be found for high confidence ML estimates, neither for
+classifications by machines nor by architects. After controlling for
+location, building characteristics and quality, buyers show no
+willingness to pay a premium for \emph{Revival} architecture (Columns 4
+and 6).
 
@@
 on the same street and within 100 m (\(\mathbf{VintNeigh}\)) does not
-change the pecking order of building vintages much (Table
+change the pecking order of building styles much (Table
 \ref{tab:hedreg}, Column 7). Neighboring styles are compared to the base
@@
 Table \ref{tab:hedregint} presents the \(\iota\) interaction
-coefficients (Eq. \ref{eq:hed}) for vintage-neighboring vintage
-combinations with sufficient numbers of observations (see Table
-\ref{tab:vintneigh}). The last row suggests that a general claim that
-\emph{Revival} neighbors exert positive externalities and increase
-property values relative to \emph{Contemporary} surroundings cannot be
-confirmed empirically. Again, we find no statistically significant
-difference.
+coefficients (Eq. \ref{eq:hed}) for style-neighboring style combinations
+with sufficient numbers of observations (see Table \ref{tab:vintneigh}).
+The last row suggests that a general claim that \emph{Revival} neighbors
+exert positive externalities and increase property values relative to
+\emph{Contemporary} surroundings cannot be confirmed empirically. Again,
+we find no statistically significant difference.
 
@@
 have been classified by architecture experts into relevant architectural
-styles or vintages. We subsequently trained a neural network classifier
-to automatically classify all residential buildings of a mid-sized
-English city into architectural styles or vintages. The suggested
-classifier is trained on feature vectors of buildings and their nearest
-neighbors to exploit spatial correlation in observed classifications.
+styles. We subsequently trained a neural network classifier to
+automatically classify all residential buildings of a mid-sized English
+city into architectural styles. The suggested classifier is trained on
+feature vectors of buildings and their nearest neighbors to exploit
+spatial correlation in observed classifications.
 
 The large ground truth data set allows for a comparison of human expert
-classifications with predictions made by ML classifiers. Poor image
-quality, for instance obstructed views or the lack of informative
-features such as windows, is correlated with misclassifications.
-Importantly, for cases in which the ML classifiers are relatively
-indecisive between classes, visual cues that are correlated with vintage
-but not part of a building's architecture (for instance trees or cars)
-bias the estimates. Fore these less certain cases, more valuable homes
-are systematically more likely to be classified as e.g. \emph{Late
-Victorian/Edw.} and less likely to be considered \emph{Contemporary}. A
-follow up study could investigate which elements in the building
-pictures lead to the misclassifications (Ribeiro, Singh, and Guestrin
-2016). Given the danger of systematic biases, one should remain wary of
-ML estimates derived from ground truth data sizable enough to train
-models -- but too small to investigate any biases.
+versus machine classifications. Poor image quality, for instance
+obstructed views or the lack of informative features such as windows, is
+correlated with misclassifications. Importantly, for cases in which the
+ML classifiers are relatively indecisive between classes, visual cues
+that are correlated with the exterior's style but not part of a
+building's architecture (for instance trees or cars) bias the estimates.
+Fore these less certain cases, more valuable homes are systematically
+more likely to be classified as e.g. \emph{Late Victorian/Edw.} and less
+likely to be considered \emph{Contemporary}. A follow up study could
+investigate which elements in the building pictures lead to the
+misclassifications (Ribeiro, Singh, and Guestrin 2016). Given the danger
+of systematic biases, one should remain wary of ML estimates derived
+from data sets sizable enough to train models -- but too small to
+investigate any biases.
 
@@
 \begin{figure}[htb!]
-\caption{Examples of Estimated Building Vintages}
+\caption{Examples of machine-based style classifications}
 \begin{tabular}{lllllll}

### 2019-09-14 text/manuscript_assa.Rmd
reorganised data section

@@
 ---
-title: "Machine Learning, Building Styles and Property Values"
+title: "Machine Learning, Architectural Styles and Property Values"
 author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
@@
 
-# Methodology
+# ML classification of building styles
 
@@
 
-Two final-year architectural students classified a large sub-sample of approximately 25,000 images from our data set of Cambridge houses.
-This is a much larger sample than needed in our case.
+Two final-year architectural students classified a large sub-sample of approximately 25,000 images from our data set of Cambridge houses.\footnote{The full set of classified images are available for download at the authors' websites.} This is a much larger sample than needed in our case.
 In our case, each category requires less than 250 observations to reach saturated training accuracy levels.
@@
 
-* an input layer the size of the feature vectors,
+* an input layer the size of the feature vectors, e.g. 2048 or 4096, respectively,
 
@@
 
-## Building style and property price
+# Architectural styles and property values
+
+## Residential transaction data
+
+Residential real estate transactions are public data in the UK, collected and published by the Land Registry [@LandRegistry2016a].
+The records include the date of transaction, price paid, street address, a classification of the property type (flat, detached, semi-detached, or terraced house), the estate type (freehold or leasehold) and an indicator for newly built properties.
+We select transactions from Cambridge proper which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000.
+Linking recently taken images to sales data from 24 years assumes that houses have not changed their architectural styles -- which seems reasonable.
+We are not aware of any conversions of just the exterior of buildings.
+In case of full redevelopments, we exclude any sales for a given address pre-dating the redevelopment, ensuring that a currently taken pictures represents the house at all included transactions.
+Table \ref{tab:sumstats} presents summary statistics for the sample.
+
+\begin{center}
+  -- Insert Table \ref{tab:sumstats} about here --
+\end{center}
+
+The Ordnance Survey *AddressBase* [@OrdnanceSurvey2017] links street addresses to building outlines on Ordnance Survey maps [@OrdnanceSurvey2017a], which allows us to calculate the buildings floor plate (in $m^2$) and to estimate the building's volume from digital elevation models [@EnvironmentAgency2015], as suggested by @Lindenthal2017.
+We control for the location of each building by calculating the distance to the city center proxied by Great St.
+Mary's Church, and non-parametrically by using 69 indicator variables for each of the smallest census tracts (*Lower Super Output Areas*, LSOA) subdividing Cambridge [@ONS2017].
+LSOAs typically have 1,000--3,000 residents and 400--1,200 households of comparable economic and socio-demographic characteristics [@ONS2017b].
+
+## Hedonic regression setup
 
@@
 
-Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Style}$ and the prevailing vintage of other buildings in the direct proximity $(\mathbf{StyleNeigh})$.
+Here, the natural logarithm of sales prices is explained by a linear combination of hedonic attributes described in vector $\mathbf{X}$, vectors of year $\mathbf{Y}$ and neighborhood $\bm{Loc}$ dummy variables and the building's estimated $\mathbf{Style}$ and the prevailing styles of other buildings in the direct proximity $(\mathbf{StyleNeigh})$.
+$\mathbf{Style\cdot StyleNeigh}$ is a vector of interaction terms for the building's and the  neighborhood's dominant style.
 The intercept is denoted by $\alpha$ while $\bm{\beta}$, $\bm{\delta}$, $\bm{\eta}$, $\bm{\iota}$, $\bm{\gamma}$ and $\bm{\lambda}$ are vectors of regression coefficients.
@@
 
-Are buildings with different appearances imperfect substitutes catering to multiple groups of households with distinct style preferences?
+Are buildings with different appearances imperfect substitutes catering to multiple groups of households with distinct style or vintage preferences?
 @Buitelaar2017 indicate that any premium for an architectural style must stem from either differences in construction prices (which they do not find in their Dutch sample) or from supply constraints, as new construction potentially does not capture the demand for traditional styles.
@@
 \ref{eq:hed} for a subset of newly constructed buildings will show whether construction prices or supply constraints for new homes built according to different architectural styles persist -- if too few vernacular buildings were built, prices should reflect such a shortage.
-
-# Data
-
-Residential real estate transactions are public data in the UK, collected and published by the Land Registry [@LandRegistry2016a].
-The records include the date of transaction, price paid, street address, a classification of the property type (flat, detached, semi-detached, or terraced house), the estate type (freehold or leasehold) and an indicator for newly built properties.
-We select transactions from Cambridge proper which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000.
-Linking recently taken images to sales data from 24 years assumes that houses have not changed their architectural styles -- which seems reasonable.
-We are not aware of any conversions of just the exterior of buildings.
-Full redevelopments did occur and we exclude sales for a given address pre-dating any redevelopment.
-Table \ref{tab:sumstats} presents summary statistics for the sample.
-
-The Ordnance Survey *AddressBase* [@OrdnanceSurvey2017] links street addresses to building outlines on Ordnance Survey maps [@OrdnanceSurvey2017a], which allows us to calculate the buildings floor plate (in $m^2$) and to estimate the building's volume from digital elevation models [@EnvironmentAgency2015], as suggested by @Lindenthal2017.
-We control for the location of each building by calculating the distance to the city center proxied by Great St.
-Mary's Church, and non-parametrically by using 69 indicator variables for each of the smallest census tracts (*Lower Super Output Areas*, LSOA) subdividing Cambridge [@ONS2017].
-LSOAs typically have 1,000--3,000 residents and 400--1,200 households of comparable economic and socio-demographic characteristics [@ONS2017b].
-
-Overall, we collect pictures of more than 48,000 distinct buildings from the Google Street View API.
-The subset of 25,000 pictures that has been classified by trained architects into the seven styles will serve as \emph{ground truth} for our study.
-Two additional categories identify buildings hidden by *greenery* or uninformative pictures featuring *plain walls*.
-The classified images are available at the authors' websites.
+Singling out new buildings crucially controls for the otherwise unobserved age of buildings, which is tightly intertwined with its aesthetics.
 
@@
 \begin{center}
-  -- Insert Table \ref{tab:sumstats} and Table \ref{tab:hedreg} about here --
+  -- Insert Table \ref{tab:hedreg} about here --
 \end{center}
@@
 \end{figure}
+
+\begin{table}[!htbp] \centering 
+  \caption{Summary statistics residential property transactions} 
+  \label{tab:sumstats} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\toprule
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\midrule
+Price & 23,768 & 253,646.20 & 170,987.20 & 10,000 & 127,000 & 326,374.8 & 1,000,000 \\ 
+Year & 23,768 & 2,004.89 & 6.59 & 1,995 & 1,999 & 2,010 & 2,018 \\ 
+ln(volume) & 23,768 & 286.00 & 188.14 & 0.00 & 215.50 & 370.89 & 1,926.45 \\ 
+ln(area) & 23,768 & 63.25 & 28.44 & 4.94 & 45.74 & 72.46 & 1,058.70 \\ 
+ln(dist. city center) & 23,768 & 2,477.63 & 1,007.55 & 112.78 & 1,652.39 & 3,166.05 & 5,023.62 \\ 
+New & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
+Type: detached & 23,768 & 0.13 & 0.34 & 0 & 0 & 0 & 1 \\ 
+Type: semi-detached & 23,768 & 0.35 & 0.48 & 0 & 0 & 1 & 1 \\ 
+Type: terraced & 23,768 & 0.52 & 0.50 & 0 & 0 & 1 & 1 \\ 
+Georgian & 23,768 & 0.03 & 0.16 & 0 & 0 & 0 & 1 \\ 
+Early Vic. & 23,768 & 0.15 & 0.36 & 0 & 0 & 0 & 1 \\ 
+Late Vic./Edw. & 23,768 & 0.21 & 0.40 & 0 & 0 & 0 & 1 \\ 
+Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
+Postwar & 23,768 & 0.23 & 0.42 & 0 & 0 & 0 & 1 \\ 
+Contemporary & 23,768 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
+Revival & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
+Neigh: Georgian & 23,768 & 0.02 & 0.12 & 0 & 0 & 0 & 1 \\ 
+Neigh: Early Vic. & 23,768 & 0.14 & 0.35 & 0 & 0 & 0 & 1 \\ 
+Neigh: Late V./Edw. & 23,768 & 0.22 & 0.41 & 0 & 0 & 0 & 1 \\ 
+Neigh: Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
+Neigh: Postwar & 23,768 & 0.25 & 0.43 & 0 & 0 & 1 & 1 \\ 
+Neigh: Contemporary & 23,768 & 0.02 & 0.15 & 0 & 0 & 0 & 1 \\ 
+Neigh: Revival & 23,768 & 0.03 & 0.18 & 0 & 0 & 0 & 1 \\ 
+\bottomrule
+\end{tabular} 
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\singlespacing
+\footnotesize \emph{Notes:} Summary statistics for sample of 23,768 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images.
+The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models, as suggested by @Lindenthal2017a.
+We control for the location of each building by calculating the distance to the city center proxied by Great St.
+Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA).
+Building styles based on machine classifications.
+\end{minipage}
+\end{table}
 
@@
 \begin{table}[!htbp] \centering 
-  \caption{Summary statistics residential property transactions} 
-  \label{tab:sumstats} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\toprule
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\midrule
-Price & 23,768 & 253,646.20 & 170,987.20 & 10,000 & 127,000 & 326,374.8 & 1,000,000 \\ 
-Year & 23,768 & 2,004.89 & 6.59 & 1,995 & 1,999 & 2,010 & 2,018 \\ 
-ln(volume) & 23,768 & 286.00 & 188.14 & 0.00 & 215.50 & 370.89 & 1,926.45 \\ 
-ln(area) & 23,768 & 63.25 & 28.44 & 4.94 & 45.74 & 72.46 & 1,058.70 \\ 
-ln(dist. city center) & 23,768 & 2,477.63 & 1,007.55 & 112.78 & 1,652.39 & 3,166.05 & 5,023.62 \\ 
-New & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
-Type: detached & 23,768 & 0.13 & 0.34 & 0 & 0 & 0 & 1 \\ 
-Type: semi-detached & 23,768 & 0.35 & 0.48 & 0 & 0 & 1 & 1 \\ 
-Type: terraced & 23,768 & 0.52 & 0.50 & 0 & 0 & 1 & 1 \\ 
-Georgian & 23,768 & 0.03 & 0.16 & 0 & 0 & 0 & 1 \\ 
-Early Vic. & 23,768 & 0.15 & 0.36 & 0 & 0 & 0 & 1 \\ 
-Late Vic./Edw. & 23,768 & 0.21 & 0.40 & 0 & 0 & 0 & 1 \\ 
-Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
-Postwar & 23,768 & 0.23 & 0.42 & 0 & 0 & 0 & 1 \\ 
-Contemporary & 23,768 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
-Revival & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
-Neigh: Georgian & 23,768 & 0.02 & 0.12 & 0 & 0 & 0 & 1 \\ 
-Neigh: Early Vic. & 23,768 & 0.14 & 0.35 & 0 & 0 & 0 & 1 \\ 
-Neigh: Late V./Edw. & 23,768 & 0.22 & 0.41 & 0 & 0 & 0 & 1 \\ 
-Neigh: Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
-Neigh: Postwar & 23,768 & 0.25 & 0.43 & 0 & 0 & 1 & 1 \\ 
-Neigh: Contemporary & 23,768 & 0.02 & 0.15 & 0 & 0 & 0 & 1 \\ 
-Neigh: Revival & 23,768 & 0.03 & 0.18 & 0 & 0 & 0 & 1 \\ 
-\bottomrule
-\end{tabular} 
-\begin{minipage}{\textwidth}
-\vspace{0.25cm}
-\singlespacing
-\footnotesize \emph{Notes:} Summary statistics for sample of 23,768 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images.
-The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models, as suggested by @Lindenthal2017a.
-We control for the location of each building by calculating the distance to the city center proxied by Great St.
-Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA).
-Building styles based on machine classifications.
-\end{minipage}
-\end{table}
-
-\begin{table}[!htbp] \centering 
   \caption{Hedonic Regression Estimates} 

### 2019-09-14 text/manuscript_assa.tex
reorganised data section

@@
 \hypersetup{unicode=true,
-            pdftitle={Machine Learning, Building Styles and Property Values},
+            pdftitle={Machine Learning, Architectural Styles and Property Values},
             pdfauthor={Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson (University of Alabama)},
@@
 
-  \title{Machine Learning, Building Styles and Property Values}
+  \title{Machine Learning, Architectural Styles and Property Values}
     \pretitle{\vspace{\droptitle}\centering\huge}
@@
   \postdate{\par}
-    \date{13 September 2019}
+    \date{14 September 2019}
 
@@
 
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
+\hypertarget{ml-classification-of-building-styles}{%
+\section{ML classification of building
+styles}\label{ml-classification-of-building-styles}}
 
@@
 Two final-year architectural students classified a large sub-sample of
-approximately 25,000 images from our data set of Cambridge houses. This
-is a much larger sample than needed in our case. In our case, each
+approximately 25,000 images from our data set of Cambridge
+houses.\footnote{The full set of classified images are available for download at the authors' websites.}
+This is a much larger sample than needed in our case. In our case, each
 category requires less than 250 observations to reach saturated training
@@
 \item
-  an input layer the size of the feature vectors,
+  an input layer the size of the feature vectors, e.g.~2048 or 4096,
+  respectively,
 \item
@@
 
-\hypertarget{building-style-and-property-price}{%
-\subsection{Building style and property
-price}\label{building-style-and-property-price}}
-
-Merging the machine's classification with sales data (Land Registry
-2017) we estimate a hedonic regression equation that establishes
-marginal prices for the building style (similar to Moorhouse and Smith
-1994; Asabere, Hachey, and Grubaugh 1989; Vandell and Lane 1989; Fuerst,
-McAllister, and Murray 2011; Plaut and Uzulena 2006), among other
-characteristics: \begin{equation} \label{eq:hed}
-  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i + \eta\mathbf{StyleNeigh}_i + \iota\mathbf{Style\cdot StyleNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
-\end{equation}
-
-Here, the natural logarithm of sales prices is explained by a linear
-combination of hedonic attributes described in vector \(\mathbf{X}\),
-vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
-variables and the building's estimated \(\mathbf{Style}\) and the
-prevailing vintage of other buildings in the direct proximity
-\((\mathbf{StyleNeigh})\). The intercept is denoted by \(\alpha\) while
-\(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\eta}\), \(\bm{\iota}\),
-\(\bm{\gamma}\) and \(\bm{\lambda}\) are vectors of regression
-coefficients. \(\epsilon\) is the IID error term. Heteroscedastic robust
-standard errors will be reported.
-
-Are buildings with different appearances imperfect substitutes catering
-to multiple groups of households with distinct style preferences?
-Buitelaar and Schilder (2017) indicate that any premium for an
-architectural style must stem from either differences in construction
-prices (which they do not find in their Dutch sample) or from supply
-constraints, as new construction potentially does not capture the demand
-for traditional styles. For Cambridge, new supply will inevitably be of
-either contemporary or revival style as historic vintages (and their
-styles), by definition, are not supplied any more. Estimating Eq.
-\ref{eq:hed} for a subset of newly constructed buildings will show
-whether construction prices or supply constraints for new homes built
-according to different architectural styles persist -- if too few
-vernacular buildings were built, prices should reflect such a shortage.
-
-\hypertarget{data}{%
-\section{Data}\label{data}}
+\hypertarget{architectural-styles-and-property-values}{%
+\section{Architectural styles and property
+values}\label{architectural-styles-and-property-values}}
+
+\hypertarget{residential-transaction-data}{%
+\subsection{Residential transaction
+data}\label{residential-transaction-data}}
 
@@
 seems reasonable. We are not aware of any conversions of just the
-exterior of buildings. Full redevelopments did occur and we exclude
-sales for a given address pre-dating any redevelopment. Table
-\ref{tab:sumstats} presents summary statistics for the sample.
+exterior of buildings. In case of full redevelopments, we exclude any
+sales for a given address pre-dating the redevelopment, ensuring that a
+currently taken pictures represents the house at all included
+transactions. Table \ref{tab:sumstats} presents summary statistics for
+the sample.
+
+\begin{center}
+  -- Insert Table \ref{tab:sumstats} about here --
+\end{center}
 
@@
 
-Overall, we collect pictures of more than 48,000 distinct buildings from
-the Google Street View API. The subset of 25,000 pictures that has been
-classified by trained architects into the seven styles will serve as
-\emph{ground truth} for our study. Two additional categories identify
-buildings hidden by \emph{greenery} or uninformative pictures featuring
-\emph{plain walls}. The classified images are available at the authors'
-websites.
+\hypertarget{hedonic-regression-setup}{%
+\subsection{Hedonic regression setup}\label{hedonic-regression-setup}}
+
+Merging the machine's classification with sales data (Land Registry
+2017) we estimate a hedonic regression equation that establishes
+marginal prices for the building style (similar to Moorhouse and Smith
+1994; Asabere, Hachey, and Grubaugh 1989; Vandell and Lane 1989; Fuerst,
+McAllister, and Murray 2011; Plaut and Uzulena 2006), among other
+characteristics: \begin{equation} \label{eq:hed}
+  ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i + \eta\mathbf{StyleNeigh}_i + \iota\mathbf{Style\cdot StyleNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+\end{equation}
+
+Here, the natural logarithm of sales prices is explained by a linear
+combination of hedonic attributes described in vector \(\mathbf{X}\),
+vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
+variables and the building's estimated \(\mathbf{Style}\) and the
+prevailing styles of other buildings in the direct proximity
+\((\mathbf{StyleNeigh})\). \(\mathbf{Style\cdot StyleNeigh}\) is a
+vector of interaction terms for the building's and the neighborhood's
+dominant style. The intercept is denoted by \(\alpha\) while
+\(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\eta}\), \(\bm{\iota}\),
+\(\bm{\gamma}\) and \(\bm{\lambda}\) are vectors of regression
+coefficients. \(\epsilon\) is the IID error term. Heteroscedastic robust
+standard errors will be reported.
+
+Are buildings with different appearances imperfect substitutes catering
+to multiple groups of households with distinct style or vintage
+preferences? Buitelaar and Schilder (2017) indicate that any premium for
+an architectural style must stem from either differences in construction
+prices (which they do not find in their Dutch sample) or from supply
+constraints, as new construction potentially does not capture the demand
+for traditional styles. For Cambridge, new supply will inevitably be of
+either contemporary or revival style as historic vintages (and their
+styles), by definition, are not supplied any more. Estimating Eq.
+\ref{eq:hed} for a subset of newly constructed buildings will show
+whether construction prices or supply constraints for new homes built
+according to different architectural styles persist -- if too few
+vernacular buildings were built, prices should reflect such a shortage.
+Singling out new buildings crucially controls for the otherwise
+unobserved age of buildings, which is tightly intertwined with its
+aesthetics.
 
@@
 \end{figure}
-
-\input{confusion_matrix.tex}
-
-\begin{table}[!htb] 
-\caption{Prediction certainty: Herfindahl index from ensemble model} 
-\label{tab:herftab} 
-\footnotesize
-\begin{tabular}{lccccccc}
-\toprule 
-  & \multicolumn{7}{c}{\emph{Architects}} \\ 
-  \cmidrule(lr){2-8} 
-& Georgian &  Early Vic. & Late V. /Edw. & Interwar & Postwar & Cont. & Revival \\
-
-Mean Herf. & 0.88 &  0.80 & 0.79 & 0.77 & 0.68 &  0.70 &  0.70 \\  
- \midrule 
-\emph{Machine} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
-\cmidrule(lr){2-8} 
-Georgian & -- & -0.21 (-9.87) & -0.28 (-13.11) & -0.33 (-9.95) & -0.27 (-6.30) & -0.25 (-7.97) & -0.25 (-7.54) \\
- Early Vic. & -0.22 (-6.28) &  -- & -0.19 (-19.20) & -0.31 (-13.70) & -0.21 (-10.05) & -0.21 (-7.53) & -0.15 (-3.84) \\
- Late V./Edw. & -0.36 (-5.89) & -0.24 (-18.03) &  -- & -0.26 (-21.88) & -0.23 (-9.08) & -0.24 (-4.96) & -0.16 (-4.33) \\
- Interwar & -0.12 (-1.55) & -0.32 (-12.77) & -0.24 (-19.87) &  -- & -0.13 (-22.67) & -0.25 (-12.58) & -0.16 (-6.49) \\
- Postwar & -0.51 (-33.71) & -0.30 (-6.24) & -0.36 (-13.13) & -0.26 (-34.82) & -- & -0.22 (-10.34) & -0.24 (-7.70) \\
- Cont. & -0.44 (-3.31) & -0.37 (-17.78) & -0.38 (-17.63) & -0.39 (-25.39) & -0.18 (-15.67) & -- & -0.19 (-7.71) \\
- Revival & -0.09 (-0.42) & -0.40 (-20.64) & -0.41 (-22.54) & -0.31 (-19.71) & -0.28 (-24.06) & -0.22 (-12.40) &  -- \\
-\bottomrule 
-\end{tabular}
-\begin{minipage}{\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 styles $s$ received, calculated as: $Herf_i=\sum_{s=1}^{s=7} (votes_s/votes_{all})^2$.
-A high score indicates high levels of consensus within the ensemble.
-The Herf.
-scores tend to be lower at off-diagonal cells, indicating lower consensus for misclassifications.
-\end{minipage}
-\end{table}
-
-\begin{table}[ht] 
-\centering 
- \caption{Mean Values for image quality variables, by style}
-
-\label{tab:imgqualsumstats}
-\begin{tabular}{lcccc} 
-\toprule 
-Architects' classifications & Share Blocked & House Area & Window Area & Image Offset \\ 
-\midrule
- Georgian & 0.07 & 0.81 & 0.15 & 0.07 \\ 
- Early Vic. & 0.06 & 0.86 & 0.16 & 0.05 \\ 
- Late V./Edw. & 0.11 & 0.84 & 0.17 & 0.08 \\ 
- Interwar & 0.19 & 0.70 & 0.11 & 0.12 \\ 
- Postwar & 0.16 & 0.64 & 0.07 & 0.11 \\ 
- Cont. & 0.09 & 0.72 & 0.11 & 0.09 \\ 
- Revival & 0.10 & 0.78 & 0.11 & 0.09 \\ 
- \bottomrule
-\end{tabular}
-\begin{minipage}{0.9\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated.
-Images taken not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
-\end{minipage}
-\end{table}
-
-\begin{table}[!htb] 
-\caption{Difference in photo characteristics by correctly and incorrectly classified images} 
-\label{tab:diffimgchar} 
-\centering 
-\begingroup\scriptsize 
-\begin{tabular}{lrrrrrrr}
-
-\toprule
-
-\emph{Machine} & \multicolumn{7}{c}{\emph{Architects}} \\ 
-  \cmidrule(lr){2-8} 
-& Georgian & Early Vic. & Late V./Edw. & Interwar & Postwar & Cont. & Revival \\
-
- \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel A: Total share of house blocked by vehicles or trees}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
-Georgian &  -- &  0 (0.16) & -0.03 (-1.37) & -0.07 (-2.16) & -0.06 (-0.91) & -0.02 (-0.86) &  0.02 (0.39) \\  
-  Early Vic. & -0.04 (-2.80) &  -- & -0.04 (-7.42) & -0.11 (-8.26) & -0.09 (-5.45) & -0.03 (-1.97) &  0.01 (0.47) \\  
-  Late V./Edw. &  0.03 (0.91) &  0.03 (2.55) &  -- &  0.01 (0.40) &  0.01 (0.57) &  0.01 (0.17) &  0.08 (1.89) \\  
-  Interwar &  0.17 (2.24) &  0.11 (3.71) &  0.09 (5.73) &  -- &  0.03 (4.16) &  0.18 (4.42) &  0.07 (2.40) \\  
-  Postwar &  0.13 (0.96) &  0.03 (1.44) &  0.11 (2.88) & -0.01 (-1.20) &  -- &  0.09 (3.39) &  0.04 (1.09) \\  
-  Cont. &  0.16 (0.77) & -0.02 (-1.91) &  0.03 (1.14) & -0.03 (-0.92) & -0.04 (-3.06) &  -- & -0.03 (-1.32) \\  
-  Revival &  0.18 (0.74) &  0.03 (0.92) &  0.01 (0.26) & -0.05 (-3.03) & -0.06 (-4.90) &  0.04 (2.02) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel B: Share of house area}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
-  Georgian &  -- & -0.11 (-3.43) & -0.10 (-2.67) &  0.09 (1.94) &  0.10 (0.96) &  0.11 (1.29) & -0.02 (-0.31) \\  
-  Early Vic. &  0.05 (1.30) &  -- &  0.03 (1.75) &  0.07 (2.45) &  0.18 (5.01) &  0.12 (2.19) &  0.05 (1.03) \\  
-  Late V./Edw. & -0.09 (-2.08) & -0.07 (-3.10) &  -- &  0.02 (1.07) &  0.08 (2.23) & -0.08 (-1.29) &  0.04 (0.71) \\  
-  Interwar &  0.08 (0.55) & -0.16 (-3.68) & -0.14 (-6.48) &  -- &  0.03 (2.92) & -0.04 (-1.03) & -0.09 (-2.65) \\  
-  Postwar & -0.33 (-1.98) & -0.24 (-3.82) & -0.18 (-3.25) & -0.05 (-4.60) &  -- & -0.12 (-2.78) & -0.16 (-4.57) \\  
-  Cont. & -0.21 (-1.58) & -0.16 (-2.99) & -0.15 (-3.45) & -0.02 (-0.55) &  0.01 (0.23) &  -- & -0.06 (-1.43) \\  
-  Revival & -0.03 (-0.15) & -0.04 (-0.69) & -0.11 (-2.70) &  0.06 (2.51) &  0.08 (3.30) &  0.05 (1.30) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel C: Share of window area}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
- Georgian &  -- & -0.06 (-6.02) & -0.02 (-1.10) & -0.02 (-1.92) &  0.03 (1.26) & -0.03 (-1.28) & -0.01 (-0.42) \\  
-  Early Vic. & -0.01 (-0.60) &  -- & -0.01 (-1.51) &  0.03 (2.72) &  0.04 (5.30) &  0.01 (0.70) &  0.02 (1.83) \\  
-  Late V./Edw. &  0 (0.09) & -0.02 (-2.67) &  -- &  0.04 (4.85) &  0.02 (1.81) &  0.02 (0.98) &  0.02 (1.59) \\  
-  Interwar & -0.03 (-0.92) & -0.09 (-10) & -0.08 (-13.20) &  -- &  0.01 (2.98) & -0.03 (-2.41) & -0.03 (-3.48) \\  
-  Postwar & -0.07 (-4.42) & -0.09 (-5.80) & -0.08 (-4.50) & -0.02 (-4.95) &  -- & -0.05 (-4.42) & -0.05 (-5.63) \\  
-  Cont. & -0.07 (-2.04) & -0.08 (-6.97) & -0.05 (-3.73) & -0.01 (-1.46) &  0.01 (2.50) &  -- & -0.02 (-2.58) \\  
-  Revival & -0.02 (-0.18) & -0.06 (-4.39) & -0.03 (-1.71) &  0.01 (1.04) &  0.02 (2.50) & -0.02 (-2.33) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel D: Image offset}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
- Georgian &  -- &  0.04 (5.44) &  0.02 (2.61) & -0.02 (-1.71) & -0.03 (-1.33) &  0.01 (1) &  0.01 (0.55) \\  
-  Early Vic. &  0.01 (0.64) &  -- & -0.02 (-6.59) & -0.03 (-3.82) & -0.04 (-4.98) & -0.01 (-0.93) & -0.03 (-2.78) \\  
-  Late V./Edw. &  0.04 (1.96) &  0.03 (4.68) &  -- & -0.01 (-1.25) & -0.02 (-2.14) &  0.01 (0.46) &  0 (0.25) \\  
-  Interwar &  0.03 (1.16) &  0.06 (6.28) &  0.05 (9.75) &  -- &  0.01 (2.35) &  0 (0.06) &  0.03 (3.19) \\  
-  Postwar &  0.04 (1.07) &  0.06 (3.31) &  0.04 (3.37) &  0 (1.11) &  -- &  0.02 (1.95) &  0.06 (4.20) \\  
-  Cont. &  0.08 (2.11) &  0.05 (3.87) &  0.04 (3.40) & -0.01 (-1.32) & -0.02 (-4.26) &  -- &  0 (0.20) \\  
-  Revival &  0 (0.02) &  0.03 (2.06) &  0.01 (1) & -0.01 (-1.85) & -0.01 (-1.02) &  0.02 (2.22) &  -- \\  
-\bottomrule
-
-\end{tabular} 
- \begin{minipage}{\textwidth} 
-\footnotesize 
-\vspace{0.25cm}
-\emph{Notes:} Cross-tabulation of photo characteristics by machine and architects' classifications.
-Off-diagonal elements ($Machine_{j}-Architects_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given classification by architects.
-For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic.
-to the set of correctly classified Georgian photos.
-The numbers in italic represent the mean characteristic value for each set of correctly classified photos.
-T-stats are in parenthesis.
-\end{minipage} 
-\endgroup 
-\end{table}
-
-\begin{figure}[htb!]
-\caption{Examples of machine-based style classifications}
-\begin{tabular}{lllllll}
-  \hline
-\emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interwar} & \emph{Postwar} & \emph{Contemp.} & \emph{Revival} \\ 
-  \hline
-\includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058205_KqBBtZS8ecncUe8oqjErqQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102767_u_7T3iAyG9xNgeN_ETY7aQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141478_FT9houQ2x66NPnNEGxTkvA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065714_pzExlR026vDKdQaJiLkdkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010137600_qYxYCsLRPpOfCyv8IjfnlA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677225_srJnz_31ujVFzn-xh_DYfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413689_VylY6Sy3vLvjqbtHeryMdQ.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010056385_XQsTJ2p5Te54CScFmblMHA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102769_c_e4WlmafqN2JXQ2ZhYEkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017237_yWs7fxQ0r8Ecx_ajaYc-rg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141115_xG0eSas79cN59fH4xvm5Yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023665_B2Is2WMV8SGjf7Tg9tLS7w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748070_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176986_bNOie2HS7GPQxPOtoevEHw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058145_xBAz4f8lI2MTivvvWv6wyQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103488_Y1L2niOkEGB1IKe4tsl1yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021367_JF-P4lOQQouZ6lHtM4J3oA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065349_HDvoqsiHXGx4xc62JSUNJA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009993819_748OTBKSFyJZU2DP7TbboQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677000_8l6ywNIej2136uZeb3qKqA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500088807_4vu-eMLHmhX3JmHNwyulmQ.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059206__nUymOPxCgpQugahoE7EPw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103870_ywN_BuvuLW6kbLLP0QgJMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017412_aOsldmaOT-MAce6q6qkmTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010107971_veilqmDOA-AfCuz4tWyg7g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025542_8rvXwCYBTCQu0eVM9nhN9Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555322_FffLx_XVBUOvZgiXRdSAnA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066754_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060140_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103819_mF6OqQrRTOlAoGdaraQsTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010097999_xTD3YceIrtPJZwPz5d0G6Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065347_pouLRqJd7pkk41jryvYQ4A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992776_QxMV8eRavS1riXfGzpSkBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555341_NVXmLF7mim1nGBZAdgw_ew.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500569086_g5RwBQ7D5edS2obfSogNIw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060139_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101711_wNQ403N-0pQd5fChNztfYA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021374_55tKverBLF4C0oo8U4XABg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065352_kDKqKaGpPwLeCBKJIQmeCg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010015484_zlR1vVJ7F0L6hcsFoZEydw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500548748_i6QAKtN2HhGsTVDBan2DKw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057955271_dMXMWNaIwddWdHidEuXowA.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060141_W3ZIE8mPY6LJb-_hKatlUw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103226_XO6qx_5Q9tNnNF958OBO3g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017109_MbGvl1GxhZjQ_qhD7puDBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009995496_N4NgCofyWASyYfcSPTjdBA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010068890_aswyTpwrE_IfdbINnYx7XQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010104229_qFV1-weLxn8SRW4Ib2wexQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010199676_smIagQ34MLIcJOrjvIu9uw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059966_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101704_ZQFxujswdAj7EGqRlp8sXQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017361_WxMCM3nht5EX_K9pqIK-kQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066620_4TqmJVLf3urSJo4ESg1zfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023689_KpXUKEdjoQ9swgoB2oXA3w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748058_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066718_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060813_VlKeIvrTv6UwOE9HD2LgJg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103859_P5YwPMree6QCxExkKqIzbw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141515_5g5Bhsn_4iW-90aFMrIaSA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066361_gliMrVbagcfkfZjLw4mKlw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500527045_p4zTtg8OzsbWjHYscCf-rA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748076_zDr74LLmVeyKyx7dPnXK6A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413682_drSMg0SQ9TU4Og8pXOgSxw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059967_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103388_CZH157SXYmF3dEVMKlWBfQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025644_bJ8zv37pDsP0CImvDMKC0w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010144910_COpJNwPw67J78VXCoN_HMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992797_JUTa4GsWaXplyCP6XeVAvw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500086356_n92s3snPX2zAwEiJnA-Pxg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176201_dDyXoyEbeMXUhCagwazbiA.jpg} \\
-   \hline
-\end{tabular}
-\label{fig:vint_examples}
-\begin{minipage}{0.7\textwidth}
-\footnotesize \emph{Notes:} For a brief discussion of the building styles see page \pageref{def_eras}.
-\end{minipage}
-\end{figure}
-
-\begin{figure}[htb!]
-  \caption{Difference of $F_1$-scores: spatial model vs. base model }
-  \centering
-    \includegraphics[width=0.8\textwidth]{figures/barplot_f1scores.jpg}
-  \label{fig:boxplot}
-\begin{minipage}{0.7\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} The bar plot shows difference in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
-a classifier using building level information only (red).
-\end{minipage}
-\end{figure}
-
-\begin{table}[htb!]
-\caption{Machine style classifications as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
-\label{tab:aic}
-\centering
-\begin{tabular}{lrrrr}
-  \toprule
- & \emph{No ML pred.} & \emph{Base pred.} & \emph{Spatial pred., all} & \emph{Spatial pred., high certainty} \\ 
-  \midrule
-  Georgian & 1,282 & 1,052 & 1,037 & 714 \\ 
-  Early Victorian & 10,231 & 7,597 & 7,259 & 4,594 \\ 
-  Late Vic./Edw. & 16,204 & 11,059 & 10,491 & 6,173 \\ 
-  Interwar & 18,333 & 14,471 & 13,637 & 7,670 \\ 
-  Postwar & 16,845 & 14,873 & 14,648 & 7,613 \\ 
-  Contemporary & 2,885 & 2,281 & 2,240 & 1,054 \\ 
-  Revival & 3,336 & 2,564 & 2,480 & 1,089 \\ 
-   \bottomrule
-\end{tabular}
-\begin{minipage}{0.7\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:}
-AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), the suggested spatial ML predictor (Column 3 \& 4).
-Across building styles, the AIC are lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4).
-This suggests that the spatial predictor performs best.
-\end{minipage}
-\end{table}
 
@@
 
+\input{confusion_matrix.tex}
+
+\begin{table}[!htb] 
+\caption{Prediction certainty: Herfindahl index from ensemble model} 
+\label{tab:herftab} 
+\footnotesize
+\begin{tabular}{lccccccc}
+\toprule 
+  & \multicolumn{7}{c}{\emph{Architects}} \\ 
+  \cmidrule(lr){2-8} 
+& Georgian &  Early Vic. & Late V. /Edw. & Interwar & Postwar & Cont. & Revival \\
+
+Mean Herf. & 0.88 &  0.80 & 0.79 & 0.77 & 0.68 &  0.70 &  0.70 \\  
+ \midrule 
+\emph{Machine} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
+\cmidrule(lr){2-8} 
+Georgian & -- & -0.21 (-9.87) & -0.28 (-13.11) & -0.33 (-9.95) & -0.27 (-6.30) & -0.25 (-7.97) & -0.25 (-7.54) \\
+ Early Vic. & -0.22 (-6.28) &  -- & -0.19 (-19.20) & -0.31 (-13.70) & -0.21 (-10.05) & -0.21 (-7.53) & -0.15 (-3.84) \\
+ Late V./Edw. & -0.36 (-5.89) & -0.24 (-18.03) &  -- & -0.26 (-21.88) & -0.23 (-9.08) & -0.24 (-4.96) & -0.16 (-4.33) \\
+ Interwar & -0.12 (-1.55) & -0.32 (-12.77) & -0.24 (-19.87) &  -- & -0.13 (-22.67) & -0.25 (-12.58) & -0.16 (-6.49) \\
+ Postwar & -0.51 (-33.71) & -0.30 (-6.24) & -0.36 (-13.13) & -0.26 (-34.82) & -- & -0.22 (-10.34) & -0.24 (-7.70) \\
+ Cont. & -0.44 (-3.31) & -0.37 (-17.78) & -0.38 (-17.63) & -0.39 (-25.39) & -0.18 (-15.67) & -- & -0.19 (-7.71) \\
+ Revival & -0.09 (-0.42) & -0.40 (-20.64) & -0.41 (-22.54) & -0.31 (-19.71) & -0.28 (-24.06) & -0.22 (-12.40) &  -- \\
+\bottomrule 
+\end{tabular}
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 styles $s$ received, calculated as: $Herf_i=\sum_{s=1}^{s=7} (votes_s/votes_{all})^2$.
+A high score indicates high levels of consensus within the ensemble.
+The Herf.
+scores tend to be lower at off-diagonal cells, indicating lower consensus for misclassifications.
+\end{minipage}
+\end{table}
+
+\begin{table}[ht] 
+\centering 
+ \caption{Mean Values for image quality variables, by style}
+
+\label{tab:imgqualsumstats}
+\begin{tabular}{lcccc} 
+\toprule 
+Architects' classifications & Share Blocked & House Area & Window Area & Image Offset \\ 
+\midrule
+ Georgian & 0.07 & 0.81 & 0.15 & 0.07 \\ 
+ Early Vic. & 0.06 & 0.86 & 0.16 & 0.05 \\ 
+ Late V./Edw. & 0.11 & 0.84 & 0.17 & 0.08 \\ 
+ Interwar & 0.19 & 0.70 & 0.11 & 0.12 \\ 
+ Postwar & 0.16 & 0.64 & 0.07 & 0.11 \\ 
+ Cont. & 0.09 & 0.72 & 0.11 & 0.09 \\ 
+ Revival & 0.10 & 0.78 & 0.11 & 0.09 \\ 
+ \bottomrule
+\end{tabular}
+\begin{minipage}{0.9\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated.
+Images taken not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
+\end{minipage}
+\end{table}
+
+\begin{table}[!htb] 
+\caption{Difference in photo characteristics by correctly and incorrectly classified images} 
+\label{tab:diffimgchar} 
+\centering 
+\begingroup\scriptsize 
+\begin{tabular}{lrrrrrrr}
+
+\toprule
+
+\emph{Machine} & \multicolumn{7}{c}{\emph{Architects}} \\ 
+  \cmidrule(lr){2-8} 
+& Georgian & Early Vic. & Late V./Edw. & Interwar & Postwar & Cont. & Revival \\
+
+ \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel A: Total share of house blocked by vehicles or trees}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+Georgian &  -- &  0 (0.16) & -0.03 (-1.37) & -0.07 (-2.16) & -0.06 (-0.91) & -0.02 (-0.86) &  0.02 (0.39) \\  
+  Early Vic. & -0.04 (-2.80) &  -- & -0.04 (-7.42) & -0.11 (-8.26) & -0.09 (-5.45) & -0.03 (-1.97) &  0.01 (0.47) \\  
+  Late V./Edw. &  0.03 (0.91) &  0.03 (2.55) &  -- &  0.01 (0.40) &  0.01 (0.57) &  0.01 (0.17) &  0.08 (1.89) \\  
+  Interwar &  0.17 (2.24) &  0.11 (3.71) &  0.09 (5.73) &  -- &  0.03 (4.16) &  0.18 (4.42) &  0.07 (2.40) \\  
+  Postwar &  0.13 (0.96) &  0.03 (1.44) &  0.11 (2.88) & -0.01 (-1.20) &  -- &  0.09 (3.39) &  0.04 (1.09) \\  
+  Cont. &  0.16 (0.77) & -0.02 (-1.91) &  0.03 (1.14) & -0.03 (-0.92) & -0.04 (-3.06) &  -- & -0.03 (-1.32) \\  
+  Revival &  0.18 (0.74) &  0.03 (0.92) &  0.01 (0.26) & -0.05 (-3.03) & -0.06 (-4.90) &  0.04 (2.02) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel B: Share of house area}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+  Georgian &  -- & -0.11 (-3.43) & -0.10 (-2.67) &  0.09 (1.94) &  0.10 (0.96) &  0.11 (1.29) & -0.02 (-0.31) \\  
+  Early Vic. &  0.05 (1.30) &  -- &  0.03 (1.75) &  0.07 (2.45) &  0.18 (5.01) &  0.12 (2.19) &  0.05 (1.03) \\  
+  Late V./Edw. & -0.09 (-2.08) & -0.07 (-3.10) &  -- &  0.02 (1.07) &  0.08 (2.23) & -0.08 (-1.29) &  0.04 (0.71) \\  
+  Interwar &  0.08 (0.55) & -0.16 (-3.68) & -0.14 (-6.48) &  -- &  0.03 (2.92) & -0.04 (-1.03) & -0.09 (-2.65) \\  
+  Postwar & -0.33 (-1.98) & -0.24 (-3.82) & -0.18 (-3.25) & -0.05 (-4.60) &  -- & -0.12 (-2.78) & -0.16 (-4.57) \\  
+  Cont. & -0.21 (-1.58) & -0.16 (-2.99) & -0.15 (-3.45) & -0.02 (-0.55) &  0.01 (0.23) &  -- & -0.06 (-1.43) \\  
+  Revival & -0.03 (-0.15) & -0.04 (-0.69) & -0.11 (-2.70) &  0.06 (2.51) &  0.08 (3.30) &  0.05 (1.30) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel C: Share of window area}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+ Georgian &  -- & -0.06 (-6.02) & -0.02 (-1.10) & -0.02 (-1.92) &  0.03 (1.26) & -0.03 (-1.28) & -0.01 (-0.42) \\  
+  Early Vic. & -0.01 (-0.60) &  -- & -0.01 (-1.51) &  0.03 (2.72) &  0.04 (5.30) &  0.01 (0.70) &  0.02 (1.83) \\  
+  Late V./Edw. &  0 (0.09) & -0.02 (-2.67) &  -- &  0.04 (4.85) &  0.02 (1.81) &  0.02 (0.98) &  0.02 (1.59) \\  
+  Interwar & -0.03 (-0.92) & -0.09 (-10) & -0.08 (-13.20) &  -- &  0.01 (2.98) & -0.03 (-2.41) & -0.03 (-3.48) \\  
+  Postwar & -0.07 (-4.42) & -0.09 (-5.80) & -0.08 (-4.50) & -0.02 (-4.95) &  -- & -0.05 (-4.42) & -0.05 (-5.63) \\  
+  Cont. & -0.07 (-2.04) & -0.08 (-6.97) & -0.05 (-3.73) & -0.01 (-1.46) &  0.01 (2.50) &  -- & -0.02 (-2.58) \\  
+  Revival & -0.02 (-0.18) & -0.06 (-4.39) & -0.03 (-1.71) &  0.01 (1.04) &  0.02 (2.50) & -0.02 (-2.33) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel D: Image offset}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+ Georgian &  -- &  0.04 (5.44) &  0.02 (2.61) & -0.02 (-1.71) & -0.03 (-1.33) &  0.01 (1) &  0.01 (0.55) \\  
+  Early Vic. &  0.01 (0.64) &  -- & -0.02 (-6.59) & -0.03 (-3.82) & -0.04 (-4.98) & -0.01 (-0.93) & -0.03 (-2.78) \\  
+  Late V./Edw. &  0.04 (1.96) &  0.03 (4.68) &  -- & -0.01 (-1.25) & -0.02 (-2.14) &  0.01 (0.46) &  0 (0.25) \\  
+  Interwar &  0.03 (1.16) &  0.06 (6.28) &  0.05 (9.75) &  -- &  0.01 (2.35) &  0 (0.06) &  0.03 (3.19) \\  
+  Postwar &  0.04 (1.07) &  0.06 (3.31) &  0.04 (3.37) &  0 (1.11) &  -- &  0.02 (1.95) &  0.06 (4.20) \\  
+  Cont. &  0.08 (2.11) &  0.05 (3.87) &  0.04 (3.40) & -0.01 (-1.32) & -0.02 (-4.26) &  -- &  0 (0.20) \\  
+  Revival &  0 (0.02) &  0.03 (2.06) &  0.01 (1) & -0.01 (-1.85) & -0.01 (-1.02) &  0.02 (2.22) &  -- \\  
+\bottomrule
+
+\end{tabular} 
+ \begin{minipage}{\textwidth} 
+\footnotesize 
+\vspace{0.25cm}
+\emph{Notes:} Cross-tabulation of photo characteristics by machine and architects' classifications.
+Off-diagonal elements ($Machine_{j}-Architects_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given classification by architects.
+For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic.
+to the set of correctly classified Georgian photos.
+The numbers in italic represent the mean characteristic value for each set of correctly classified photos.
+T-stats are in parenthesis.
+\end{minipage} 
+\endgroup 
+\end{table}
+
+\begin{figure}[htb!]
+\caption{Examples of machine-based style classifications}
+\begin{tabular}{lllllll}
+  \hline
+\emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interwar} & \emph{Postwar} & \emph{Contemp.} & \emph{Revival} \\ 
+  \hline
+\includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058205_KqBBtZS8ecncUe8oqjErqQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102767_u_7T3iAyG9xNgeN_ETY7aQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141478_FT9houQ2x66NPnNEGxTkvA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065714_pzExlR026vDKdQaJiLkdkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010137600_qYxYCsLRPpOfCyv8IjfnlA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677225_srJnz_31ujVFzn-xh_DYfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413689_VylY6Sy3vLvjqbtHeryMdQ.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010056385_XQsTJ2p5Te54CScFmblMHA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102769_c_e4WlmafqN2JXQ2ZhYEkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017237_yWs7fxQ0r8Ecx_ajaYc-rg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141115_xG0eSas79cN59fH4xvm5Yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023665_B2Is2WMV8SGjf7Tg9tLS7w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748070_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176986_bNOie2HS7GPQxPOtoevEHw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058145_xBAz4f8lI2MTivvvWv6wyQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103488_Y1L2niOkEGB1IKe4tsl1yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021367_JF-P4lOQQouZ6lHtM4J3oA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065349_HDvoqsiHXGx4xc62JSUNJA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009993819_748OTBKSFyJZU2DP7TbboQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677000_8l6ywNIej2136uZeb3qKqA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500088807_4vu-eMLHmhX3JmHNwyulmQ.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059206__nUymOPxCgpQugahoE7EPw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103870_ywN_BuvuLW6kbLLP0QgJMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017412_aOsldmaOT-MAce6q6qkmTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010107971_veilqmDOA-AfCuz4tWyg7g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025542_8rvXwCYBTCQu0eVM9nhN9Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555322_FffLx_XVBUOvZgiXRdSAnA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066754_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060140_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103819_mF6OqQrRTOlAoGdaraQsTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010097999_xTD3YceIrtPJZwPz5d0G6Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065347_pouLRqJd7pkk41jryvYQ4A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992776_QxMV8eRavS1riXfGzpSkBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555341_NVXmLF7mim1nGBZAdgw_ew.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500569086_g5RwBQ7D5edS2obfSogNIw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060139_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101711_wNQ403N-0pQd5fChNztfYA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021374_55tKverBLF4C0oo8U4XABg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065352_kDKqKaGpPwLeCBKJIQmeCg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010015484_zlR1vVJ7F0L6hcsFoZEydw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500548748_i6QAKtN2HhGsTVDBan2DKw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057955271_dMXMWNaIwddWdHidEuXowA.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060141_W3ZIE8mPY6LJb-_hKatlUw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103226_XO6qx_5Q9tNnNF958OBO3g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017109_MbGvl1GxhZjQ_qhD7puDBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009995496_N4NgCofyWASyYfcSPTjdBA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010068890_aswyTpwrE_IfdbINnYx7XQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010104229_qFV1-weLxn8SRW4Ib2wexQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010199676_smIagQ34MLIcJOrjvIu9uw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059966_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101704_ZQFxujswdAj7EGqRlp8sXQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017361_WxMCM3nht5EX_K9pqIK-kQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066620_4TqmJVLf3urSJo4ESg1zfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023689_KpXUKEdjoQ9swgoB2oXA3w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748058_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066718_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060813_VlKeIvrTv6UwOE9HD2LgJg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103859_P5YwPMree6QCxExkKqIzbw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141515_5g5Bhsn_4iW-90aFMrIaSA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066361_gliMrVbagcfkfZjLw4mKlw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500527045_p4zTtg8OzsbWjHYscCf-rA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748076_zDr74LLmVeyKyx7dPnXK6A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413682_drSMg0SQ9TU4Og8pXOgSxw.jpg} \\
+  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059967_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103388_CZH157SXYmF3dEVMKlWBfQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025644_bJ8zv37pDsP0CImvDMKC0w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010144910_COpJNwPw67J78VXCoN_HMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992797_JUTa4GsWaXplyCP6XeVAvw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500086356_n92s3snPX2zAwEiJnA-Pxg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176201_dDyXoyEbeMXUhCagwazbiA.jpg} \\
+   \hline
+\end{tabular}
+\label{fig:vint_examples}
+\begin{minipage}{0.7\textwidth}
+\footnotesize \emph{Notes:} For a brief discussion of the building styles see page \pageref{def_eras}.
+\end{minipage}
+\end{figure}
+
+\begin{figure}[htb!]
+  \caption{Difference of $F_1$-scores: spatial model vs. base model }
+  \centering
+    \includegraphics[width=0.8\textwidth]{figures/barplot_f1scores.jpg}
+  \label{fig:boxplot}
+\begin{minipage}{0.7\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} The bar plot shows difference in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
+a classifier using building level information only (red).
+\end{minipage}
+\end{figure}
+
+\begin{table}[htb!]
+\caption{Machine style classifications as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
+\label{tab:aic}
+\centering
+\begin{tabular}{lrrrr}
+  \toprule
+ & \emph{No ML pred.} & \emph{Base pred.} & \emph{Spatial pred., all} & \emph{Spatial pred., high certainty} \\ 
+  \midrule
+  Georgian & 1,282 & 1,052 & 1,037 & 714 \\ 
+  Early Victorian & 10,231 & 7,597 & 7,259 & 4,594 \\ 
+  Late Vic./Edw. & 16,204 & 11,059 & 10,491 & 6,173 \\ 
+  Interwar & 18,333 & 14,471 & 13,637 & 7,670 \\ 
+  Postwar & 16,845 & 14,873 & 14,648 & 7,613 \\ 
+  Contemporary & 2,885 & 2,281 & 2,240 & 1,054 \\ 
+  Revival & 3,336 & 2,564 & 2,480 & 1,089 \\ 
+   \bottomrule
+\end{tabular}
+\begin{minipage}{0.7\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:}
+AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), the suggested spatial ML predictor (Column 3 \& 4).
+Across building styles, the AIC are lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4).
+This suggests that the spatial predictor performs best.
+\end{minipage}
+\end{table}
+
 \begin{table}[!htbp] \centering 

### 2020-04-13 text/manuscript_assa.Rmd
Tables and Figures on separate pages
Are we back in the game?

@@
    - \usepackage[backend=bibtex, style=authoryear]{biblatex}
+
 fig_width: 6
@@
 bibliography: references.bib
-abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View.
-Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of these styles.
+abstract: "This paper introduces an algorithm that collects pictures of individual buildings from Google Street View.
+It then trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of these styles explicitly.
 Third, it investigates whether architectural styles influence house prices.
 For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings.
-Additionally, we are able to provide guidance on how to detect and overcome some of the limitations of machine learning methods through a large-scale comparison of predictions and expert classifications."
+Importantly, this paper explores how to detect and overcome biases in machine learning methods through a large-scale comparison of predictions and expert classifications, partially opening up the `black box' of automatic building classification systems."
 ---
 
-# Introduction
 \let\svthefootnote\thefootnote
@@
 \addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
+
+\newpage
+
+# Introduction
+
 If new developments were only pleasing to the eye, so Britain's *Building Better, Building Beautiful Commission* advising Government, nimbyism would cease and housing supply could finally reach the levels demanded by a growing and more affluent population [@economistlineofbeauty2018].
@@
 We then perform a viewshed analysis and identify which exterior walls are visible from the panorama point, ignoring any wall segments where the direct line of sight from the panorama point is obstructed by other buildings.
-We can then estimate the camera bearing (green line) and zoom factor, based on the fan of the lines of sight (in blue).\footnote{Code necessary to replicate this analysis is available from the author's GitHub.com code repositories: \href{https://github.com/thies}{https://github.com/thies}.}
+We can then estimate the camera bearing (green line) and zoom factor, based on the fan of the lines of sight (in blue).\footnote{Code necessary to replicate this analysis is available from the authors' GitHub.com code repositories.}
 
@@
 
+\newpage
+
 \begin{figure}[hbt]
@@
 \end{figure}
+
+\newpage
 
@@
 \footnotesize \emph{Notes:} Summary statistics for sample of 23,768 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images.
-The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models, as suggested by @Lindenthal2017a.
+The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models (Lindenthal, 2017b).
 We control for the location of each building by calculating the distance to the city center proxied by Great St.
@@
 
+\newpage
+
 \input{confusion_matrix.tex}
+
+\newpage
 
@@
 
+\newpage
+\clearpage
+
 \begin{table}[ht] 
@@
 \end{table}
+
+\newpage
+\clearpage
 
@@
 
+\newpage
+\clearpage
+
 \begin{figure}[htb!]
@@
 
+\newpage
+
 \begin{figure}[htb!]
@@
 \end{table}
+
+\newpage
 
@@
 
+\newpage
+
 \begin{table}[ht]
@@
 \end{minipage}
+\end{table}
 
-\end{table}
+\newpage
 

### 2020-04-13 text/manuscript_assa.tex
Tables and Figures on separate pages
Are we back in the game?

@@
   \postdate{\par}
-    \date{14 September 2019}
+    \date{13 April 2020}
 
@@
 \begin{abstract}
-This paper first introduces an algorithm that collects pictures of
-individual buildings from Google Street View. Second, it trains a deep
-convolutional neural network (CNN) to classify residential buildings
-into architectural styles, taking into account spatial dependencies of
-these styles. Third, it investigates whether architectural styles
+This paper introduces an algorithm that collects pictures of individual
+buildings from Google Street View. It then trains a deep convolutional
+neural network (CNN) to classify residential buildings into
+architectural styles, taking into account spatial dependencies of these
+styles explicitly. Third, it investigates whether architectural styles
 influence house prices. For re-sales, the architectural style is a
 significant determinant of transaction prices while no such effect is
-found for new buildings. Additionally, we are able to provide guidance
-on how to detect and overcome some of the limitations of machine
-learning methods through a large-scale comparison of predictions and
-expert classifications.
+found for new buildings. Importantly, this paper explores how to detect
+and overcome biases in machine learning methods through a large-scale
+comparison of predictions and expert classifications, partially opening
+up the `black box' of automatic building classification systems.
 \end{abstract}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
 
@@
 \addtocounter{footnote}{-1}\let\thefootnote\svthefootnote
+
+\newpage
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 U-shaped age function and distinct price discounts for postwar and
-contemporary styles (vis-à-vis more historic styles). Francke and Minne
-(2017) investigate the depreciation of residential real estate in the
-Netherlands and decompose land versus structure values singling out the
-effect of ``physical deterioration, functional obsolescence and and
+contemporary styles (vis-à-vis more historic styles). Francke and van de
+Minne (2017) investigate the depreciation of residential real estate in
+the Netherlands and decompose land versus structure values singling out
+the effect of ``physical deterioration, functional obsolescence and and
 vintage effects''. They find that buildings from the 1930s carry a
@@
 
-Unfortunately, the traditional approaches chosen by e.g. Buitelaar and
+Unfortunately, the traditional approaches chosen by e.g.~Buitelaar and
 Schilder (2017) or Ahlfeldt and Mastro (2012) do not scale well. Each
@@
 factor, based on the fan of the lines of sight (in
-blue).\footnote{Code necessary to replicate this analysis is available from the author's GitHub.com code repositories: \href{https://github.com/thies}{https://github.com/thies}.}
+blue).\footnote{Code necessary to replicate this analysis is available from the authors' GitHub.com code repositories.}
 
@@
 \emph{Late Victorian} style while starter homes are disproportionally
-more likely to be classified as e.g. \emph{Early Victorian}? We expect
+more likely to be classified as e.g.~\emph{Early Victorian}? We expect
 that in cases in which the ensemble provided a high confidence score,
@@
 Fore these less certain cases, more valuable homes are systematically
-more likely to be classified as e.g. \emph{Late Victorian/Edw.} and less
+more likely to be classified as e.g.~\emph{Late Victorian/Edw.} and less
 likely to be considered \emph{Contemporary}. A follow up study could
@@
 
+\newpage
+\clearpage
+
 \begin{table}[!htb] 
@@
 \end{minipage}
-
 \end{table}
+
+\newpage
 
@@
 through airborne laser scanning.'' \emph{Computers, Environment and
-Urban Systems} 39. Elsevier Ltd: 81--92.
+Urban Systems} 39: 81--92.
 \url{https://doi.org/10.1016/j.compenvurbsys.2013.01.001}.
@@
 qualities of the urban environment.'' \emph{Computers, Environment and
-Urban Systems} 65. The Authors: 113--25.
+Urban Systems} 65: 113--25.
 \url{https://doi.org/10.1016/j.compenvurbsys.2017.06.003}.
@@
 The Economist. 2018. ``The line of beauty.'' \emph{The Economist},
-November. London.
+November.
 \url{https://www.economist.com/britain/2018/11/17/how-to-defeat-nimbyism-build-more-beautiful-houses}.

### 2020-04-14 text/manuscript_jrefe.tex
TeX file generated

--- 2020-04-13 text/manuscript_assa.tex
@@
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+%
 \documentclass[]{article}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Machine Learning, Architectural Styles and Property Values},
-            pdfauthor={Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson (University of Alabama)},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \IfFileExists{parskip.sty}{%
@@
 }
+\usepackage{hyperref}
+\hypersetup{
+            pdftitle={Machine Learning, Architectural Styles and Property Values},
+            pdfauthor={Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson (University of Alabama)},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{0}
 % Redefines (sub)paragraphs to behave more like sections
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{Machine Learning, Architectural Styles and Property Values}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson
-(University of Alabama)}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{13 April 2020}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
@@
 \usepackage[backend=bibtex, style=authoryear]{biblatex}
+\usepackage[]{biblatex}
+\addbibresource{references.bib}
+
+\title{Machine Learning, Architectural Styles and Property Values}
+\author{Thies Lindenthal* (University of Cambridge) \& Erik B. Johnson
+(University of Alabama)}
+\date{14 April 2020}
 
@@
 Government, nimbyism would cease and housing supply could finally reach
-the levels demanded by a growing and more affluent population (The
-Economist 2018). The inaugural chair of this new commission boldly
-suggested that if we built \emph{``as our Georgian and Victorian
-forebears built} {[}\ldots{}{]}. \emph{All objections to new building
-would slip away in the sheer relief of the public''} (Scruton 2018).
-Even Prince Charles, in similar spirit, put forward ten principles for
-urban growth and architecture that emphasize tradition and aesthetics
-(HRH The Prince of Wales 2014). When governments and princes occupy
-themselves with beauty, economists surely may take a closer look as
-well. In this paper, we aim to identify the architectural styles of
-residential buildings using computer vision techniques and to
+the levels demanded by a growing and more affluent population
+\autocite{economistlineofbeauty2018}. The inaugural chair of this new
+commission boldly suggested that if we built \emph{``as our Georgian and
+Victorian forebears built} {[}\ldots{}{]}. \emph{All objections to new
+building would slip away in the sheer relief of the public''}
+\autocite{scruton2018}. Even Prince Charles, in similar spirit, put
+forward ten principles for urban growth and architecture that emphasize
+tradition and aesthetics \autocite{princecharles2014}. When governments
+and princes occupy themselves with beauty, economists surely may take a
+closer look as well. In this paper, we aim to identify the architectural
+styles of residential buildings using computer vision techniques and to
 empirically search for any transaction price premia associated with
@@
 for measuring previously unobserved characteristics of the urban
-environment. Naik et al. (2017) describe how neighborhood demographics
-may impact the physical appearance of neighborhoods. Gebru et al. (2017)
-use classified vehicle make and model information to predict income,
-race, education, and voting patterns at the precinct level. Glaeser et
-al. (2018) predict income in New York City. Naik, Raskar, and Hidalgo
-(2016) create a neighborhood safety based Streetscore which is shown to
-be highly correlated with neighborhood population density and household
-income. De Nadai et al. (2016) find that greenery and street facing
-windows contribute to a positive appearance of safety while Liu et al.
-(2017) evaluate the quality and upkeep of the built environment along
-Beijing's streets.
-
-Glaeser, Kincaid, and Naik (2018) push the level of observation from the
+environment. \textcite{Naik2017} describe how neighborhood demographics
+may impact the physical appearance of neighborhoods.
+\textcite{Gebru2017} use classified vehicle make and model information
+to predict income, race, education, and voting patterns at the precinct
+level. \textcite{Glaeser2016} predict income in New York City.
+\textcite{Naik2016AER} create a neighborhood safety based Streetscore
+which is shown to be highly correlated with neighborhood population
+density and household income. \textcite{Nadai2016} find that greenery
+and street facing windows contribute to a positive appearance of safety
+while \textcite{Liu2017} evaluate the quality and upkeep of the built
+environment along Beijing's streets.
+
+\textcite{GlaeserKincaidNaik2018} push the level of observation from the
 block, street, or street-section level to the individual
@@
 bi-directional: The appearance of buildings that went through
-foreclosure deteriorated significantly (Glaeser, Kincaid, and Naik
-2018).
+foreclosure deteriorated significantly
+\autocite{GlaeserKincaidNaik2018}.
 
@@
 influencing real estate prices {[}which{]} are constantly missing and
-are not accessible in official and mass appraiser databases'' (Helbich
-et al. 2013).
+are not accessible in official and mass appraiser databases''
+\autocite{Helbich2013}.
 
@@
 cocktail party conversation topic -- and they may also influence market
-prices. Using architectural assessments by human experts, Buitelaar and
-Schilder (2017) find a sizable premium of 5\% for new buildings in the
-Netherlands that refer to traditional styles and a staggering 15\%
-premium for new buildings that closely follow traditional shapes, facade
-composition and details. Their study carefully disentangles the
+prices. Using architectural assessments by human experts,
+\textcite{Buitelaar2017} find a sizable premium of 5\% for new buildings
+in the Netherlands that refer to traditional styles and a staggering
+15\% premium for new buildings that closely follow traditional shapes,
+facade composition and details. Their study carefully disentangles the
 architectural style from other unobserved characteristics such as
@@
 These controls are crucial, as earlier work has established that age and
-style variables tend to be highly correlated. Coulson and McMillen
-(2008), for instance, suggest a non-parametric estimator and establish a
+style variables tend to be highly correlated. \textcite{Coulson2008},
+for instance, suggest a non-parametric estimator and establish a
 U-shaped age function and distinct price discounts for postwar and
-contemporary styles (vis-à-vis more historic styles). Francke and van de
-Minne (2017) investigate the depreciation of residential real estate in
-the Netherlands and decompose land versus structure values singling out
-the effect of ``physical deterioration, functional obsolescence and and
-vintage effects''. They find that buildings from the 1930s carry a
-strong price premium.
+contemporary styles (vis-à-vis more historic styles).
+\textcite{Francke2017a} investigate the depreciation of residential real
+estate in the Netherlands and decompose land versus structure values
+singling out the effect of ``physical deterioration, functional
+obsolescence and and vintage effects''. They find that buildings from
+the 1930s carry a strong price premium.
 
@@
 analysis of the externalities of architecture. Buildings hardly ever
-stand in isolation and Ahlfeldt and Mastro (2012) investigate the
-influence a building's architecture exerts on its surroundings. They
-observe a positive price effect for residential buildings in the direct
-proximity of iconic homes by Frank Lloyd Wright in Oak Park, Illinois. A
+stand in isolation and \textcite{Ahlfeldt2012} investigate the influence
+a building's architecture exerts on its surroundings. They observe a
+positive price effect for residential buildings in the direct proximity
+of iconic homes by Frank Lloyd Wright in Oak Park, Illinois. A
 building's exterior does not need to be an architectural masterpiece to
@@
 to a wildly different neighboring shape, everything else remaining
-equal, is detrimental to property values (Lindenthal 2017a).
-
-Unfortunately, the traditional approaches chosen by e.g.~Buitelaar and
-Schilder (2017) or Ahlfeldt and Mastro (2012) do not scale well. Each
-observation has to be classified into architectural styles by a human
-expert, which is time-consuming and costly, imposing an upper limit on
-the number of observations and the level of detail captured for each
-observation in any given sample. Google Street View offers a solution to
-this nexus as it captures the images of almost all buildings in many
-cities around the world at high level of accuracy and detail. The
-challenge we address in this paper is to extract and utilize building
-level information from this ubiquitous sensor, using freely available
-deep learning techniques.
+equal, is detrimental to property values \autocite{Lindenthal2017b}.
+
+Unfortunately, the traditional approaches chosen by
+e.g.~\textcite{Buitelaar2017} or \textcite{Ahlfeldt2012} do not scale
+well. Each observation has to be classified into architectural styles by
+a human expert, which is time-consuming and costly, imposing an upper
+limit on the number of observations and the level of detail captured for
+each observation in any given sample. Google Street View offers a
+solution to this nexus as it captures the images of almost all buildings
+in many cities around the world at high level of accuracy and detail.
+The challenge we address in this paper is to extract and utilize
+building level information from this ubiquitous sensor, using freely
+available deep learning techniques.
 
@@
 For major US cities, the accuracy of building image search results is
-higher, which should help studies such as Glaeser, Kincaid, and Naik
-(2018).
+higher, which should help studies such as
+\textcite{GlaeserKincaidNaik2018}.
 
@@
 available by using LIDAR based building outlines instead, which would be
-in the spirit of Glaeser et al. (2018).
+in the spirit of \textcite{Glaeser2016}.
 
@@
 for each picture, using the \emph{Inception-v3} deep convolutional
-neural network (Szegedy et al. 2015). \emph{Inception-v3} has been
+neural network \autocite{Szegedy2015}. \emph{Inception-v3} has been
 trained for the ImageNet Large Scale Visual Recognition Challenge
@@
 
-Glaeser, Kincaid, and Naik (2018) rely on an different ILSVRC
-competitor, \emph{Resnet-101} (He et al. 2016). They reduce the
+\textcite{GlaeserKincaidNaik2018} rely on an different ILSVRC
+competitor, \emph{Resnet-101} \autocite{He2016}. They reduce the
 extracted feature vectors to lower dimensionality (1024 to 100
@@
 building styles, similar to spatially correlated land cover
-classifications in Ghimire, Rogan, and Miller (2010).
+classifications in \textcite{Ghimire2010a}.
 
@@
 factors might tilt the scale towards an incorrect class. A sizable
-difference in estimated marginal prices for machine's classifications
+difference in estimated marginal prices for machine classifications
 versus the estimates for architects' classifications in the subsequent
@@
 Residential real estate transactions are public data in the UK,
-collected and published by the Land Registry (Land Registry 2017). The
-records include the date of transaction, price paid, street address, a
-classification of the property type (flat, detached, semi-detached, or
-terraced house), the estate type (freehold or leasehold) and an
-indicator for newly built properties. We select transactions from
-Cambridge proper which were recorded between January 1995 and October
-2018, excluding any leaseholds, flats and properties classified as type
-``other'', and sales with prices below £50,000 or in excess of
-£2,000,000. Linking recently taken images to sales data from 24 years
-assumes that houses have not changed their architectural styles -- which
-seems reasonable. We are not aware of any conversions of just the
-exterior of buildings. In case of full redevelopments, we exclude any
-sales for a given address pre-dating the redevelopment, ensuring that a
-currently taken pictures represents the house at all included
-transactions. Table \ref{tab:sumstats} presents summary statistics for
-the sample.
+collected and published by the Land Registry
+\autocite{LandRegistry2016a}. The records include the date of
+transaction, price paid, street address, a classification of the
+property type (flat, detached, semi-detached, or terraced house), the
+estate type (freehold or leasehold) and an indicator for newly built
+properties. We select transactions from Cambridge which were recorded
+between January 1995 and October 2018, excluding any leaseholds, flats
+and properties classified as type ``other'', and sales with prices below
+£50,000 or in excess of £2,000,000. Linking recently taken images to
+sales data from 24 years assumes that houses have not changed their
+architectural styles -- which seems reasonable. We are not aware of any
+conversions of just the exterior of buildings. In case of full
+redevelopments, we exclude any sales for a given address pre-dating the
+redevelopment, ensuring that a currently taken picture represents the
+house at all included transactions. Table \ref{tab:sumstats} presents
+summary statistics for the sample.
 
@@
 
-The Ordnance Survey \emph{AddressBase} (Ordnance Survey 2017a) links
-street addresses to building outlines on Ordnance Survey maps (Ordnance
-Survey 2017b), which allows us to calculate the buildings floor plate
-(in \(m^2\)) and to estimate the building's volume from digital
-elevation models (Environment Agency 2015), as suggested by Lindenthal
-(2017b). We control for the location of each building by calculating the
-distance to the city center proxied by Great St.~Mary's Church, and
-non-parametrically by using 69 indicator variables for each of the
-smallest census tracts (\emph{Lower Super Output Areas}, LSOA)
-subdividing Cambridge (Office for National Statistics 2019). LSOAs
+The Ordnance Survey \emph{AddressBase} \autocite{OrdnanceSurvey2017}
+links street addresses to building outlines on Ordnance Survey maps
+\autocite{OrdnanceSurvey2017a}, which allows us to calculate the
+buildings floor plate (in \(m^2\)) and to estimate the building's volume
+from digital elevation models \autocite{EnvironmentAgency2015}, as
+suggested by \textcite{Lindenthal2017}. We control for the location of
+each building by calculating the distance to the city center proxied by
+Great St.~Mary's Church, and non-parametrically by using 69 indicator
+variables for each of the smallest census tracts (\emph{Lower Super
+Output Areas}, LSOA) subdividing Cambridge \autocite{ONS2017}. LSOAs
 typically have 1,000--3,000 residents and 400--1,200 households of
-comparable economic and socio-demographic characteristics (Office for
-National Statistics 2017).
+comparable economic and socio-demographic characteristics
+\autocite{ONS2017b}.
 
@@
 
-Merging the machine's classification with sales data (Land Registry
-2017) we estimate a hedonic regression equation that establishes
-marginal prices for the building style (similar to Moorhouse and Smith
-1994; Asabere, Hachey, and Grubaugh 1989; Vandell and Lane 1989; Fuerst,
-McAllister, and Murray 2011; Plaut and Uzulena 2006), among other
-characteristics: \begin{equation} \label{eq:hed}
+Merging the machine's classification with sales data
+\autocite{LandRegistry2016a} we estimate a hedonic regression equation
+that establishes marginal prices for the building style
+\autocites[similar
+to][]{Moorhouse1994}{Asabere1989}{Vandell1989}{Fuerst2011}{Plaut2006},
+among other characteristics: \begin{equation} \label{eq:hed}
   ln(Price_i) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i + \eta\mathbf{StyleNeigh}_i + \iota\mathbf{Style\cdot StyleNeigh}_i  +\gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
@@
 \(\bm{\gamma}\) and \(\bm{\lambda}\) are vectors of regression
-coefficients. \(\epsilon\) is the IID error term. Heteroscedastic robust
-standard errors will be reported.
+coefficients. \(\epsilon\) is the IID error term. Heteroscedasticity
+robust standard errors will be reported.
 
@@
 to multiple groups of households with distinct style or vintage
-preferences? Buitelaar and Schilder (2017) indicate that any premium for
-an architectural style must stem from either differences in construction
+preferences? \textcite{Buitelaar2017} indicate that any premium for an
+architectural style must stem from either differences in construction
 prices (which they do not find in their Dutch sample) or from supply
@@
 whether construction prices or supply constraints for new homes built
-according to different architectural styles persist -- if too few
+according to different architectural styles prevail -- if too few
 vernacular buildings were built, prices should reflect such a shortage.
 Singling out new buildings crucially controls for the otherwise
-unobserved age of buildings, which is tightly intertwined with its
-aesthetics.
+unobserved age of these buildings, which is tightly intertwined with
+their aesthetics.
 
@@
 Figure \ref{fig:vint_examples} displays the pictures which carry the
-highest out-of-sample scores for each style The model is clearly able to
-differentiate based on small cues, even when only parts of the facade
+highest out-of-sample scores for each style. The model is clearly able
+to differentiate based on small cues, even when only parts of the facade
 are captured on the picture.
@@
 
-The majority of misclassification is concentrated in temporally adjacent
-eras: 10 percent of \emph{Late Victorian/Edwardian} buildings are
-labelled as \emph{Early Victorian} or 18 percent of \emph{Postwar}
+The majority of misclassifications is concentrated in temporally
+adjacent eras: 10 percent of \emph{Late Victorian/Edwardian} buildings
+are labelled as \emph{Early Victorian} or 18 percent of \emph{Postwar}
 buildings are erroneously regarded as stemming from the \emph{Interwar}
@@
 
-The sample images classified by architects is not necessarily
+The sample of images classified by architects is not necessarily
 representative of the overall population so we re-estimate the model
@@
 style coefficients become more positive relative to the base, implying
-that our automatic classification is biased and tends to classify
-unattractive buildings to the \emph{Contemporary} style. Reversely, more
-attractive buildings are disproportionally often misclassified as
-\emph{Late Vic./Edw.}, pushing up the corresponding coefficient to
-\(0.11\). This bias vanishes in the third model, which uses only
-confidently estimated machine styles (Column 3).
+that our automatic classification is biased and tends to classify bland
+or low quality buildings to the \emph{Contemporary} style. Reversely,
+more attractive or higher quality buildings are disproportionately often
+misclassified as \emph{Late Vic./Edw.}, pushing up the corresponding
+coefficient to \(0.11\). This bias vanishes in the third model, which
+uses only confidently estimated machine styles (Column 3).
 
 Models 4--6 follow the same logic as 1--3 but are estimated for
-\emph{new} buildings only. Basically this contrasts houses which might
-\emph{look} different from the street, having either contemporary or
-revival facades, but which are all modern homes at their core.
-Differences in e.g.~materials, floor plans, green space and gardens are
-minimal. For newly built homes, no effect of \emph{Revival} architecture
-on price can be found for high confidence ML estimates, neither for
-classifications by machines nor by architects. After controlling for
-location, building characteristics and quality, buyers show no
-willingness to pay a premium for \emph{Revival} architecture (Columns 4
-and 6).
+\emph{new} buildings only, which are either in the contemporary or the
+revival style. Basically this contrasts houses which might \emph{look}
+different from the street, having either contemporary or revival
+facades, but which are all modern homes at their core. Differences in
+e.g.~materials, floor plans, green space and gardens are minimal. For
+newly built homes, no effect of \emph{Revival} architecture on price can
+be found for high confidence ML estimates, neither for classifications
+by machines nor by architects. After controlling for location, building
+characteristics and quality, buyers show no willingness to pay a premium
+for \emph{Revival} architecture (Columns 4 and 6).
 
 Introducing a variable capturing the most prominent style of buildings
-on the same street and within 100 m (\(\mathbf{VintNeigh}\)) does not
+on the same street and within 100 m (\(\mathbf{StyleNeigh}\)) does not
 change the pecking order of building styles much (Table
@@
 negative coefficients on dissimilar neighboring styles support a finding
-by Lindenthal (2017b) that shows that a harmonious match of a building's
-shape with its direct environment leads to a price premium -- or a
-discount in case of shape mismatches. In relative terms, \emph{Postwar}
-buildings are the least popular neighbors. The difference between
-\emph{Revival} and \emph{Contemporary} neighbors is not statistically
-significant. We fail to find evidence in favor of positive externalities
-from revival architecture. Everything else equal, buildings within
-ensembles of \emph{Contemporary} generally do not achieve higher
-transaction prices than buildings in more historic areas (as Table
-\ref{tab:comb} will confirm later).
+by \textcite{Lindenthal2017} that shows that a harmonious match of a
+building's shape with its direct environment leads to a price premium --
+or a discount in case of shape mismatches. In relative terms,
+\emph{Postwar} buildings are the least popular neighbors. The difference
+between \emph{Revival} and \emph{Contemporary} neighbors is not
+statistically significant. We fail to find evidence in favor of positive
+externalities from revival architecture. Everything else equal,
+buildings within ensembles of \emph{Contemporary} generally do not
+achieve higher transaction prices than buildings in more historic areas
+(as Table \ref{tab:comb} will confirm later).
 
@@
 building's architecture (for instance trees or cars) bias the estimates.
-Fore these less certain cases, more valuable homes are systematically
+For these less certain cases, more valuable homes are systematically
 more likely to be classified as e.g.~\emph{Late Victorian/Edw.} and less
@@
 investigate which elements in the building pictures lead to the
-misclassifications (Ribeiro, Singh, and Guestrin 2016). Given the danger
-of systematic biases, one should remain wary of ML estimates derived
-from data sets sizable enough to train models -- but too small to
-investigate any biases.
+misclassifications \autocite{Ribeiro2016}. Given the danger of
+systematic biases, one should remain wary of ML estimates derived from
+data sets sizable enough to train models -- but too small to investigate
+any biases.
 
@@
 quality and location of buildings. This applies to both direct price
-effects but also indirect effects of a buildings appearance on the value
-of neighboring homes. Further work will extend the spatial scope of the
-study area to the UK in general and to other countries.
+effects but also indirect effects of a building's appearance on the
+value of neighboring homes. Further work will extend the spatial scope
+of the study area to the UK in general and to other countries.
 
@@
 \footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated.
-Images taken not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
+Images not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
 \end{minipage}
@@
 to the set of correctly classified Georgian photos.
-The numbers in italic represent the mean characteristic value for each set of correctly classified photos.
 T-stats are in parenthesis.
@@
 \vspace{0.25cm}
-\footnotesize \emph{Notes:} The bar plot shows difference in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
+\footnotesize \emph{Notes:} The bar plot shows differences in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
 a classifier using building level information only (red).
@@
 \footnotesize \emph{Notes:}
-AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), the suggested spatial ML predictor (Column 3 \& 4).
+AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), and the suggested spatial ML predictor (Column 3 \& 4).
 Across building styles, the AIC are lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4).
@@
 
-\hypertarget{bibliography}{%
-\section*{Bibliography}\label{bibliography}}
-\addcontentsline{toc}{section}{Bibliography}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Ahlfeldt2012}{}%
-Ahlfeldt, Gabriel, and Alexandra Mastro. 2012. ``Valuing Iconic Design:
-Frank Lloyd Wright Architecture in Oak Park, Illinois.'' \emph{Housing
-Studies} 27 (8): 1079--99.
-\url{https://doi.org/10.1080/02673037.2012.728575}.
-
-\leavevmode\hypertarget{ref-Asabere1989}{}%
-Asabere, Paul K., George Hachey, and Steven Grubaugh. 1989.
-``Architecture , Historic Zoning , and the Value of Homes.''
-\emph{Journal of Real Estate Finance and Economics} 2 (3): 181--95.
-\url{https://doi.org/10.1007/BF00152347}.
-
-\leavevmode\hypertarget{ref-Buitelaar2017}{}%
-Buitelaar, Edwin, and Frans Schilder. 2017. ``The Economics of Style:
-Measuring the Price Effect of Neo-Traditional Architecture in Housing.''
-\emph{Real Estate Economics} 45 (1): 7--27.
-\url{https://doi.org/10.1111/1540-6229.12137}.
-
-\leavevmode\hypertarget{ref-Coulson2008}{}%
-Coulson, N. Edward, and Daniel P. McMillen. 2008. ``Estimating time, age
-and vintage effects in housing prices.'' \emph{Journal of Housing
-Economics} 17 (2): 138--51.
-\url{https://doi.org/10.1016/j.jhe.2008.03.002}.
-
-\leavevmode\hypertarget{ref-Nadai2016}{}%
-De Nadai, Marco, Radu L. Vieriu, Gloria Zen, Stefan Dragicevic, Nikhil
-Naik, Michele Caraviello, Cesar A. Hidalgo, Nicu Sebe, and Bruno Lepri.
-2016. ``Are Safer Looking Neighborhoods More Lively? A Multimodal
-Investigation into Urban Life,'' August.
-\url{http://arxiv.org/abs/1608.00462}.
-
-\leavevmode\hypertarget{ref-EnvironmentAgency2015}{}%
-Environment Agency. 2015. ``LIDAR Composite DSM - 1m.''
-\url{https://data.gov.uk/dataset/lidar-composite-dsm-1m1}.
-
-\leavevmode\hypertarget{ref-Francke2017a}{}%
-Francke, Marc K., and Alex M. van de Minne. 2017. ``Land, Structure and
-Depreciation.'' \emph{Real Estate Economics} 45 (2): 415--51.
-\url{https://doi.org/10.1111/1540-6229.12146}.
-
-\leavevmode\hypertarget{ref-Fuerst2011}{}%
-Fuerst, Franz, Patrick McAllister, and Claudia B Murray. 2011.
-``Designer buildings: estimating the economic value of `signature'
-architecture.'' \emph{Environment and Planning A} 43 (1): 166--84.
-\url{https://doi.org/10.1068/a43270}.
-
-\leavevmode\hypertarget{ref-Gebru2017}{}%
-Gebru, Timnit, Jonathan Krause, Yilun Wang, Duyun Chen, Jia Deng, Erez
-Lieberman Aiden, and Li Fei-Fei. 2017. ``Using Deep Learning and Google
-Street View to Estimate the Demographic Makeup of the US.'' \emph{PNAS}
-114 (50): 13108--13. \url{https://doi.org/10.1073/pnas.1700035114}.
-
-\leavevmode\hypertarget{ref-Ghimire2010a}{}%
-Ghimire, B., J. Rogan, and J. Miller. 2010. ``Contextual land-cover
-classification: Incorporating spatial dependence in land-cover
-classification models using random forests and the Getis statistic.''
-\emph{Remote Sensing Letters} 1 (1): 45--54.
-\url{https://doi.org/10.1080/01431160903252327}.
-
-\leavevmode\hypertarget{ref-GlaeserKincaidNaik2018}{}%
-Glaeser, Edward L., Michael Scott Kincaid, and Nikhil Naik. 2018.
-``Computer Vision and Real Estate: Do Looks Matter and Do Incentives
-Determine Looks?'' \url{http://www.nber.org/papers/w25174}.
-
-\leavevmode\hypertarget{ref-Glaeser2016}{}%
-Glaeser, Edward L., Scott Duke Kominers, Michael Luca, and Nikhil Naik.
-2018. ``Big Data and Big Cities: The Promises and Limitations of
-Improved Measures of Urban Life.'' \emph{Economic Inquiry} 56 (1):
-114--37. \url{https://doi.org/10.1111/ecin.12364}.
-
-\leavevmode\hypertarget{ref-He2016}{}%
-He, Kaiming, Xiangyu Zhang, Shaoqing Ren, and Jian Sun. 2016. ``Deep
-Residual Learning for Image Recognition.'' \emph{The IEEE Conference on
-Computer Vision and Pattern Recognition (CVPR)}, 770--78.
-
-\leavevmode\hypertarget{ref-Helbich2013}{}%
-Helbich, Marco, Andreas Jochem, Werner Mücke, and Bernhard Höfle. 2013.
-``Boosting the predictive accuracy of urban hedonic house price models
-through airborne laser scanning.'' \emph{Computers, Environment and
-Urban Systems} 39: 81--92.
-\url{https://doi.org/10.1016/j.compenvurbsys.2013.01.001}.
-
-\leavevmode\hypertarget{ref-princecharles2014}{}%
-HRH The Prince of Wales. 2014. ``Facing up to the future: Prince Charles
-on 21st century architecture.'' \emph{Architectural Review}, December.
-\url{https://www.architectural-review.com/essays/viewpoints/facing-up-to-the-future-prince-charles-on-21st-century-architecture/8674119.article}.
-
-\leavevmode\hypertarget{ref-LandRegistry2016a}{}%
-Land Registry. 2017. ``Price Paid Data.''
-\url{http://landregistry.data.gov.uk/app/ppd}.
-
-\leavevmode\hypertarget{ref-Lindenthal2017b}{}%
-Lindenthal, Thies. 2017a. ``Beauty in the Eye of the Home-Owner:
-Aesthetic Zoning and Residential Property Values.'' \emph{Real Estate
-Economics}, 1--26. \url{https://doi.org/10.1111/1540-6229.12204}.
-
-\leavevmode\hypertarget{ref-Lindenthal2017}{}%
----------. 2017b. \emph{Estimating Supply Elasticities for Residential
-Real Estate in the United Kingdom}. Comprehens. Elsevier Inc.
-\url{https://doi.org/https://doi.org/10.1016/B978-0-12-409548-9.09682-2}.
-
-\leavevmode\hypertarget{ref-Liu2017}{}%
-Liu, Lun, Elisabete A. Silva, Chunyang Wu, and Hui Wang. 2017. ``A
-machine learning-based method for the large-scale evaluation of the
-qualities of the urban environment.'' \emph{Computers, Environment and
-Urban Systems} 65: 113--25.
-\url{https://doi.org/10.1016/j.compenvurbsys.2017.06.003}.
-
-\leavevmode\hypertarget{ref-Moorhouse1994}{}%
-Moorhouse, John C., and Margaret Supplee Smith. 1994. ``The Market for
-Residential Architecture: 19th century Row Houses in Boston's South
-End.'' \emph{Journal of Urban Economics} 35 (3): 267--77.
-\url{https://doi.org/10.1006/juec.1994.1016}.
-
-\leavevmode\hypertarget{ref-Naik2017}{}%
-Naik, Nikhil, Scott Duke Kominers, Ramesh Raskar, Edward L. Glaeser, and
-César A. Hidalgo. 2017. ``Computer vision uncovers predictors of
-physical urban change.'' \emph{Proceedings of the National Academy of
-Sciences} 114 (29): 7571--6.
-\url{https://doi.org/10.1073/pnas.1619003114}.
-
-\leavevmode\hypertarget{ref-Naik2016AER}{}%
-Naik, Nikhil, Ramesh Raskar, and César A. Hidalgo. 2016. ``Cities Are
-Physical Too: Using Computer Vision to Measure the Quality and Impact of
-Urban Appearance.'' \emph{American Economic Review} 106 (5): 128--32.
-\url{https://doi.org/10.1257/aer.p20161030}.
-
-\leavevmode\hypertarget{ref-ONS2017b}{}%
-Office for National Statistics. 2017. ``A Beginner's Guide to UK
-Geography.''
-
-\leavevmode\hypertarget{ref-ONS2017}{}%
----------. 2019. ``Open Geography Portal -- 2011 Census Boundaries.''
-\url{https://www.ons.gov.uk/methodology/geography/ukgeographies/censusgeography}.
-
-\leavevmode\hypertarget{ref-OrdnanceSurvey2017}{}%
-Ordnance Survey. 2017a. ``AddressBase.''
-\url{https://www.ordnancesurvey.co.uk/business-and-government/help-and-support/products/addressbase-premium.html}.
-
-\leavevmode\hypertarget{ref-OrdnanceSurvey2017a}{}%
----------. 2017b. ``OS Maps Local.''
-\url{https://www.ordnancesurvey.co.uk/business-and-government/products/os-open-map-local.html}.
-
-\leavevmode\hypertarget{ref-Plaut2006}{}%
-Plaut, Steven, and Egita Uzulena. 2006. ``Architectural Design and the
-Value of Housing in Riga, Latvia.'' \emph{International Real Estate
-Review} 9 (1): 112--31.
-
-\leavevmode\hypertarget{ref-Ribeiro2016}{}%
-Ribeiro, Marco Tulio, Sameer Singh, and Carlos Guestrin. 2016. ``"Why
-Should I Trust You?" Explaining the Predictions of Any Classifier.'' In
-\emph{22nd Acm Sigkdd International Conference on Knowledge Discovery
-and Data Mining}, 1135-----1144. San Francisco.
-
-\leavevmode\hypertarget{ref-scruton2018}{}%
-Scruton, Roger. 2018. ``The Fabric of the City.'' Colin Amery Memorial
-Lecture. Policy Exchange.
-\url{https://policyexchange.org.uk/wp-content/uploads/2018/11/The-Fabric-of-the-City.pdf}.
-
-\leavevmode\hypertarget{ref-Szegedy2015}{}%
-Szegedy, Christian, Vincent Vanhoucke, Sergey Ioffe, Jonathon Shlens,
-and Zbigniew Wojna. 2015. ``Rethinking the Inception Architecture for
-Computer Vision.'' \url{https://doi.org/10.1109/CVPR.2016.308}.
-
-\leavevmode\hypertarget{ref-economistlineofbeauty2018}{}%
-The Economist. 2018. ``The line of beauty.'' \emph{The Economist},
-November.
-\url{https://www.economist.com/britain/2018/11/17/how-to-defeat-nimbyism-build-more-beautiful-houses}.
-
-\leavevmode\hypertarget{ref-Vandell1989}{}%
-Vandell, Kerry D., and Jonathan S. Lane. 1989. ``The Economics of
-Architecture and Urban Design: Some Preliminary Findings.'' \emph{AREUEA
-Journal} 17 (2): 235--60.
+\printbibliography[title=Bibliography]
 

### 2020-11-06 text/manuscript_assa.Rmd
Table updates

@@
 For close calls, however, where models within the ensemble cannot agree, other factors might tilt the scale towards an incorrect class.
-A sizable difference in estimated marginal prices for machine's classifications versus the estimates for architects' classifications in the subsequent hedonic regression (Eq.
+A sizable difference in estimated marginal prices for machine classifications versus the estimates for architects' classifications in the subsequent hedonic regression (Eq.
 \ref{eq:hed}, below) would indicate such a bias.
@@
 The records include the date of transaction, price paid, street address, a classification of the property type (flat, detached, semi-detached, or terraced house), the estate type (freehold or leasehold) and an indicator for newly built properties.
-We select transactions from Cambridge proper which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000.
+We select transactions from Cambridge which were recorded between January 1995 and October 2018, excluding any leaseholds, flats and properties classified as type "other", and sales with prices below £50,000 or in excess of £2,000,000.
 Linking recently taken images to sales data from 24 years assumes that houses have not changed their architectural styles -- which seems reasonable.
 We are not aware of any conversions of just the exterior of buildings.
-In case of full redevelopments, we exclude any sales for a given address pre-dating the redevelopment, ensuring that a currently taken pictures represents the house at all included transactions.
+In case of full redevelopments, we exclude any sales for a given address pre-dating the redevelopment, ensuring that a currently taken picture represents the house at all included transactions.
 Table \ref{tab:sumstats} presents summary statistics for the sample.
@@
 $\epsilon$ is the IID error term.
-Heteroscedastic robust standard errors will be reported.
+Heteroscedasticity robust standard errors will be reported.
 
@@
 Estimating Eq.
-\ref{eq:hed} for a subset of newly constructed buildings will show whether construction prices or supply constraints for new homes built according to different architectural styles persist -- if too few vernacular buildings were built, prices should reflect such a shortage.
-Singling out new buildings crucially controls for the otherwise unobserved age of buildings, which is tightly intertwined with its aesthetics.
+\ref{eq:hed} for a subset of newly constructed buildings will show whether construction prices or supply constraints for new homes built according to different architectural styles prevail -- if too few vernacular buildings were built, prices should reflect such a shortage.
+Singling out new buildings crucially controls for the otherwise unobserved age of these buildings, which is tightly intertwined with their aesthetics.
 
@@
 A visual inspection of classifications is additionally reassuring.
-Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each style The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.
+Figure \ref{fig:vint_examples} displays the pictures which carry the highest out-of-sample scores for each style.
+The model is clearly able to differentiate based on small cues, even when only parts of the facade are captured on the picture.
 
@@
 
-The majority of misclassification is concentrated in temporally adjacent eras: 10 percent of *Late Victorian/Edwardian* buildings are labelled as *Early Victorian* or 18 percent of *Postwar* buildings are erroneously regarded as stemming from the *Interwar* period.
+The majority of misclassifications is concentrated in temporally adjacent eras: 10 percent of *Late Victorian/Edwardian* buildings are labelled as *Early Victorian* or 18 percent of *Postwar* buildings are erroneously regarded as stemming from the *Interwar* period.
 Hardly ever is a contemporary building mistaken for a historic home.
@@
 
-The sample images classified by architects is not necessarily representative of the overall population so we re-estimate the model using machine classifications for *all* buildings for which we were able to extract usable pictures from Google Street View.
-Overall, the style coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify unattractive buildings to the *Contemporary* style.
-Reversely, more attractive buildings are disproportionally often misclassified as *Late Vic./Edw.*, pushing up the corresponding coefficient to $0.11$.
+The sample of images classified by architects is not necessarily representative of the overall population so we re-estimate the model using machine classifications for *all* buildings for which we were able to extract usable pictures from Google Street View.
+Overall, the style coefficients become more positive relative to the base, implying that our automatic classification is biased and tends to classify bland or low quality buildings to the *Contemporary* style.
+Reversely, more attractive or higher quality buildings are disproportionately often misclassified as *Late Vic./Edw.*, pushing up the corresponding coefficient to $0.11$.
 This bias vanishes in the third model, which uses only confidently estimated machine styles (Column 3).
 
-Models 4--6 follow the same logic as 1--3 but are estimated for *new* buildings only.
+Models 4--6 follow the same logic as 1--3 but are estimated for *new* buildings only, which are either in the contemporary or the revival style.
 Basically this contrasts houses which might *look* different from the street, having either contemporary or revival facades, but which are all modern homes at their core.
@@
 
-Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{VintNeigh}$) does not change the pecking order of building styles much (Table \ref{tab:hedreg}, Column 7).
+Introducing a variable capturing the most prominent style of buildings on the same street and within 100 m ($\mathbf{StyleNeigh}$) does not change the pecking order of building styles much (Table \ref{tab:hedreg}, Column 7).
 Neighboring styles are compared to the base case of a *Contemporary* house in a *Contemporary* street.
@@
 Importantly, for cases in which the ML classifiers are relatively indecisive between classes, visual cues that are correlated with the exterior's style but not part of a building's architecture (for instance trees or cars) bias the estimates.
-Fore these less certain cases, more valuable homes are systematically more likely to be classified as e.g.
+For these less certain cases, more valuable homes are systematically more likely to be classified as e.g.
 *Late Victorian/Edw.* and less likely to be considered *Contemporary*.
@@
 We do not find evidence for a preference of residents for specific architecture after controlling for quality and location of buildings.
-This applies to both direct price effects but also indirect effects of a buildings appearance on the value of neighboring homes.
+This applies to both direct price effects but also indirect effects of a building's appearance on the value of neighboring homes.
 Further work will extend the spatial scope of the study area to the UK in general and to other countries.

### 2020-11-06 text/manuscript_assa.tex
Table updates

@@
   \postdate{\par}
-    \date{13 April 2020}
+    \date{14 April 2020}
 
@@
 indicator for newly built properties. We select transactions from
-Cambridge proper which were recorded between January 1995 and October
-2018, excluding any leaseholds, flats and properties classified as type
+Cambridge which were recorded between January 1995 and October 2018,
+excluding any leaseholds, flats and properties classified as type
 ``other'', and sales with prices below £50,000 or in excess of
@@
 sales for a given address pre-dating the redevelopment, ensuring that a
-currently taken pictures represents the house at all included
+currently taken picture represents the house at all included
 transactions. Table \ref{tab:sumstats} presents summary statistics for

### 2020-11-06 R/regressions_hedonic_price.R

@@ -12,10 +12,10 @@ setwd("~/research/paper-uk-vintages/R/")
 paths <- list()
 local.paths <- TRUE
 if(local.paths){
-  paths[["full_samples"]] <- "~/db/paper-uk-vintages/pred_full_sample.csv"
-  paths[["preds"]] <- "~/db/paper-uk-vintages/predicted_styles.csv"
-  paths[["sales"]] <- "~/Dropbox (Cambridge University)/Cambridge/data/derived/sales_2018-10.csv"
-  paths[["lsoa"]] <- "~/Dropbox (Cambridge University)/Cambridge/data/derived/lsoa_x_toid.csv"
+  paths[["full_samples"]] <- "~/dropbox/paper-uk-vintages/pred_full_sample.csv"
+  paths[["preds"]] <- "~/dropbox/paper-uk-vintages/predicted_styles.csv"
+  paths[["sales"]] <- "~/dropbox/Cambridge/data/derived/sales_2018-10.csv"
+  paths[["lsoa"]] <- "~/dropbox/Cambridge/data/derived/lsoa_x_toid.csv"
 } else {
   paths[["full_samples"]] <- "https://www.dropbox.com/s/v26ofbxg2zmzbrp/pred_full_sample.csv?dl=1"
   paths[["preds"]] <- "https://www.dropbox.com/s/3ked11qizv37lpj/predicted_styles.csv?dl=1"
@@ -114,6 +114,7 @@ reverseRegressions <- function(){
 
 #========= 
 # find dominant style of homes on same street, within 100m  
+# (not very elegant code, admittedly)
 sales <- subset(sales, !is.na(centrX))
 dnn <- dnearneigh(as.matrix(sales[,c("centrX","centrY")]), 0, 100)
 sales$neigh_era <- NA
@@ -142,44 +143,59 @@ sales$true_era <- relevel( factor(sales$true_era), "f contemporary" )
 sales$true_era[sales$true_era =="w walls"] <- NA
 sales$true_era[sales$true_era =="x greenery"] <- NA
 
-sales$era <- sales$pred_era
-rs_reg[["hed.base"]] <- lm(log(price)~lsoa11cd+factor(year)+log(dist)+propertytype+log(area2D+1)+log(volum3D+1)+new+era, data=sales)
+
+
+regsample <- subset(sales, !is.na(pred_era) & ! is.na(true_era) & ! is.na(neigh_era))
[…]

### 2020-11-06 R/regressions_hedonic_price.R
maps added

@@ -112,6 +112,9 @@ reverseRegressions <- function(){
 
 
 
+
+
+
 #========= 
 # find dominant style of homes on same street, within 100m  
 # (not very elegant code, admittedly)
@@ -235,9 +238,19 @@ for(r in c("hed.base", "hed.base.true","hed.base.true.nolsoa","hed.base.pred","h
   rmse.set1[[r]] <- round( rmse[[r]], 3)
 }
 
+rs_reg.set2 <- list()
+rs_robustse.set2 <- list()
+rmse.set2 <- list()
+for(r in c("hed.base.true","hed.base.true.nolsoa") ){
+  rs_reg.set2[[r]] <-rs_reg[[r]] 
+  rs_robustse.set2[[r]] <-rs_robustse[[r]] 
+  rmse.set2[[r]] <- round( rmse[[r]], 3)
+}
+
+
 
 stargazer(rs_reg.set1,
-          #se=rs_robustse.set1,
+          se=rs_robustse.set1,
           dep.var.labels.include = FALSE,
           dep.var.caption = "Dependent variable: ln(price)",
           omit="year|lsoa|pred_era_neigh|:neigh_era|:nera",
@@ -266,13 +279,66 @@ stargazer(rs_reg.set1,
             c("RMSE", as.vector(unlist(rmse.set1)) ))
           )
 
+# for referee
+stargazer(rs_reg.set2,
+          se=rs_robustse.set2,
+          dep.var.labels.include = FALSE,
+          dep.var.caption = "Dependent variable: ln(price)",
+          omit="year|lsoa|pred_era_neigh|:neigh_era|:nera",
+          #type="text",
+          type="latex",
+          #out = "/home/thies/research/paper-uk-vintages/text/hed_reg_table_raw.set1.tex",
+          intercept.bottom=FALSE,
+          keep.stat=c("adj.rsq", "n"),
+          digits=2,
+          title="Hedonic Regression Estimates",
+          font.size="footnotesize",
+          label="tab:hedreg",
+          no.space=TRUE,
+          covariate.labels = c("Constant", 
+                               "ln(dist. city center)",
+                               "Type: semi-detached", "Type: terraced",
+                               "ln(area)", "ln(volume)",
+                               "New",
[…]

### 2020-11-08 R/regressions_hedonic_price.R
extensions for editor

@@ -465,13 +465,17 @@ xtable(tmp)
 
 ######### SUMSTATS TABLE
 
-sales.sumstat <- subset(sales, !is.na(pred_era))
+sales.sumstat <- subset(regsample)
 sales.sumstat$x <- NULL
 sales.sumstat$y <- NULL
 sales.sumstat$centrX <- NULL
 sales.sumstat$centrY <- NULL
 sales.sumstat$toid <- NULL
 sales.sumstat$toid_num <- NULL
+sales.sumstat$optional <- NULL
+sales.sumstat$misclassified <- NULL
+sales.sumstat$herf <- NULL
+
 
 sales.sumstat$newnum <- 0
 sales.sumstat$newnum[sales.sumstat$new == "Y"] <- 1
@@ -496,12 +500,12 @@ sales.sumstat <- cbind(sales.sumstat, dummies)
 stargazer(sales.sumstat, type="latex",
           title="Summary statistics residential property transactions",
           covariate.labels = c("Price","Year", 
-                               "ln(volume)", "ln(area)", 
-                               "ln(dist. city center)",
+                               "Volume", "Area", 
+                               "Dist. city center",
                                "New",
                                "Type: detached", "Type: semi-detached", "Type: terraced",
-                               "Georgian","Early Vic.","Late Vic./Edw.","Interwar","Postwar","Contemporary","Faux Vic.",
-                               "Neigh: Georgian","Neigh: Early Vic.","Neigh: Late V./Edw.","Neigh: Interwar","Neigh: Postwar","Neigh: Contemporary","Neigh: Faux Vic."),
+                               "Georgian","Early Vic.","Late Vic./Edw.","Interwar","Postwar","Contemporary","Revival",
+                               "Neigh: Georgian","Neigh: Early Vic.","Neigh: Late V./Edw.","Neigh: Interwar","Neigh: Postwar","Neigh: Contemporary","Neigh: Revival"),
           digits=2,
           out="~/research/paper-uk-vintages/text/sumstats.raw.tex"
 )  

### 2020-11-14 text/manuscript_jrefe.tex
Table updates
manuscript updated

@@
+\documentclass[]{article}
+
 \PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[]{article}
+
+\usepackage[a4paper, margin=1in]{geometry}
 \usepackage{lmodern}
@@
 \usepackage[]{biblatex}
-\addbibresource{references.bib}
+\addbibresource{bibliography.bib}
+
+\begin{document}
 
@@
 (University of Alabama)}
-\date{14 April 2020}
-
-\begin{document}
+\date{7 November 2020}
+
 \maketitle
 \begin{abstract}
-This paper introduces an algorithm that collects pictures of individual
-buildings from Google Street View. It then trains a deep convolutional
-neural network (CNN) to classify residential buildings into
-architectural styles, taking into account spatial dependencies of these
-styles explicitly. Third, it investigates whether architectural styles
-influence house prices. For re-sales, the architectural style is a
-significant determinant of transaction prices while no such effect is
-found for new buildings. Importantly, this paper explores how to detect
-and overcome biases in machine learning methods through a large-scale
-comparison of predictions and expert classifications, partially opening
-up the `black box' of automatic building classification systems.
+This paper couples a traditional hedonic model with architectural style classifications from human experts and machine learning (ML) enabled classifiers to estimate sales price premia over architectural styles, both at the building and the neighborhood-level.
+We find statistically and economically significant price differences for houses from distinct architectural styles across an array of specifications and modeling assumptions.
+Comparisons between classifications from ML models and human experts illustrate the conditions under which ML classifiers may perform at least as reliable as human experts in mass appraisal models.
+Hedonic estimates illustrate that the impact of architectural style on price is attenuated by properties with less well-defined styles and we find no evidence for differential price effects of \emph{Revival} or \emph{Contemporary} architecture for new construction.
 \end{abstract}
@@
 Paul E.
-Glade and Lukas Heckmann-Umhau are thanked for exceptional research assistance.
+Glade and Lukas Heckmann-Umhau are thanked for their exceptional research assistance.
 Carolin Schmidt, Peter Brummund, Mike Langen, Colin Lizieri, Franz Fuerst, Stanimira Milcheva, D'Maris Coffman, Norm Miller, Stephen Malpezzi, John Clapp, Pavel Krivenko and participants at the ASSA/AREUEA 2019 annual meeting and seminars at UCL/Bartlett and the Homer Hoyt Institute offered excellent feedback and critique on earlier versions of this paper.}}
@@
 \section{Introduction}\label{introduction}}
-
-If new developments were only pleasing to the eye, so Britain's
-\emph{Building Better, Building Beautiful Commission} advising
-Government, nimbyism would cease and housing supply could finally reach
-the levels demanded by a growing and more affluent population
-\autocite{economistlineofbeauty2018}. The inaugural chair of this new
-commission boldly suggested that if we built \emph{``as our Georgian and
-Victorian forebears built} {[}\ldots{}{]}. \emph{All objections to new
-building would slip away in the sheer relief of the public''}
-\autocite{scruton2018}. Even Prince Charles, in similar spirit, put
-forward ten principles for urban growth and architecture that emphasize
-tradition and aesthetics \autocite{princecharles2014}. When governments
-and princes occupy themselves with beauty, economists surely may take a
-closer look as well. In this paper, we aim to identify the architectural
-styles of residential buildings using computer vision techniques and to
-empirically search for any transaction price premia associated with
-these styles. If aesthetics were as strong a force in the built
-environment as claimed, we should indeed find a significant effect on
-property prices.
-
-This paper assesses the value of architectural aesthetics head on by
-classifying the exterior styles of residential buildings using street
-level images. Recent work illustrates how street level imagery and
-machine learning classification is an efficient and powerful combination
-for measuring previously unobserved characteristics of the urban
-environment. \textcite{Naik2017} describe how neighborhood demographics
-may impact the physical appearance of neighborhoods.
-\textcite{Gebru2017} use classified vehicle make and model information
-to predict income, race, education, and voting patterns at the precinct
-level. \textcite{Glaeser2016} predict income in New York City.
-\textcite{Naik2016AER} create a neighborhood safety based Streetscore
-which is shown to be highly correlated with neighborhood population
+In this paper, we introduce a new data collection technique that allows us to rigorously test the notion that households have strong preferences over architectural styles.
+Our results indicate that 1) there is evidence for sales price premia associated with houses from a variety of architectural styles, 2) hedonic estimates from high confidence machine learning (ML) enabled architectural image classifications are similar to human expert estimates, and 3) any style premia are found for existing structures only and not for new buildings, indicating that debates about strong demand for historicizing aesthetics may be unfounded.
+
+Understanding household preferences for architectural styles is of increasing interest to both policymakers and researchers.
+The policy perspective is best illustrated by Britain's \emph{Building Better, Building Beautiful Commission}, which advises the government on design choices for homes and neighborhoods.
+It lists as one of its primary aims as \emph{``To make the planning system work in support of better design and style, not against it.''} \autocite{economistlineofbeauty2018} and boldly claims that matching the style of new housing to aggregate neighborhood preferences should overcome otherwise prevailing objections of incumbent households to new construction.
+
+Researchers have recently begun to quantify and define what makes for \emph{better design and style}.
+\textcite{Buitelaar2017} find evidence on the link between preferences over architectural styles and housing prices using architectural assessments by human experts, and estimate a sizable premium of 5\% for new buildings in the Netherlands that refer to traditional styles and a staggering 15\% premium for new buildings that closely follow traditional shapes, facade composition, and details.
+\textcite{Coulson2008} suggest a non-parametric estimator and establish a U-shaped age function and distinct price discounts for postwar and contemporary styles (vis-à-vis more historic styles).
+\textcite{Francke2017a} investigate the depreciation of residential real estate in The Netherlands and decompose land versus structure values singling out the effect of physical deterioration, functional obsolescence, and vintage effects.
+They find that buildings from the 1930s carry a strong price premium.
+These results support the hypothesis that preferences for house vintages (which coincide with architectural styles) may affect housing prices.
+
+Clearly, building vintage, quality, location, and architectural styles are highly correlated which implies that hedonic price estimates for architectural styles cannot simply be understood as marginal prices for aesthetics.
+We only interpret our empirical findings as `pure' architectural preferences in few cases where differences in all other dimensions can be accounted for, e.g.
+new units at similar locations that have been built to similar standards and that have not depreciated yet.
+For markets with more contemporary housing stocks, differences in functional obsolescence would be a major concern when age and style variables are correlated.
+In our case, over 93\% of the housing stock had been produced prior to 1980 and 70\% before 1940,  so concerns on contemporaneous depreciation of new structures may be alleviated as the vast majority of homes has already depreciated.
+Nevertheless, systematic differences in locations and unobservable quality characteristics and modernization standards cannot be ruled out.
+
+\textcite{Buitelaar2017} indicate that any premium for an architectural style must stem from either differences in construction prices or from supply
+constraints, as new construction potentially does not capture the demand
+for traditional styles.
+In markets where home builders are free to decide on the architectural style of the homes they supply, we would not expect any price effects beyond differences in construction costs.
+If there was, for instance, a premium for more traditional styles, developers would continue to build more of these until all demand is met.
+Our prior is therefore \emph{not} to find distinct price effects of aesthetics for newly supplied homes.
+
+Of course, residential buildings rarely stand in isolation and \textcite{Ahlfeldt2012} investigate the influence a building's architecture exerts on its surroundings.
+They observe a positive price effect for residential buildings in the direct proximity of iconic homes by Frank Lloyd Wright in Oak Park, Illinois.
+A building's exterior does not need to be an architectural masterpiece to co-determine the value of other houses close by.
+A similarly shaped neighboring building is value-enhancing while proximity to a wildly different neighboring shape, everything else remaining equal, may be detrimental to property values \autocite{Lindenthal2017b}.
+
+In traditional approaches chosen by e.g.~\textcite{Buitelaar2017} or \textcite{Ahlfeldt2012}, each observation is classified into an architectural style by a human expert, which is time-consuming, costly and is not feasible for large sample sizes.
+As \textcite{Helbich2013} state, the benefit of using new methods to observe the built environment is that ``essential determinants influencing real estate prices {[}which{]} are constantly missing and are not accessible in official and mass appraiser databases''.
+This is certainly the case in our context, as understanding the impact of architectural style on housing prices is made difficult by the paucity of sales or assessment data that includes architectural style as a characteristic.
+In addition, an expert's views may not fully reflect the market's perceptions of relevant styles -- architectural classifications and economically relevant segments might differ.
+
+Combining automated Google Street View photo data collection with deep learning/ML image classification offers a promising way forward to large and comprehensive data sets of architectural style.
+\textcite{Naik2017} describe how neighborhood demographics may impact the physical appearance of neighborhoods.
+\textcite{Gebru2017} use classified vehicle make and model information to predict income, race, education, and voting patterns at the precinct level.
+\textcite{Glaeser2016} predict income in New York City.
+\textcite{Naik2016AER} create a neighborhood safety based Streetscore which is shown to be highly correlated with neighborhood population
 density and household income. \textcite{Nadai2016} find that greenery
-and street facing windows contribute to a positive appearance of safety
+and street-facing windows contribute to a positive appearance of safety
 while \textcite{Liu2017} evaluate the quality and upkeep of the built
@@
 
-\textcite{GlaeserKincaidNaik2018} push the level of observation from the
-block, street, or street-section level to the individual
-\emph{building level}. Utilizing images of buildings' exteriors
-collected from Google Street
-View\footnote{\href{https://www.google.co.uk/maps}{https://www.google.co.uk/maps}},
-and to a lesser degree interior images from Zillow, they find that looks
-matter, at least in Boston: A one standard deviation improvement of a
-building's exterior is associated with an additional USD 70,000 in home
-value. Intuitively, the link between good looks and value is
-bi-directional: The appearance of buildings that went through
-foreclosure deteriorated significantly
-\autocite{GlaeserKincaidNaik2018}.
-
-Zooming in at individual buildings significantly increases the benefits
-of using mass collected street level imagery in economic research:
-property characteristics previously deemed ``unobservable'' can be
-directly observed in an accurate, objective, automatic and therefore
-cost effective way. Deriving additional variables from unconventional
-data sources like 3D airborne laser scanning (or in our case Google
-Street View) is fundamental since this provides ``essential determinants
-influencing real estate prices {[}which{]} are constantly missing and
-are not accessible in official and mass appraiser databases''
-\autocite{Helbich2013}.
-
-In this paper we suggest a method to collect a large number of images of
-individual UK buildings from Google Street View, classify the depicted
-buildings using deep convolutional neural networks, combine the derived
-information with sales price data and, ultimately, estimate marginal
-prices for the estimated building characteristics. Our work demonstrates
-that utilizing pretrained convolutional neural networks to detect
-complex characteristics such as housing appearances with relatively high
-accuracy comes at low computational costs and is feasible with only
-modestly-sized training data. Additionally, we illustrate how machine
-classifications may be sensitive to photo quality by comparing machine
-classifications to those made by human experts.
-
-\hypertarget{building-styles-and-property-values}{%
-\subsection{Building styles and property
-values}\label{building-styles-and-property-values}}
-
-The aesthetics of different architectural styles make for an easy
-cocktail party conversation topic -- and they may also influence market
-prices. Using architectural assessments by human experts,
-\textcite{Buitelaar2017} find a sizable premium of 5\% for new buildings
-in the Netherlands that refer to traditional styles and a staggering
-15\% premium for new buildings that closely follow traditional shapes,
-facade composition and details. Their study carefully disentangles the
-architectural style from other unobserved characteristics such as
-building quality, differences in location, or year of construction.
-These controls are crucial, as earlier work has established that age and
-style variables tend to be highly correlated. \textcite{Coulson2008},
-for instance, suggest a non-parametric estimator and establish a
-U-shaped age function and distinct price discounts for postwar and
-contemporary styles (vis-à-vis more historic styles).
-\textcite{Francke2017a} investigate the depreciation of residential real
-estate in the Netherlands and decompose land versus structure values
-singling out the effect of ``physical deterioration, functional
-obsolescence and and vintage effects''. They find that buildings from
-the 1930s carry a strong price premium.
-
-A large scale assessment of buildings' exteriors will allow for an
-analysis of the externalities of architecture. Buildings hardly ever
-stand in isolation and \textcite{Ahlfeldt2012} investigate the influence
-a building's architecture exerts on its surroundings. They observe a
-positive price effect for residential buildings in the direct proximity
-of iconic homes by Frank Lloyd Wright in Oak Park, Illinois. A
-building's exterior does not need to be an architectural masterpiece to
-co-determine the value of other houses close by. Homogeneity of building
-shapes within street segments does influence property values. A
-similarly shaped neighboring building is value enhancing while proximity
-to a wildly different neighboring shape, everything else remaining
-equal, is detrimental to property values \autocite{Lindenthal2017b}.
-
-Unfortunately, the traditional approaches chosen by
-e.g.~\textcite{Buitelaar2017} or \textcite{Ahlfeldt2012} do not scale
-well. Each observation has to be classified into architectural styles by
-a human expert, which is time-consuming and costly, imposing an upper
-limit on the number of observations and the level of detail captured for
-each observation in any given sample. Google Street View offers a
-solution to this nexus as it captures the images of almost all buildings
-in many cities around the world at high level of accuracy and detail.
-The challenge we address in this paper is to extract and utilize
-building level information from this ubiquitous sensor, using freely
-available deep learning techniques.
+In contrast to the block, street, or street-section level classifications used in the majority of previous studies that use automated image classification, \textcite{GlaeserKincaidNaik2018} push the level of observation to the individual \emph{building level}.
+Utilizing images of buildings' exteriors collected from Google Street View\footnote{\href{https://www.google.co.uk/maps}{https://www.google.co.uk/maps}}, and to a lesser degree interior images from Zillow, they find that looks matter, at least in Boston: A one standard deviation improvement of a building's exterior is associated with an additional USD 70,000 in home value.
+Intuitively, the link between good looks and value is
+bi-directional: The appearance of buildings that went through foreclosure deteriorated significantly \autocite{GlaeserKincaidNaik2018}.
+
+We follow the framework used by \textcite{GlaeserKincaidNaik2018} and focus on individual buildings as our unit of observation.
+This focus unlocks one of the main benefits of using mass collected street-level imagery in economic research: property characteristics previously deemed ``unobservable'' can be directly observed in an increasingly accurate and objective manner and may be implemented in a more efficient, accessible, and cost-effective way.
+
+In addition to reducing the cost of data collection, the ability for low-cost classification of a large sample of structures in an urban area enables researchers to detect not only the architectural style of the building but also to characterize the style of other buildings in the vicinity.
+This allows us to examine the interaction between the style of a building and that of its neighbors.
+
+To analyze the accuracy of our method of detecting architectural style, we compare our algorithmic results with an extensive data set of architectural style classifications compiled by human experts.
+The relatively large and costly comparison group provides insights into ML-based classification accuracy and the robustness of hedonic estimates to human and ML classifications.
+In addition, the measurable uncertainty in the ML classifications may also be a useful source of variation to exploit for style identification.
+For example, it may be the case that the impact of architectural style on sales price for existing buildings may be attenuated for buildings that are more difficult to classify.
+To our knowledge, this step is not present in the existing literature and provides additional insight into the efficacy of the technique for application in other domains.
+
+ We find evidence that for existing buildings, the architectural style has an impact on the sales price and that the estimates are very similar for both human expert and high confidence ML classified images.
+The price effects of human-expert defined architectural styles are greater in images where there is agreement with the ML classifications.
+The presence of architectural style in our hedonic specifications reduces the RMSE of our models.
+The preferred architectural style for resales appears to be \emph{Revival} with \emph{Interwar}, \emph{Postwar}, and \emph{Early Victorian} commanding the smallest premium.
+Immediately proximate neighbor styles also have an impact on sales price, with Contemporary neighborhoods clearly preferred to Georgian, Early Victorian, and Postwar.
+Importantly for policymakers, we do not identify a premium for either Revival or Contemporary styles for new construction.
+
+We begin by describing the traditional hedonic data used in the paper.
+Second, we describe the methodology for the automated architectural style classification.
+Third, we compare the results of the automated predictions with expert classifications.
+Next, we present an array of hedonic regressions using both architect and ML-based classification and discuss results.
+Finally, we conclude with a discussion of the policy implications of the estimates and the feasibility of ML-based classification of architectural style.
+
+\hypertarget{Data}{%
+\section{Data}\label{data}
+}
+
+Residential real estate transactions in England and Wales are
+collected and published by the Land Registry
+\autocite{LandRegistry2016a}. Their records include the date of transaction, the price paid, street address, a classification of the
+property type (flat, detached, semi-detached, or terraced house), the
+estate type (freehold or leasehold), and an indicator for newly built
+properties. We select transactions from Cambridge, England, which were recorded
+between January 1995 and October 2018, excluding any leaseholds, apartments
+and properties classified as type ``other'', and sales with prices below
+£50,000 or in excess of £2,000,000.
+Notably, the Land Registry data lack relevant variables such as year of construction, home and lot size, or similar quality indicators.
+We, therefore, augment the transaction data with core hedonic variables from other sources and to control for a variety of building-specific effects that may be correlated with both sales price and architectural style.
+
+The Ordnance Survey (OS)\footnote{\url{https://www.ordnancesurvey.co.uk/}} provides high-resolution maps that show the two-dimensional footprint of buildings in the UK.
+Using these maps, we calculate each building's floor plate (in \(m^2\)) and estimate its volume by combining the building outlines with digital elevation models from the \textcite{EnvironmentAgency2015}, as suggested by \textcite{Lindenthal2017}.
+Additionally, we measure the distance from each residential property to the city center, proxied by Great St.~Mary's Church.
+The \textcite{ONS2017} subdivides Cambridge into 69 unique \emph{Lower Super Output Areas} (LSOA) and we rely on these boundaries when constructing neighborhood dummy variables.
+An LSOA typically has 1,000--3,000 residents and 400--1,200 households of comparable economic and socio-demographic characteristics \autocite{ONS2017b}.
 
 \hypertarget{ml-classification-of-building-styles}{%
-\section{ML classification of building
-styles}\label{ml-classification-of-building-styles}}
+\subsection{Architectural Style Data}\label{ml-classification-of-building-styles}}
+
+Our main variable of interest, architectural style, follows the classifications commonly used by realtors, home-buyers, and architects.
+Styles are distinctive in Cambridge: Table \ref{tab:styles_rubric} provides a description of the construction eras and the distinctive motifs for each style as defined by members of the Architecture Department at the University of Cambridge.
+
+\begin{center}
+  -- Insert Table \ref{tab:styles_rubric} about here --
+\end{center}
+
+We aim to collect images of all residential buildings in Cambridge from Street View.
+Approximately 50,000 buildings found on the OS maps have footprints between 30 and 500 $m^2$.
+For 85\% of these candidates, we can download street-level images on Google Street View.
+However, not all of them turn out to be residential buildings.
+A sample of 25,000 of these images is categorized by final year architecture students into the seven styles.
+
+ We can match 23,768 residential properties sold in Cambridge between 1995 and 2019 to images from Google Street View.
+We implicitly assume that houses have not changed their architectural styles between the time of sale and the time Google collected the images.
+This is a reasonable approach since conversions of just the exterior of buildings rarely occur.
+In case of full redevelopments, we exclude any sales for that address pre-dating the redevelopment, since we cannot rule out a change of style at redevelopment.
+
+ Importantly, 15,511 sales can also be matched to the sample of expert's classifications.
+Our hedonic models will be estimated on these observations for which we have predicted and ground truth classifications.
+This allows us to assess the prediction accuracy and robustness of the regression results to the classification approach.
+When assessing the architectural style of surrounding buildings, we use the full set of all images collected.
+Being able to cover almost the universe of all buildings in a market is a clear advantage of an automated approach.
+
+In Figure \ref{fig:vint_examples}, we present a set of representative images for each of the 7 architectural styles.
+These images come from our automated collection procedure and are a visual representation corresponding to the expert descriptions in Table \ref{tab:styles_rubric}.
+Image information here is very useful as it provides a visual mapping from the style characteristics to actual identification.
+One component which is evident in the images but not necessarily in the descriptions is the within style homogeneity of window grouping, relative pane size, and counts.
+For example, Georgian windows contain 12 equally sized panes in 4 rows and 3 columns, Early Victorian windows consist of 4 equally sized panes in 2 rows and 2 columns, Interwar windows contain an upper smaller pane and larger lower pane.
+Interestingly, the Revival style demonstrates heterogeneous window patterns that borrow from the variety of classic architectural styles.
+We revisit the impact of image quality and window visibility on prediction accuracy below.
+
+\begin{center}
+  -- Insert Figure \ref{fig:vint_examples} about here --
+\end{center}
 
@@
 
-The first challenge when trying to collect building images in the UK is
-fundamental: How can one identify the building of interest correctly?
-Simply looking up an address on Google Maps too often leads to imprecise
-`street views' and not the building-level portraits needed. Fig.
-\ref{fig:84Vin} presents a typical result from an address level search,
-showing a broad ensemble of buildings instead of singling out the
-building of interest (in this case, the partly captured terraced house
-at the very left margin).
+To provide the best information to detect style for both the architect and ML classifiers, images should be focused on the structure under examination, have a clear field of view, show minimal picture overlap with neighboring properties, and minimize potentially confounding issues such as  vehicle type.
+
+Unfortunately, in the UK, Google's Street View API regularly fails to identify the building at a given address.
+Instead, the camera location will be in close proximity to the front of the building but aimed straight ahead and down the center of the road.
+Fig.
+\ref{fig:84Vin} (a) presents a typical result from an address level API.
+Here, the Google Street View API algorithm fails to accurately capture the front of the building and the property is not even contained in the photo.
+For major US cities, the accuracy of Google's search results is higher and the Street View camera will pan towards the center of the property parcel.
+This makes the photo collection of studies such in U.S urban areas potentially much more straightforward although the API may result in images that are too 'zoomed out' resulting in images that may contain obstructed views, vehicles, and neighboring properties.
 
@@
 
-Previous work sourcing imagery from Google Street View has mostly
-focused on neighborhood or precinct characteristics where exact spatial
-assignment of objects is not required and street-level images suffice.
-For major US cities, the accuracy of building image search results is
-higher, which should help studies such as
-\textcite{GlaeserKincaidNaik2018}.
-
-Self-evidently, the images we use for classifying architectural style
-must focus on specific buildings of interest. For the UK, and many other
-countries, the Google Street View API returns the coordinates of the
-nearest camera snapshot for a given location but fails to provide an
-accurate orientation and zoom-level of the camera needed to capture the
-front of the building. To estimate the best possible view, we combine
-Street View metadata queries and Ordnance Survey maps to find the
-optimal camera orientation to center images on the front door of the
-building of interest.
+Our automated image collection algorithm utilizes a sophisticated process of viewshed analysis based on Ordnance Survey building maps and ML methods to capture images using the best camera locations, zoom, and angles while accounting for potential obstructions from buildings and trees or vehicles.
+Thus, for each property, our goal is to automate the collection of the best possible Street View image for each property in our sample.
+
+More specifically, we first use OS maps to identify each building's outline (see Figure \ref{fig:fan}).
+Second, we build a database of all possible Google Street View camera locations using Metadata queries of addresses in the Ordnance Survey.
+These metadata queries return the latitude, longitude, and dates of the most recent panorama photos collected by Google Street View.
+Next, we use the OS data to assign each property to the nearest Street View photo location in the metadata database and conduct a viewshed analysis on surrounding building outlines to assign pan and zoom parameters to find an informative view.
+The algorithm allows us to estimate the camera bearing (green line) and zoom factor, based on the fan of the lines of sight (in blue).
+The line of sight criteria identifies which exterior walls are visible from the nearest Street View point and aims away from any wall segments where the direct line of sight is obstructed by other buildings.
+A visual example of this algorithm is shown in  Figure \ref{fig:fan}.\footnote{Code necessary to replicate the full image capture including metadata capture and viewshed based camera aiming is available from \url{https://github.com/thies/paper-cambridge-vintages}}.
+For each property, we then collect the image at the highest resolution offered by Google's Street View API\footnote{\href{https://developers.google.com/maps/documentation/streetview/intro}{https://developers.google.com/maps/documentation/streetview/intro}} (640x640 color pixels).
+We test the robustness of our hedonic models to a variety of image quality concerns in the results section of the paper.
 
@@
 
-Specifically, we first look up the nearest Google Street View panorama
-point (green dot in Figure \ref{fig:fan}) based on the centroid (red
-dot) coordinates of a given building obtained from Ordnance Survey maps.
-We then perform a viewshed analysis and identify which exterior walls
-are visible from the panorama point, ignoring any wall segments where
-the direct line of sight from the panorama point is obstructed by other
-buildings. We can then estimate the camera bearing (green line) and zoom
-factor, based on the fan of the lines of sight (in
-blue).\footnote{Code necessary to replicate this analysis is available from the authors' GitHub.com code repositories.}
-
-Obstructed lines of sight due to greenery, fences, garden walls or large
-vehicles cannot be detected from the Ordnance Survey maps. We therefore
-use a first stage image classification procedure to identify if the
-building image is obstructed and we proceed the second-closest location
-if the line of sight is obstructed.
-
-By combining land registry maps with the snapshot location, we are able
-to automatically build a set of building frontage images for
-approximately 48,000 properties in Cambridge (UK). The Ordnance Survey
-maps do not provide any use type classifications so we collect images on
-all buildings that have a ground plate between 40 and 250 \(m^2\). This
-method, however, could easily be adapted to photograph buildings in
-locations for which high-resolution building level maps are not
-available by using LIDAR based building outlines instead, which would be
-in the spirit of \textcite{Glaeser2016}.
-
-\hypertarget{from-pixels-to-computer-vision}{%
-\subsubsection{From pixels to computer
-vision}\label{from-pixels-to-computer-vision}}
-
-We download all pictures at the highest resolution offered by Google's
-Street View
-API\footnote{\href{https://developers.google.com/maps/documentation/streetview/intro}{https://developers.google.com/maps/documentation/streetview/intro}}
-(640x640 color pixels). We then obtain 2048-dimensional feature vectors
-for each picture, using the \emph{Inception-v3} deep convolutional
+Figure \ref{fig:84Vin} (b) shows how the suggested approach can improve the quality of the harvested images.
+The new image is focused appropriately on the relevant property, it contains minimal neighbor information.
+and the view is not overly obstructed by other structures, greenery, or vehicles.
+As a result, the image contains the relevant identifying architectural style characteristics such as a clearly identified roofline, front door, window panes, and bay window.
+
+\hypertarget{image-classification}{%
+\section{Methodology: Style classification}\label{image-classification}}
+
+With the images collected, we next focus on training an ML learning model to classify the architectural style observed in each of the collected Street View images.
+The first step in building our ML model is to construct a training data set.
+Our training data set consists of images from 25,000 randomly sample properties classified into one of seven different architectural styles by final year students from the Architecture Department at the University of Cambridge\footnote{The full set of classified images are available for download at the authors' websites.} A sample of 25,000 is much more training data than is actually needed.
+By applying transfer learning to an existing image recognition model, we require less than 250 observations per category to reach saturated training accuracy levels.
+We use this ``surplus'' training data to perform out of sample comparisons between our ML predictions and human expert classifications.
+This large set of expert classified data also allows us to perform robustness, and falsification checks on the hedonic regressions for the 15,369 overlapping observations where we have transaction data with both human and ML-based style classifications.
+
+\hypertarget{transfer-learning}{%
+\subsection{Training the model}\label{transfer-learning}}
+
+We simplify the calibration of our architectural style prediction model by utilizing transfer learning.
+Transfer learning freezes the parameters from a pre-trained image recognition model, removes the final steps in the model, and then trains a new model on the vector of outputs from the truncated pre-trained model to produce new classifications\footnote{For examples, see \url{https://www.tensorflow.org/tutorials/images/transfer_learning}}.
+Transfer learning methods enable the use of smaller training data sets and impose a much lower computational burden than traditional deep learning models.
+For our purposes, we use the \emph{Inception-v3} deep convolutional
 neural network \autocite{Szegedy2015}. \emph{Inception-v3} has been
@@
 evaluates image classification and object detection algorithms for a
-wide range of objects. The pretrained classifications would allow us to
-identify pets, vehicles or people on the pictures -- assessing
+wide range of objects. The pre-trained classifications would allow us to
+identify pets, vehicles, or people in the pictures -- assessing
 architectural style, however, is beyond the canned classifiers'
 capabilities.
-
-\textcite{GlaeserKincaidNaik2018} rely on an different ILSVRC
-competitor, \emph{Resnet-101} \autocite{He2016}. They reduce the
-extracted feature vectors to lower dimensionality (1024 to 100
-dimensions) based on principal component analysis (PCA). We follow a
-different strategy and double the dimensionality by including the
-feature vector of the closest building in the sample, which, in most
-cases, is the direct neighbor. The feature vectors of neighbors have
-been collected in exactly the same way as those for other buildings in
-the sample. Doubling up allows us to model spatial dependencies in
-building styles, similar to spatially correlated land cover
-classifications in \textcite{Ghimire2010a}.
-
-\hypertarget{image-classification}{%
-\subsection{Image classification}\label{image-classification}}
-
-Cambridge's houses can be classified into seven broad styles:
-\footnote{We are grateful to colleagues from the Architecture Department at the University of Cambridge to provide these general style descriptions.}
-
-\begin{itemize}
-\item
-  \emph{Georgian} (c1714--1837) houses feature key characteristics such
-  as sash windows, fan lights above doors, the use of stucco on facades,
-  often wrought work grilles, railings etc.\label{def_eras}
-\item
-  In the \emph{Early Victorian} era (c1837--c1870s), a growing taste for
-  individualized embellishment led to the development of elaborate
-  features such as carved barge boards or finials. The development of
-  sheet glass led to sash windows becoming more affordable, and,
-  increasingly, wider.
-\item
-  In the \emph{Late Victorian} era (c1870s--1901), bay windows became
-  more and more widespread, and increasingly substantial. Stylistic
-  movements such as the Queen Anne revival style contributed richly
-  ornamental details to the formal repertoire employed by designers.
-  Stained glass became more popular.
-\item
-  \emph{Edwardian} architecture (1901-1910) tends to be less ornate than
-  late Victorian architecture.
-\item
-  The \emph{Interwar} period (1918--1939) saw the cost of building
-  construction fall, amidst a drive to provide better housing for the
-  working classes. New housing types were being favored.
-\item
-  The \emph{Postwar} (1950-1980) styles continued on this path, with an
-  embrace of high-rise as well as low rise housing. Facades vary greatly
-  between brick, tiling, pebbledash and render.
-\item
-  The cut-off year for our \emph{Contemporary} era to begin is 1980.
-  \emph{Revival} style-homes are contemporary buildings trying to
-  emulate historic, mostly Victorian, architecture.
-\end{itemize}
-
-Two final-year architectural students classified a large sub-sample of
-approximately 25,000 images from our data set of Cambridge
-houses.\footnote{The full set of classified images are available for download at the authors' websites.}
-This is a much larger sample than needed in our case. In our case, each
-category requires less than 250 observations to reach saturated training
-accuracy levels. We greatly exceed this number for the purpose of this
-paper so that we can compare the out-of-sample convolutional neural
-network predictions to the architects' classifications. This allows us
-to examine the power and size of the assignment tests. In addition
-having both human and machine classification for a large sample of the
-data allows for robustness checks on the machine comparisons.
-
-We create stratified training samples of 600 buildings from each
-category but \emph{Georgian}, which is the least common style in
-Cambridge and for which we can only sample 330 examples. This leaves a
-sufficiently sized out-of-sample verification data set of 21,000 homes.
-
-The multinomial classifier model design remains parsimonious, comprising
-of:
-
-\begin{itemize}
-\item
-  an input layer the size of the feature vectors, e.g.~2048 or 4096,
-  respectively,
-\item
-  one dense layer (relu) half the size of the input layer, one
-  subsequent dropout (rate 0.5) layer,
-\item
-  one dense layer (relu) a quarter the size of the input layer, one
-  subsequent dropout (rate 0.5) layer,
-\item
-  and the final dense output layer with softmax activation.
-\end{itemize}
-
-All classifiers are implemented using the Keras/Tensorflow
-APIs\footnote{Keras: \href{https://keras.io/}{https://keras.io/}, Tensorflow: \href{https://github.com/tensorflow/tensorflow}{https://github.com/tensorflow/tensorflow}}.
+To allow for the detection of new objects, transfer learning techniques strip off the last steps of the model.
+The output of the original deep learning model is essentially just a deeply recursive dimension reduction engine that outputs a 2048-dimensional feature vector for each picture.
+This feature vector describes the outline shapes, locations, and colors that were important for the ImageNet classifications.
+
+\textcite{GlaeserKincaidNaik2018} rely on a different ILSVRC competitor, \emph{Resnet-101} \autocite{He2016}.
+They reduce the extracted feature vectors to lower dimensionality (1024 to 100 dimensions) based on principal component analysis (PCA).
+In our analysis, we follow a different strategy and actually double the dimensionality (4096) of our feature vectors by including the feature vector of the closest building in the sample, which, in most cases, is the direct neighbor.
+The feature vectors of neighbors have been collected in exactly the same way as those for other buildings in the sample.
+Doubling up allows us to model spatial dependencies in building styles, similar to spatially correlated land cover classifications in \textcite{Ghimire2010a}.
+
+Having obtained feature vectors for each image, we train a simple multinomial classifier comprising of 1) an input layer the size of the feature vectors, e.g.~2048 or 4096, respectively, 2) one dense layer rectified linear activation function (relu) half the size of the input layer, one subsequent dropout (rate 0.5) layer, 3)   one dense layer (relu) a quarter the size of the input layer, 4) one subsequent dropout (rate 0.5) layer, and 5) the final dense output layer with softmax activation.
+The dropout layers help avoid overfitting, thus increasing the generalizability of the predictors.
+When classifying a building picture, the softmax activation layer returns a vector of style-scores, each between 0 to 1, that jointly sum up to 1.
+We select the style with the highest score as the best estimate.\footnote{By not excluding observations where multiple scores are vying for the top rank we retain as many observations as possible but risk a higher misclassification rate.
+We examine the role of model `confidence' in the ML Classification Diagnostics section.} All classifiers are implemented using the Keras/TensorflowAPIs\footnote{Keras: \href{https://keras.io/}{https://keras.io/}, Tensorflow:\href{https://github.com/tensorflow/tensorflow}{https://github.com/tensorflow/tensorflow}}.
 The computational burden of this rather shallow model design is modest.
 
-For 100 randomly drawn data sets, all stratified on style, we train two
-models each: The first is based on the building specific feature vectors
-(2048 dimensions) only while the second also incorporates the feature
-vector of the nearest neighbor (combined 4096 dimensions). In cases
-where trees, fences or large vehicles obstruct the view or where the
-front of a building cannot be classified with high certainty, the image
-of the nearest neighbor provides a ``second opinion'' that is spatially
-correlated with the observation of interest. Finally we classify all
-buildings not used in training or evaluating the model (truly
-out-of-sample).
-
-When classifying a building picture, each models returns a vector of
-style-scores, each between 0 to 1, that jointly sum up to 1. We select
-the style with the highest score as the best estimate. By not excluding
-observations where multiple scores are vying for the top rank we retain
-as many observations as possible but risk a higher misclassification
-rate.
-
-Two variables are obtained from the distribution of classifications per
-observation: The ensemble classifier arrives at predictions by majority
-vote. In addition, a confidence measure is computed as the Herfindahl
-index of classifications by ensemble member models. If, for instance, 20
-models classified a building as \emph{Contemporary} but 80 others as
-\emph{Revival}, the ensemble majority vote is \emph{Revival}. The
-corresponding Herfindahl score is calculated as
-\((20/100)^2 + (80/100)^2 = 0.68\).
-
-We tabulate confusion matrices and evaluate the classification
-performance in terms of recall, precision and \(F_1\)-scores. More
-formally, the next step regresses the style classifications by
-architects, captured by binomial variables \(D_{TrueVint}\), against a
-vector of hedonic variables \(\mathbf{X}\), vectors of year
-\(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy variables and the
-building's \(\mathbf{Style}\), estimated both with and without spatial
-dependencies. The intercept is denoted by \(\alpha\) while
-\(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\gamma}\) and \(\bm{\lambda}\)
-are vectors of regression coefficients, and \(\epsilon\) is the error
-term.
+Next, we turn to an analysis of the predictive accuracy of the models under a variety of assumptions and diagnostic tests.
+
+\hypertarget{style-classification-diagnostics}{%
+\subsection{Classification Diagnostics}\label{style-classification-diagnostics}}
+
+We use a variety of methods to quantify and explain the variation in ML prediction accuracy under differing modeling assumptions.
+First, we report the accuracy of the  predictions using a confusion matrix (a contingency table of true and predicted classifications) that also offers recall, precision, and $F_{1}$ scores.
+Second, we explore how the style classification prediction error is affected by the modeling assumptions.
+Third, we test the sensitivity of predictions to variation in the training data.
+After quantifying the behavior of the style predictive models, we next turn to describe how image characteristics such as aim quality affect the accuracy of the classifier.
+This final analysis should help inform other researchers and practitioners in best practices for image collection in order to maximize predictive accuracy.
+
+Table \ref{tab:confmat} contains confusion matrices for two different ML classifiers and a `high confidence' prediction criteria.
+Each confusion matrix measures how the ML style predictions compare to the architects'.
+Panel A illustrates the predictive performance for an ML model based on an image of both a building and its nearest neighbor.
+Panel B includes only the highest confidence predictions from the spatial classifier used to construct Panel A.
+Panel C contains predictions from an ML classifier based on a single building image.
+
+Diagonal elements in the confusion matrices represent the count of images where the ML and the architect agree while off-diagonal elements are cases where the ML misclassifies the style.
+Consider the \emph{Interwar} style in Panel A.
+There are 5,884 images where the ML correctly classifies the style.
+For the \emph{Interwar} column, the ML incorrectly classifies 38 images as \emph{Georgian}, 86 as \emph{Early Victorian},  213 as \emph{Late Victorian/Edwardian}, 514 as \emph{Postwar}, 101 as \emph{Contemporary}, and 139 as \emph{Revival}.
+Thus, of 6,975 true \emph{Interwar} images, the ML misclassifies 1,091 and correctly detects 5,884.
+Recall measures the ability of the ML to detect within a given category and is the share of correctly classified images out of the total for a category.
+For \emph{Interwar} the recall rate is then 5,884/6,975=0.84.
+
+Now consider the \emph{Interwar} row which contains information on all images that the ML classifies as \emph{Interwar}.
+There are 10 \emph{Georgians}, 46 \emph{Early Victorian}, 254 \emph{Late Victorian/Edwardian}, 997 \emph{Postwar}, 56 \emph{Contemporary}, and 54 \emph{Revival} incorrectly classified as \emph{Interwar}.
+In total, there are 1,417 images incorrectly classified as \emph{Interwar} and 5,884 correctly classified.
+Thus, 81\% of the images classified by the ML as \emph{Interwar} are actually \emph{Interwar}.
+This is the Precision or the share of buildings predicted to belong to a category that is actually from the category.
+The $F_1-score$ is the harmonic mean of Precision and Recall.
+
+Across models, classification error is most likely to occur in styles that occurred in consecutive eras.
+For example, in Panel A,  10\% of \emph{Late Victorian/Edwardian} styles are classified as \emph{Early Victorian} and 14\% of \emph{Georgians} are misclassified as \emph{Earl Victorian}.
+On the other hand, for distant eras, the misclassification likelihood is much lower and the ML exhibits less confusion.
+The more classical \emph{Georgian} and \emph{Early Victorian} styles are each only assigned to Interwar 3\% of the time.
+
+Recall, precision scores, and $F_{1}$ scores are higher for the spatial ML classifier shown in Panel A relative to spatially naive ML classifier in Panel C.
+Pronounced increases include the increase in recall for \emph{Postwar} from 0.61 to 0.71 due to a reduction in \emph{Postwar} images being incorrectly classified as \emph{Interwar}.
+Also notable is the increase in recall for \emph{Revival} from 0.58 to 0.67.
+
+Table \ref{tab:confmat} Panel B is based on the spatially dependent model but only contains classifications where the maximum ML style prediction score was above 0.8.
+These `high confidence' ML images improve the measurable performance of the ML model relative to the full sample.
+Across styles, $F_{1}$ scores see a substantial increase.
+Notably, recall rates for \emph{Early Victorian} and \emph{Interwar} are now above .90 and \emph{Contemporary} increases from 0.72 to 0.86.
+In other words, images that are easier for the ML to classify are also the ones where the ML is correct at a higher frequency.
+
+%are highly correlated with image prediction confidence (styles which had the lowest $F_{1}$ scores in Panel C are also those with the most low confidence predictions).
+This is a useful result, since the distribution of image prediction confidence is directly observable to researchers, while the $F_{1}$ score may require a substantial amount of expert classified out-of-sample data.
+
+%This sample restriction has a small overall effect on Early Victorian and Late Victorian/Edwardian as over 85\% of the sample is retained.
+For Contemporary and Revival, however, only 25\% of the prediction sample remains after the censure.
+
+Figure \ref{fig:boxplot} shows the distribution of $F_{1}$ scores from Table \ref{tab:confmat} across ML modeling assumptions and architectural styles.
+This figure demonstrates the benefits of including the neighbor image in our modeling strategy.
+In addition, the marginal contribution to the $F_{1}$ score from using a spatial classifier appears to be of a similar magnitude to that of including only `high confidence' images and greatly improves model accuracy without the cost of dropping images from the sample.
+
+\begin{center}
+  -- Insert Table \ref{tab:confmat} and Figure \ref{fig:boxplot} about here --
+\end{center}
+
+Next, we regress the architects' style classifications captured by binomial variables \(D_{Architects}\), on a vector of hedonic variables \(\mathbf{X}\), vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy variables, and the automatically estimated style \(\mathbf{ML}\).
+The intercept is denoted by \(\alpha\) while \(\bm{\beta}\), \(\bm{\delta}\), \(\bm{\gamma}\) and \(\bm{\lambda}\) are vectors of regression coefficients, and \(\epsilon\) is the error term.
+These models are estimated both with and without spatial dependencies and capture the ability of the ML to predict the architect style classifications net of other hedonic variables.
 
 \begin{equation} \label{eq:rev}
-  logit( D_{TrueVint,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{Style}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
+  logit( D_{Architects,i} ) = \alpha + \beta\mathbf{X_i} + \delta\mathbf{ML}_i +  \gamma\mathbf{Y}_i + \lambda\mathbf{Loc}_i +  \epsilon_i
 \end{equation}
@@
 well-performing classifier, the \(\delta\) coefficients will be
-statistically significant and, more importantly, differences in the
-Akaike Information Criterion (AIC) allow for comparisons across the
-suggested ML classifiers.
-
-Will the resulting classifiers be biased with respect to property
-values, picking up correlated but irrelevant cues such as greenery,
-upkeep, or cars brands instead of building exteriors? Are, for instance,
-more valuable houses more likely to be classified as the popular
-\emph{Late Victorian} style while starter homes are disproportionally
-more likely to be classified as e.g.~\emph{Early Victorian}? We expect
-that in cases in which the ensemble provided a high confidence score,
-building features are clearly detectable on the pictures. For close
-calls, however, where models within the ensemble cannot agree, other
-factors might tilt the scale towards an incorrect class. A sizable
-difference in estimated marginal prices for machine classifications
-versus the estimates for architects' classifications in the subsequent
-hedonic regression (Eq. \ref{eq:hed}, below) would indicate such a bias.
-
-\hypertarget{architectural-styles-and-property-values}{%
-\section{Architectural styles and property
-values}\label{architectural-styles-and-property-values}}
-
-\hypertarget{residential-transaction-data}{%
-\subsection{Residential transaction
-data}\label{residential-transaction-data}}
-
-Residential real estate transactions are public data in the UK,
-collected and published by the Land Registry
-\autocite{LandRegistry2016a}. The records include the date of
-transaction, price paid, street address, a classification of the
-property type (flat, detached, semi-detached, or terraced house), the
-estate type (freehold or leasehold) and an indicator for newly built
-properties. We select transactions from Cambridge which were recorded
-between January 1995 and October 2018, excluding any leaseholds, flats
-and properties classified as type ``other'', and sales with prices below
-£50,000 or in excess of £2,000,000. Linking recently taken images to
-sales data from 24 years assumes that houses have not changed their
-architectural styles -- which seems reasonable. We are not aware of any
-conversions of just the exterior of buildings. In case of full
-redevelopments, we exclude any sales for a given address pre-dating the
-redevelopment, ensuring that a currently taken picture represents the
-house at all included transactions. Table \ref{tab:sumstats} presents
-summary statistics for the sample.
+statistically significant and, more importantly, the
+Akaike Information Criterion (AIC) will be relatively low.
+A summary of AIC results is shown in Table \ref{tab:aic}.
+Column 1 (\emph{No ML pred.}) contains the AIC for style prediction models based solely on the hedonic variables.
+Column 2 (\emph{Base pred.}) includes both the hedonic variables and the single image (spatially naive) ML.
+The AIC for all styles decreases with the inclusion of this `base' ML predictor.
+In Column 3 (\emph{Spatial pred.
+all}), we include hedonic variables along with the spatially aware ML predictor.
+Again, the ability to predict improves across all architectural styles.
+The improvement is especially notable in the final column (\emph{Spatial pred.
+high certainty}), where the AIC is cut in half for the `high certainty' subsample of the spatial predictors.
+As expected, the AIC rankings are consistent with $F_{1}$ rankings in Table \ref{tab:confmat}.
+By including the hedonic variables as well as location and time dummies in the regression, we are able to see that building style is not fully explained by size, volume, location, and building type.
+The AIC results clearly show that 1) a model based on hedonic variables alone does not predict actual style as well as a model that includes the predicted style from the image and 2) subsetting on high confidence ML classified images increases AIC.
+
+\begin{center}
+  -- Insert Table \ref{tab:aic} about here --
+\end{center}
+
+Subsequently, we measure the sensitivity of our predictions to sampling variation in the training data.
+This test is only possible due to the extremely high number of training data images.
+We begin by creating 100 models that are calibrated using 250 randomly selected training data images for each style category in the data set.
+For each image in the out-of-sample data, we then capture the highest probability style type prediction.
+With these predictions, we perform two calculations.
+First, we utilize these predictions as an ensemble model and assign the most commonly predicted ML class as the architectural style.
+For example, if an image is predicted to be a Georgian architectural style 80 of 100 times (80 ``votes''), Early Victorian 10 times, Late Victorian 5 times, and Revival 5 times the building is assigned the Georgian style.
+Second, we use the predictions to generate a Herfindahl index for each image.
+In the example case the Herfindahl index for image $i$ is calculated as
+
+\begin{equation}\label{eq:herf}
+Herf_{i} = \sum_{s=1}^{7}\left(\frac{votes_{s}}{votes_{all}}\right)^{2} = 0.8^2 + 0.1^2 + 0.05^2 + 0.05^2 = 0.655
+\end{equation}
+
+The Herfindahl scores for misclassified images (off-diagonal elements in Table \ref{tab:herftab}) indicate are all negative.
+This provides strong evidence that high consensus ensemble models are more likely to be accurate than low consensus models.
+All off-diagonal elements in the lower panel of Table \ref{tab:herftab} are negative, suggesting that, in general, the Herfindahl index is a good predictor of correctly classified images.
+In other words, there is less consensus for misclassified images.
+
+The next step examines the \emph{objects} in each image.
+This serves two purposes 1) we can gain a better understanding of how image composition affects our ML prediction accuracy and 2) we can validate the quality of our automated image collection algorithm.
+We again turn to ML automation and use an off-the-shelf object detection algorithm (Inception/Resnet) that can identify broadly defined objects in images such as trees, vehicles, houses, doors, or windows without any additional training.\footnote{In this case, "faster rcnn inception resnet v2 atrous oidv2", available from \url{https://github.com/tensorflow/models/blob/master/research/object_detection/g3doc/detection_model_zoo.md}} With this information, we are able to validate the performance of the viewshed collection algorithm according to several measures.
+
+First, we identify the locations (bounding boxes) of cars, trees, buildings, and windows in each image.
+Next, we construct a variety of measures of image quality including house area, share blocked, window area and image offset.
+
+We measure ``house area'' as the share of the image that is taken up by the house bounding box.\footnote{If more than one house is detected, then the largest of the houses is used as the measure.} Share blocked measures how obstructed the view of the house is by cars or trees.
+Recall from the viewshed exercise that we aim away from structures in order to get a clean line of sight.
+However, buildings may have obstructed lines of sight due to greenery, fences, garden walls, or large vehicles that cannot be detected from the Ordnance Survey maps.
+A high `shared blocked' image should provide less information for our ML style classifier and result in lower accuracy.
+As discussed in the architectural style descriptions, one of the most important visual differences across architectural styles is window alignment and composition.
+We quantify this with the measure `window area' which calculates the share of the image area that contains windows.
+We use ``image offset'' to detect images not collected at an optimal angle or zoom factor.
+To quantify this, we calculate the offset between the bounding box for the largest detected building and the center of the image.
+\footnote{Higher offset scores may result from either imperfectly defined ordnance building outline data (which may occur with some frequency), another building obstructing the viewshed algorithm causing the camera to pan or zoom away from the obstacle, or a tree or car causing a complete view obstruction in which case the algorithm will move to the next best location.} Table \ref{tab:imgqualsumstats} shows the mean values by architectural style for each of the quality measures.
+Overall, \emph{Georgian} and \emph{Contemporary} styles have the highest quality scores.
+Even for \emph{Postwar}, our lowest-performing style, the average image contains 64\% house with windows taking up 7\% of the image.
+
+We explore the relationship between the image quality measures classification accuracy in Table \ref{tab:diffimgchar}.
+Panel A compares the mean values for views obstructed by trees or vehicles for correctly (on-diagonal) and incorrectly (off-diagonal) classified images.
+In most cases, the off-diagonal values are positive as obstacles in the line of sight correlate with a higher likelihood of misclassifications.
+This helps alleviate concerns that the style detection model is loading on trees, cars, or other building structures.
+This also shows that ML misclassification is more likely to occur when the building is less directly observable.
+If the house takes up a larger share of the image (Panel B), misclassifications are reduced (negative differences).
+The strongest effect is for the window area, which appears to give valuable cues about a house's style (Panel C).
+Finally, images with houses that are not in the center of the frame tend to be misclassified more frequently (positive differences in Panel D).
+In summary, image quality appears to be correlated with style prediction accuracy.
+
+\begin{center}
+  -- Insert Table \ref{tab:imgqualsumstats} and Table \ref{tab:diffimgchar} about here
+\end{center}
+
+Summary statistics for the transaction level dataset are shown in Table \ref{tab:sumstats}.
+New construction is only 4\% of the sample and terraced and semi-detached residential properties comprise 87\% of the sample.
+Importantly, based upon architectural style, the residential housing stock in Cambridge is old with only about 7\% of properties from post-1980 eras of Contemporary and Revival architecture.
+Interestingly, the two most common architectural styles are the ubiquitous 20th-century styles of Interwar and Postwar which together make up 55\% of all sales.
+Classical styles such as Georgian, Early Victorian, and Late Victorian/Edwardian together account for 39\% of sales.
+Neighborhood style shares seem to closely match the individual style shares which hint at a high degree of architectural style clustering in the city.
 
@@
 
-The Ordnance Survey \emph{AddressBase} \autocite{OrdnanceSurvey2017}
-links street addresses to building outlines on Ordnance Survey maps
-\autocite{OrdnanceSurvey2017a}, which allows us to calculate the
-buildings floor plate (in \(m^2\)) and to estimate the building's volume
-from digital elevation models \autocite{EnvironmentAgency2015}, as
-suggested by \textcite{Lindenthal2017}. We control for the location of
-each building by calculating the distance to the city center proxied by
-Great St.~Mary's Church, and non-parametrically by using 69 indicator
-variables for each of the smallest census tracts (\emph{Lower Super
-Output Areas}, LSOA) subdividing Cambridge \autocite{ONS2017}. LSOAs
-typically have 1,000--3,000 residents and 400--1,200 households of
-comparable economic and socio-demographic characteristics
-\autocite{ONS2017b}.
-
-\hypertarget{hedonic-regression-setup}{%
-\subsection{Hedonic regression setup}\label{hedonic-regression-setup}}
-
-Merging the machine's classification with sales data
+Figure \ref{fig:spatial} visualizes the spatial distribution of the regression sample.
+The maps trace Cambridge's historic expansion, with \emph{Georgian} houses clustering in the city center, surrounded by first \emph{Early Victorian} then \emph{Late Victorian/Edwardian}, \emph{Interwar} and \emph{Postwar} homes.
+\emph{Contemporary} and \emph{Revival}, however, are widely distributed across Cambridge's neighborhoods, usually filling in previously undeveloped or brownfield sites, densifying the city.
+Neighborhoods might be dominated by a single building style - but only very few comprise of more than 80\% of buildings of one style.
+These extreme cases are only found in large \emph{Interwar} or \emph{Postwar} expansion areas.
+Luckily, many more houses from these frequent styles are found in other neighborhoods, which avoiding excessive multicollinearity between style and neighborhood variables.
+
+\begin{center}
+  -- Insert Figure \ref{fig:spatial} about here --
+\end{center}
+
+\hypertarget{results}{%
+\section{Hedonic Estimation}\label{results}}
+
+%Will the resulting classifiers be biased with respect to property
+%values, picking up correlated but irrelevant cues such as greenery,
+%upkeep, or cars brands instead of building exteriors? Are, for instance,
+%more valuable houses more likely to be classified as the popular
+%\emph{Late Victorian} style while starter homes are disproportionately
+%more likely to be classified as e.g.~\emph{Early Victorian}? We expect
+%that in cases in which the machine based predictions provided a high confidence %score, building features are clearly detectable on the pictures and/or building %styles are well defined.
+For close calls, however, other factors might tilt the %scale towards an incorrect class.
+A sizable difference in estimated marginal prices %for machine classifications
+%versus the estimates for architects' classifications in the subsequent
+%hedonic regression (Eq. \ref{eq:hed}, below) would indicate such a bias.
+
+%Almost 16,000 of the 25,000 buildings for which we have an architect's
+%classification could be matched to the 23,768 sales transactions that
+%have been recorded for Cambridge between 1995 and 2018. The remaining
+%9,000 houses have not been sold since 1995 - but the information on
+%their architectural style is still valuable for our measures of
+%neighborhood styles. Thus, we observe both the machine's and the
+%architects' classification for the majority of buildings in the data
+%set.
+
+%A visual inspection of classifications is additionally reassuring.
+%Figure \ref{fig:vint_examples} displays the pictures which carry the
+%highest out-of-sample scores for each style. The model is clearly able
+%to differentiate based on small cues, even when only parts of the facade
+%are captured on the picture.
+
+The hedonic estimations use both the ML and architect classifications for a variety of direct, robustness, and falsification tests. Merging the ML classifications with sales data
 \autocite{LandRegistry2016a} we estimate a hedonic regression equation
@@
 combination of hedonic attributes described in vector \(\mathbf{X}\),
-vectors of year \(\mathbf{Y}\) and neighborhood \(\bm{Loc}\) dummy
+vectors of year \(\mathbf{Y}\) and neighborhood \(\mathbf{Loc}\) dummy
 variables and the building's estimated \(\mathbf{Style}\) and the
@@
 to multiple groups of households with distinct style or vintage
-preferences? \textcite{Buitelaar2017} indicate that any premium for an
-architectural style must stem from either differences in construction
-prices (which they do not find in their Dutch sample) or from supply
-constraints, as new construction potentially does not capture the demand
-for traditional styles. For Cambridge, new supply will inevitably be of
-either contemporary or revival style as historic vintages (and their
-styles), by definition, are not supplied any more. Estimating Eq.
-\ref{eq:hed} for a subset of newly constructed buildings will show
-whether construction prices or supply constraints for new homes built
+preferences? For Cambridge, 47\% of new supply has been of contemporary and 36\% of or revival style. Estimating Eq.
+\ref{eq:hed} for a subset of newly constructed buildings from these two styles will show whether construction prices or supply constraints for new homes built
 according to different architectural styles prevail -- if too few
@@
 Singling out new buildings crucially controls for the otherwise
-unobserved age of these buildings, which is tightly intertwined with
+unobserved age and quality of these buildings, which is tightly intertwined with
 their aesthetics.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Almost 16,000 of the 25,000 buildings for which we have an architect's
-classification could be matched to the 23,768 sales transactions that
-have been recorded for Cambridge between 1995 and 2018. The remaining
-9,000 houses have not been sold since 1995 - but the information on
-their architectural style is still valuable for our measures of
-neighborhood styles. Thus, we observe both the machine's and the
-architects' classification for the majority of buildings in the data
-set.
-
-\begin{center}
-  -- Insert Table \ref{tab:confmat} about here --
-\end{center}
-
-The agreement between classifications by the machine and by the
-architects is reassuringly strong. When relying on feature vectors of
-the buildings and their closest neighbors, 67 to 84 percent of true
-classifications are matched with correctly estimated labels (Table
-\ref{tab:confmat}, Panel A). The recall rates are especially high for
-older styles: For \emph{Georgians}, it is 79 percent, \emph{Early
-Victorian} 81 percent, \emph{Late Victorian/Edwardian} 78 percent,
-\emph{Interwar} 84 percent, respectively. For more recent \emph{Postwar}
-buildings, the rate drops to 71 percent, for \emph{Contemporary} to 72
-percent and for \emph{Revival} to 67 percent.
-
-A visual inspection of classifications is additionally reassuring.
-Figure \ref{fig:vint_examples} displays the pictures which carry the
-highest out-of-sample scores for each style. The model is clearly able
-to differentiate based on small cues, even when only parts of the facade
-are captured on the picture.
-
-The Herfindahl scores for classifications vary substantially across
-styles, as classified by the architects (Table \ref{tab:herftab}),
-indicating that the models within the ensemble, for instance, agree more
-often on a building being \emph{Georgian} than finding consensus for
-other styles. For \emph{Contemporary} or \emph{Revival} styles,
-individual classifications differ most. All off-diagonal elements in the
-lower panel of Table \ref{tab:herftab} are negative, suggesting that, in
-general, the Herfindahl index is a good predictor of misclassified
-images.
-
-A closer inspection of the misclassified images sheds some light on the
-limits of automatically collected street level imagery. What do
-misclassified images have in common? Off-the-shelf object detection
-algorithms can identify broadly defined objects such as trees, vehicles,
-houses, doors, or windows without any additional training. Using an
-Inception/Resnet object detection model trained on Open
-Images\footnote{In this case, "faster rcnn inception resnet v2 atrous oidv2", available from \url{https://github.com/tensorflow/models/blob/master/research/object_detection/g3doc/detection_model_zoo.md}},
-we calculate the share of the image area taken up by cars or trees as a
-measure of view obstruction. The more image area is showing buildings
-and, importantly, windows the more meaningful input an automatic
-classifier can draw from, resulting in better classifications. In
-addition, images not taken at an optimal angle or zoom factor are
-detected by calculating the distance between the bounding box for the
-largest building detected on the image and the center of the image: For
-well-centered images, this offset will be small.
-
-Table \ref{tab:imgqualsumstats} presents the mean values for the image
-quality variables. Table \ref{tab:diffimgchar}, Panel A, compares the
-mean values for views obstructed by trees or vehicles for correctly (on
-diagonal) and incorrectly classified images. In most cases, the
-off-diagonal values are positive, showing that more obstacles in the
-view of sight correlate with a higher likelihood of misclassifications.
-Similarly, if more of the image area shows a house (Panel B),
-misclassifications are reduced (negative differences). This effect is
-stronger for windows, which appear to give valuable cues about a house's
-style (Panel C). Finally, houses that are not in the center of the
-building tend to be misclassified more frequently (positive differences
-in Panel D). In sum, bad quality images lead to misclassifications.
-
-\begin{center}
-  -- Insert Table \ref{tab:herftab}, Table \ref{tab:imgqualsumstats} and Table \ref{tab:diffimgchar} about here --
-\end{center}
-
-The number of misclassifications decreases decidedly when considering
-observations with high ensemble confidence only: The majority vote based
-on the most confident two-thirds of machine classifications only are
-more in line with the architects' classifications, as higher recall,
-precision and \(F_1\)-scores in Table \ref{tab:confmat}, Panel B, show.
-The improvement is most evident in the precision rates. For the
-relatively rare categories of \emph{Georgian} and \emph{Revival} about
-the same number of buildings classified as \emph{Georgian/Revival} in
-Panel A actually belong to a different style, according to the human
-experts. The precision shoots up from 0.50 to 0.70 for \emph{Georgian}
-and from 0.52 to 0.82 for \emph{Revival} when excluding the not so
-confident lower third of predictions in Panel B.
-
-The majority of misclassifications is concentrated in temporally
-adjacent eras: 10 percent of \emph{Late Victorian/Edwardian} buildings
-are labelled as \emph{Early Victorian} or 18 percent of \emph{Postwar}
-buildings are erroneously regarded as stemming from the \emph{Interwar}
-period. Hardly ever is a contemporary building mistaken for a historic
-home.
-
-\begin{center}
-  -- Insert Figure \ref{fig:vint_examples} about here --
-\end{center}
-
-Overall, the spatial softmax classification incorporating the nearest
-neighbor's feature vector outperforms the base classifier: pairwise
-differences of the \(F_1\)-scores from the spatial and the base
-classifier are clearly positive (Fig. \ref{fig:boxplot}). AIC values for
-28 binomial models based on Eq. \ref{eq:rev} decrease as hedonic
-characteristics, location and time dummies are augmented by the base and
-spatial ML predictor (Table \ref{tab:aic}). For all building styles, the
-AIC are lowest for the spatial ML predictor. In sum, the spatial
-classifier performs better for UK style data than a classifier based on
-single buildings only.
-
-\begin{center}
-  -- Insert Table \ref{tab:aic} and Figure \ref{fig:boxplot} about here --
-\end{center}
-
-\hypertarget{hedonic-regression-estimates}{%
-\subsection{Hedonic regression
-estimates}\label{hedonic-regression-estimates}}
-
-Successively, the estimated coefficients from 8 different versions of
-the hedonic regression specified in Eq. (\ref{eq:hed}) are reported in
-Tables \ref{tab:hedreg} and \ref{tab:hedregint}. For all models, the
-hedonic control variables show the expected signs: Negative coefficients
-for the relative distance to the city center, discounts for terraced
-homes and semi-detached homes relative to detached houses, positive
-elasticities for building floor plate and building volumes and a price
-premium for new buildings compared to second-hand homes. Year and
-neighborhood dummies control for time effects and local amenities but
-their coefficients are not reported due to space constraints. The
-combination of location dummies and the distance to the city center
-measure controls for proximity to the city center \emph{within} each
-neighborhood.
+\hypertarget{Results}{%
+\subsection{Results}\label{hedonic-regression-estimates}}
+
+The estimated coefficients from 8 different versions of the hedonic regression specified in Eq.\eqref{eq:hed} are reported in Tables \ref{tab:hedreg} and \ref{tab:hedregint}.
+For all models, the hedonic control variables show the expected signs: Negative coefficients for the relative distance to the city center, discounts for terraced homes and semi-detached homes relative to detached houses, positive elasticities for building floor plate, and building volumes and a price premium for new buildings compared to second-hand homes.
+Year of sale and neighborhood dummies control for time effects and local amenities but their coefficients are not reported due to space constraints.
+The combination of location dummies and the distance to the city center measure controls for proximity to the city center \emph{within} each neighborhood.
 
@@
 
-The first column in Table \ref{tab:hedreg} presents the estimated
-regression coefficients for the architects' classifications. The base
-style \emph{Contemporary} is more expensive than almost all other
-styles, which show negative coefficients that are significantly
-different from 0. A clear pecking order appears: \emph{Georgian} and
-\emph{Revival} buildings demand the highest premium \((+0.04)\),
-followed by \emph{Late Victorian/Edwardian} \((+0.01)\),
-\emph{Contemporary} (base), \emph{Early Victorian} \((-0.13)\),
-\emph{Interwar} \((-0.15)\) and \emph{Postwar} \((-0.22)\).
-
-The sample of images classified by architects is not necessarily
-representative of the overall population so we re-estimate the model
-using machine classifications for \emph{all} buildings for which we were
-able to extract usable pictures from Google Street View. Overall, the
-style coefficients become more positive relative to the base, implying
-that our automatic classification is biased and tends to classify bland
-or low quality buildings to the \emph{Contemporary} style. Reversely,
-more attractive or higher quality buildings are disproportionately often
-misclassified as \emph{Late Vic./Edw.}, pushing up the corresponding
-coefficient to \(0.11\). This bias vanishes in the third model, which
-uses only confidently estimated machine styles (Column 3).
-
-Models 4--6 follow the same logic as 1--3 but are estimated for
-\emph{new} buildings only, which are either in the contemporary or the
-revival style. Basically this contrasts houses which might \emph{look}
-different from the street, having either contemporary or revival
-facades, but which are all modern homes at their core. Differences in
-e.g.~materials, floor plans, green space and gardens are minimal. For
-newly built homes, no effect of \emph{Revival} architecture on price can
-be found for high confidence ML estimates, neither for classifications
-by machines nor by architects. After controlling for location, building
-characteristics and quality, buyers show no willingness to pay a premium
-for \emph{Revival} architecture (Columns 4 and 6).
-
-Introducing a variable capturing the most prominent style of buildings
-on the same street and within 100 m (\(\mathbf{StyleNeigh}\)) does not
-change the pecking order of building styles much (Table
-\ref{tab:hedreg}, Column 7). Neighboring styles are compared to the base
-case of a \emph{Contemporary} house in a \emph{Contemporary} street. The
-negative coefficients on dissimilar neighboring styles support a finding
-by \textcite{Lindenthal2017} that shows that a harmonious match of a
-building's shape with its direct environment leads to a price premium --
-or a discount in case of shape mismatches. In relative terms,
-\emph{Postwar} buildings are the least popular neighbors. The difference
-between \emph{Revival} and \emph{Contemporary} neighbors is not
-statistically significant. We fail to find evidence in favor of positive
-externalities from revival architecture. Everything else equal,
-buildings within ensembles of \emph{Contemporary} generally do not
+Column (1) in Table \ref{tab:hedreg} presents the estimated
+regression coefficients for a rudimentary base model: Hedonic variables, location and time dummies jointly explain more than three-quarters of the variation in transaction prices and the root mean square error (RMSE) is 0.235.
+
+Adding the architects' classifications as explanatory variables in Model (2), reduces the RMSE to 0.225 - which is 4 percent lower than the error in (1).
+The coefficients on the architectural styles reveal an interesting and intuitive pattern: The base style \emph{Contemporary} is more expensive than almost all other styles, which show negative coefficients that are significantly
+different from 0.
+A clear pecking order appears:  \emph{Postwar} exhibits the strongest price discount \((-0.22)\), followed by \emph{Interwar} \((-0.14)\), and \emph{Early Victorian} \((-0.13)\).
+These discounts are economically and statistically significant.
+We do not detect a significant price differential for  \emph{Georgian} and \emph{Late Victorian/Edwardian} properties, while \emph{Revival} architecture appears to command a small premium \((+0.04)\) over homes built in the \emph{Contemporary} style.
+Model (3) uses the ML predictions for the style variables instead of the architect's expert classifications.
+Overall, the style coefficients become more positive relative to the base.
+It must be the case that there is a negative correlation between properties incorrectly classified as \emph{Contemporary} and sales price.
+This may result from the disproportionate misclassification of more attractive or higher quality \emph{Contemporary} to one of the other styles or less attractive buildings being misclassified as \emph{Contemporary}.
+This bias vanishes in Model (4), which uses only ML classifications of high confidence (at the cost of dropping 1/3 of the sample).
+The RMSE creeps slightly up for Models (3) - but is lower for (4) than for the model with the architect defined style covariates (admittedly, the sample has changed, so the comparison is not fair).
+Importantly, Model (4) shows that the ML-based results approximate the architects' estimates (Model 2) if the analysis is restricted to high confidence classifications.
+
+Model (5) is a falsification test to investigate if unobservable variables correlated with style are driving our results.
+We select all cases in which the experts and the ML classifier disagree (3,063 observations) and re-estimate Model (2).
+This basically leaves only the 'difficult to classify' images.
+If the correlation of architectural style with unobserved building quality, age, interior updates, backyard sizes, etc.
+are actually driving results then these estimates should be the same as those in Model (2).
+If, on the other hand, distinct and easily recognizable architectural style really matters and correlated unobservables are not driving the results, then these point estimates should be insignificant.
+Interestingly, the architects' (true!) classifications cease to have a strong price effect.
+All coefficients gravitate towards 0 -- even the significant discount on \emph{Postwar} is cut in half.
+Apparently, if exterior styles are more difficult to categorize, the style classifications might still matter to architects but are less meaningful for buyers and sellers.
+For this reason, we base the remaining analysis on the set of high confidence machine observations where the observable hedonic attributes of architectural style are more clearly defined.
+
+In Model (6), we control for age and quality by selecting only transactions of new homes of either \emph{Contemporary} or \emph{Revival} styles.\footnote{The comparison may only be done on these style types as the buildings with the other architectural styles are inherited from previous eras and are no longer constructed.}  Basically, this contrasts houses that might \emph{look} different from the street, having either contemporary or revival façades, but which are all modern homes at their core.
+All have been built according to modern specifications, using the same technologies and materials, and only differ in their appearance.
+After controlling for location, building characteristics and quality, buyers show no willingness to pay a premium for \emph{Revival} architecture.
+
+Exploring the impact of the prominent style of buildings on the same street and within 100 m (\(\mathbf{StyleNeigh}\)) of the sales property, we find that the magnitude and significance of the own style estimates in Table \ref{tab:hedreg}, Column 3 and Column 7, are stable and the rank ordering of the style impact is maintained.
+Neighbor style does have a small if muted impact on prices.
+\emph{Postwar}, \emph{Early Victorian} and \emph{Interwar} buildings are the least popular neighbors.
+Other neighbors are economically and statistically insignificant relative to a \emph{Contemporary} neighborhood.
+Importantly, we find no evidence in favor of positive externalities from revival architecture: the difference between \emph{Revival} and \emph{Contemporary} neighbors is not statistically significant.
+Everything else equal, buildings within ensembles of \emph{Revival} do not
 achieve higher transaction prices than buildings in more historic areas
@@
 
-Table \ref{tab:hedregint} presents the \(\iota\) interaction
-coefficients (Eq. \ref{eq:hed}) for style-neighboring style combinations
-with sufficient numbers of observations (see Table \ref{tab:vintneigh}).
-The last row suggests that a general claim that \emph{Revival} neighbors
-exert positive externalities and increase property values relative to
-\emph{Contemporary} surroundings cannot be confirmed empirically. Again,
-we find no statistically significant difference.
+Table \ref{tab:hedregint} presents the \(\iota\) interaction coefficients (Eq.
+\ref{eq:hed}) for style-neighboring style combinations.
+Some style combinations have insufficient numbers of observations, as tabulated in Table \ref{tab:vintneigh}, and drop out.
+Neighboring styles are compared to the base case of a \emph{Contemporary} house in a \emph{Contemporary} street.
+We find that after controlling for neighborhood and building style, there is little additional impact from the building neighborhood interaction terms.
+The main exception to this rule is the positive impact that a \emph{Georgian} style building in a \emph{Georgian}, \emph{Early Victorian}, or \emph{Late Victorian/Edwardian} neighborhood.
+The negative (although statistically insignificant) coefficients on dissimilar neighboring styles support a finding by \textcite{Lindenthal2017} that shows that a harmonious match of a building's shape with its direct environment may lead to a price premium.
 
@@
 \emph{Revival} facades over modern designs can be observed (differences
-in last two columns of Table \ref{tab:comb}). For large scale new
+in the last two columns of Table \ref{tab:comb}). For large scale new
 construction, however, \emph{Revival} buildings surrounded by other
-historicizing buildings do not sell for more than \emph{Contemporary}
+historical buildings do not sell at a premium relative to \emph{Contemporary}
 buildings in a more modern setting.
+
+As a final robustness check, we present rerun the pricing models and include with year and neighborhood ($ \mathbf{Y}\times\mathbf{Loc}$) interaction effects.
+The main limitation of introducing the interaction is that we do not have enough observations to run Model (5) and  which was based on the set of new constructions due to the limited sample size.
+The results are shown in Table \ref{tab:hedreg_year_loc_int}.
+
+\begin{center}
+    -- Insert Table \ref{tab:hedreg_year_loc_int} about here --
+\end{center}
 
@@
 
-The contributions of this paper are threefold: First, it introduces an
-algorithm that collects pictures of \emph{individual} buildings from
+In this paper, we study the relationship between architectural style and residential sales price.
+We present evidence for economically significant price differences between buildings from different architectural styles -- but not for architectural style on its own.
+Analyzing house transaction prices from Cambridge, we find that any marginal price estimates are very similar for classifications by both human experts and confident ML classifiers.
+The preferred architectural style for resales appears to be \emph{Revival} with \emph{Interwar}, \emph{Postwar}, and \emph{Early Victorian} commanding the smallest premium.
+Immediately proximate neighbor styles also have an impact on sales price, with Contemporary neighborhoods clearly preferred to \emph{Georgian, Early Victorian,} and \emph{Postwar}.
+The effects are much more strong in images where architectural style is easily defined.
+
+Importantly, for policymakers, we do not identify a premium on either \emph{Revival} or \emph{Contemporary} styles for new construction.
+After accounting for building quality and location, which tend to be better for older vintages, no evidence for a premium for historicizing architecture emerges from data on newly built homes.
+Observing the real-life choices made by home-buyers is more informative than any debate of aesthetics fueled by newspaper columnists, think tanks, or ideological beliefs in general.
+
+Our analysis also highlights that it is very helpful to collect and analyze property images taken from the street perspective.
+This may be especially useful in contexts such as ours where traditional hedonic data is thin or in applications where predictive power is the goal.
+Including architectural style also reduces the RMSE of our models and we are certain that many more variables can be harvested from street-level images.
+
+%For newly constructed homes, we do not find a positive price effect of revival architecture on neighboring homes.
+Objecting to new construction might be in the interest of existing home-owners as it limits supply and thereby drives up the value of their homes.
+Objections based on architectural preferences are not supported by market data.
+
+%4) Architect vs machine: The machine seems to see things that the architects did not pick up - Model (5)
+
+On the more technical side, this paper offers four contributions: First, it introduces an algorithm that collects pictures of \emph{individual} buildings from
 Google Street View. Earlier work has not achieved this level of detail
@@
 only in the UK. The image collection and classification method can
-easily be ported to other study areas which have existing Street View
-data and either LIDAR based building outlines or high resolution
-satellite images. In a follow-up project, we are working on an improved
+easily be ported to other study areas that have existing Street View
+data and either LIDAR based building outlines or high-resolution satellite images. In a follow-up project, we are working on an improved
 classification workflow in which a customized object detection model is
@@
 feature vectors of buildings and their nearest neighbors to exploit
-spatial correlation in observed classifications.
-
-The large ground truth data set allows for a comparison of human expert
-versus machine classifications. Poor image quality, for instance
+spatial correlation in observed classifications. The large ground truth data set allows for a comparison of human expert versus machine classifications. Poor image quality, caused by
 obstructed views or the lack of informative features such as windows, is
 correlated with misclassifications. Importantly, for cases in which the
-ML classifiers are relatively indecisive between classes, visual cues
-that are correlated with the exterior's style but not part of a
-building's architecture (for instance trees or cars) bias the estimates.
-For these less certain cases, more valuable homes are systematically
-more likely to be classified as e.g.~\emph{Late Victorian/Edw.} and less
-likely to be considered \emph{Contemporary}. A follow up study could
+ML classifiers are relatively indecisive between classes, the hedonic estimates of architect classified styles are attenuated. A follow-up study could
 investigate which elements in the building pictures lead to the
@@
 
-Third, we test whether revival or vernacular architecture leads to price
-premia over contemporary architecture. We do not find evidence for a
-preference of residents for specific architecture after controlling for
-quality and location of buildings. This applies to both direct price
-effects but also indirect effects of a building's appearance on the
-value of neighboring homes. Further work will extend the spatial scope
-of the study area to the UK in general and to other countries.
+Third, we explore how spatial dependencies in image classifications can be exploited in deep neural networks.
+Including information from neighboring houses improves the predictive power of the image classifier significantly.
+
+The last contribution is more practical.
+We investigate how prediction accuracy is influenced by the image quality and find the obvious: Obstructions in the line-of-sight such as trees or cars make pictures of houses less informative.
+Future research could utilize building images taken from multiple angles to circumvent obstacles and to arrive at more reliable classifications.
+Street-level images are an excitingly rich data source for urban economics and real estate research -- it just takes a bit of effort to tap into it.
 
@@
 
+\begin{table}[!htbp] \centering 
+  \caption{Architectural Style Descriptions}
+  \label{tab:styles_rubric} 
+\begin{tabular}{@{\extracolsep{5pt}}lll} 
+\toprule
+Style & \multicolumn{1}{c}{Era} & \multicolumn{1}{c}{Characteristics} \\ 
+\midrule
+Georgian & c1714--1837 &  sash windows, fan lights above doors, stucco on facades, \\
+& & wrought work grilles and railings\\
+& & \\
+Early Victorian & c1837-c1870s & elaborate features such as carved barge boards or finials. \\
+& & sash windows more affordable and wider \\
+& & \\
+Late Victorian/Edwardian & c1870s-1910 & substantial bay windows,\\
+& & heterogeneous ornamentation, stained glass \\
+& & \\
+Interwar & 1918-1939 & cost of building construction falls,  \\
+ & & Distinctive two-pane windows \\
+& & \\
+Postwar & 1950-1980 & embrace of high-rise as well as low-rise housing. Facades \\
+& &  vary between brick, tiling, pebbledash and render. \\
+& & \\
+Contemporary & 1980 - present & innovative and distinctive building techniques \\
+& & \\
+Revival & & contemporary buildings that emulate historic, \\
+& & mostly replica Victorian architecture \\
+\bottomrule
+\end{tabular}
+
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\singlespacing
+\footnotesize \emph{Notes:} Prepared by members the Architecture Department at the University of Cambridge.
+\end{minipage}
+\end{table}
+
+\begin{figure}[htb!]
+\caption{Examples of Architectural Styles}
+\begin{tabular}{lllllll}
+  \hline
+\emph{Georg.} & \emph{Early Vic.} & \emph{LateV/Ed} & \emph{Interwar} & \emph{Postwar} & \emph{Contemp.} & \emph{Revival} \\ 
+  \hline
+\includegraphics[width=45px]{images//0001000010058205_KqBBtZS8ecncUe8oqjErqQ.jpg} & \includegraphics[width=45px]{images//0001000010102767_u_7T3iAyG9xNgeN_ETY7aQ.jpg} & \includegraphics[width=45px]{images//0001000010141478_FT9houQ2x66NPnNEGxTkvA.jpg} & \includegraphics[width=45px]{images//0001000010065714_pzExlR026vDKdQaJiLkdkw.jpg} & \includegraphics[width=45px]{images//0001000010137600_qYxYCsLRPpOfCyv8IjfnlA.jpg} & \includegraphics[width=45px]{images//1000002057677225_srJnz_31ujVFzn-xh_DYfw.jpg} & \includegraphics[width=45px]{images//1000002500413689_VylY6Sy3vLvjqbtHeryMdQ.jpg} \\
+  \includegraphics[width=45px]{images//0001000010056385_XQsTJ2p5Te54CScFmblMHA.jpg} & \includegraphics[width=45px]{images//0001000010102769_c_e4WlmafqN2JXQ2ZhYEkw.jpg} & \includegraphics[width=45px]{images//0001000010017237_yWs7fxQ0r8Ecx_ajaYc-rg.jpg} & \includegraphics[width=45px]{images//0001000010141115_xG0eSas79cN59fH4xvm5Yw.jpg} & \includegraphics[width=45px]{images//0001000010023665_B2Is2WMV8SGjf7Tg9tLS7w.jpg} & \includegraphics[width=45px]{images//1000002500748070_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{images//0001000010176986_bNOie2HS7GPQxPOtoevEHw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010058145_xBAz4f8lI2MTivvvWv6wyQ.jpg} & \includegraphics[width=45px]{images//0001000010103488_Y1L2niOkEGB1IKe4tsl1yw.jpg} & \includegraphics[width=45px]{images//0001000010021367_JF-P4lOQQouZ6lHtM4J3oA.jpg} & \includegraphics[width=45px]{images//0001000010065349_HDvoqsiHXGx4xc62JSUNJA.jpg} & \includegraphics[width=45px]{images//0001000009993819_748OTBKSFyJZU2DP7TbboQ.jpg} & \includegraphics[width=45px]{images//1000002057677000_8l6ywNIej2136uZeb3qKqA.jpg} & \includegraphics[width=45px]{images//1000002500088807_4vu-eMLHmhX3JmHNwyulmQ.jpg} \\
+  \includegraphics[width=45px]{images//0001000010059206__nUymOPxCgpQugahoE7EPw.jpg} & \includegraphics[width=45px]{images//0001000010103870_ywN_BuvuLW6kbLLP0QgJMA.jpg} & \includegraphics[width=45px]{images//0001000010017412_aOsldmaOT-MAce6q6qkmTQ.jpg} & \includegraphics[width=45px]{images//0001000010107971_veilqmDOA-AfCuz4tWyg7g.jpg} & \includegraphics[width=45px]{images//0001000010025542_8rvXwCYBTCQu0eVM9nhN9Q.jpg} & \includegraphics[width=45px]{images//1000002500555322_FffLx_XVBUOvZgiXRdSAnA.jpg} & \includegraphics[width=45px]{images//0001000010066754_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010060140_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{images//0001000010103819_mF6OqQrRTOlAoGdaraQsTQ.jpg} & \includegraphics[width=45px]{images//0001000010097999_xTD3YceIrtPJZwPz5d0G6Q.jpg} & \includegraphics[width=45px]{images//0001000010065347_pouLRqJd7pkk41jryvYQ4A.jpg} & \includegraphics[width=45px]{images//0001000009992776_QxMV8eRavS1riXfGzpSkBw.jpg} & \includegraphics[width=45px]{images//1000002500555341_NVXmLF7mim1nGBZAdgw_ew.jpg} & \includegraphics[width=45px]{images//1000002500569086_g5RwBQ7D5edS2obfSogNIw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010060139_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{images//0001000010101711_wNQ403N-0pQd5fChNztfYA.jpg} & \includegraphics[width=45px]{images//0001000010021374_55tKverBLF4C0oo8U4XABg.jpg} & \includegraphics[width=45px]{images//0001000010065352_kDKqKaGpPwLeCBKJIQmeCg.jpg} & \includegraphics[width=45px]{images//0001000010015484_zlR1vVJ7F0L6hcsFoZEydw.jpg} & \includegraphics[width=45px]{images//1000002500548748_i6QAKtN2HhGsTVDBan2DKw.jpg} & \includegraphics[width=45px]{images//1000002057955271_dMXMWNaIwddWdHidEuXowA.jpg} \\
+  \includegraphics[width=45px]{images//0001000010060141_W3ZIE8mPY6LJb-_hKatlUw.jpg} & \includegraphics[width=45px]{images//0001000010103226_XO6qx_5Q9tNnNF958OBO3g.jpg} & \includegraphics[width=45px]{images//0001000010017109_MbGvl1GxhZjQ_qhD7puDBw.jpg} & \includegraphics[width=45px]{images//0001000009995496_N4NgCofyWASyYfcSPTjdBA.jpg} & \includegraphics[width=45px]{images//0001000010068890_aswyTpwrE_IfdbINnYx7XQ.jpg} & \includegraphics[width=45px]{images//0001000010104229_qFV1-weLxn8SRW4Ib2wexQ.jpg} & \includegraphics[width=45px]{images//0001000010199676_smIagQ34MLIcJOrjvIu9uw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010059966_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{images//0001000010101704_ZQFxujswdAj7EGqRlp8sXQ.jpg} & \includegraphics[width=45px]{images//0001000010017361_WxMCM3nht5EX_K9pqIK-kQ.jpg} & \includegraphics[width=45px]{images//0001000010066620_4TqmJVLf3urSJo4ESg1zfw.jpg} & \includegraphics[width=45px]{images//0001000010023689_KpXUKEdjoQ9swgoB2oXA3w.jpg} & \includegraphics[width=45px]{images//1000002500748058_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{images//0001000010066718_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010060813_VlKeIvrTv6UwOE9HD2LgJg.jpg} & \includegraphics[width=45px]{images//0001000010103859_P5YwPMree6QCxExkKqIzbw.jpg} & \includegraphics[width=45px]{images//0001000010141515_5g5Bhsn_4iW-90aFMrIaSA.jpg} & \includegraphics[width=45px]{images//0001000010066361_gliMrVbagcfkfZjLw4mKlw.jpg} & \includegraphics[width=45px]{images//1000002500527045_p4zTtg8OzsbWjHYscCf-rA.jpg} & \includegraphics[width=45px]{images//1000002500748076_zDr74LLmVeyKyx7dPnXK6A.jpg} & \includegraphics[width=45px]{images//1000002500413682_drSMg0SQ9TU4Og8pXOgSxw.jpg} \\
+  \includegraphics[width=45px]{images//0001000010059967_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{images//0001000010103388_CZH157SXYmF3dEVMKlWBfQ.jpg} & \includegraphics[width=45px]{images//0001000010025644_bJ8zv37pDsP0CImvDMKC0w.jpg} & \includegraphics[width=45px]{images//0001000010144910_COpJNwPw67J78VXCoN_HMA.jpg} & \includegraphics[width=45px]{images//0001000009992797_JUTa4GsWaXplyCP6XeVAvw.jpg} & \includegraphics[width=45px]{images//1000002500086356_n92s3snPX2zAwEiJnA-Pxg.jpg} & \includegraphics[width=45px]{images//0001000010176201_dDyXoyEbeMXUhCagwazbiA.jpg} \\
+   \hline
+\end{tabular}
+\label{fig:vint_examples}
+\begin{minipage}{0.75\textwidth}
+\footnotesize \emph{Notes:} In these images, it is clear that much of the visual heterogeneity in style is due to differences in windows, doors, and rooflines.
+For example, there are clear differences across styles based on groupings and number of panes per windows and shapes of pediments, lintels, or fanlights above doors.
+Some characteristics stand out such as the presence of bay windows for Late V./Edwardian properties and angularity, asymmetry of windows in the Contemporary class, and roofing style and setback in the Postwar period.
+\end{minipage}
+\end{figure}
+
+\clearpage
+
 \begin{figure}[hbt]
-  \caption{`Street View', not `Building View' -- Identification of buildings remains a challenge in the UK}
+  \caption{Improving Camera Aim for Automatic Image Collections}
   \centering
   \vspace{0.25cm}
-    \includegraphics[width=0.8\textwidth]{figures/84VineryRD.png}
+  \begin{tabular}{cc}
+    \includegraphics[width=0.55\textwidth]{figures/84VineryRD.png} & \includegraphics[width=0.3\textwidth]{figures/84VineryRoadGoodAim.png} \\
+    \emph{(a) Default Camera Aim} & \emph{(b) Improved Aim}\\
+
+\end{tabular}
+
   \label{fig:84Vin}
@@
 \emph{Notes:} For the UK, the Google Street View API returns the coordinates of the nearest camera snapshot for a given location but fails to provide an accurate orientation and zoom-level of the camera needed to capture the front of the building exactly.
-In this typical example, the building of interest is only partially shown at the very left margin of this result.
+In (a) the building of interest is not even visible in the picture.
+The image at (b) was taken with pan and zoom parameters, derived by our viewshed algorithm.
+Even for a terraced property, the structure contains minimal neighbor information, the roofline is captured, vehicles on the street are not visible the image is not obstructed by other structures.
 \emph{Image source}: Google Street View. 
@@
 \end{figure}
-
-\newpage
 
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{Summary statistics residential property transactions} 
-  \label{tab:sumstats} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\toprule
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\midrule
-Price & 23,768 & 253,646.20 & 170,987.20 & 10,000 & 127,000 & 326,374.8 & 1,000,000 \\ 
-Year & 23,768 & 2,004.89 & 6.59 & 1,995 & 1,999 & 2,010 & 2,018 \\ 
-ln(volume) & 23,768 & 286.00 & 188.14 & 0.00 & 215.50 & 370.89 & 1,926.45 \\ 
-ln(area) & 23,768 & 63.25 & 28.44 & 4.94 & 45.74 & 72.46 & 1,058.70 \\ 
-ln(dist. city center) & 23,768 & 2,477.63 & 1,007.55 & 112.78 & 1,652.39 & 3,166.05 & 5,023.62 \\ 
-New & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
-Type: detached & 23,768 & 0.13 & 0.34 & 0 & 0 & 0 & 1 \\ 
-Type: semi-detached & 23,768 & 0.35 & 0.48 & 0 & 0 & 1 & 1 \\ 
-Type: terraced & 23,768 & 0.52 & 0.50 & 0 & 0 & 1 & 1 \\ 
-Georgian & 23,768 & 0.03 & 0.16 & 0 & 0 & 0 & 1 \\ 
-Early Vic. & 23,768 & 0.15 & 0.36 & 0 & 0 & 0 & 1 \\ 
-Late Vic./Edw. & 23,768 & 0.21 & 0.40 & 0 & 0 & 0 & 1 \\ 
-Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
-Postwar & 23,768 & 0.23 & 0.42 & 0 & 0 & 0 & 1 \\ 
-Contemporary & 23,768 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
-Revival & 23,768 & 0.04 & 0.20 & 0 & 0 & 0 & 1 \\ 
-Neigh: Georgian & 23,768 & 0.02 & 0.12 & 0 & 0 & 0 & 1 \\ 
-Neigh: Early Vic. & 23,768 & 0.14 & 0.35 & 0 & 0 & 0 & 1 \\ 
-Neigh: Late V./Edw. & 23,768 & 0.22 & 0.41 & 0 & 0 & 0 & 1 \\ 
-Neigh: Interwar & 23,768 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
-Neigh: Postwar & 23,768 & 0.25 & 0.43 & 0 & 0 & 1 & 1 \\ 
-Neigh: Contemporary & 23,768 & 0.02 & 0.15 & 0 & 0 & 0 & 1 \\ 
-Neigh: Revival & 23,768 & 0.03 & 0.18 & 0 & 0 & 0 & 1 \\ 
-\bottomrule
-\end{tabular} 
-\begin{minipage}{\textwidth}
-\vspace{0.25cm}
-\singlespacing
-\footnotesize \emph{Notes:} Summary statistics for sample of 23,768 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images.
-The buildings floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models (Lindenthal, 2017b).
-We control for the location of each building by calculating the distance to the city center proxied by Great St.
-Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA).
-Building styles based on machine classifications.
-\end{minipage}
-\end{table}
+\input{confusion_matrix.tex}
 
@@
 
-\input{confusion_matrix.tex}
-
-\newpage
-
-\begin{table}[!htb] 
-\caption{Prediction certainty: Herfindahl index from ensemble model} 
-\label{tab:herftab} 
-\footnotesize
-\begin{tabular}{lccccccc}
-\toprule 
-  & \multicolumn{7}{c}{\emph{Architects}} \\ 
-  \cmidrule(lr){2-8} 
-& Georgian &  Early Vic. & Late V. /Edw. & Interwar & Postwar & Cont. & Revival \\
-
-Mean Herf. & 0.88 &  0.80 & 0.79 & 0.77 & 0.68 &  0.70 &  0.70 \\  
- \midrule 
-\emph{Machine} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
-\cmidrule(lr){2-8} 
-Georgian & -- & -0.21 (-9.87) & -0.28 (-13.11) & -0.33 (-9.95) & -0.27 (-6.30) & -0.25 (-7.97) & -0.25 (-7.54) \\
- Early Vic. & -0.22 (-6.28) &  -- & -0.19 (-19.20) & -0.31 (-13.70) & -0.21 (-10.05) & -0.21 (-7.53) & -0.15 (-3.84) \\
- Late V./Edw. & -0.36 (-5.89) & -0.24 (-18.03) &  -- & -0.26 (-21.88) & -0.23 (-9.08) & -0.24 (-4.96) & -0.16 (-4.33) \\
- Interwar & -0.12 (-1.55) & -0.32 (-12.77) & -0.24 (-19.87) &  -- & -0.13 (-22.67) & -0.25 (-12.58) & -0.16 (-6.49) \\
- Postwar & -0.51 (-33.71) & -0.30 (-6.24) & -0.36 (-13.13) & -0.26 (-34.82) & -- & -0.22 (-10.34) & -0.24 (-7.70) \\
- Cont. & -0.44 (-3.31) & -0.37 (-17.78) & -0.38 (-17.63) & -0.39 (-25.39) & -0.18 (-15.67) & -- & -0.19 (-7.71) \\
- Revival & -0.09 (-0.42) & -0.40 (-20.64) & -0.41 (-22.54) & -0.31 (-19.71) & -0.28 (-24.06) & -0.22 (-12.40) &  -- \\
-\bottomrule 
-\end{tabular}
-\begin{minipage}{\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 styles $s$ received, calculated as: $Herf_i=\sum_{s=1}^{s=7} (votes_s/votes_{all})^2$.
-A high score indicates high levels of consensus within the ensemble.
-The Herf.
-scores tend to be lower at off-diagonal cells, indicating lower consensus for misclassifications.
-\end{minipage}
-\end{table}
-
-\newpage
 \clearpage
-
-\begin{table}[ht] 
-\centering 
- \caption{Mean Values for image quality variables, by style}
-
-\label{tab:imgqualsumstats}
-\begin{tabular}{lcccc} 
-\toprule 
-Architects' classifications & Share Blocked & House Area & Window Area & Image Offset \\ 
-\midrule
- Georgian & 0.07 & 0.81 & 0.15 & 0.07 \\ 
- Early Vic. & 0.06 & 0.86 & 0.16 & 0.05 \\ 
- Late V./Edw. & 0.11 & 0.84 & 0.17 & 0.08 \\ 
- Interwar & 0.19 & 0.70 & 0.11 & 0.12 \\ 
- Postwar & 0.16 & 0.64 & 0.07 & 0.11 \\ 
- Cont. & 0.09 & 0.72 & 0.11 & 0.09 \\ 
- Revival & 0.10 & 0.78 & 0.11 & 0.09 \\ 
- \bottomrule
-\end{tabular}
-\begin{minipage}{0.9\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated.
-Images not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
-\end{minipage}
-\end{table}
-
-\newpage
-\clearpage
-
-\begin{table}[!htb] 
-\caption{Difference in photo characteristics by correctly and incorrectly classified images} 
-\label{tab:diffimgchar} 
-\centering 
-\begingroup\scriptsize 
-\begin{tabular}{lrrrrrrr}
-
-\toprule
-
-\emph{Machine} & \multicolumn{7}{c}{\emph{Architects}} \\ 
-  \cmidrule(lr){2-8} 
-& Georgian & Early Vic. & Late V./Edw. & Interwar & Postwar & Cont. & Revival \\
-
- \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel A: Total share of house blocked by vehicles or trees}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
-Georgian &  -- &  0 (0.16) & -0.03 (-1.37) & -0.07 (-2.16) & -0.06 (-0.91) & -0.02 (-0.86) &  0.02 (0.39) \\  
-  Early Vic. & -0.04 (-2.80) &  -- & -0.04 (-7.42) & -0.11 (-8.26) & -0.09 (-5.45) & -0.03 (-1.97) &  0.01 (0.47) \\  
-  Late V./Edw. &  0.03 (0.91) &  0.03 (2.55) &  -- &  0.01 (0.40) &  0.01 (0.57) &  0.01 (0.17) &  0.08 (1.89) \\  
-  Interwar &  0.17 (2.24) &  0.11 (3.71) &  0.09 (5.73) &  -- &  0.03 (4.16) &  0.18 (4.42) &  0.07 (2.40) \\  
-  Postwar &  0.13 (0.96) &  0.03 (1.44) &  0.11 (2.88) & -0.01 (-1.20) &  -- &  0.09 (3.39) &  0.04 (1.09) \\  
-  Cont. &  0.16 (0.77) & -0.02 (-1.91) &  0.03 (1.14) & -0.03 (-0.92) & -0.04 (-3.06) &  -- & -0.03 (-1.32) \\  
-  Revival &  0.18 (0.74) &  0.03 (0.92) &  0.01 (0.26) & -0.05 (-3.03) & -0.06 (-4.90) &  0.04 (2.02) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel B: Share of house area}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
-  Georgian &  -- & -0.11 (-3.43) & -0.10 (-2.67) &  0.09 (1.94) &  0.10 (0.96) &  0.11 (1.29) & -0.02 (-0.31) \\  
-  Early Vic. &  0.05 (1.30) &  -- &  0.03 (1.75) &  0.07 (2.45) &  0.18 (5.01) &  0.12 (2.19) &  0.05 (1.03) \\  
-  Late V./Edw. & -0.09 (-2.08) & -0.07 (-3.10) &  -- &  0.02 (1.07) &  0.08 (2.23) & -0.08 (-1.29) &  0.04 (0.71) \\  
-  Interwar &  0.08 (0.55) & -0.16 (-3.68) & -0.14 (-6.48) &  -- &  0.03 (2.92) & -0.04 (-1.03) & -0.09 (-2.65) \\  
-  Postwar & -0.33 (-1.98) & -0.24 (-3.82) & -0.18 (-3.25) & -0.05 (-4.60) &  -- & -0.12 (-2.78) & -0.16 (-4.57) \\  
-  Cont. & -0.21 (-1.58) & -0.16 (-2.99) & -0.15 (-3.45) & -0.02 (-0.55) &  0.01 (0.23) &  -- & -0.06 (-1.43) \\  
-  Revival & -0.03 (-0.15) & -0.04 (-0.69) & -0.11 (-2.70) &  0.06 (2.51) &  0.08 (3.30) &  0.05 (1.30) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel C: Share of window area}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
- Georgian &  -- & -0.06 (-6.02) & -0.02 (-1.10) & -0.02 (-1.92) &  0.03 (1.26) & -0.03 (-1.28) & -0.01 (-0.42) \\  
-  Early Vic. & -0.01 (-0.60) &  -- & -0.01 (-1.51) &  0.03 (2.72) &  0.04 (5.30) &  0.01 (0.70) &  0.02 (1.83) \\  
-  Late V./Edw. &  0 (0.09) & -0.02 (-2.67) &  -- &  0.04 (4.85) &  0.02 (1.81) &  0.02 (0.98) &  0.02 (1.59) \\  
-  Interwar & -0.03 (-0.92) & -0.09 (-10) & -0.08 (-13.20) &  -- &  0.01 (2.98) & -0.03 (-2.41) & -0.03 (-3.48) \\  
-  Postwar & -0.07 (-4.42) & -0.09 (-5.80) & -0.08 (-4.50) & -0.02 (-4.95) &  -- & -0.05 (-4.42) & -0.05 (-5.63) \\  
-  Cont. & -0.07 (-2.04) & -0.08 (-6.97) & -0.05 (-3.73) & -0.01 (-1.46) &  0.01 (2.50) &  -- & -0.02 (-2.58) \\  
-  Revival & -0.02 (-0.18) & -0.06 (-4.39) & -0.03 (-1.71) &  0.01 (1.04) &  0.02 (2.50) & -0.02 (-2.33) &  -- \\
-
-\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
- & \multicolumn{7}{c}{\emph{ Panel D: Image offset}}\\ 
-\cmidrule(lr){1-1} \cmidrule(lr){2-8}
-
- Georgian &  -- &  0.04 (5.44) &  0.02 (2.61) & -0.02 (-1.71) & -0.03 (-1.33) &  0.01 (1) &  0.01 (0.55) \\  
-  Early Vic. &  0.01 (0.64) &  -- & -0.02 (-6.59) & -0.03 (-3.82) & -0.04 (-4.98) & -0.01 (-0.93) & -0.03 (-2.78) \\  
-  Late V./Edw. &  0.04 (1.96) &  0.03 (4.68) &  -- & -0.01 (-1.25) & -0.02 (-2.14) &  0.01 (0.46) &  0 (0.25) \\  
-  Interwar &  0.03 (1.16) &  0.06 (6.28) &  0.05 (9.75) &  -- &  0.01 (2.35) &  0 (0.06) &  0.03 (3.19) \\  
-  Postwar &  0.04 (1.07) &  0.06 (3.31) &  0.04 (3.37) &  0 (1.11) &  -- &  0.02 (1.95) &  0.06 (4.20) \\  
-  Cont. &  0.08 (2.11) &  0.05 (3.87) &  0.04 (3.40) & -0.01 (-1.32) & -0.02 (-4.26) &  -- &  0 (0.20) \\  
-  Revival &  0 (0.02) &  0.03 (2.06) &  0.01 (1) & -0.01 (-1.85) & -0.01 (-1.02) &  0.02 (2.22) &  -- \\  
-\bottomrule
-
-\end{tabular} 
- \begin{minipage}{\textwidth} 
-\footnotesize 
-\vspace{0.25cm}
-\emph{Notes:} Cross-tabulation of photo characteristics by machine and architects' classifications.
-Off-diagonal elements ($Machine_{j}-Architects_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given classification by architects.
-For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic.
-to the set of correctly classified Georgian photos.
-T-stats are in parenthesis.
-\end{minipage} 
-\endgroup 
-\end{table}
-
-\newpage
-\clearpage
-
-\begin{figure}[htb!]
-\caption{Examples of machine-based style classifications}
-\begin{tabular}{lllllll}
-  \hline
-\emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interwar} & \emph{Postwar} & \emph{Contemp.} & \emph{Revival} \\ 
-  \hline
-\includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058205_KqBBtZS8ecncUe8oqjErqQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102767_u_7T3iAyG9xNgeN_ETY7aQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141478_FT9houQ2x66NPnNEGxTkvA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065714_pzExlR026vDKdQaJiLkdkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010137600_qYxYCsLRPpOfCyv8IjfnlA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677225_srJnz_31ujVFzn-xh_DYfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413689_VylY6Sy3vLvjqbtHeryMdQ.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010056385_XQsTJ2p5Te54CScFmblMHA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010102769_c_e4WlmafqN2JXQ2ZhYEkw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017237_yWs7fxQ0r8Ecx_ajaYc-rg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141115_xG0eSas79cN59fH4xvm5Yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023665_B2Is2WMV8SGjf7Tg9tLS7w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748070_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176986_bNOie2HS7GPQxPOtoevEHw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010058145_xBAz4f8lI2MTivvvWv6wyQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103488_Y1L2niOkEGB1IKe4tsl1yw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021367_JF-P4lOQQouZ6lHtM4J3oA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065349_HDvoqsiHXGx4xc62JSUNJA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009993819_748OTBKSFyJZU2DP7TbboQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057677000_8l6ywNIej2136uZeb3qKqA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500088807_4vu-eMLHmhX3JmHNwyulmQ.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059206__nUymOPxCgpQugahoE7EPw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103870_ywN_BuvuLW6kbLLP0QgJMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017412_aOsldmaOT-MAce6q6qkmTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010107971_veilqmDOA-AfCuz4tWyg7g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025542_8rvXwCYBTCQu0eVM9nhN9Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555322_FffLx_XVBUOvZgiXRdSAnA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066754_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060140_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103819_mF6OqQrRTOlAoGdaraQsTQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010097999_xTD3YceIrtPJZwPz5d0G6Q.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065347_pouLRqJd7pkk41jryvYQ4A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992776_QxMV8eRavS1riXfGzpSkBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500555341_NVXmLF7mim1nGBZAdgw_ew.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500569086_g5RwBQ7D5edS2obfSogNIw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060139_8_DVq9QCmlMezNuDHGixwg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101711_wNQ403N-0pQd5fChNztfYA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010021374_55tKverBLF4C0oo8U4XABg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010065352_kDKqKaGpPwLeCBKJIQmeCg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010015484_zlR1vVJ7F0L6hcsFoZEydw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500548748_i6QAKtN2HhGsTVDBan2DKw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002057955271_dMXMWNaIwddWdHidEuXowA.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060141_W3ZIE8mPY6LJb-_hKatlUw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103226_XO6qx_5Q9tNnNF958OBO3g.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017109_MbGvl1GxhZjQ_qhD7puDBw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009995496_N4NgCofyWASyYfcSPTjdBA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010068890_aswyTpwrE_IfdbINnYx7XQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010104229_qFV1-weLxn8SRW4Ib2wexQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010199676_smIagQ34MLIcJOrjvIu9uw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059966_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010101704_ZQFxujswdAj7EGqRlp8sXQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010017361_WxMCM3nht5EX_K9pqIK-kQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066620_4TqmJVLf3urSJo4ESg1zfw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010023689_KpXUKEdjoQ9swgoB2oXA3w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748058_DkW5iwQYtGox02-tF2i9rQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066718_dJmIRHcgebzrGzDR_Cahaw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010060813_VlKeIvrTv6UwOE9HD2LgJg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103859_P5YwPMree6QCxExkKqIzbw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010141515_5g5Bhsn_4iW-90aFMrIaSA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010066361_gliMrVbagcfkfZjLw4mKlw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500527045_p4zTtg8OzsbWjHYscCf-rA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500748076_zDr74LLmVeyKyx7dPnXK6A.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500413682_drSMg0SQ9TU4Og8pXOgSxw.jpg} \\
-  \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010059967_e8c8bmHUpyKpiIZ1YO9ypg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010103388_CZH157SXYmF3dEVMKlWBfQ.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010025644_bJ8zv37pDsP0CImvDMKC0w.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010144910_COpJNwPw67J78VXCoN_HMA.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000009992797_JUTa4GsWaXplyCP6XeVAvw.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/1000002500086356_n92s3snPX2zAwEiJnA-Pxg.jpg} & \includegraphics[width=45px]{/home/thies/db/Cambridge/data/images/cambridge/0001000010176201_dDyXoyEbeMXUhCagwazbiA.jpg} \\
-   \hline
-\end{tabular}
-\label{fig:vint_examples}
-\begin{minipage}{0.7\textwidth}
-\footnotesize \emph{Notes:} For a brief discussion of the building styles see page \pageref{def_eras}.
-\end{minipage}
-\end{figure}
-
-\newpage
-
-\begin{figure}[htb!]
-  \caption{Difference of $F_1$-scores: spatial model vs. base model }
-  \centering
-    \includegraphics[width=0.8\textwidth]{figures/barplot_f1scores.jpg}
-  \label{fig:boxplot}
-\begin{minipage}{0.7\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} The bar plot shows differences in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
-a classifier using building level information only (red).
-\end{minipage}
-\end{figure}
-
-\newpage
-
 \begin{table}[htb!]
-\caption{Machine style classifications as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
+\caption{ML classifications as dependent variables (Eq. \ref{eq:rev} AIC comparison) }
 \label{tab:aic}
@@
 AIC values for 28 binomial models in which the occurrence of building styles (in rows) is explained by hedonic characteristics, location and time dummies (Column 1), augmented by the base ML predictor (Column 2), and the suggested spatial ML predictor (Column 3 \& 4).
-Across building styles, the AIC are lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4).
+Across building styles, the AIC is lowest for the spatial ML predictor, especially when uncertain predictions are omitted (Column 4).
 This suggests that the spatial predictor performs best.
@@
 \end{table}
+
+\begin{figure}[htb!]
+  \caption{Difference of $F_1$-scores: spatial model vs. base model }
+  \centering
+    \includegraphics[width=0.8\textwidth]{figures/barplot_f1scores.jpg}
+  \label{fig:boxplot}
+\begin{minipage}{0.7\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} The bar plot shows differences in the $F_1$-scores per category for the classifiers using both building level and neighbor information (dark and light blue) vs.
+a classifier using building-level information only (red).
+\end{minipage}
+\end{figure}
+
+\clearpage
+
+\begin{table}[!htb] 
+\caption{Prediction certainty: Herfindahl index from ensemble model} 
+\label{tab:herftab} 
+\footnotesize
+\begin{tabular}{lccccccc}
+\toprule 
+  & \multicolumn{7}{c}{\emph{Architects}} \\ 
+  \cmidrule(lr){2-8} 
+& Georgian &  Early Vic. & Late V. /Edw. & Interwar & Postwar & Cont. & Revival \\
+
+Mean Herf. & 0.88 &  0.80 & 0.79 & 0.77 & 0.68 &  0.70 &  0.70 \\  
+ \midrule 
+\emph{ML} & \multicolumn{7}{c}{\emph{Difference from correct classifications (diagonal), t-stats in parenthesis}} \\
+\cmidrule(lr){2-8} 
+Georgian & -- & -0.21 (-9.87) & -0.28 (-13.11) & -0.33 (-9.95) & -0.27 (-6.30) & -0.25 (-7.97) & -0.25 (-7.54) \\
+ Early Vic. & -0.22 (-6.28) &  -- & -0.19 (-19.20) & -0.31 (-13.70) & -0.21 (-10.05) & -0.21 (-7.53) & -0.15 (-3.84) \\
+ Late V./Edw. & -0.36 (-5.89) & -0.24 (-18.03) &  -- & -0.26 (-21.88) & -0.23 (-9.08) & -0.24 (-4.96) & -0.16 (-4.33) \\
+ Interwar & -0.12 (-1.55) & -0.32 (-12.77) & -0.24 (-19.87) &  -- & -0.13 (-22.67) & -0.25 (-12.58) & -0.16 (-6.49) \\
+ Postwar & -0.51 (-33.71) & -0.30 (-6.24) & -0.36 (-13.13) & -0.26 (-34.82) & -- & -0.22 (-10.34) & -0.24 (-7.70) \\
+ Cont. & -0.44 (-3.31) & -0.37 (-17.78) & -0.38 (-17.63) & -0.39 (-25.39) & -0.18 (-15.67) & -- & -0.19 (-7.71) \\
+ Revival & -0.09 (-0.42) & -0.40 (-20.64) & -0.41 (-22.54) & -0.31 (-19.71) & -0.28 (-24.06) & -0.22 (-12.40) &  -- \\
+\bottomrule 
+\end{tabular}
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} For each ensemble classification $i$, we derive the Herfindahl scores as the sum of the squared share of votes from individual models for each of the 7 styles $s$ received, calculated as: $Herf_i=\sum_{s=1}^{s=7} (votes_s/votes_{all})^2$.
+A high score indicates high levels of consensus within the ensemble.
+The Herf.
+scores tend to be lower at off-diagonal cells, indicating lower consensus for misclassifications.
+\end{minipage}
+\end{table}
+
+\begin{table}[ht] 
+\centering 
+ \caption{Mean Values for image quality variables, by style}
+\label{tab:imgqualsumstats}
+\begin{tabular}{lcccc} 
+\toprule 
+Architects' classifications & Share Blocked & House Area & Window Area & Image Offset \\ 
+\midrule
+ Georgian & 0.07 & 0.81 & 0.15 & 0.07 \\ 
+ Early Vic. & 0.06 & 0.86 & 0.16 & 0.05 \\ 
+ Late V./Edw. & 0.11 & 0.84 & 0.17 & 0.08 \\ 
+ Interwar & 0.19 & 0.70 & 0.11 & 0.12 \\ 
+ Postwar & 0.16 & 0.64 & 0.07 & 0.11 \\ 
+ Cont. & 0.09 & 0.72 & 0.11 & 0.09 \\ 
+ Revival & 0.10 & 0.78 & 0.11 & 0.09 \\ 
+ \bottomrule
+\end{tabular}
+\begin{minipage}{0.9\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} Using an Inception/Resnet object detection model trained on Open Images, basic object on the images are detected and the share of the image area taken up by cars, trees, buildings and windows are calculated.
+Images not taken at an optimal angle or zoom factor are detected by calculating the offset between the bounding box for the largest detected building and the center of the image.
+\end{minipage}
+\end{table}
+
+\newpage
+\clearpage
+
+\begin{table}[!htb] 
+\caption{Differences in photo characteristics by correctly and incorrectly classified images} 
+\label{tab:diffimgchar} 
+\centering 
+\begingroup\scriptsize 
+\begin{tabular}{lrrrrrrr}
+
+\toprule
+
+\emph{ML} & \multicolumn{7}{c}{\emph{Architects}} \\ 
+  \cmidrule(lr){2-8} 
+& Georgian & Early Vic. & Late V./Edw. & Interwar & Postwar & Cont. & Revival \\
+
+ \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel A: Total share of house blocked by vehicles or trees}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+Georgian &  -- &  0 (0.16) & -0.03 (-1.37) & -0.07 (-2.16) & -0.06 (-0.91) & -0.02 (-0.86) &  0.02 (0.39) \\  
+  Early Vic. & -0.04 (-2.80) &  -- & -0.04 (-7.42) & -0.11 (-8.26) & -0.09 (-5.45) & -0.03 (-1.97) &  0.01 (0.47) \\  
+  Late V./Edw. &  0.03 (0.91) &  0.03 (2.55) &  -- &  0.01 (0.40) &  0.01 (0.57) &  0.01 (0.17) &  0.08 (1.89) \\  
+  Interwar &  0.17 (2.24) &  0.11 (3.71) &  0.09 (5.73) &  -- &  0.03 (4.16) &  0.18 (4.42) &  0.07 (2.40) \\  
+  Postwar &  0.13 (0.96) &  0.03 (1.44) &  0.11 (2.88) & -0.01 (-1.20) &  -- &  0.09 (3.39) &  0.04 (1.09) \\  
+  Cont. &  0.16 (0.77) & -0.02 (-1.91) &  0.03 (1.14) & -0.03 (-0.92) & -0.04 (-3.06) &  -- & -0.03 (-1.32) \\  
+  Revival &  0.18 (0.74) &  0.03 (0.92) &  0.01 (0.26) & -0.05 (-3.03) & -0.06 (-4.90) &  0.04 (2.02) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel B: Share of house area}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+  Georgian &  -- & -0.11 (-3.43) & -0.10 (-2.67) &  0.09 (1.94) &  0.10 (0.96) &  0.11 (1.29) & -0.02 (-0.31) \\  
+  Early Vic. &  0.05 (1.30) &  -- &  0.03 (1.75) &  0.07 (2.45) &  0.18 (5.01) &  0.12 (2.19) &  0.05 (1.03) \\  
+  Late V./Edw. & -0.09 (-2.08) & -0.07 (-3.10) &  -- &  0.02 (1.07) &  0.08 (2.23) & -0.08 (-1.29) &  0.04 (0.71) \\  
+  Interwar &  0.08 (0.55) & -0.16 (-3.68) & -0.14 (-6.48) &  -- &  0.03 (2.92) & -0.04 (-1.03) & -0.09 (-2.65) \\  
+  Postwar & -0.33 (-1.98) & -0.24 (-3.82) & -0.18 (-3.25) & -0.05 (-4.60) &  -- & -0.12 (-2.78) & -0.16 (-4.57) \\  
+  Cont. & -0.21 (-1.58) & -0.16 (-2.99) & -0.15 (-3.45) & -0.02 (-0.55) &  0.01 (0.23) &  -- & -0.06 (-1.43) \\  
+  Revival & -0.03 (-0.15) & -0.04 (-0.69) & -0.11 (-2.70) &  0.06 (2.51) &  0.08 (3.30) &  0.05 (1.30) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel C: Share of window area}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+ Georgian &  -- & -0.06 (-6.02) & -0.02 (-1.10) & -0.02 (-1.92) &  0.03 (1.26) & -0.03 (-1.28) & -0.01 (-0.42) \\  
+  Early Vic. & -0.01 (-0.60) &  -- & -0.01 (-1.51) &  0.03 (2.72) &  0.04 (5.30) &  0.01 (0.70) &  0.02 (1.83) \\  
+  Late V./Edw. &  0 (0.09) & -0.02 (-2.67) &  -- &  0.04 (4.85) &  0.02 (1.81) &  0.02 (0.98) &  0.02 (1.59) \\  
+  Interwar & -0.03 (-0.92) & -0.09 (-10) & -0.08 (-13.20) &  -- &  0.01 (2.98) & -0.03 (-2.41) & -0.03 (-3.48) \\  
+  Postwar & -0.07 (-4.42) & -0.09 (-5.80) & -0.08 (-4.50) & -0.02 (-4.95) &  -- & -0.05 (-4.42) & -0.05 (-5.63) \\  
+  Cont. & -0.07 (-2.04) & -0.08 (-6.97) & -0.05 (-3.73) & -0.01 (-1.46) &  0.01 (2.50) &  -- & -0.02 (-2.58) \\  
+  Revival & -0.02 (-0.18) & -0.06 (-4.39) & -0.03 (-1.71) &  0.01 (1.04) &  0.02 (2.50) & -0.02 (-2.33) &  -- \\
+
+\cmidrule(lr){1-1} \cmidrule(lr){2-8} 
+ & \multicolumn{7}{c}{\emph{ Panel D: Image offset}}\\ 
+\cmidrule(lr){1-1} \cmidrule(lr){2-8}
+
+ Georgian &  -- &  0.04 (5.44) &  0.02 (2.61) & -0.02 (-1.71) & -0.03 (-1.33) &  0.01 (1) &  0.01 (0.55) \\  
+  Early Vic. &  0.01 (0.64) &  -- & -0.02 (-6.59) & -0.03 (-3.82) & -0.04 (-4.98) & -0.01 (-0.93) & -0.03 (-2.78) \\  
+  Late V./Edw. &  0.04 (1.96) &  0.03 (4.68) &  -- & -0.01 (-1.25) & -0.02 (-2.14) &  0.01 (0.46) &  0 (0.25) \\  
+  Interwar &  0.03 (1.16) &  0.06 (6.28) &  0.05 (9.75) &  -- &  0.01 (2.35) &  0 (0.06) &  0.03 (3.19) \\  
+  Postwar &  0.04 (1.07) &  0.06 (3.31) &  0.04 (3.37) &  0 (1.11) &  -- &  0.02 (1.95) &  0.06 (4.20) \\  
+  Cont. &  0.08 (2.11) &  0.05 (3.87) &  0.04 (3.40) & -0.01 (-1.32) & -0.02 (-4.26) &  -- &  0 (0.20) \\  
+  Revival &  0 (0.02) &  0.03 (2.06) &  0.01 (1) & -0.01 (-1.85) & -0.01 (-1.02) &  0.02 (2.22) &  -- \\  
+\bottomrule
+
+\end{tabular} 
+ \begin{minipage}{\textwidth} 
+\footnotesize 
+\vspace{0.25cm}
+\emph{Notes:} Cross-tabulation of photo characteristics by ML and architects' classifications.
+Off-diagonal elements ($ML_{j}-Architects_{i}$) describe the difference in measure intensity between correctly and incorrectly classified photos for a given classification by architects.
+For example, cell \{Early Vic., Georgian\} compares the mean characteristic value for the set of photos which are actually Georgian but misclassified as Early Vic.
+to the set of correctly classified Georgian photos.
+T-stats are in parenthesis.
+\end{minipage} 
+\endgroup 
+\end{table}
+\newpage
+
+\begin{table}[!htbp] \centering 
+  \caption{Summary statistics residential property transactions} 
+  \label{tab:sumstats} 
+\begin{tabular}{@{\extracolsep{5pt}}lcrrrrrr} 
+\toprule
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\midrule
+Price & 15,369 & 256,806.40 & 168,364.40 & 10,000 & 130,000 & 331,000 & 1,000,000 \\ 
+Year & 15,369 & 2,004.97 & 6.60 & 1,995 & 1,999 & 2,010 & 2,018 \\ 
+Volume ($m^3$) & 15,369 & 285.16 & 168.30 & 0.00 & 224.33 & 367.97 & 1,452.23 \\ 
+Area ($m^2$)& 15,369 & 61.47 & 22.49 & 30.12 & 46.03 & 70.45 & 199.57 \\ 
+Dist. city center (m) & 15,369 & 2,314.00 & 924.52 & 528.40 & 1,571.10 & 2,895.54 & 4,916.95 \\ 
+New & 15,369 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
+Type: detached & 15,369 & 0.09 & 0.29 & 0 & 0 & 0 & 1 \\ 
+Type: semi-detached & 15,369 & 0.36 & 0.48 & 0 & 0 & 1 & 1 \\ 
+Type: terraced & 15,369 & 0.55 & 0.50 & 0 & 0 & 1 & 1 \\ 
+\midrule
+Georgian & 15,369 & 0.02 & 0.13 & 0 & 0 & 0 & 1 \\ 
+Early Vic. & 15,369 & 0.18 & 0.39 & 0 & 0 & 0 & 1 \\ 
+Late Vic./Edw. & 15,369 & 0.25 & 0.43 & 0 & 0 & 0 & 1 \\ 
+Interwar & 15,369 & 0.32 & 0.46 & 0 & 0 & 1 & 1 \\ 
+Postwar & 15,369 & 0.17 & 0.38 & 0 & 0 & 0 & 1 \\ 
+Contemporary & 15,369 & 0.04 & 0.18 & 0 & 0 & 0 & 1 \\ 
+Revival & 15,369 & 0.03 & 0.17 & 0 & 0 & 0 & 1 \\ 
+\midrule
+Neigh: Georgian & 15,369 & 0.02 & 0.13 & 0 & 0 & 0 & 1 \\ 
+Neigh: Early Vic. & 15,369 & 0.17 & 0.38 & 0 & 0 & 0 & 1 \\ 
+Neigh: Late V./Edw. & 15,369 & 0.26 & 0.44 & 0 & 0 & 1 & 1 \\ 
+Neigh: Interwar & 15,369 & 0.32 & 0.47 & 0 & 0 & 1 & 1 \\ 
+Neigh: Postwar & 15,369 & 0.18 & 0.39 & 0 & 0 & 0 & 1 \\ 
+Neigh: Contemporary & 15,369 & 0.03 & 0.16 & 0 & 0 & 0 & 1 \\ 
+Neigh: Revival & 15,369 & 0.02 & 0.14 & 0 & 0 & 0 & 1 \\ 
+\bottomrule
+\end{tabular} 
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\singlespacing
+\footnotesize \emph{Notes:} Summary statistics for a sample of 15,511 residential real estate transactions for the city of Cambridge (UK) between 1995 and 2018 where buildings could be matched with Google Street View images.
+The buildings' floor plate (in $m^2$) is based on OS maps and the buildings' volumes are estimated from digital elevation models (Lindenthal, 2017b).
+We control for the location of each building by calculating the distance to the city center proxied by Great St.
+Mary's Church, and non-parametrically by using 69 location dummies (based on LSOA).
+Building styles based on ML classifications.
+\end{minipage}
+\end{table}
+
+\begin{figure}[ht]
+\centering
+\caption{ Spatial distribution of house sales, by architectural styles}
+\label{fig:spatial}
+\begin{tabular}{cccc}
+\toprule
+Georgian & Early Vic. & Late Vic./Ed. & Interwar \\
+ \includegraphics[width=1.3in]{figures/a georgian.pdf} & \includegraphics[width=1.3in]{figures/b victorian.pdf} & \includegraphics[width=1.3in]{figures/c edwardian late victorian.pdf} & \includegraphics[width=1.3 in]{figures/d interwar.pdf} \\
+ Postwar & Contemporary & Revival \\
+  \includegraphics[width=1.3in]{figures/e postwar.pdf} & \includegraphics[width=1.3in]{figures/f contemporary.pdf} & \includegraphics[width=1.3in]{figures/g cont victorian.pdf}  \\
+\bottomrule
+\end{tabular}
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} The locations of 15,369 housing transactions, styles classified by human experts, are marked by black dots. Neighborhood boundaries in the background. 
+\end{minipage}
+\end{figure}
 
@@
  & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
+ & base & true & pred. & high conf. & misclass. & new & neigh. & style $\times$ neigh\\
+
 \midrule
-Constant & 13.20$^{***}$ & 13.45$^{***}$ & 13.29$^{***}$ & 13.21$^{***}$ & 15.61$^{***}$ & 18.89$^{***}$ & 13.14$^{***}$ & 13.20$^{***}$ \\ 
-  & (0.20) & (0.17) & (0.20) & (1.74) & (1.72) & (3.77) & (0.20) & (0.20) \\ 
-  ln(dist. city center) & $-$0.45$^{***}$ & $-$0.50$^{***}$ & $-$0.47$^{***}$ & $-$0.48$^{**}$ & $-$0.72$^{***}$ & $-$1.12$^{***}$ & $-$0.44$^{***}$ & $-$0.45$^{***}$ \\ 
-  & (0.03) & (0.02) & (0.03) & (0.23) & (0.21) & (0.07) & (0.03) & (0.03) \\ 
-  Type: semi-detached & $-$0.12$^{***}$ & $-$0.14$^{***}$ & $-$0.13$^{***}$ & 0.01 & $-$0.12$^{**}$ & $-$0.10 & $-$0.13$^{***}$ & $-$0.13$^{***}$ \\ 
-  & (0.01) & (0.01) & (0.01) & (0.04) & (0.05) & (0.07) & (0.01) & (0.01) \\ 
-  Type: terraced & $-$0.19$^{***}$ & $-$0.20$^{***}$ & $-$0.19$^{***}$ & $-$0.01 & $-$0.10$^{*}$ & $-$0.12 & $-$0.20$^{***}$ & $-$0.20$^{***}$ \\ 
-  & (0.01) & (0.01) & (0.01) & (0.04) & (0.05) & (0.11) & (0.01) & (0.01) \\ 
-  ln(area) & 0.40$^{***}$ & 0.40$^{***}$ & 0.40$^{***}$ & 0.33$^{***}$ & 0.29$^{***}$ & 0.21$^{***}$ & 0.39$^{***}$ & 0.39$^{***}$ \\ 
-  & (0.01) & (0.01) & (0.01) & (0.07) & (0.09) & (0.01) & (0.01) & (0.01) \\ 
-  ln(volume) & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & 0.01 & 0.02$^{***}$ & 0.02 & 0.01$^{***}$ & 0.01$^{***}$ \\ 
-  & (0.001) & (0.001) & (0.001) & (0.01) & (0.01) & (0.09) & (0.001) & (0.002) \\ 
-  New & 0.09$^{***}$ & 0.18$^{***}$ & 0.13$^{***}$ &  &  &  & 0.11$^{***}$ & 0.10$^{***}$ \\ 
-  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.02) \\ 
-  \cmidrule{2-9}
-  & \multicolumn{8}{c}{\emph{Base: Contemporary}} \\
-  Georgian & $-$0.04 & 0.06$^{***}$ & $-$0.04 &  &  &  & 0.01 & 0.15$^{**}$ \\ 
-  & (0.03) & (0.02) & (0.03) &  &  &  & (0.03) & (0.06) \\ 
-  Early Vic. & $-$0.13$^{***}$ & $-$0.01 & $-$0.11$^{***}$ &  &  &  & $-$0.04$^{**}$ & 0.01 \\ 
-  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.07) \\ 
-  Late Vic./Edw. & 0.01 & 0.11$^{***}$ & 0.04$^{**}$ &  &  &  & 0.06$^{***}$ & 0.15$^{**}$ \\ 
-  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.08) \\ 
-  Interwar & $-$0.15$^{***}$ & $-$0.02$^{**}$ & $-$0.13$^{***}$ &  &  &  & $-$0.08$^{***}$ & $-$0.15$^{**}$ \\ 
-  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.06) \\ 
-  Postwar & $-$0.22$^{***}$ & $-$0.06$^{***}$ & $-$0.19$^{***}$ &  &  &  & $-$0.12$^{***}$ & $-$0.17$^{***}$ \\ 
-  & (0.02) & (0.01) & (0.02) &  &  &  & (0.02) & (0.04) \\ 
-  Revival & 0.04$^{**}$ & 0.05$^{***}$ & 0.03 & $-$0.10 & 0.13$^{***}$ & 0.12 & 0.05$^{**}$ & 0.07$^{*}$ \\ 
-  & (0.02) & (0.01) & (0.02) & (0.09) & (0.04) &  (0.09) & (0.02) & (0.04) \\ 
-    \cmidrule{2-9}
-  & \multicolumn{8}{c}{\emph{Base: Neigh. Contemporary}} \\
-
-   Neigh: Georgian &  &  &  &  &  &  & $-$0.10$^{**}$ & $-$0.44$^{***}$ \\ 
-  &  &  &  &  &  &  & (0.04) & (0.05) \\ 
-  Neigh: Early Vic. &  &  &  &  &  &  & $-$0.13$^{***}$ & $-$0.15$^{***}$ \\ 
-  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
-  Neigh: Late V./Edw. &  &  &  &  &  &  & $-$0.05$^{**}$ & $-$0.15$^{*}$ \\ 
-  &  &  &  &  &  &  & (0.02) & (0.08) \\ 
-  Neigh: Interwar &  &  &  &  &  &  & $-$0.11$^{***}$ & $-$0.01 \\ 
-  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
-  Neigh: Postwar &  &  &  &  &  &  & $-$0.14$^{***}$ & $-$0.24$^{***}$ \\ 
-  &  &  &  &  &  &  & (0.02) & (0.04) \\ 
-  Neigh: Revival &  &  &  &  &  &  & $-$0.03 & $-$0.03 \\ 
-  &  &  &  &  &  &  & (0.02) & (0.06) \\  
+ Constant & 13.55$^{***}$ & 13.18$^{***}$ & 13.26$^{***}$ & 13.01$^{***}$ & 12.93$^{***}$ & 14.52$^{***}$ & 12.94$^{***}$ & 12.97$^{***}$ \\ 
+  & (0.20) & (0.20) & (0.20) & (0.22) & (0.44) & (1.67) & (0.23) & (0.23) \\ 
+  ln(dist. city center) & $-$0.52$^{***}$ & $-$0.44$^{***}$ & $-$0.48$^{***}$ & $-$0.44$^{***}$ & $-$0.41$^{***}$ & $-$0.62$^{***}$ & $-$0.43$^{***}$ & $-$0.43$^{***}$ \\ 
+  & (0.03) & (0.03) & (0.03) & (0.03) & (0.06) & (0.04) & (0.03) & (0.03) \\ 
+  Type: semi-detached & $-$0.11$^{***}$ & $-$0.12$^{***}$ & $-$0.12$^{***}$ & $-$0.10$^{***}$ & $-$0.14$^{***}$ & 0.03 & $-$0.10$^{***}$ & $-$0.10$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) & (0.04) & (0.01) & (0.01) \\ 
+  Type: terraced & $-$0.16$^{***}$ & $-$0.19$^{***}$ & $-$0.18$^{***}$ & $-$0.17$^{***}$ & $-$0.16$^{***}$ & $-$0.004 & $-$0.17$^{***}$ & $-$0.17$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) & (0.08) & (0.01) & (0.01) \\ 
+  ln(area) & 0.41$^{***}$ & 0.39$^{***}$ & 0.40$^{***}$ & 0.41$^{***}$ & 0.41$^{***}$ & 0.34$^{***}$ & 0.41$^{***}$ & 0.41$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) & (0.01) & (0.01) & (0.01) \\ 
+  ln(volume) & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & $-$0.004 & 0.01 & 0.01$^{***}$ & 0.01$^{***}$ \\ 
+  & (0.001) & (0.001) & (0.001) & (0.002) & (0.004) & (0.11) & (0.002) & (0.002) \\ 
+  New & 0.19$^{***}$ & 0.10$^{***}$ & 0.18$^{***}$ & 0.10$^{***}$ & 0.13$^{***}$ &  & 0.09$^{***}$ & 0.08$^{***}$ \\ 
+  & (0.02) & (0.02) & (0.02) & (0.03) & (0.03) &  & (0.03) & (0.03) \\ 
+   \midrule
+ \multicolumn{3}{l}{\emph{Base: Contemporary}}
+\vspace{2mm} \\
+  Georgian &  & $-$0.04 & 0.07$^{***}$ & $-$0.08$^{**}$ & $-$0.01 &  & $-$0.08$^{**}$ & $-$0.27$^{***}$ \\ 
+  &  & (0.03) & (0.02) & (0.03) & (0.05) &  & (0.04) & (0.05) \\ 
+  Early Vic. &  & $-$0.13$^{***}$ & $-$0.01 & $-$0.15$^{***}$ & $-$0.03 &  & $-$0.11$^{***}$ & $-$0.11$^{*}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.03) &  & (0.02) & (0.06) \\ 
+  Late Vic./Edw. &  & 0.01 & 0.12$^{***}$ & 0.004 & 0.03 &  & 0.003 & 0.12 \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.03) &  & (0.02) & (0.09) \\ 
+  Interwar &  & $-$0.14$^{***}$ & $-$0.03$^{**}$ & $-$0.18$^{***}$ & $-$0.04 &  & $-$0.15$^{***}$ & $-$0.18$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.03) &  & (0.02) & (0.07) \\ 
+  Postwar &  & $-$0.22$^{***}$ & $-$0.09$^{***}$ & $-$0.26$^{***}$ & $-$0.11$^{***}$ &  & $-$0.19$^{***}$ & $-$0.23$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.03) &  & (0.02) & (0.06) \\ 
+  Revival &  & 0.04$^{**}$ & 0.07$^{***}$ & 0.03 & 0.08$^{**}$ & $-$0.06 & 0.02 & 0.07 \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.03) & (0.08) & (0.03) & (0.06) \\ 
+ \midrule
+ \multicolumn{3}{l}{\emph{Base: Neigh. Contemporary}}
+\vspace{2mm} \\
+  Neigh: Georgian &  &  &  &  &  &  & $-$0.001 & $-$0.43$^{***}$ \\ 
+  &  &  &  &  &  &  & (0.05) & (0.07) \\ 
+  Neigh: Early Vic. &  &  &  &  &  &  & $-$0.07$^{**}$ & $-$0.12$^{***}$ \\ 
+  &  &  &  &  &  &  & (0.03) & (0.04) \\ 
+  Neigh: Late V./Edw. &  &  &  &  &  &  & $-$0.004 & $-$0.12 \\ 
+  &  &  &  &  &  &  & (0.03) & (0.10) \\ 
+  Neigh: Interwar &  &  &  &  &  &  & $-$0.06$^{**}$ & 0.01 \\ 
+  &  &  &  &  &  &  & (0.03) & (0.05) \\ 
+  Neigh: Postwar &  &  &  &  &  &  & $-$0.10$^{***}$ & $-$0.10$^{**}$ \\ 
+  &  &  &  &  &  &  & (0.03) & (0.05) \\ 
+  Neigh: Revival &  &  &  &  &  &  & 0.01 & 0.05 \\ 
+  &  &  &  &  &  &  & (0.03) & (0.04) \\ 
   \midrule
@@
 Interaction terms & No & No & No & No & No & No & No & Table \ref{tab:hedregint} \\ 
-Observations & 15,642 & 23,415 & 15,721 & 377 & 567 & 348 & 15,503 & 15,503 \\ 
-Adjusted R$^{2}$ & 0.88 & 0.88 & 0.88 & 0.93 & 0.91 & 0.92 & 0.89 & 0.89 \\ 
+Observations & 15,369 & 15,369 & 15,369 & 11,627 & 3,063 & 317 & 11,627 & 11,627 \\ 
+Adjusted R$^{2}$ & 0.87 & 0.88 & 0.88 & 0.89 & 0.87 & 0.93 & 0.89 & 0.89 \\ 
+RMSE & 0.235 & 0.225 & 0.228 & 0.219 & 0.235 & 0.119 & 0.218 & 0.217 \\ 
 \bottomrule
@@
 Standard errors are robust (White's estimator).
-Models (1) and (4) are estimated using the architects' classifications only.
-Models (2) and (5) are estimated based on all observations that have been automatically classified.
-Models (3) and (6) are also based on automatic classifications but the sample is reduced to high confidence predictions only.
-Models (4-6) are estimated on sales of newly completed buildings only.
-The interaction terms for Model (8) are in Table \ref{tab:hedregint}.
+Models (2) and (6) are estimated using the architects' classifications only; (3) is based on ML observations that have been automatically classified, while (4), (7) and (8) are based on high confidence ML predictions only; (5) uses architect's classifications on the subset of data where the architect and ML model style predictions match; (6) is estimated on sales of newly completed buildings.
+The interaction terms for (8) are presented in Table \ref{tab:hedregint}.
 \end{minipage}
@@
 \newpage
+
+\begin{table}[ht]
+\centering
+\caption{Coefficients interaction terms: Building and neighborhood style}
+\label{tab:hedregint}
+\begin{tabular}{lccccccc}
+\toprule
+\emph{Neigh.} & \multicolumn{7}{c}{\emph{Building}} \\
+ \cmidrule(lr){1-1}
+ \cmidrule(lr){2-8}
+& \emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interw.} & \emph{Postw.} & \emph{Cont.} & \emph{Revival} \\ 
+  \cmidrule(lr){2-8}
+
+Georg. & 0.61** & 0.41 & 0.77*** & N/A & N/A & -- & N/A \\ 
+ & (0.27) & (0.25) & (0.28) &  &  &  &  \\ 
+Early Vic. & 0.27* & 0.05 & -0.11 & 0.03 & 0.10 & -- & 0.07 \\ 
+    & (0.16) & (0.11) & (0.13) & (0.10) & (0.11) &  & (0.12) \\ 
+Late V./Edw. & 0.36** & 0.09 & -0.01 & 0.15 & 0.06 & -- & 0.10 \\ 
+ & (0.17) & (0.12) & (0.14) & (0.11) & (0.12) &  & (0.14) \\ 
+Interw. & N/A & -0.13 & -0.17 & -0.03 & -0.03 & -- & -0.10 \\ 
+ &  & (0.11) & (0.13) & (0.09) & (0.09) &  & (0.11) \\ 
+Postw. & N/A & 0.19 & -0.19 & 0.03 & 0.05 & -- & -0.11 \\ 
+ &  & (0.16) & (0.14) & (0.09) & (0.09) &  & (0.12) \\ 
+Cont. & -- & -- & -- & -- & -- & -- & -- \\ 
+ &  & &  &  &  & &  \\ 
+Revival & N/A & N/A & -0.45*** & 0.10 & -0.06 & -- & -0.10 \\ 
+ &  &  & (0.16) & (0.10) & (0.11) &  & (0.11) \\ 
+\bottomrule
+\end{tabular}
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
+Standard errors are robust (White's estimator).
+This table features the coefficients for interaction terms of building style and neighborhood styles only, while Table \ref{tab:hedreg}, Column 8 presents all other coefficients for this model.
+\end{minipage}
+\end{table}
 
@@
 \vspace{0.25cm}
-\footnotesize \emph{Notes:} The style of direct neighborhoods is defined as the most frequent detected style on the same street, within 100m. 
-\end{minipage}
-\end{table}
-
-\newpage
-
-\begin{table}[ht]
-\centering
-\caption{Coefficients interaction terms: Building and neighborhood style}
-\label{tab:hedregint}
-\begin{tabular}{lccccccc}
-\toprule
-\emph{Neigh.} & \multicolumn{7}{c}{\emph{Building}} \\
- \cmidrule(lr){1-1}
- \cmidrule(lr){2-8}
-& \emph{Georg.} & \emph{Early Vic.} & \emph{Late V./Edw.} & \emph{Interw.} & \emph{Postw.} & \emph{Cont.} & \emph{Revival} \\ 
-  \cmidrule(lr){2-8}
-
-Georgian & 0.19 & 0.25 & 0.56** & -- & -- & -- & -- \\ 
-   & (0.29) & (0.25) & (0.27) & -- & -- & -- & -- \\ 
-Early Vic. & -0.14 & -0.04 & -0.13 & 0.03 & 0.07 & -- & 0.10 \\ 
-  & (0.18) & (0.09) & (0.12) & (0.09) & (0.08) & -- & (0.10) \\ 
-Late V./Edw. & -0.004 & 0.002 & -0.01 & 0.18* & 0.08 & -- & 0.13 \\ 
-   & (0.19) & (0.11) & (0.13) & (0.10) & (0.10) & -- & (0.12) \\ 
-Interwar & -0.23 & -0.20** & -0.17 & -0.03 & -0.07 & -- & -0.15 \\ 
-  & (0.19) & (0.09) & (0.11) & (0.08) & (0.06) & -- & (0.09) \\ 
-Postwar & 0.18 & 0.03 & -0.05 & 0.15** & 0.14*** & -- & 0.01 \\ 
-   & (0.28) & (0.11) & (0.12) & (0.07) & (0.05) & -- & (0.09) \\ 
-Contemporary & -- & -- & -- & -- & -- & -- & -- \\ 
-  & -- & -- & -- & -- & -- & -- & -- \\ 
-  Revival & -- & -- & -0.43*** & 0.09 & 0.04 & -- & -0.04 \\ 
-   & -- & -- & (0.15) & (0.08) & (0.07) & -- & (0.09) \\ 
-\bottomrule
-\end{tabular}
-\begin{minipage}{\textwidth}
-\vspace{0.25cm}
-\footnotesize \emph{Notes:} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
-Standard errors are robust (White's estimator).
-This table features the coefficients for interaction terms of building style and neighborhood styles only, while Table \ref{tab:hedreg}, Column 8 presents all other coefficients for this model.
+\footnotesize \emph{Notes:} The style of direct neighborhoods is defined as the most frequently detected style on the same street, within 100m. 
 \end{minipage}
@@
   \cmidrule(lr){2-8}
-Georgian & -0.11 & -0.17 & 0.27 & -- &--  & -0.44 &--  \\ 
-  Early Vic. & -0.15 & -0.18 & -0.13 & -0.28 & -0.25 & -0.15 & 0.02 \\ 
-  Late Vic./Edw. & -0.00 & -0.13 & -0.00 & -0.12 & -0.24 & -0.15 & 0.06 \\ 
-  Interwar & -0.10 & -0.19 & -0.03 & -0.20 & -0.26 & -0.01 & -0.09 \\ 
-  Postwar & 0.09 & -0.19 & -0.13 & -0.23 & -0.27 & -0.24 & -0.16 \\ 
-  Contemporary & 0.15 & 0.01 & 0.15 & -0.15 & -0.17 & 0.00 & 0.07 \\ 
-  Revival & -- & -- & -0.30 & -0.09 & -0.16 & -0.03 & 0.00 \\ 
+Georgian & -0.09 & -0.14 & 0.46 & N/A & N/A & -0.43 & N/A \\ 
+  Early Vic. & -0.11 & -0.18 & -0.11 & -0.26 & -0.25 & -0.12 & 0.03 \\ 
+  Late Vic./Edw. & -0.02 & -0.14 & 0.00 & -0.14 & -0.29 & -0.12 & 0.06 \\ 
+  Interwar & N/A & -0.24 & -0.04 & -0.20 & -0.25 & 0.01 & -0.02 \\ 
+  Postwar & N/A & -0.02 & -0.17 & -0.25 & -0.29 & -0.10 & -0.14 \\ 
+  Contemporary & -0.27 & -0.11 & 0.12 & -0.18 & -0.23 & 0.00 & 0.07 \\ 
+  Revival & N/A & N/A  & -0.27 & -0.03 & -0.24 & 0.05 & 0.02 \\ 
 \bottomrule
@@
 \vspace{0.25cm}
-\footnotesize \emph{Notes:} The combined effect of building styles on property values is calculated by adding up the direct, neighborhood and interaction effects (Table \ref{tab:hedregint}).
+\footnotesize \emph{Notes:} The combined effect of building styles on property values is calculated by adding up the direct, neighborhood, and interaction effects (Table \ref{tab:hedregint}).
 A revival building surrounded by other revival buildings, for instance, commands no premium over a contemporary building in a new neighborhood.
@@
 \clearpage
+\begin{table}[!htbp] \centering 
+  \caption{Hedonic Regression Estimates - Year x Neighborhood Fixed effects} 
+  \label{tab:hedreg_year_loc_int} 
+\footnotesize 
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{7}{c}{Dependent variable: ln(price)} \\ 
+\cline{2-8} 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7)\\ 
+ & base & true & pred. & high conf. & misclass. & neigh. & style $\times$ neigh\\
+
+\hline \\[-1.8ex] 
+ Constant & 13.55$^{***}$ & 13.21$^{***}$ & 13.25$^{***}$ & 13.01$^{***}$ & 13.30$^{***}$ & 12.90$^{***}$ & 12.89$^{***}$ \\ 
+  & (0.24) & (0.24) & (0.23) & (0.26) & (0.64) & (0.27) & (0.27) \\ 
+  ln(dist. city center) & $-$0.50$^{***}$ & $-$0.44$^{***}$ & $-$0.47$^{***}$ & $-$0.43$^{***}$ & $-$0.47$^{***}$ & $-$0.41$^{***}$ & $-$0.41$^{***}$ \\ 
+  & (0.03) & (0.03) & (0.03) & (0.03) & (0.08) & (0.03) & (0.03) \\ 
+  Type: semi-detached & $-$0.12$^{***}$ & $-$0.12$^{***}$ & $-$0.12$^{***}$ & $-$0.10$^{***}$ & $-$0.14$^{***}$ & $-$0.10$^{***}$ & $-$0.10$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) & (0.01) & (0.01) \\ 
+  Type: terraced & $-$0.16$^{***}$ & $-$0.19$^{***}$ & $-$0.19$^{***}$ & $-$0.16$^{***}$ & $-$0.16$^{***}$ & $-$0.16$^{***}$ & $-$0.17$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) & (0.01) & (0.01) \\ 
+  ln(area) & 0.41$^{***}$ & 0.39$^{***}$ & 0.40$^{***}$ & 0.41$^{***}$ & 0.42$^{***}$ & 0.41$^{***}$ & 0.41$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.01) & (0.01) & (0.03) & (0.01) & (0.01) \\ 
+  ln(volume) & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & 0.01$^{***}$ & $-$0.01 & 0.01$^{***}$ & 0.01$^{***}$ \\ 
+  & (0.002) & (0.002) & (0.002) & (0.002) & (0.004) & (0.002) & (0.002) \\ 
+  New & 0.15$^{***}$ & 0.07$^{***}$ & 0.14$^{***}$ & 0.06$^{*}$ & 0.17$^{***}$ & 0.05 & 0.03 \\ 
+  & (0.02) & (0.02) & (0.02) & (0.03) & (0.05) & (0.03) & (0.03) \\ 
+     \midrule
+ \multicolumn{3}{l}{\emph{Base: Contemporary}}
+\vspace{2mm} \\
+  Georgian &  & $-$0.02 & 0.08$^{***}$ & $-$0.08$^{**}$ & $-$0.07 & $-$0.09$^{**}$ & $-$0.25$^{***}$ \\ 
+  &  & (0.03) & (0.03) & (0.03) & (0.07) & (0.04) & (0.07) \\ 
+  Early Vic. &  & $-$0.12$^{***}$ & 0.003 & $-$0.14$^{***}$ & $-$0.06 & $-$0.11$^{***}$ & $-$0.24$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.04) & (0.03) & (0.07) \\ 
+  Late Vic./Edw. &  & 0.03 & 0.14$^{***}$ & 0.02 & 0.002 & 0.01 & 0.17$^{*}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.04) & (0.03) & (0.10) \\ 
+  Interwar &  & $-$0.13$^{***}$ & $-$0.01 & $-$0.17$^{***}$ & $-$0.05 & $-$0.14$^{***}$ & $-$0.21$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.04) & (0.02) & (0.07) \\ 
+  Postwar &  & $-$0.21$^{***}$ & $-$0.07$^{***}$ & $-$0.25$^{***}$ & $-$0.14$^{***}$ & $-$0.20$^{***}$ & $-$0.23$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.02) & (0.04) & (0.02) & (0.07) \\ 
+  Revival &  & 0.06$^{***}$ & 0.10$^{***}$ & 0.05$^{*}$ & 0.07 & 0.03 & 0.18$^{***}$ \\ 
+  &  & (0.02) & (0.02) & (0.03) & (0.05) & (0.03) & (0.07) \\ 
+       \midrule
+ \multicolumn{3}{l}{\emph{Base: Neigh. Contemporary}}
+\vspace{2mm} \\
+  Neigh: Georgian &  &  &  &  &  & 0.01 & $-$0.68$^{***}$ \\ 
+  &  &  &  &  &  & (0.05) & (0.13) \\ 
+  Neigh: Early Vic. &  &  &  &  &  & $-$0.06$^{**}$ & $-$0.11$^{**}$ \\ 
+  &  &  &  &  &  & (0.03) & (0.05) \\ 
+  Neigh: Late V./Edw. &  &  &  &  &  & 0.002 & $-$0.06 \\ 
+  &  &  &  &  &  & (0.03) & (0.11) \\ 
+  Neigh: Interwar &  &  &  &  &  & $-$0.05$^{*}$ & 0.02 \\ 
+  &  &  &  &  &  & (0.03) & (0.05) \\ 
+  Neigh: Postwar &  &  &  &  &  & $-$0.09$^{***}$ & $-$0.12$^{**}$ \\ 
+  &  &  &  &  &  & (0.03) & (0.05) \\ 
+  Neigh: Revival &  &  &  &  &  & 0.03 & 0.12$^{**}$ \\ 
+  &  &  &  &  &  & (0.03) & (0.05) \\ 
+ \hline \\[-1.8ex] 
+Year dummies & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Neigh. dummies & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Year x Neigh dummies & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Style Interaction terms & No & No & No & No & No & No & Yes \\ 
+Observations & 15,369 & 15,369 & 15,369 & 11,627 & 3,063 & 11,627 & 11,627 \\ 
+Adjusted R$^{2}$ & 0.87 & 0.88 & 0.88 & 0.89 & 0.88 & 0.89 & 0.89 \\ 
+RMSE & 0.224 & 0.214 & 0.217 & 0.203 & 0.184 & 0.202 & 0.202 \\ 
+\bottomrule
+\end{tabular}
+\begin{minipage}{\textwidth}
+\vspace{0.25cm}
+\footnotesize \emph{Notes:} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
+Standard errors are robust (White's estimator).
+Model (2) and (6) are estimated using the architects' classifications; (3) is based on ML observations that have been automatically classified, while (4), (6) and (7) are based on high confidence ML predictions only; (5) uses architect's classifications on the subset of data where the architect and ML model style predictions match.
+\end{minipage}
+\end{table}
+
+\clearpage
 
